### 2019-07-01 Document/paper.tex
Uploading new graphs in paper

\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{subfig}
\usepackage{array}

\usepackage{multirow}
\usepackage{multicol}
\usepackage{blindtext}
\newcolumntype{?}{!{\vrule width 1pt}}
\newcommand{\Mpch}{\,{\rm Mpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
\newcommand{\kpch}{\,{\rm kpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
\newcommand{\kpc}{\,{\rm kpc}\,}

\newenvironment{Table}
   {\par\bigskip\noindent\minipage{\columnwidth}\centering}
   {\endminipage\par\bigskip}

\title[Dark Matter halo shape in the AURIGA simulations]{The shape of dark matter
  halos in the AURIGA simulations}  
\author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
Jesus Prada,$^{1}$\thanks{E-mail: jd.prada1760@uniandes.edu.co}
Jaime E. Forero-Romero,$^{1}$
Volker Springel$^{2}$
\\
% List of institutions
$^{1}$Departamento de F\'sica, Universidad de los Andes, Cra. 1 No.
18A-10, Edificio Ip, Bogot\', Colombia.\\
$^{2}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg
Germany.\\
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2018}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
We measure the shape of the dark matter halos of Milky Way type galaxies.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}

A robust prediction of the Cold Dark Matter (CDM) paradigm is that DM
halos are ellipsoidal and can be characterized by the principal axes
$a>b>c$.
This ellipsoidal shape is mostly due to the anisotropical and
clumpy accretion of matter influenced by environmental structures.
Numerical studies how that the shape has a strong mass dependence
\citep{Allgood_et_al._2006}, halos are also rounder at the outerskirts
than at the inner part. 
Shape also evolves with cosmic time, halos get
rounder as they evolve.

There is however a high degree of uncertainty on what is the degree of
uncertainty on the degree of ellipticity of the Milky Way DM halo.
This problem has been addressed both by observations and simulations.
The difficulty in making an observational measurement lies in the
indirect nature of the effect; i.e. the ellipticity can only be
constrained by its effects on quantities such as stellar radial
velocities.
In simulations the uncertainty on predicting the MW DM ellipticity is 
driven by the different physical effects that should be modeled and
its different possible numerical implementations.

Observationally some studies prefer oblate (i.e. a=b>c) configurations at small
distances around $\leq 20$ kpc
\citep[see][]{Law_and_Majewski_2010,Bovy_et_el._2016,Loebman_et_al._2012,Olling_and_Merrifield_2000,Banerjee_and_Chanda_2011} 
and more triaxial and prolate configurations on the outter distances
$\geq 20$ kpc 
\citep[see][]{Vera-Ciro_and_Helmi_2013,Law_and_Majewski_2009,Deg_and_Widrow_2013,Banerjee_and_Chanda_2011}.
However, some  studies are inclined towards prolate configurations even at the inner
parts of the halo \citep[see][]{Bowden_et_al._2016}, and
although it previously seemed that a triaxial DM halo on the
outerskirts would be necessary to fully explain the characterization
of the Sagittarius stream \citep{Law_and_Majewski_2009}, recent studies
questioned this claim by reporting inconsistencies with narrow stellar
streams \citet{Pearson_et_al._2015} or finding that
the relaxation of other constraints may make this claim unnecessary
\citet{Ibata_et_al._2013}.

In simulations there is strong evidence claiming that the presence of
baryons produces axisymmetrical halos.  
For instance, some studies have shown that the DM halo shape must be
axisymmetrical to ensure the stability of a hydrodynamical disk
embeded in a static DM halo. 
Other have studied this rounding effect by simulating the disk as rigid
potential inside an N-body triaxial DM
halo \cite{Debattista_et_al._2008,Debattista_et_al._2013,Kazantzidis_et_al._2010}
finding that the halo responds to the disk by becoming less triaxial.

The caveat of the studies mentioned above is that they do not
follow baryons in the whole cosmological context. 
Other studies overcome this limitation by using resimulations 
\citep{Abadi_et_al._2010,Bryan_et_al._2013} finding that the
feeback related to star formation in the disk drives the strenght of
the round effect. 
Recently \cite{2018arXiv180907255C} made a study in a cosmological
simulation to compare the effect of including baryons. They do find,
on average, rounder halo shapes once hydrodynamic effects are
included, but it is uncertain the strenght of this statistical effect
on galaxies similar to the MW.

All these difficulties (enough numerical resolution, explicit
cosmological context, appropriate feedback physics to produce
realistic MW disks) have limited the studies that want to study the
rounding effect of baryons in MW-like galaxies.
In this work we overcome all these limitations by analyzing the
results of state-of-the-art hydrodynamical simulations of isolated
halos that resemble the Milky Way.
We also perform a convergence study with simulation performed at
different resolution levels and explicitly compare the role of DM only
vs. DM+hydro on the MW DM halo shape.

\begin{table*}
\centering
\begin{tabular}{l|cc|cc|cc|cc}
\hline
\hline
Halo & \multicolumn{2}{c}{$N_P$/$10^6$} & \multicolumn{2}{c}{$M_P$/$10^5M_\odot$} & 
\multicolumn{2}{c}{$R_{vir}$/kpc} & \multicolumn{2}{c}{$M_{vir}$/$10^{14} M_\odot$}  \\ \hline
& DM & MHD& DM & MHD& DM & MHD& DM & MHD\\ \hline \hline
halo 1&4.068&2.447&2.397&2.022&196.927&187.674&9.062&7.844\\
halo 2&5.625&5.457&2.481&2.093&235.094&233.934&15.418&15.191\\
halo 3&3.826&3.852&2.645&2.231&210.693&210.955&11.099&11.141\\
halo 4&4.585&4.530&2.590&2.185&219.378&215.438&12.529&11.866\\
halo 5&3.262&3.290&2.533&2.137&196.984&197.246&9.071&9.106\\ 
halo 6 ($\star$)&3.184&3.110&2.337&1.972&191.840&189.342&8.378&8.054\\ 
halo 7&3.878&3.729&2.296&1.937&197.864&196.509&9.193&9.005\\
halo 8&2.772&2.796&2.451&2.068&190.716&191.764&8.231&8.368\\
halo 9&3.038&3.010&2.738&2.310&195.826&190.640&8.911&8.222\\
halo 10&2.700&2.751&2.541&2.144&187.139&188.147&7.777&7.904\\
halo 11&4.146&4.116&2.541&2.144&221.821&219.568&12.952&12.560\\
halo 12&2.865&2.908&2.645&2.231&192.280&192.038&8.436&8.404\\
halo 13&3.520&3.600&2.393&2.019&202.139&203.815&9.801&10.048\\
halo 14&4.200&4.475&2.499&2.108&215.535&218.927&11.882&12.453\\
halo 15&2.888&2.845&2.541&2.144&199.848&200.658&9.471&9.588\\ 
halo 16 ($\star$)&3.821&3.871&2.499&2.108&212.590&212.632&11.401&11.408\\ 
halo 17&2.752&2.781&2.552&2.153&188.067&187.404&7.893&7.811\\
halo 18&3.770&3.624&2.738&2.310&201.124&207.293&9.655&10.571\\
halo 19&2.989&3.086&2.645&2.231&200.244&200.325&9.527&9.540\\
halo 20&3.903&3.822&2.481&2.093&210.097&211.423&11.005&11.214\\ 
halo 21 ($\star$) &4.105&4.075&2.640&2.227&219.527&219.823&12.555&12.604\\ 
halo 22&2.794&2.766&2.625&2.215&188.363&184.801&7.931&7.489\\ 
halo 23 ($\star$) &3.977&4.073&2.795&2.358&217.768&215.959&12.254&11.952\\
halo 24 ($\star$) &4.466&4.426&2.522&2.127&217.440&215.147&12.199&11.817\\ 
halo 25&2.902&2.806&2.645&2.231&199.922&198.299&9.482&9.254\\
halo 26 &4.610&4.716&2.506&2.115&219.984&218.939&12.633&12.454\\
halo 27 ($\star$) & 5.060&5.018&2.590&2.185&228.036&226.225&14.071&13.740\\ 
halo 28 & 4.184&4.276&2.645&2.231&216.979&217.997&12.121&12.294\\
halo 29 & 4.827&4.613&2.499&2.108&225.791&219.935&13.660&12.625\\
halo 30 & 3.268&3.112&2.579&2.176&195.043&194.741&8.805&8.763\\
\hline
\hline
\end{tabular}
\caption{Specifications of each level 4 galaxy (halo). 
  The DM and MHD versions of each parameters are presented together. 
  The columns correspond to: (1) Halo name, (2,3) Millions of DM
  particles belonging to the halo, (4,5) DM particle mass in
  $10^5M_\odot$, (6,7) Halo Virial radius in kpc and (8,9) halo virial
  mass in $10^{14}M_\odot$. Halos marked with a star ($\star$) are
  correspond to halos resimulated at higher resolution (level 3).}  
\label{tab:level4}
\end{table*}

\begin{table*}
\centering
\begin{tabular}{l?cc?cc?cc?cc}
\hline
\hline
Halo & \multicolumn{2}{c?}{$N_P$/$10^6$} & \multicolumn{2}{c?}{$M_P$/$10^5M_\odot$} & \multicolumn{2}{c?}{$R_{vir}$/kpc}&\multicolumn{2}{c}{$M_{vir}$/$10^{14}M_\odot$}  \\ \hline
& DM & MHD& DM & MHD& DM & MHD& DM & MHD\\ \hline \hline
halo 6&24.902&24.185&0.292&0.246&191.741&188.367&8.365&7.932\\
halo 16&29.750&30.334&0.312&0.263&212.622&212.542&11.406&11.395\\
halo 21&31.993&31.503&0.330&0.278&219.731&220.250&12.588&12.679\\
halo 23&31.379&31.618&0.349&0.295&217.793&213.358&12.259&11.524\\
halo 24&34.987&35.153&0.315&0.266&217.313&213.963&12.179&11.624\\
halo 27&39.617&39.056&0.324&0.273&227.908&223.484&14.048&13.244\\
\hline
\hline
\end{tabular}
\caption{Same layout Table \ref{tab:level3} for Level 3 simulations (higher
  resolution than Level 4 simulations).}
\label{tab:level3}
\end{table*}

\section{Numerical Simulations}

In this work we use the results of the state-of-the art Auriga
simulations \citep{auriga}. 
The objects in those simulations were selected from a set of 30
isolated halos in the Evolution and Assembly of GaLaxies and their
Environments (EAGLE)  project \citep{Eagle}.   
These halos were randomly selected from a sample of the most isolated
halos whose virial mass $M_{200}$ varied between $10^{12}M_\odot$ and
$2\times 10^{12}M_\odot$. 
These halos were re-simulated with higher resolution an varying
physical realism using the AREPO code \citep{arepo}.

All 30 halos were simulated within resolution defined for Aquarius
simulations corresponding to $\sim 3\times 10^6$ high resolution DM
particles of $\sim 2.5 \times 10^5 M_\odot$.  
This resolution is labeled as Level 4, the main details for each halo
are consigned in Table \ref{tab:level4}. 
From these 30 halos, 6 of them where re-simulated at higher resolution
(labeled as Level 3) taking into account a spatial factor of 2 in each
dimension.   
Details of Level 3 halos are in Table \ref{tab:level3}. 
Furthermore, for each halo in each level of resolution there are two
versions of the simulation: DM-only and DM plus baryons with
magneto-hydrodynamical (MHD) physics.

\begin{figure*}
  \centering
  \subfloat[halo 16 DM shape at small
    radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_16_inner.png}} 
  \hfill
  \subfloat[halo 16 DM shape at big
    radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_16_outer.png}} 
  \hfill 
  \caption{DM density for inner/outer (left/right panel) DM halo regions.  
  Slice 20 percent of the max-min range in the "z" position of
  particles belonging to the main structure, centered at halo defined
  position (calculated with most bounded particle) }  
  \label{fig:slices}
\end{figure*}

\section{Determining the halo shape}

%\subsection{The solid ellipsoid method}

The DM halo shape at a fixed radius is an estimate of either
the isopotential or isodensity surfaces.  
Observational inference models usually estimate the 
isopotential contours which are probed by tracers (gas, stars), while
simulations work with the isodensity contours which can be directly
calculated from particle positions.

However, in numerical simulations the density contours are not smooth
and are sensitive to the presence of small satelites. 
For this reason we choose to measure the shape by taking
volume-enclosed particles, rather than shell-enclosed.  
We follow the shape measurement method presented by
\cite{Allgood_et_al._2006} that uses the reduced
inertia tensor,

\begin{equation}
I_{ij} = \sum_k \frac{x_k^{(i)}x_k^{(j)}}{d^2_k},
\label{eq:inertia}
\end{equation}

with the positions components weighted by the k-th particle distance
$d_k^2=x_k^2+y_k^2+z_k^2$, the particle positions are measured from
the minimum of the gravitational potential in each halo.
The diagonalization of this tensor yields the principal axes of the
structure as well as the eigen-quantities which are proportional to
the squared principal axes $a>b>c$.

We start the calculations taking into account particles within a
sphere of radius $R$ and then  recharacterize the triaxial parameters
by taking into account particles within an ellipsoid of semi-axes
$r,r/q,r/s$ and re-scaled distance $d^2=x^2+(y/q)^2+(z/s)^2$, where $q
= b/a$ and $s=c/a$ are the previously calculated axial ratios. 
We repeat this process until the average deviation of semi-axes is
less than $10^{-6}$.  
This is the same method used to estimate the halo shape in the DM-only
Aquarius simulations \citep{Vera-Ciro_et_al._2011}.

We restrict the sampling of the ellipsoidal parameters to radii
between $1/16 R_{vir}$ and $2R_{vir}$, where  $R_{vir}$ is taken as the
radius enclosing a sphere with 500 times the average dark matter
density of the Universe. 
All our results use of this reference radius
unless strictly stated otherwise. 
We peform the shape measurements both as a function of radius and
redshift for all halos in the sample.

\section{Results}

\subsection{Radial trends at $z=0$}

We find that in DM-only simulations halos are monotonically rounder
with increasing radius, confirming results already reported in the
literature \citep{Vera-Ciro_et_al._2011}. 
Figure \ref{fig:slices} illustrates this effect.
There we show the density a DM-only halo at redshift zero in a thin
slice passing through the halo's centre, each panel shows the halo at
different radii.
The ellipse plotted over the contours indicates the outermost
boundary of the estimated shape ellipsoid. 
Indeed, the ellipse panel on the right (outer halo) is rounder than
the ellipse on the left (inner halo).

\begin{figure*}
\centering
{\includegraphics[width=0.6\textwidth]{./pics/MHD_Vs_DM/halo16_new.png}}
\caption{Radial profile for the axial ratios and the triaxiality parameter
  $T=\frac{1-b/a}{1-c/a}$ at redshift $z=0$. 
  Radial profile was sampled at
  redshift 0 and there are two sets of lines showing MHD and DM-only
  versions of the axial ratios profile. {\bf Aqui hay que quiar c/b,
    no es relevante}} \label{fig:triaxial_radius}
\end{figure*}

We quantify this effect by plotting the axial ratios $q$, $s$,
$s/q$ and the triaxiality $T\equiv \frac{1-q}{1-s}$ as a
function of radius. 
As a representative sample of this relations we show on Figure
\ref{fig:triaxial_radius} the radial trends for Halo 16 at
the highest resolution both for DM and MHD simulations.
The continous lines correspond to the DM simulation and shows how
the inner part of the halo $r\approx 1$\kpch has values of 
$q=0.5$, $s=0.5$ while at the virial radius the same
quantities increase to $q=0.85$, $s=0.6$; in turn the triaxiality
decreases from $T\approx 1.0$ to $T\approx0.4$.

In the same Figure \ref{fig:triaxial_radius} we also find one of the
main results of our study: halos in MHD simulations are systematically rounder, at
every radius, than its DM-only counterparts.  
The dashed line in Figure \ref{fig:triaxial_radius} shows that at
$r\approx 1$\kpch  in the MHD simulation we have $q=0.85, s=0.8$
($q=0.5, s=0.5$ in DM) and at the virial radius $q=0.95, s=0.75$
($q=0.85, s=0.6$ in DM).  
However, the triaxiality trend is not as monotonous for MHD halos is
it is in DM halos. 
The triaxiality goes almost to zero at an intermediate radius,
$r\approx 10$\kpc in the case of Halo 16 in Figure
\ref{fig:triaxial_radius}, to increase again. {\bf pasa lo mismo para
  todos los halos? es lo mismo para baja y alta resolucion de MHD?}

Figure \ref{fig:triax_DM_MHD} summarizes this comparizon for all 30 halos
in the Level 3 simulations. 
Measurements at $R_{\rm vir}/16$ are represented by circles while squares 
are measurements at $R_{\rm vir}$. 
All halos, except two, show that outer regions rounder than inner
regions.
The exceptions are cases where a merging substructures near  the
halo's center gives rise to perturbed axial ratio measurements. 
The right panel on Figure \ref{fig:triax_DM_MHD} shows the same information, this time for
the MHD simulations. 
In this case, the main radial trend continues to hold, albeit less
pronounced.
We also find that halos in MHD simulations are in general rounder than
their DM counterparts

This global behaviour can be also illustrated by the individual case
of Halo 16, shown in Figure \ref{fig:triaxial_radius}.
At the virial radius the halo is rounder than its DM counterpart as
evidenced in the axis ratios $b/a$, $c/a$ and the triaxiality.
In the MHD simulation, going from the virial radius to $10$ \kpch the
$b/a$ ratio is constant almost close to unity while in the DM-only
simulation it decreases to $0.5$.
Between $2$-$10$ \kpc the triaxiality in the DM-only simulation is in
the range $0.9-1.0$, while the MHD simulation has values between
$0-0.5$.

In Table \ref{table:median_axial_ratio_DM} and Table \ref{table:median_axial_ratio_MHD}
we summarize these trends for the median values of the axis ratio in
the DM and MHD simulations
The lower/upper bounds correspond to the first/third quartiles. 
Table  \ref{table:median_axial_ratio_DM} shows how halos are
monotonically rounder with increasing radius; while the comparison
against Table \ref{table:median_axial_ratio_MHD} shows how DM halos
are consistently rounder in MHD simulations than DM-only runs at every
radius.

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_DM.png}
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_MHD.png}
\end{center}
\caption{Axial ratios for the 30 halos in the Level 3 DM simulations
  on the left and MHD simulations on the right.
   Each dot represents the shape characterization of each halo at the
   2 times the virial radius and a  1/16 fraction of the virial radius
   differentiated by color. 
   Errorbar shows median and errors for each sampled radii. 
   Conclusion: DM halos are rounder on the outskirts {\bf Esto necesita
  correccion. Debe ser a R1/16 y R (no 2R!)}}
  \label{fig:triax_DM_MHD}
\end{figure*}

\begin{table}
\setlength{\tabcolsep}{3pt}
\begin{center}
\begin{tabular}{l|ccccc}
 &$R_{1/16}$& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$\\
\hline 
$b/a$ &$0.55^{+0.07}_{-0.07}$&$0.57^{+0.09}_{-0.08}$&$0.61^{+0.15}_{-0.08}$&$0.65^{+0.18}_{-0.10}$&$0.70^{+0.13}_{-0.10}$ \\ [0.1cm]
$c/a$ &$0.42^{+0.12}_{-0.03}$&$0.45^{+0.11}_{-0.04}$&$0.49^{+0.09}_{-0.05}$&$0.52^{+0.10}_{-0.05}$&$0.56^{+0.10}_{-0.05}$\\ [0.1cm]
$T$ &$0.89^{+0.03}_{-0.08}$&$0.88^{+0.04}_{-0.12}$&$0.84^{+0.08}_{-0.23}$&$0.81^{+0.08}_{-0.29}$&$0.75^{+0.14}_{-0.25}$\\ [0.1cm]
\end{tabular}
\end{center}
\caption{Median values of axial ratios $q,s$ and triaxiality parameter
  $T$ for DM halos in DM-only simulations at different radii. The
  median is computed over the 30 halos in Level 3 simulations.}  
\label{table:median_axial_ratio_DM}
\end{table}

\begin{table}
\setlength{\tabcolsep}{3pt}
\begin{center}
\begin{tabular}{l|ccccc}
 &$R_{1/16}$& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$\\
\hline 
$b/a$ &$0.93^{+0.04}_{-0.04}$&$0.95^{+0.03}_{-0.03}$&$0.95^{+0.02}_{-0.05}$&$0.93^{+0.04}_{-0.06}$&$0.93^{+0.04}_{-0.10}$\\[0.1cm]
$c/a$ &$0.73^{+0.05}_{-0.09}$&$0.73^{+0.07}_{-0.10}$&$0.73^{+0.08}_{-0.10}$&$0.73^{+0.09}_{-0.08}$&$0.75^{+0.07}_{-0.11}$\\[0.1cm] 
$T$ &$0.31^{+0.15}_{-0.22}$&$0.20^{+0.24}_{-0.12}$&$0.24^{+0.20}_{-0.12}$&$0.30^{+0.26}_{-0.16}$&$0.36^{+0.23}_{-0.23}$\\[0.1cm] 
\end{tabular}
\end{center}
\caption{Median values of axial ratios $q,s$ and triaxiality parameter
  $T$ for DM halos in MHD-only simulations at different radii. The
  median is computed over the 30 halos in Level 3 simulations.}  
\label{table:median_axial_ratio_MHD}
\end{table}

\subsection{Shape evolution with cosmic time}

\begin{figure*}
  \includegraphics[width=\columnwidth]{./pics/Redshift/halo_27_DM_Z_correlation.png}
  \includegraphics[width=\columnwidth]{./pics/Redshift/halo_24_level3_MHD_Z_Triax.png}
  \caption{Radial profile at $z=0$ (dashed line) and 
    the historical profile at the virial radius (colour line). 
    Results for DM simulations on the left, for MHD on the right.
    {\bf Aqui la idea es mostrar el mismo
      halo, no halos diferentes!}} 
  \label{fig:redshift_triaxial}
\end{figure*}

\begin{figure*}
  \subfloat[halo 16 DM]{\includegraphics[width=\columnwidth]{./pics/Redshift/halo_16_level3_DM_Z.png}}
  \subfloat[halo 16 MHD]{\includegraphics[width=\columnwidth]{./pics/Redshift/halo_16_level3_MHD_Z.png}}
  \caption{Radial profile (comoving) of axial ratios for halo 16 in
    terms of redshift (color). This halo maintains its shape until
    $z\approx 1$ obviating the systematic rounding effect in time from
    asymmetric potentials. Each plot-line represents the radial
    profile at a determined redshift. Conclussion: Mainly for b/a, it increases for:
    (1) for bigger radii (fixed redshift)(2) for lower redshift (fixed
    radius) It explains the correlation between radial profile and
    history, but does not require that curves match in the triaxial
    plane. {\bf En esta grafica el panel de abajo deberia ser la triaxialidad.}}
  \label{fig:RedshiftGood}
\end{figure*}

We know that DM-only have a steady and monotonous
trend towards larger sphericity with increasing radius. 
This radial trend is mimicked when the shape is measured at the virial
radius as a function of cosmic time.
The halo should become rounder with decreasing redshift, this is
expected by the continuous influence of the gravitational potential on
a collisionless fluid \citep{Vera-Ciro_et_al._2011}.

We show in the left panel of Figure \ref{fig:redshift_triaxial} an
example with this effect in Halo 27 of the DM simulations:
the radial triaxiality at $z=0$ and the historical triaxiality at
$R_{\rm vir}$ are correlated. 
The right panel on the same Figure \ref{fig:redshift_triaxial}
illustrates how this correlation is absent in MHD simulations.

This means that for DM-only halos one can approximate its shape at
higher redshift by simply sampling its 
current shape at a smaller radius. 
This correlation seems to be prompted by the continous inside-out
build-up of the dark matter halo; baryonic effects seem to jeopardize
the apparent smoother growth in DM-only simulations.

%Discuss if this correlation may be recovered if compared for example at Disk radius in stead of virial radius.\\

\subsection{DM halo - Stellar Disk Alignment}

A common assumption in observational models of the MW DM halo is that
its minor axis is perfectly aligned with the disk axis.
Although it is a reasonable assumption to guarantee the
stability of the galactic disk in simplified models of isolated
galaxies, this might not hold in an explicit cosmological context.

To examine the validity of this assumption  we sampled the shape at 5
different radii and plotted  directions in a cartesian coordinate
system where the $z$-axis always corresponds to the minor axis
measured at the virial radius.

{\bf En este caso hace falta la figura con la distribuci\'on integrada de cos theta}.
Figure \ref{fig:alignment} shows the cumulative distribution of
$\cos\theta$, where $\theta$ is the angle betwen the DM halo minor
axis and the stellar disk angular momentum.  
Each line shows the results at different radii.
We find that the majority of the disks are aligned with the minor axis
of their DM halo within $\approx 30^{\circ}$. 
Furthermore, if there is a good alignment measured at the virial
radius, this alignment is well conserved at smaller radii.

{\bf En este caso hace falta la figura de la evoluci\'on de cos theta
  como funci\'on del redshift}
However, there are some disks that show strong missalignments. 
To better understand the missalignments we plot the evolution of
$\cos\theta$ with time to find that the missalignment has been present
for the last XXX Gyr.
This trend is summarized in Figure \ref{fig:alignment_history}.

%\begin{figure*}
%  \centering
%  \subfloat[Perfectly aligned Axes]{\includegraphics[width=0.6\columnwidth]{./pics/well_axes.png}}
%  \hfill
%  \subfloat[Somewhat aligned Axes]{\includegraphics[width=0.6\columnwidth]{./pics/rotating_axes.png}}
%  \hfill
%  \subfloat[Chaotic Axes]{\includegraphics[width=0.6\columnwidth]{./pics/chaotic_axes.png}}
%  \hfill
%  \caption{Star: Minor Axis
%    Triangle: Medium Axis
%    Square: Major Axis
%    Color: Radii at which shape was sampled (show radii sampled)
%    Contour color: If orientation is above or below in this projection
%    Cross (black): Orientation of the stellar disk
%    Conclusion: Axes (minor) are not (generally) aligned with the
%    stellar disk nor are they usually aligned with each other from
%    different radii. We show some cases that may happen.} 
%  \label{fig:alignment}
%\end{figure*}

\textbf{Discussion about the distribution of alignments and their
  evolution in time: Precesion or temporary instabilities?}

\section{Discussion}

\subsection{What drives the rounding effect?}

From our characterization of radial shapes it is clear that
MHD halos are rounder than DM halos every sampled radii. 
It is also noticeable that the rounding effect of baryons is stronger
at the disk regime, where the DM halo is almost perfectly oblate. 
Furthermore, MHD halos tend towards more oblate shapes (T < 0.5)
despite DM halos tendency towards more prolate shapes (T>0.5). 
This rounding effect can be explained by gravitational effect of the
flattened axisymmetric galactic disk. 
It also explanes the weakness of this affect around $\approx 100$kpc,
where the disk potential is weaker compared to the DM halo potential.

{\bf Hace falta una grafica de la distribucion cumulativa de
  triaxialidad para (R\_vir y R\_vir/16 por separado), en cada panel se
  com para MHD vs DM.}

  \begin{figure*}
\centering
{\includegraphics[width=0.6\textwidth]{./pics/Star_Disk_Alignment/Cummulative_Alignment_Histogram_Rvir.png}}
\caption{Cummulative distribution of alignment $cos\theta$ between the minor axis vector sampled as R virial and the star disk vector} \label{fig:alignment_out}
\end{figure*}

  \begin{figure*}
\centering
{\includegraphics[width=0.6\textwidth]{./pics/Star_Disk_Alignment/Cummulative_Alignment_Histogram_Rvir_16.png}}
\caption{Cummulative distribution of alignment $cos\theta$ between the minor axis vector sampled as 1/16 of R virial and the star disk vector} \label{fig:alignment_in}
\end{figure*}

Following that linea reasoning, one would also expect that the rounding
effect of baryons is related to some  galactic parameters such as its
component masses and radii. 
We look for these kind of correlations and to find that the strongest
can be found for the stellar density.
However, the correlation is relatively low ({\bf cuanto vale el
  coeficiente de correlation}) most likely due to the different
formation histories.
In other words, the effect of the baryonic disk on the shape of the DM halo
does not fully explain the deviation from oblateness of MHD halos at
$r<10$kpc.

Figure  \ref{fig:Star_Density_effect} shows the
{\bf que es es lo que muestra esta grafica? falta las unidades de la
  densidad. y el eje vertical que es? es un cambio absoluto? fraccional?}

{\bf Finalmente cuales son las cantidades disponibles en el disco?
  cuales son las que muestran una mayor correlacion? Haria falta un
  plot con todas las correlaciones y la mencion de alguna prueba de
  machine learning del fit lineal para ver cuales son los parametros
  mas importantes.}

\textbf{Actually we have not examined the relation of c/a in MHD halos
  with some measure of c/a from the disk, that is something like
  Zdisk/Rdisk. This actually would make more sense from a physical
  point of view: effect of the potential. }

\textit{ Talk about source of triaxiality at the inner parts of the
  halos (bar?). This source of triaxiality at the inner parts explains
  why the axial ratios are $\approx 0.95$ and not exactly $1$. We
  should also discuss that the decrease in the axial ratios for bigger
  radii may actually be bigger/steeper but it is dimmed by the
  contribution of inner parts.}

\begin{figure}
  \includegraphics[width=\columnwidth]{./pics/Delta asphericity Vs Star Density.png}
  \caption{Difference in asphericities between MHD and DM shapes Vs
    Star Density of the simulation. Unsure about this graphic. Take
    delta asphericity as the strength of the rounding effect of
    baryons.}  
  \label{fig:Star_Density_effect}
\end{figure}

\subsection{Comparison against observational constraints}

\begin{table*}
\begin{tabular}{|l|cc|c|c|p{7cm}|}\hline
Reference&$q_{\rho}$&$s_{\rho}$&$R$&$\theta$&
Methodology\\ 
\hline \hline \citet{Olling_and_Merrifield_2000}& $1.00$
& $0.80$ &  $\simeq 8$kpc & $0^{\circ}$&Stellar dynamics and HI
density. \\

\multirow{2}{*}{\citet{Banerjee_and_Chanda_2011}}&${1}$&${1}$&$9$kpc&$0^{\circ}$&Method:
HI
gas. \\ &${0.5}$&${0.5}$&$24$kpc&$0^{\circ}$&Monotonical
change between radial regimes.\\

\citet{Loebman_et_al._2012}&${1.00}$&${0.47}$&$\sim
20$kpc &$0^{\circ}$&Method: SDSS statistics\\

\cite{Johnston_et_al._2005}&${1}$&$0.83-0.92$&$\lesssim
60$kpc&$0^{\circ}$&Method: Sagittarius stream\\

\citet{Bovy_et_el._2016}&${0.95}$&${0.95}$&$\lesssim
20$kpc&$90^{\circ}$ & Stellar streams\\

\citet{Deg_and_Widrow_2013}&$0.72$&$0.28$&
$20$kpc-$60$kpc$ $&$90^{\circ}$&
Mid-axis orientation. Sagittarius stream\\\hline\hline

\citet{Abadi_et_al._2010} &${0.98}$&${0.85}$& & & Simulations. Almost
  independent of radius. No feedback: boundary case\\\hline

\end{tabular}
\caption{{\bf Cuales son las incertidumbres? Con respecto a que eje
    esta medido theta?}}
\end{table*}

\begin{table*}
\begin{tabular}{|l|cc|c|c|p{7cm}|}\hline
Reference&$q_{\phi}$&$s_{\phi}$&$R$&$\theta$&
Methodology\\ \hline \hline

\citet{Bowden_et_al._2016}& 0.5-0.66 &0.5-0.66& 5kpc - 10 kpc& $90^{\circ}$&
Weak constraint on prolate halo. SDSS stars dynamics.\\

\multirow{2}{*}{\citet{Vera-Ciro_and_Helmi_2013}}&${1.00}$&${0.90}$&$\lesssim
10$kpc&$0^{\circ}$ & Sagittarius stream \& LMC \\
&${0.90}$&${0.80}$&$\gtrsim 10$kpc&$90^{\circ}$&
Mid-axis orientation on the outside. \\

\citet{Law_and_Majewski_2009}&${0.83}$&${0.67}$&
$\lesssim 60$kpc&$90^{\circ}$&Mid-axis orientation. Sagittarius
stream\\

\citet{Law_and_Majewski_2010}&${0.99}$&${0.72}$&
$20$kpc-$60$kpc$$&$90^{\circ}$&Mid-axis orientation, Sagittarius
stream\\

\citet{Deg_and_Widrow_2013} & $0.82$&$0.40$&
$20$kpc $60$kpc$ $&$90^{\circ}$&
Mid-axis orientation. Sagittarius stream\\\hline \hline

\citet{Chua_et_al._2018}&${0.88\pm0.10}$&${0.70\pm0.11}$&$0.15R_{200}$&
& Illustris\\

\citet{Bryan_et_al._2013}&$0.84-0.86$&$0.66-0.70$&$R_{200}$& & 
For different cosmologies and feedback recipies. Calculated from a fit
at $M_\odot=10^12$\\\hline

\end{tabular}
\caption{{\bf Cuales son las incertidumbres? Con respecto a que eje
    esta medido theta?}}
\end{table*}
%\end{multicols}

Half of the observational constraints are computed in terms of
isodensity contours, the other half in terms of isopotential contours.
To compare our results against the second kind we must either
translate the isodensity results or recompute in terms of isopotential
regions.
For this purpose, we run a simple iterative algorithm to find an
approximation of the shape of the isopotential contour.

First, we calculate the mean and standard deviation of the potential over a
spherical shell of width equals to $10\%$ of the radius at which it is
sampled. 
Then, we calculate the inertia tensor of particles with potential
within $1\sigma$ around the mean potential and calculate its triaxial
characterization with the reduced inertia tensor. 
We repeat the
process of calculating the potential mean and standard deviation until
convergence is achieved with tolerance of $10^{-4}$.

In Figure \ref{fig:density_potential} we compare the two approaches to
measure the axial rations and plot the analytic expectation for $q$, 
$(1-q_{\phi})\approx \frac{1}{3}(1-q_{\rho})$
\citep{Binney_and_Tremaine_2008}, taking the volume-enclosed axial
ratios  as an approximation for the isodensity contour ratios
$q_{\rho}$. 
This plot is computed at four different radii.

Although the analytic expression is meant to be used on the outer
regions of logarithmic axisymmetric halos, it works well as a first
approximation for nearly axisymmetric halos as those produced by our
simulations 
We find that the difference between the measured and the
approximated isopotential axial ratios is not bigger than $quantity
percent$ {\bf }.

{\bf Aqui hace falta una grafica comparando explicitamente los
  valores para q y para s, esto para diferentes radios.
  Otro punto importante es que se tiene q, pero como se
  relaciona s?
  Ademas hay que calcularlos para los radius aproximados que se
  presentan en las tablas observacionales y en las de simulaciones.
  10-20kpc se acerca a 1/8Rvir, 20-25 1/4Rvir, 60kpc aproximadamente 1/2Rvir
}

\begin{figure*}
\centering
{\includegraphics[width=0.6\textwidth]{./pics/Shape_Methods/q_pot_Vs_q_den.png}}
\caption{Comparison of q calculated with isopotential and with density enclosed volumes. Continuous lines represent the Binney and Tremaine approximations for different ratios s. Scatter points represent the calculated shapes with an isopotential approximation and with the Allgood method} \label{fig:shape_comp}
\end{figure*}

\begin{figure*}
\centering
{\includegraphics[width=0.6\textwidth]{./pics/Shape_Methods/s_pot_Vs_s_den.png}}
\caption{Comparison of s calculated with isopotential and with density enclosed volumes. Continuous lines represent the Binney \& Tremaine approximation. In the case of the ratio s, it does not depend on q.ds Scatter points represent the calculated shapes with an isopotential approximation and with the Allgood method} \label{fig:shape_comp}
\end{figure*}

\begin{table}
\setlength{\tabcolsep}{3pt}
\begin{tabular}{l|cccc}
 & $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$ \\
\hline \hline
$\bar{q}$&$0.98^{+0.01}_{-0.02}$&$0.97^{+0.01}_{-0.04}$&$0.96^{+0.03}_{-0.06}$&$0.94^{+0.03}_{-0.07}$ \\[0.1cm]
$\bar{s}$&$0.89^{+0.04}_{-0.06}$&$0.88^{+0.04}_{-0.04}$&$0.87^{+0.05}_{-0.05}$&$0.85^{+0.05}_{-0.05}$ \\[0.1cm]
$\bar{T}$&$0.18^{+0.23}_{-0.10}$&$0.36^{+0.19}_{-0.21}$&$0.40^{+0.26}_{-0.20}$&$0.48^{+0.23}_{-0.21}$ \\[0.1cm]
\hline
\end{tabular}
\caption{Median values of isopotential axial ratios $q,s$ and triaxiality parameter $T$ for DM halos in MHD simulations at different radii (columns). }
\label{tabe:isopotential}
\end{table}

\section{Conclusions}

\section*{Acknowledgements}
This project has received funding from the European Union's Horizon
2020 Research and Innovation Programme under the Marie
Sk\l{}odowska-Curie grant agreement No 734374.

 \bibliographystyle{mnras}
 \bibliography{references}
\end{document}

### 2019-07-08 Document/paper.tex
Spericity study

@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_DM.png}
- \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_MHD.png}
+\includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Lvl_4_Triax_Plane_DM.png}
+ \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Lvl_4_Triax_Plane_MHD.png}
 \end{center}
@@
   on the left and MHD simulations on the right.
-   Each dot represents the shape characterization of each halo at the
-   2 times the virial radius and a  1/16 fraction of the virial radius
+   Each dot represents the shape characterization of each halo at the virial radius and a  1/8 fraction of the virial radius
    differentiated by color. 
@@
    Conclusion: DM halos are rounder on the outskirts {\bf Esto necesita
-  correccion. Debe ser a R1/16 y R (no 2R!)}}
+  correccion. Debe ser a R1/16 y R (no 2R!) Corregido!}}
   \label{fig:triax_DM_MHD}
@@
 
-Figure  \ref{fig:Star_Density_effect} shows the
-{\bf que es es lo que muestra esta grafica? falta las unidades de la
-  densidad. y el eje vertical que es? es un cambio absoluto? fraccional?}
-
 {\bf Finalmente cuales son las cantidades disponibles en el disco?
@@
   mas importantes.}
+
+  We measured the sphericity of a halo shape defined as the distance 
+  from the point that characterizes the shape in the triaxiality plane
+  to the point $(q=1,s=1)$, which represents a perfect sphere. Taking this 
+  as our metric of interest, the sphericity question becomes a search for
+  important variables and tendencies that affect this quantity. For this case,
+  given the small sample of 30 halos, we chose to study this problem with different 
+  3 methods to account for the lacking statistical consistency. We analyzed the effect
+  of the Star disk Radius, Baryonic fraction, Gas density, BH density, Gas Radius and
+  Star density.\\
+
+  We started with a simple linear Lasso regression to force a classification of 
+  important variables. Then, we converted this problem in a binary classification problem
+  by partitioning the samples in two balanced groups according to the studied metric which was then fitted using Random forest.
+  Finally, we concluded this analysis with an MCMC sampling of the likelyhood of a linear model
+  with varying slope and intercept parameters.\\
+
+  The results of each method are presented below:
+
+  \begin{table}
+\setlength{\tabcolsep}{3pt}
+\begin{center}
+\begin{tabular}{l|ccc}
+ Variable/Method& Lasso& Random Forest & MCMC \\
+ & (slope) & (feature importance)&(signal-to noise)\\
+\hline 
+Star disk Radius &$-0.168 (1)$&$23\% (2)$&$-0.140$  (3)\\[0.1cm]
+Gas Radius&$0.081 (5)$&$12.6\% (5)$&$0.217 (1)$\\[0.1cm] 
+Star Density &$-0.064 (6)$&$15.2\% (4)$&$-0.102 (6)$\\[0.1cm]
+BH Density&$0.084 (4)$&$16.1\% (3)$&$0.108 (5)$\\[0.1cm] 
+Gas Density &$0.097 (3)$&$28.4 \%(1)$&$0.202 (2)$\\[0.1cm] 
+Baryonic fraction &$-0.167 (2)$&$4\% (6)$&$/0.146 (4)$\\[0.1cm]  
+\end{tabular}
+\end{center}
+\caption{Results of variable importance of the three methods used to analyse
+		 the effect of baryons on the rounding effect of halos. Each method has a different
+		 metric for the variable importance and are not comparable but in rankings}  
+\label{table:sphericity}
+\end{table} 
+  \begin{figure*}
+\centering
+{\includegraphics[width=0.6\textwidth]{./pics/Sphericity/Sphericity_signal_to_noise.png}}
+\caption{Distribution of likelihood for different values of the linear parameters. This gives us an idea of the consistency of the fit } \label{fig:sphericity}
+\end{figure*}
 

### 2019-07-10 Document/paper.tex
figura 1 extendida nuevo caption

@@
   \centering
-  \subfloat[halo 16 DM shape at small
-    radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_16_inner.png}} 
+  \subfloat[DM shape at small radius]{\includegraphics[width=0.5\textwidth]{level4_DM_halo_24_2.png}} 
   \hfill
-  \subfloat[halo 16 DM shape at big
-    radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_16_outer.png}} 
+  \subfloat[DM shape at large radius]{\includegraphics[width=0.5\textwidth]{level4_DM_halo_24_4.png}} 
   \hfill
-  \caption{DM density for inner/outer (left/right panel) DM halo regions.  
-  Slice 20 percent of the max-min range in the "z" position of
-  particles belonging to the main structure, centered at halo defined
-  position (calculated with most bounded particle) }  
+
+  \subfloat[MHD shape at small radius]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_2.png}} 
+  \hfill
+  \subfloat[MHD shape at large radius]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_4.png}} 
+  \hfill 
+  \caption{DM density in a slice with width one tenth of the virial radius.
+  The black ellipses show the result of the fitting procedure. 
+  Upper panels correspond to DM only simulations, lower panels to MHD simulations.
+  Left panels show data at small radii, while right panels at large radii.}
 \label{fig:slices}

### 2019-07-10 Document/paper.tex
new plots

@@
   Upper panels correspond to DM only simulations, lower panels to MHD simulations.
-  Left panels show data at small radii, while right panels at large radii.}
+  Left panels show data at small radii, while right panels at large
+  radii.
+  The cut is made along the minor axis of the halo shape.}
 \label{fig:slices}
 \end{figure*}
+
+\begin{figure*}
+\centering
+{\includegraphics[width=0.6\textwidth]{./pics/MHD_Vs_DM/halo16_new.png}}
+\caption{Radial profile for the axial ratios $b/a$, $c/a$, and the triaxiality parameter
+  $T$ at redshift $z=0$.
+  The continous/dashed lines correspond to the MHD/DM simulations respectively.
+  The vertical line corresponds to the virial radius.}
+\label{fig:triaxial_radius}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Lvl_4_Triax_Plane_DM.png}
+ \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Lvl_4_Triax_Plane_MHD.png}
+\end{center}
+\caption{Axial ratios for the 30 halos in the Level 3 DM simulations
+  on the left and MHD simulations on the right.
+   Each dot represents the shape characterization of each halo 
+   Red circles represent measurements at the virial radius and the
+   blue squares are measurements at 1/8 of the virial radius.   
+   The crosses represent the mean values and standard deviation of
+   each sample.
+   Overall we can see three things. 
+   First, in DM only simulations halos are rounder in the outskirts
+   than in the inner part.
+   Second, halos in MHD are rounder than its DM only counterparts.
+   Third, halos in MHD simulations are slightly rounder in the inner
+   part compared to the outskirts.}
+  \label{fig:triax_DM_MHD}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_DM.pdf}
+\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_MHD.pdf}
+\caption{Cumulative fraction of the triaxiality for all 30 halos in
+  Level 4 simulations. Right/left panel correspond to DM/MHD
+  simulations respectively. 
+  This quantifies the main trends we find: in DM only simulations
+  rounder in the outskirts, halos in MHD are rounder than DM only, and
+  in MHD simulations halos tend to be rounder at the inner regions
+  than its outskirts.}
+\label{fig:triax_cumulative}
+\end{figure*}
+
+\begin{figure}
+\includegraphics[width=0.9\columnwidth]{delta_triaxialiy_distro.pdf}
+\caption{Cumulative fraction of the changes in the triaxility betwen
+  MHD and DM simulations at different radii. 
+  At all radii at least $80\%$ of the halos became rounder in the MHD
+  simulations. 
+  However, the effect is more pronounced at smaller radii.}
+\label{fig:triax_difference}
+\end{figure}
 
@@
 between $1/16 R_{vir}$ and $2R_{vir}$, where  $R_{vir}$ is taken as the
-radius enclosing a sphere with 500 times the average dark matter
+radius enclosing a sphere with 200 times the average dark matter
 density of the Universe. 
@@
 the ellipse on the left (inner halo).
-
-\begin{figure*}
-\centering
-{\includegraphics[width=0.6\textwidth]{./pics/MHD_Vs_DM/halo16_new.png}}
-\caption{Radial profile for the axial ratios and the triaxiality parameter
-  $T=\frac{1-b/a}{1-c/a}$ at redshift $z=0$. 
-  Radial profile was sampled at
-  redshift 0 and there are two sets of lines showing MHD and DM-only
-  versions of the axial ratios profile. {\bf Aqui hay que quiar c/b,
-    no es relevante}} \label{fig:triaxial_radius}
-\end{figure*}
 
@@
 radius.
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Lvl_4_Triax_Plane_DM.png}
- \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Lvl_4_Triax_Plane_MHD.png}
-\end{center}
-\caption{Axial ratios for the 30 halos in the Level 3 DM simulations
-  on the left and MHD simulations on the right.
-   Each dot represents the shape characterization of each halo at the virial radius and a  1/8 fraction of the virial radius
-   differentiated by color. 
-   Errorbar shows median and errors for each sampled radii. 
-   Conclusion: DM halos are rounder on the outskirts {\bf Esto necesita
-  correccion. Debe ser a R1/16 y R (no 2R!) Corregido!}}
-  \label{fig:triax_DM_MHD}
-\end{figure*}
 
@@
 
-{\bf Hace falta una grafica de la distribucion cumulativa de
-  triaxialidad para (R\_vir y R\_vir/16 por separado), en cada panel se
-  com para MHD vs DM.}
-
-  \begin{figure*}
+\begin{figure}
 \centering
-{\includegraphics[width=0.6\textwidth]{./pics/Star_Disk_Alignment/Cummulative_Alignment_Histogram_Rvir.png}}
-\caption{Cummulative distribution of alignment $cos\theta$ between the minor axis vector sampled as R virial and the star disk vector} \label{fig:alignment_out}
-\end{figure*}
-
-  \begin{figure*}
-\centering
-{\includegraphics[width=0.6\textwidth]{./pics/Star_Disk_Alignment/Cummulative_Alignment_Histogram_Rvir_16.png}}
-\caption{Cummulative distribution of alignment $cos\theta$ between the minor axis vector sampled as 1/16 of R virial and the star disk vector} \label{fig:alignment_in}
-\end{figure*}
+\includegraphics[width=0.5\textwidth]{cumulative_alignment.pdf}
+\caption{Cumulative distribution of alignment $\cos\theta$ between the
+  minor axis of the dark matter halo at different radii and the
+  stellar disk.} \label{fig:alignment_out}
+\end{figure}
 
@@
 \end{table}
-  \begin{figure*}
-\centering
-{\includegraphics[width=0.6\textwidth]{./pics/Sphericity/Sphericity_signal_to_noise.png}}
-\caption{Distribution of likelihood for different values of the linear parameters. This gives us an idea of the consistency of the fit } \label{fig:sphericity}
-\end{figure*}
+
+%  \begin{figure*}
+%\centering
+%{\includegraphics[width=0.6\textwidth]{./pics/Sphericity/Sphericity_signal_to_noise.png}}
+%\caption{Distribution of likelihood for different values of the linear parameters. This gives us an idea% of the consistency of the fit } \label{fig:sphericity}
+%\end{figure*}
 

### 2019-07-10 Document/paper.tex

@@
     the historical profile at the virial radius (colour line). 
-    Results for DM simulations on the left, for MHD on the right.
-    {\bf Aqui la idea es mostrar el mismo
-      halo, no halos diferentes!}} 
+    Results for DM simulations on the left, for MHD on the right.{\bf
+      Update with halo 24}}
   \label{fig:redshift_triaxial}
@@
 
-\begin{figure}
-  \includegraphics[width=\columnwidth]{./pics/Delta asphericity Vs Star Density.png}
-  \caption{Difference in asphericities between MHD and DM shapes Vs
-    Star Density of the simulation. Unsure about this graphic. Take
-    delta asphericity as the strength of the rounding effect of
-    baryons.}  
-  \label{fig:Star_Density_effect}
-\end{figure}
+%\begin{figure}
+%  \includegraphics[width=\columnwidth]{./pics/Delta asphericity Vs Star Density.png}
+%  \caption{Difference in asphericities between MHD and DM shapes Vs
+%    Star Density of the simulation. Unsure about this graphic. Take
+%    delta asphericity as the strength of the rounding effect of
+%    baryons.}  
+%  \label{fig:Star_Density_effect}
+%\end{figure}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.4\textwidth]{q_pot_vs_q_den.pdf}
+\includegraphics[width=0.4\textwidth]{s_pot_vs_s_den.pdf}
+\caption{Comparison of $q$ and $s$ calculated with isopotential or
+  density enclosed volumes. 
+  Continuous lines represent the Binney and Tremaine approximations
+  and the dots are the measurements on the simulations.}
+\label{fig:shape_comp} 
+\end{figure*}
 
@@
 
-\begin{figure*}
-\centering
-{\includegraphics[width=0.6\textwidth]{./pics/Shape_Methods/q_pot_Vs_q_den.png}}
-\caption{Comparison of q calculated with isopotential and with density enclosed volumes.
-Continuous lines represent the Binney and Tremaine approximations for different ratios s.
-Scatter points represent the calculated shapes with an isopotential approximation and with the Allgood method} \label{fig:shape_comp}
-\end{figure*}
-
-\begin{figure*}
-\centering
-{\includegraphics[width=0.6\textwidth]{./pics/Shape_Methods/s_pot_Vs_s_den.png}}
-\caption{Comparison of s calculated with isopotential and with density enclosed volumes.
-Continuous lines represent the Binney \& Tremaine approximation.
-In the case of the ratio s, it does not depend on q.ds Scatter points represent the calculated shapes with an isopotential approximation and with the Allgood method} \label{fig:shape_comp}
-\end{figure*}
-
 \begin{table}

### 2019-07-14 Document/paper.tex
updated tex
abstract

@@
 
-\title[Dark Matter halo shape in the AURIGA simulations]{The shape of dark matter
-  halos in the AURIGA simulations}  
+\title[The shape of dark matter haloes in the AURIGA simulations]
+{Dark Matter halo shape in the AURIGA simulations: radial
+  dependence, time evolution and correlation with baryonic disk
+  properties}
 \author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
@@
 \begin{abstract}
-We measure the shape of the dark matter halos of Milky Way type galaxies.
+We present shape measurements of dark matter halos in a suit
+of 30 cosmological simulations from the Auriga project.
+One half of the Auriga simulations include Magnetohydrodynamics and stellar
+formation, the other half is performed in a dark matter only setting.
+We find a strong influence of baryons in making dark matter halos rounder at all
+radii compared to its dark matter only counterparts.
+This change in triaxility its more pronounced towards the inner
+regions of the halo.
+At distances close to the disk rounder dark matter distributions
+correlate with massive stellar disks and low gas density.
+The dark matter shape shows a strong alignment with the
+stellar disk shape as a function of radius, the stronger aligmnet is
+found at $~50$kpc, this alignment weakens at smaller and larger radii. 
+In dark matter only simulations the time evolution of the shape
+measured at the virial radius correlates with the radial shape
+evolution at present day.  
+However, this correlation is lost once the baryonic effects are
+included. 
+We conclude that in our simulation suite that baryonic physics
+produces rounder halos with a strong correlation between its inner
+shape and the stellar and gaseous properties of the disk.
 \end{abstract}
@@
 \begin{keywords}
-keyword1 -- keyword2 -- keyword3
+galaxies: evolution --- galaxies: formation --- galaxies: haloes ---
+dark matter
 \end{keywords}
@@
 
-%  \begin{figure*}
-%\centering
-%{\includegraphics[width=0.6\textwidth]{./pics/Sphericity/Sphericity_signal_to_noise.png}}
-%\caption{Distribution of likelihood for different values of the linear parameters. This gives us an idea% of the consistency of the fit } \label{fig:sphericity}
-%\end{figure*}
+\begin{figure*}
+\centering
+\includegraphics[width=0.9\textwidth]{delta_T_correlations.pdf}
+\caption{Changes in the triaxiality at $R_{\rm vir}/8$ as a function of different halo and disk properties.}
+\label{fig:sphericity}
+\end{figure*}
 

### 2019-07-14 Document/paper.tex
edit

@@
 
-In this work we use the results of the state-of-the art Auriga
-simulations \citep{auriga}. 
+In this work we use the results of the state-of-the artAuriga
+simulations
+
+The Auriga project offers cosmological zoom in simulations of MW-sized 
+dark matter halos in a $\Lambda CDM$ cosmology. 
+This simulations come in two versions: dark matter only and
+baryonic physics including magetohydrodynamics (MHD).
+A detailed description of the simulations and their
+disk properties can be founc in \citep{auriga}, here we summarize its
+main features.
+
 The objects in those simulations were selected from a set of 30
@@
 These halos were randomly selected from a sample of the most isolated
-halos whose virial mass $M_{200}$ varied between $10^{12}M_\odot$ and
+halos whose virial mass $M_{200}$ was between $10^{12}M_\odot$ and
 $2\times 10^{12}M_\odot$. 
+The cosmological parameters in these simulatins correspond to
+$\Omega_m=0.307$, $\Omega_b=0.048$, $\Omega_\Lambda=0.693$ and a
+dimensionless Hubble parameter $h=0.6777$ [CITATION PLANCK 2014]
+
 These halos were re-simulated with higher resolution an varying

### 2019-07-14 Document/paper.tex
edit intro

@@
 \newcolumntype{?}{!{\vrule width 1pt}}
+\newcommand{\Msun}{\,{\rm Mpc}$_{\odot}$\,}
 \newcommand{\Mpch}{\,{\rm Mpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
@@
 
-In this work we use the results of the state-of-the artAuriga
-simulations
-
 The Auriga project offers cosmological zoom in simulations of MW-sized 
@@
 These halos were randomly selected from a sample of the most isolated
-halos whose virial mass $M_{200}$ was between $10^{12}M_\odot$ and
+halos at $z=0$ whose virial mass $M_{200}$ was between $10^{12}M_\odot$ and
 $2\times 10^{12}M_\odot$. 
@@
 
-These halos were re-simulated with higher resolution an varying
-physical realism using the AREPO code \citep{arepo}.
+The selected halos were re-simulated at higher resultion by applying a
+zoom-in technique with varying physical realism using the moving-mesh AREPO code
+that includes gravity, ideal magnetohydrodynamics (MHD), 
+phenomenological descriptions for star formation, chemical enrichment
+from supernovae and its stellar feedback.  The simulation also follows
+the formation and evolution of black holes together with the Active
+Galactic Nuclei feedback \citep{arepo} [CITATIONPAKMORE].
 
-All 30 halos were simulated within resolution defined for Aquarius
+The 30 zoom-on halos have a dark matter particle mass of $\sim 3\times
+10^5$\Msun.
 simulations corresponding to $\sim 3\times 10^6$ high resolution DM

### 2019-07-14 Document/paper.tex
simulation descriptioin

@@
 The 30 zoom-on halos have a dark matter particle mass of $\sim 3\times
-10^5$\Msun.
-simulations corresponding to $\sim 3\times 10^6$ high resolution DM
-particles of $\sim 2.5 \times 10^5 M_\odot$.  
+10^5$\Msun while the barynic mass resolution is $\sim 5\times 10^4$\Msun.
+The softening lenght for gravitational force computation for stellar
+particles and high-resolution dark matter particles 
+is fixed to be 500 $h^{-1}$ pc in comoving coordinates up to $z=1$,
+and 396 pc in physical coordinates afterwards.
+The gravitational softening lenght for gas cells changes with the mean
+cell radius but is limited to be larger than the stellar softening
+lenght and 1850 pc physical.
+
 This resolution is labeled as Level 4, the main details for each halo

### 2019-07-14 Document/paper.tex
sim description

@@
 
-The 30 zoom-on halos have a dark matter particle mass of $\sim 3\times
+The 30 zoom-in halos have a dark matter particle mass of $\sim 3\times
 10^5$\Msun while the barynic mass resolution is $\sim 5\times 10^4$\Msun.
@@
 lenght and 1850 pc physical. 
+This setup corresponds to \texttt{Level4} resolution.
+From these 30 halos, 6 of them where re-simulated at higher resolution
+taking into account a spatial factor of 2 in each spatial dimension,
+this is the \texttt{Level3} resolution.
 
-This resolution is labeled as Level 4, the main details for each halo
-are consigned in Table \ref{tab:level4}. 
-From these 30 halos, 6 of them where re-simulated at higher resolution
-(labeled as Level 3) taking into account a spatial factor of 2 in each
-dimension.   
-Details of Level 3 halos are in Table \ref{tab:level3}. 
-Furthermore, for each halo in each level of resolution there are two
-versions of the simulation: DM-only and DM plus baryons with
-magneto-hydrodynamical (MHD) physics.
+In this work we analyse all the 30 halos in the \texttt{Level4}
+resolution. 
+All the results that we report at $z=0$ as a function of radius and
+the correlations with disk properties are performed with that sample.
+For the measurement on shape evolution with time we use the 6 halos in
+the \texttt{Level3} simulations.
+Finally, all  halos described so far have also been simulated at the same
+resolutions without MHD using dark matter particles only, we refer to
+these halos as the DMO (Dark Matter Only) sample.
 

### 2019-07-14 Document/paper.tex
edit

@@
 
-\title[The shape of dark matter haloes in the AURIGA simulations]
-{Dark Matter halo shape in the AURIGA simulations: radial
-  dependence, time evolution and correlation with baryonic disk
+\title[The shape of dark matter haloes in the Auriga simulations]
+{Dark matter halo shape in the Auriga simulations: radial
+  dependence, time evolution and correlation with baryon disk
   properties}
@@
 $^{1}$Departamento de F\'sica, Universidad de los Andes, Cra. 1 No.
-18A-10, Edificio Ip, Bogot\', Colombia.\\
+18A-10, Edificio Ip, Bogot\'a, Colombia.\\
 $^{2}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg
@@
 of 30 cosmological simulations from the Auriga project.
-One half of the Auriga simulations include Magnetohydrodynamics and stellar
-formation, the other half is performed in a dark matter only setting.
+For all measurements we compare the results with full
+magnetohydrodynamics and dark matter only physics.
 We find a strong influence of baryons in making dark matter halos rounder at all

### 2019-07-14 Document/paper.tex
edit method

@@
 The Auriga project offers cosmological zoom in simulations of MW-sized 
-dark matter halos in a $\Lambda CDM$ cosmology. 
+dark matter halos in a $\Lambda$CDM cosmology. 
 This simulations come in two versions: dark matter only and
@@
 this is the \texttt{Level3} resolution.  
+There are $\sim 4\times 10^6$ dark matter particles within the virial radius
+of \texttt{Level4} halos at $z=0$, this number increases to $\sim 3\times 10^7$ in
+\texttt{Level3} simulations.
 
-In this work we analyse all the 30 halos in the \texttt{Level4}
-resolution. 
-All the results that we report at $z=0$ as a function of radius and
-the correlations with disk properties are performed with that sample.
+In this work all the results that we report at $z=0$ as a function of radius and
+the correlations with disk properties correspond to the 30 halos in
+the \texttt{Level4} resolution. 
 For the measurement on shape evolution with time we use the 6 halos in
@@
 calculated from particle positions.  
+Furthermore, the density contours in thin shells are very sensitive to
+the presence of small satelites.  
+For this reason we measure the shape by taking
+volume-enclosed particles, rather than shell-enclosed.
 
-However, in numerical simulations the density contours are not smooth
-and are sensitive to the presence of small satelites. 
-For this reason we choose to measure the shape by taking
-volume-enclosed particles, rather than shell-enclosed.  
-We follow the shape measurement method presented by
-\cite{Allgood_et_al._2006} that uses the reduced
-inertia tensor,
+We measure the shape using the reduced inertia tensor \citep{Allgood_et_al._2006},
 
@@
 
-with the positions components weighted by the k-th particle distance
-$d_k^2=x_k^2+y_k^2+z_k^2$, the particle positions are measured from
-the minimum of the gravitational potential in each halo.
-The diagonalization of this tensor yields the principal axes of the
-structure as well as the eigen-quantities which are proportional to
-the squared principal axes $a>b>c$.
+where the particle positions are measured from the minimum of the
+gravitational potential in each halo and each is weighted by the k-th
+particle distance 
+$d_k^2=x_k^2+y_k^2+z_k^2$,
+
+The diagonalization of this tensor yields the eigenvectors and
+eigenvalues that represent an ellipsoidal dark matter halo.
+The axis lenghts of this ellipsoid $a\geq b \geq c$ are the square
+root of the ${\bf I}$ eigenvalues and the direction of the principal
+axis are the corresponding eigenvectors
 
@@
 
-We restrict the sampling of the ellipsoidal parameters to radii
-between $1/16 R_{vir}$ and $2R_{vir}$, where  $R_{vir}$ is taken as the
-radius enclosing a sphere with 200 times the average dark matter
+Following the convergence critery by \cite{Vera-Crito_et_al.2011} we
+restrict the sampling of the ellipsoidal parameters to radii  between
+$\sim 2$kpc and $R_{200}$, where  $R_{200}$ correspond to the  radius enclosing a sphere with 200 times the average dark matter
 density of the Universe. 
-All our results use of this reference radius
-unless strictly stated otherwise. 
-We peform the shape measurements both as a function of radius and
-redshift for all halos in the sample.
+On average, over the 30 halos in the \texttt{Level4} sample
+$R_{200}=200\pm 10$kpc. 
+For \texttt{Level3} halos we go down to distances $\sim 0.2$ kpc.
 

### 2019-07-14 Document/paper.tex
edit

@@
    part compared to the outskirts.}
-  \label{fig:triax_DM_MHD}
+  \label{fig:triaxiality_plane}
 \end{figure*}
@@
 
-\section{Determining the halo shape}
+\section{Halo Shape Measurement}
 
@@
 restrict the sampling of the ellipsoidal parameters to radii  between
-$\sim 2$kpc and $R_{200}$, where  $R_{200}$ correspond to the  radius enclosing a sphere with 200 times the average dark matter
-density of the Universe. 
+$\sim 2$kpc and $R_{200}$, where  $R_{200}$ correspond to the  radius
+enclosing a sphere with 200 times the average dark matter density of
+the Universe.  
 On average, over the 30 halos in the \texttt{Level4} sample
@@
 
-\subsection{Radial trends at $z=0$}
+\subsection{The effect of baryons at $z=0$}
 
-We find that in DM-only simulations halos are monotonically rounder
-with increasing radius, confirming results already reported in the
+In the DMO sample we find that halos are rounder with increasing
+radius
+The upper panels in Figure \ref{fig:slices} illustrates this effect.
+The contours show a projected DM slice while the ellipsoid corresponds
+to the full 3D shape determination. 
+There we see a highly ellipsoidal halo shape at radii $\sim 3$kpc
+that becomes less triaxial at $\sim 50$ kpc.
+
+We summarize this trends in Figure \label{fig:triaxiality_plane} by
+plotting the results of all the 30 halos in the DMO sample.
+There we plot the results for every halo in the $c/a$-$b/a$ plane at
+two different radii $R_{200}/8 (\sim 20$kpc$)$
+
+our results for all the 30 halos in the DMO sample
+
+confirming results already reported in the
 literature \citep{Vera-Ciro_et_al._2011}.
-Figure \ref{fig:slices} illustrates this effect.
-There we show the density a DM-only halo at redshift zero in a thin
-slice passing through the halo's centre, each panel shows the halo at
-different radii.
-The ellipse plotted over the contours indicates the outermost
-boundary of the estimated shape ellipsoid. 
-Indeed, the ellipse panel on the right (outer halo) is rounder than
-the ellipse on the left (inner halo).
 

### 2019-07-14 Document/paper.tex
edit

@@
 
-\begin{table*}
-\centering
-\begin{tabular}{l|cc|cc|cc|cc}
-\hline
-\hline
-Halo & \multicolumn{2}{c}{$N_P$/$10^6$} & \multicolumn{2}{c}{$M_P$/$10^5M_\odot$} & 
-\multicolumn{2}{c}{$R_{vir}$/kpc} & \multicolumn{2}{c}{$M_{vir}$/$10^{14} M_\odot$}  \\ \hline
-& DM & MHD& DM & MHD& DM & MHD& DM & MHD\\ \hline \hline
-halo 1&4.068&2.447&2.397&2.022&196.927&187.674&9.062&7.844\\
-halo 2&5.625&5.457&2.481&2.093&235.094&233.934&15.418&15.191\\
-halo 3&3.826&3.852&2.645&2.231&210.693&210.955&11.099&11.141\\
-halo 4&4.585&4.530&2.590&2.185&219.378&215.438&12.529&11.866\\
-halo 5&3.262&3.290&2.533&2.137&196.984&197.246&9.071&9.106\\ 
-halo 6 ($\star$)&3.184&3.110&2.337&1.972&191.840&189.342&8.378&8.054\\ 
-halo 7&3.878&3.729&2.296&1.937&197.864&196.509&9.193&9.005\\
-halo 8&2.772&2.796&2.451&2.068&190.716&191.764&8.231&8.368\\
-halo 9&3.038&3.010&2.738&2.310&195.826&190.640&8.911&8.222\\
-halo 10&2.700&2.751&2.541&2.144&187.139&188.147&7.777&7.904\\
-halo 11&4.146&4.116&2.541&2.144&221.821&219.568&12.952&12.560\\
-halo 12&2.865&2.908&2.645&2.231&192.280&192.038&8.436&8.404\\
-halo 13&3.520&3.600&2.393&2.019&202.139&203.815&9.801&10.048\\
-halo 14&4.200&4.475&2.499&2.108&215.535&218.927&11.882&12.453\\
-halo 15&2.888&2.845&2.541&2.144&199.848&200.658&9.471&9.588\\ 
-halo 16 ($\star$)&3.821&3.871&2.499&2.108&212.590&212.632&11.401&11.408\\ 
-halo 17&2.752&2.781&2.552&2.153&188.067&187.404&7.893&7.811\\
-halo 18&3.770&3.624&2.738&2.310&201.124&207.293&9.655&10.571\\
-halo 19&2.989&3.086&2.645&2.231&200.244&200.325&9.527&9.540\\
-halo 20&3.903&3.822&2.481&2.093&210.097&211.423&11.005&11.214\\ 
-halo 21 ($\star$) &4.105&4.075&2.640&2.227&219.527&219.823&12.555&12.604\\ 
-halo 22&2.794&2.766&2.625&2.215&188.363&184.801&7.931&7.489\\ 
-halo 23 ($\star$) &3.977&4.073&2.795&2.358&217.768&215.959&12.254&11.952\\
-halo 24 ($\star$) &4.466&4.426&2.522&2.127&217.440&215.147&12.199&11.817\\ 
-halo 25&2.902&2.806&2.645&2.231&199.922&198.299&9.482&9.254\\
-halo 26 &4.610&4.716&2.506&2.115&219.984&218.939&12.633&12.454\\
-halo 27 ($\star$) & 5.060&5.018&2.590&2.185&228.036&226.225&14.071&13.740\\ 
-halo 28 & 4.184&4.276&2.645&2.231&216.979&217.997&12.121&12.294\\
-halo 29 & 4.827&4.613&2.499&2.108&225.791&219.935&13.660&12.625\\
-halo 30 & 3.268&3.112&2.579&2.176&195.043&194.741&8.805&8.763\\
-\hline
-\hline
-\end{tabular}
-\caption{Specifications of each level 4 galaxy (halo). 
-  The DM and MHD versions of each parameters are presented together. 
-  The columns correspond to: (1) Halo name, (2,3) Millions of DM
-  particles belonging to the halo, (4,5) DM particle mass in
-  $10^5M_\odot$, (6,7) Halo Virial radius in kpc and (8,9) halo virial
-  mass in $10^{14}M_\odot$. Halos marked with a star ($\star$) are
-  correspond to halos resimulated at higher resolution (level 3).}  
-\label{tab:level4}
-\end{table*}
-
-\begin{table*}
-\centering
-\begin{tabular}{l?cc?cc?cc?cc}
-\hline
-\hline
-Halo & \multicolumn{2}{c?}{$N_P$/$10^6$} & \multicolumn{2}{c?}{$M_P$/$10^5M_\odot$} & \multicolumn{2}{c?}{$R_{vir}$/kpc}&\multicolumn{2}{c}{$M_{vir}$/$10^{14}M_\odot$}  \\ \hline
-& DM & MHD& DM & MHD& DM & MHD& DM & MHD\\ \hline \hline
-halo 6&24.902&24.185&0.292&0.246&191.741&188.367&8.365&7.932\\
-halo 16&29.750&30.334&0.312&0.263&212.622&212.542&11.406&11.395\\
-halo 21&31.993&31.503&0.330&0.278&219.731&220.250&12.588&12.679\\
-halo 23&31.379&31.618&0.349&0.295&217.793&213.358&12.259&11.524\\
-halo 24&34.987&35.153&0.315&0.266&217.313&213.963&12.179&11.624\\
-halo 27&39.617&39.056&0.324&0.273&227.908&223.484&14.048&13.244\\
-\hline
-\hline
-\end{tabular}
-\caption{Same layout Table \ref{tab:level3} for Level 3 simulations (higher
-  resolution than Level 4 simulations).}
-\label{tab:level3}
-\end{table*}
-
 \section{Numerical Simulations}
@@
 \begin{figure*}
-\centering
-{\includegraphics[width=0.6\textwidth]{./pics/MHD_Vs_DM/halo16_new.png}}
-\caption{Radial profile for the axial ratios $b/a$, $c/a$, and the triaxiality parameter
-  $T$ at redshift $z=0$.
-  The continous/dashed lines correspond to the MHD/DM simulations respectively.
-  The vertical line corresponds to the virial radius.}
-\label{fig:triaxial_radius}
-\end{figure*}
-
-\begin{figure*}
 \begin{center}
@@
   than its outskirts.}
-\label{fig:triax_cumulative}
+\label{fig:triaxial_cumulative}
 \end{figure*}
+
+%\begin{figure*}
+%\centering
+%{\includegraphics[width=0.6\textwidth]{./pics/MHD_Vs_DM/halo16_new.png}}
+%\caption{Radial profile for the axial ratios $b/a$, $c/a$, and the triaxiality parameter
+%  $T$ at redshift $z=0$.
+%  The continous/dashed lines correspond to the MHD/DM simulations respectively.
+%  The vertical line corresponds to the virial radius.}
+%\label{fig:triaxial_radius}
+%\end{figure*}
 
@@
 In the DMO sample we find that halos are rounder with increasing
-radius
+radius.
 The upper panels in Figure \ref{fig:slices} illustrates this effect.
@@
 
-We summarize this trends in Figure \label{fig:triaxiality_plane} by
+We summarize this trend in Figure \ref{fig:triaxiality_plane} by
 plotting the results of all the 30 halos in the DMO sample.
-There we plot the results for every halo in the $c/a$-$b/a$ plane at
-two different radii $R_{200}/8 (\sim 20$kpc$)$
-
-our results for all the 30 halos in the DMO sample
-
-confirming results already reported in the
+The left panel shows every halo in the $c/a$-$b/a$ plane at
+two different radii $R_{200}/8 (\sim 20$kpc$)$ and $R_{200}$. 
+The outer part of the halo is systematically rounder tha its inner
+region. 
+Nevertheless the halo shape can still be considerated to be prolate at
+all radii. 
+These plots confirm the results already reported in the
 literature \citep{Vera-Ciro_et_al._2011}.
 
-We quantify this effect by plotting the axial ratios $q$, $s$,
-$s/q$ and the triaxiality $T\equiv \frac{1-q}{1-s}$ as a
-function of radius. 
-As a representative sample of this relations we show on Figure
+A different picture presents itself in the MHD sample.
+There all halos become rounder at all radii than its DMO
+counterpart.
+The lower panel in Figure \ref{fig:slices} can be directly compared to
+its MHD counterpart; there we observe how at large radii the halo
+becomes almost spherical. 
+The right panel in Figure \ref{fig:triaxiality_plane} shows the
+results for the 30 halos in the MHD sample.
+This time the bulk of the halos can be considered oblate and close to
+spherical.
+
+In Figure \ref{fig:triaxial_cumulative} we summarize the results at
+different radii using the cumulative distributions for the 
+triaxility parameter $T$ defined as 
+\begin{equation}
+T=\frac{a^2-b^2}{a^2-c^2}.
+\label{eq:triaxiality}
+\end{equation}
+The left panel of this Figure shows that in the DMO sample the
+triaxility has a median larger than $0.5$ at all radii, furthermore
+this median value increases as we move towards the inner part of the
+halo.
+The right panel shows the exact complementary picture in the MHD
+sampe.
+There the median triaxility is alwas smaller than $0.5$ and this
+triaxility is smaller as we move closer to the galactic disk.
+
+As a representative sample of the effect of baryons relations we show on Figure
 \ref{fig:triaxial_radius} the radial trends for Halo 16 at

### 2019-07-14 Document/paper.tex
triaxiality
edit

@@
 of 30 cosmological simulations from the Auriga project.
-For all measurements we compare the results with full
-magnetohydrodynamics and dark matter only physics.
+For all measurements we compare the results in full
+magnetohydrodynamics against dark matter only physics.
 We find a strong influence of baryons in making dark matter halos rounder at all
@@
   However, the effect is more pronounced at smaller radii.}
-\label{fig:triax_difference}
+\label{fig:delta_triaxial_cumulative}
 \end{figure}
@@
 
-As a representative sample of the effect of baryons relations we show on Figure
-\ref{fig:triaxial_radius} the radial trends for Halo 16 at
-the highest resolution both for DM and MHD simulations.
-The continous lines correspond to the DM simulation and shows how
-the inner part of the halo $r\approx 1$\kpch has values of 
-$q=0.5$, $s=0.5$ while at the virial radius the same
-quantities increase to $q=0.85$, $s=0.6$; in turn the triaxiality
-decreases from $T\approx 1.0$ to $T\approx0.4$.
-
-In the same Figure \ref{fig:triaxial_radius} we also find one of the
-main results of our study: halos in MHD simulations are systematically rounder, at
-every radius, than its DM-only counterparts.  
-The dashed line in Figure \ref{fig:triaxial_radius} shows that at
-$r\approx 1$\kpch  in the MHD simulation we have $q=0.85, s=0.8$
-($q=0.5, s=0.5$ in DM) and at the virial radius $q=0.95, s=0.75$
-($q=0.85, s=0.6$ in DM).  
-However, the triaxiality trend is not as monotonous for MHD halos is
-it is in DM halos. 
-The triaxiality goes almost to zero at an intermediate radius,
-$r\approx 10$\kpc in the case of Halo 16 in Figure
-\ref{fig:triaxial_radius}, to increase again. {\bf pasa lo mismo para
-  todos los halos? es lo mismo para baja y alta resolucion de MHD?}
-
-Figure \ref{fig:triax_DM_MHD} summarizes this comparizon for all 30 halos
-in the Level 3 simulations. 
-Measurements at $R_{\rm vir}/16$ are represented by circles while squares 
-are measurements at $R_{\rm vir}$. 
-All halos, except two, show that outer regions rounder than inner
-regions.
-The exceptions are cases where a merging substructures near  the
-halo's center gives rise to perturbed axial ratio measurements. 
-The right panel on Figure \ref{fig:triax_DM_MHD} shows the same information, this time for
-the MHD simulations. 
-In this case, the main radial trend continues to hold, albeit less
-pronounced.
-We also find that halos in MHD simulations are in general rounder than
-their DM counterparts
-
-This global behaviour can be also illustrated by the individual case
-of Halo 16, shown in Figure \ref{fig:triaxial_radius}.
-At the virial radius the halo is rounder than its DM counterpart as
-evidenced in the axis ratios $b/a$, $c/a$ and the triaxiality.
-In the MHD simulation, going from the virial radius to $10$ \kpch the
-$b/a$ ratio is constant almost close to unity while in the DM-only
-simulation it decreases to $0.5$.
-Between $2$-$10$ \kpc the triaxiality in the DM-only simulation is in
-the range $0.9-1.0$, while the MHD simulation has values between
-$0-0.5$.
-
-In Table \ref{table:median_axial_ratio_DM} and Table \ref{table:median_axial_ratio_MHD}
-we summarize these trends for the median values of the axis ratio in
-the DM and MHD simulations
-The lower/upper bounds correspond to the first/third quartiles. 
-Table  \ref{table:median_axial_ratio_DM} shows how halos are
-monotonically rounder with increasing radius; while the comparison
-against Table \ref{table:median_axial_ratio_MHD} shows how DM halos
-are consistently rounder in MHD simulations than DM-only runs at every
-radius.
-
-\begin{table}
-\setlength{\tabcolsep}{3pt}
-\begin{center}
-\begin{tabular}{l|ccccc}
- &$R_{1/16}$& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$\\
-\hline 
-$b/a$ &$0.55^{+0.07}_{-0.07}$&$0.57^{+0.09}_{-0.08}$&$0.61^{+0.15}_{-0.08}$&$0.65^{+0.18}_{-0.10}$&$0.70^{+0.13}_{-0.10}$ \\ [0.1cm]
-$c/a$ &$0.42^{+0.12}_{-0.03}$&$0.45^{+0.11}_{-0.04}$&$0.49^{+0.09}_{-0.05}$&$0.52^{+0.10}_{-0.05}$&$0.56^{+0.10}_{-0.05}$\\ [0.1cm]
-$T$ &$0.89^{+0.03}_{-0.08}$&$0.88^{+0.04}_{-0.12}$&$0.84^{+0.08}_{-0.23}$&$0.81^{+0.08}_{-0.29}$&$0.75^{+0.14}_{-0.25}$\\ [0.1cm]
-\end{tabular}
-\end{center}
-\caption{Median values of axial ratios $q,s$ and triaxiality parameter
-  $T$ for DM halos in DM-only simulations at different radii. The
-  median is computed over the 30 halos in Level 3 simulations.}  
-\label{table:median_axial_ratio_DM}
-\end{table}
-
-\begin{table}
-\setlength{\tabcolsep}{3pt}
-\begin{center}
-\begin{tabular}{l|ccccc}
- &$R_{1/16}$& $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$\\
-\hline 
-$b/a$ &$0.93^{+0.04}_{-0.04}$&$0.95^{+0.03}_{-0.03}$&$0.95^{+0.02}_{-0.05}$&$0.93^{+0.04}_{-0.06}$&$0.93^{+0.04}_{-0.10}$\\[0.1cm]
-$c/a$ &$0.73^{+0.05}_{-0.09}$&$0.73^{+0.07}_{-0.10}$&$0.73^{+0.08}_{-0.10}$&$0.73^{+0.09}_{-0.08}$&$0.75^{+0.07}_{-0.11}$\\[0.1cm] 
-$T$ &$0.31^{+0.15}_{-0.22}$&$0.20^{+0.24}_{-0.12}$&$0.24^{+0.20}_{-0.12}$&$0.30^{+0.26}_{-0.16}$&$0.36^{+0.23}_{-0.23}$\\[0.1cm] 
-\end{tabular}
-\end{center}
-\caption{Median values of axial ratios $q,s$ and triaxiality parameter
-  $T$ for DM halos in MHD-only simulations at different radii. The
-  median is computed over the 30 halos in Level 3 simulations.}  
-\label{table:median_axial_ratio_MHD}
-\end{table}
+Next we want to test to what extend the global effect of decreasing
+triaxility in MHD simulations compared to the DMO sample 
+holds for individual halos. 
+We compute $\Delta_T\equiv T_{MHD}-T_{DMO}$ the difference between the
+triaxility in the MHD and the DMO simulation for each individual halo. 
+Figure \label{fig:delta_triaxial_cumulative} shows the cumulative
+distribution at the same radii as in
+Figure \label{fig:delta_triaxial_cumulative}.
 
@@
 
-  \begin{table}
-\setlength{\tabcolsep}{3pt}
-\begin{center}
-\begin{tabular}{l|ccc}
- Variable/Method& Lasso& Random Forest & MCMC \\
- & (slope) & (feature importance)&(signal-to noise)\\
-\hline 
-Star disk Radius &$-0.168 (1)$&$23\% (2)$&$-0.140$  (3)\\[0.1cm]
-Gas Radius&$0.081 (5)$&$12.6\% (5)$&$0.217 (1)$\\[0.1cm] 
-Star Density &$-0.064 (6)$&$15.2\% (4)$&$-0.102 (6)$\\[0.1cm]
-BH Density&$0.084 (4)$&$16.1\% (3)$&$0.108 (5)$\\[0.1cm] 
-Gas Density &$0.097 (3)$&$28.4 \%(1)$&$0.202 (2)$\\[0.1cm] 
-Baryonic fraction &$-0.167 (2)$&$4\% (6)$&$/0.146 (4)$\\[0.1cm]  
-\end{tabular}
-\end{center}
-\caption{Results of variable importance of the three methods used to analyse
-		 the effect of baryons on the rounding effect of halos. Each method has a different
-		 metric for the variable importance and are not comparable but in rankings}  
-\label{table:sphericity}
-\end{table}
-
 \begin{figure*}
@@
 %\end{figure}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.4\textwidth]{q_pot_vs_q_den.pdf}
-\includegraphics[width=0.4\textwidth]{s_pot_vs_s_den.pdf}
-\caption{Comparison of $q$ and $s$ calculated with isopotential or
-  density enclosed volumes. 
-  Continuous lines represent the Binney and Tremaine approximations
-  and the dots are the measurements on the simulations.}
-\label{fig:shape_comp} 
-\end{figure*}
 
@@
 
-\begin{table}
-\setlength{\tabcolsep}{3pt}
-\begin{tabular}{l|cccc}
- & $R_{1/8}$& $R_{1/4}$& $R_{1/2}$& $R_1$ \\
-\hline \hline
-$\bar{q}$&$0.98^{+0.01}_{-0.02}$&$0.97^{+0.01}_{-0.04}$&$0.96^{+0.03}_{-0.06}$&$0.94^{+0.03}_{-0.07}$ \\[0.1cm]
-$\bar{s}$&$0.89^{+0.04}_{-0.06}$&$0.88^{+0.04}_{-0.04}$&$0.87^{+0.05}_{-0.05}$&$0.85^{+0.05}_{-0.05}$ \\[0.1cm]
-$\bar{T}$&$0.18^{+0.23}_{-0.10}$&$0.36^{+0.19}_{-0.21}$&$0.40^{+0.26}_{-0.20}$&$0.48^{+0.23}_{-0.21}$ \\[0.1cm]
-\hline
-\end{tabular}
-\caption{Median values of isopotential axial ratios $q,s$ and triaxiality parameter $T$ for DM halos in MHD simulations at different radii (columns). }
-\label{tabe:isopotential}
-\end{table}
-
 \section{Conclusions}

### 2019-07-14 Document/paper.tex
new path

@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Lvl_4_Triax_Plane_DM.png}
- \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Lvl_4_Triax_Plane_MHD.png}
+\includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_DM.png}
+ \includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_MHD.png}
 \end{center}
@@
 \begin{figure}
-\includegraphics[width=0.9\columnwidth]{delta_triaxialiy_distro.pdf}
+\includegraphics[width=0.9\columnwidth]{delta_triaxiality_distro.pdf}
 \caption{Cumulative fraction of the changes in the triaxility betwen

### 2019-07-15 Document/paper.tex
edit

@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_DM.png}
- \includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_MHD.png}
+\includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_DM.pdf}
+ \includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_MHD.pdf}
 \end{center}
@@
 volume-enclosed particles, rather than shell-enclosed.  
+This method yields results in good agreement to the isodensity
+contours for radii smaller than half the virial radius as explored by
+\citep{Vera-Ciro_et_al._2011}.
 
@@
 particle distance 
-$d_k^2=x_k^2+y_k^2+z_k^2$,
+$d_k^2=x_k^2+y_k^2+z_k^2$.
 
@@
 holds for individual halos. 
-We compute $\Delta_T\equiv T_{MHD}-T_{DMO}$ the difference between the
+We compute $\Delta T\equiv T_{\rm MHD}-T_{\rm DMO}$ the difference between the
 triaxility in the MHD and the DMO simulation for each individual halo. 

### 2019-07-15 Document/paper.tex
new plot on the cumulative alignment

@@
 $^{2}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg
-Germany.\\
+paperGermany.\\
 }
@@
 
-%\begin{figure*}
-%\centering
-%{\includegraphics[width=0.6\textwidth]{./pics/MHD_Vs_DM/halo16_new.png}}
-%\caption{Radial profile for the axial ratios $b/a$, $c/a$, and the triaxiality parameter
-%  $T$ at redshift $z=0$.
-%  The continous/dashed lines correspond to the MHD/DM simulations respectively.
-%  The vertical line corresponds to the virial radius.}
-%\label{fig:triaxial_radius}
-%\end{figure*}
-
 \begin{figure}
@@
 \end{figure}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=1.0\textwidth]{cumulative_alignment_DM.pdf}
+\includegraphics[width=1.0\textwidth]{cumulative_alignment_MHD.pdf}
+\end{center}
+\caption{Cumulative alignment}
+\label{fig:cumulative_alignment}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+  \subfloat[DM shape at small radius]{\includegraphics[width=0.4\textwidth]{Z_Triax_level3_set_A_DM.pdf}} 
+  \subfloat[DM shape at large radius]{\includegraphics[width=0.4\textwidth]{Z_Triax_level3_set_A_MHD.pdf}} 
+\end{center}
+\caption{}
+\label{fig:triaxial_history}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+  \subfloat[DM shape at small radius]{\includegraphics[width=0.4\textwidth]{Z_Triax_level3_set_B_DM.pdf}} 
+  \subfloat[DM shape at large radius]{\includegraphics[width=0.4\textwidth]{Z_Triax_level3_set_B_MHD.pdf}} 
+\end{center}
+\caption{}
+\label{fig:triaxial_history}
+\end{figure*}
 
@@
 This method yields results in good agreement to the isodensity
-contours for radii smaller than half the virial radius as explored by
+contours in the inner halo region, roughly for radii smaller than one
+quarter the virial radius as explored by
 \citep{Vera-Ciro_et_al._2011}.
@@
 
-\begin{figure*}
-  \includegraphics[width=\columnwidth]{./pics/Redshift/halo_27_DM_Z_correlation.png}
-  \includegraphics[width=\columnwidth]{./pics/Redshift/halo_24_level3_MHD_Z_Triax.png}
-  \caption{Radial profile at $z=0$ (dashed line) and 
-    the historical profile at the virial radius (colour line). 
-    Results for DM simulations on the left, for MHD on the right.{\bf
-      Update with halo 24}}
-  \label{fig:redshift_triaxial}
-\end{figure*}
+In the previous section we stablished that DMO halos at $z=0$ have
+a steady and monotenouse trend towards decreasing triaxility with
+increasing radius.
+\cite{Vera-Ciro_et_al._2011} found that this  radial trend at $z=0$ 
+correlates with the halo shape as a function of cosmic time, i.e.
+the halo becomes less triaxial as cosmic time progresses. 
+This correlation was interpreted as each radial shell retaining memory
+of the accreting conditions at the virial radius at the time of
+collapse.
 
-\begin{figure*}
-  \subfloat[halo 16 DM]{\includegraphics[width=\columnwidth]{./pics/Redshift/halo_16_level3_DM_Z.png}}
-  \subfloat[halo 16 MHD]{\includegraphics[width=\columnwidth]{./pics/Redshift/halo_16_level3_MHD_Z.png}}
-  \caption{Radial profile (comoving) of axial ratios for halo 16 in
-    terms of redshift (color). This halo maintains its shape until
-    $z\approx 1$ obviating the systematic rounding effect in time from
-    asymmetric potentials. Each plot-line represents the radial
-    profile at a determined redshift. Conclussion: Mainly for b/a, it increases for:
-    (1) for bigger radii (fixed redshift)(2) for lower redshift (fixed
-    radius) It explains the correlation between radial profile and
-    history, but does not require that curves match in the triaxial
-    plane. {\bf En esta grafica el panel de abajo deberia ser la triaxialidad.}}
-  \label{fig:RedshiftGood}
-\end{figure*}
+Here we use the six \texttt{level3} halos to measure to what extent
+the presence of baryons affect this memory effect.
+The left column of Figure \ref{fig:redshift_triaxial} shows the six
+halos in the triaxility plane. 
+The colour dots show the time evolution while the black line
+corresponds to the radial trend at $z=0$.
+The close overlap of the spatial and temporal trends confirms the
+memory effect found by \cite{Vera-Ciro_et_al.2011}.
 
-We know that DM-only have a steady and monotonous
-trend towards larger sphericity with increasing radius. 
-This radial trend is mimicked when the shape is measured at the virial
-radius as a function of cosmic time.
-The halo should become rounder with decreasing redshift, this is
-expected by the continuous influence of the gravitational potential on
-a collisionless fluid \citep{Vera-Ciro_et_al._2011}.
+In the MHD sample the memory effect is less evident. 
+The right column of Figure \ref{fig:redshif_triaxial} shows the
+corresponding results for the six halos in the MHD sample.
 
-We show in the left panel of Figure \ref{fig:redshift_triaxial} an
-example with this effect in Halo 27 of the DM simulations:
-the radial triaxiality at $z=0$ and the historical triaxiality at
-$R_{\rm vir}$ are correlated. 
-The right panel on the same Figure \ref{fig:redshift_triaxial}
-illustrates how this correlation is absent in MHD simulations.
-
-This means that for DM-only halos one can approximate its shape at
-higher redshift by simply sampling its 
-current shape at a smaller radius. 
-This correlation seems to be prompted by the continous inside-out
-build-up of the dark matter halo; baryonic effects seem to jeopardize
-the apparent smoother growth in DM-only simulations.
-
-%Discuss if this correlation may be recovered if compared for example at Disk radius in stead of virial radius.\\
+%Discuss if this correlation may be recovered if compared for example
+%at Disk radius in stead of virial radius.\\
 

### 2019-07-16 Document/paper.tex
edit tables

@@
 \begin{center}
-  \subfloat[DM shape at small radius]{\includegraphics[width=0.4\textwidth]{Z_Triax_level3_set_A_DM.pdf}} 
-  \subfloat[DM shape at large radius]{\includegraphics[width=0.4\textwidth]{Z_Triax_level3_set_A_MHD.pdf}} 
+  \subfloat[DM shape at small radius]{\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_DM.pdf}} 
+  \subfloat[DM shape at large radius]{\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_MHD.pdf}} 
 \end{center}
 \caption{}
-\label{fig:triaxial_history}
+\label{fig:triaxial_history_A}
 \end{figure*}
@@
 \begin{center}
-  \subfloat[DM shape at small radius]{\includegraphics[width=0.4\textwidth]{Z_Triax_level3_set_B_DM.pdf}} 
-  \subfloat[DM shape at large radius]{\includegraphics[width=0.4\textwidth]{Z_Triax_level3_set_B_MHD.pdf}} 
+  \subfloat[DM shape at small radius]{\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_B_DM.pdf}} 
+  \subfloat[DM shape at large radius]{\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_B_MHD.pdf}} 
 \end{center}
 \caption{}
-\label{fig:triaxial_history}
+\label{fig:triaxial_history_B}
 \end{figure*}
 
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.8\textwidth]{correlation_T_MHD_disk.pdf}
+\end{center}
+\caption{A}
+\label{fig:disk_correlations}
+\end{figure*}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.45\textwidth]{triaxiality_observations.pdf}
+\end{center}
+\caption{A}
+\label{fig:observations}
+\end{figure}
+
 \section{Halo Shape Measurement}
-
-%\subsection{The solid ellipsoid method}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{cumulative_alignment.pdf}
-\caption{Cumulative distribution of alignment $\cos\theta$ between the
-  minor axis of the dark matter halo at different radii and the
-  stellar disk.} \label{fig:alignment_out}
-\end{figure}
-
 Following that linea reasoning, one would also expect that the rounding
@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=0.9\textwidth]{delta_T_correlations.pdf}
-\caption{Changes in the triaxiality at $R_{\rm vir}/8$ as a function of different halo and disk properties.}
-\label{fig:sphericity}
-\end{figure*}
-
-\textbf{Actually we have not examined the relation of c/a in MHD halos
-  with some measure of c/a from the disk, that is something like
-  Zdisk/Rdisk. This actually would make more sense from a physical
-  point of view: effect of the potential. }
-
 \textit{ Talk about source of triaxiality at the inner parts of the
@@
 %\end{figure}
-
-\subsection{Comparison against observational constraints}
-
-\begin{table*}
-\begin{tabular}{|l|cc|c|c|p{7cm}|}\hline
-Reference&$q_{\rho}$&$s_{\rho}$&$R$&$\theta$&
-Methodology\\ 
-\hline \hline \citet{Olling_and_Merrifield_2000}& $1.00$
-& $0.80$ &  $\simeq 8$kpc & $0^{\circ}$&Stellar dynamics and HI
-density. \\
-
-\multirow{2}{*}{\citet{Banerjee_and_Chanda_2011}}&${1}$&${1}$&$9$kpc&$0^{\circ}$&Method:
-HI
-gas. \\ &${0.5}$&${0.5}$&$24$kpc&$0^{\circ}$&Monotonical
-change between radial regimes.\\
-
-\citet{Loebman_et_al._2012}&${1.00}$&${0.47}$&$\sim
-20$kpc &$0^{\circ}$&Method: SDSS statistics\\
-
-\cite{Johnston_et_al._2005}&${1}$&$0.83-0.92$&$\lesssim
-60$kpc&$0^{\circ}$&Method: Sagittarius stream\\
-
-\citet{Bovy_et_el._2016}&${0.95}$&${0.95}$&$\lesssim
-20$kpc&$90^{\circ}$ & Stellar streams\\
-
-\citet{Deg_and_Widrow_2013}&$0.72$&$0.28$&
-$20$kpc-$60$kpc$ $&$90^{\circ}$&
-Mid-axis orientation. Sagittarius stream\\\hline\hline
-
-\citet{Abadi_et_al._2010} &${0.98}$&${0.85}$& & & Simulations. Almost
-  independent of radius. No feedback: boundary case\\\hline
-
-\end{tabular}
-\caption{{\bf Cuales son las incertidumbres? Con respecto a que eje
-    esta medido theta?}}
-\end{table*}
-
-\begin{table*}
-\begin{tabular}{|l|cc|c|c|p{7cm}|}\hline
-Reference&$q_{\phi}$&$s_{\phi}$&$R$&$\theta$&
-Methodology\\ \hline \hline
-
-\citet{Bowden_et_al._2016}& 0.5-0.66 &0.5-0.66& 5kpc - 10 kpc& $90^{\circ}$&
-Weak constraint on prolate halo. SDSS stars dynamics.\\
-
-\multirow{2}{*}{\citet{Vera-Ciro_and_Helmi_2013}}&${1.00}$&${0.90}$&$\lesssim
-10$kpc&$0^{\circ}$ & Sagittarius stream \& LMC \\
-&${0.90}$&${0.80}$&$\gtrsim 10$kpc&$90^{\circ}$&
-Mid-axis orientation on the outside. \\
-
-\citet{Law_and_Majewski_2009}&${0.83}$&${0.67}$&
-$\lesssim 60$kpc&$90^{\circ}$&Mid-axis orientation. Sagittarius
-stream\\
-
-\citet{Law_and_Majewski_2010}&${0.99}$&${0.72}$&
-$20$kpc-$60$kpc$$&$90^{\circ}$&Mid-axis orientation, Sagittarius
-stream\\
-
-\citet{Deg_and_Widrow_2013} & $0.82$&$0.40$&
-$20$kpc $60$kpc$ $&$90^{\circ}$&
-Mid-axis orientation. Sagittarius stream\\\hline \hline
-
-\citet{Chua_et_al._2018}&${0.88\pm0.10}$&${0.70\pm0.11}$&$0.15R_{200}$&
-& Illustris\\
-
-\citet{Bryan_et_al._2013}&$0.84-0.86$&$0.66-0.70$&$R_{200}$& & 
-For different cosmologies and feedback recipies. Calculated from a fit
-at $M_\odot=10^12$\\\hline
-
-\end{tabular}
-\caption{{\bf Cuales son las incertidumbres? Con respecto a que eje
-    esta medido theta?}}
-\end{table*}
-%\end{multicols}
 

### 2019-07-17 Document/paper.tex
caption figure 1

@@
   \centering
-  \subfloat[DM shape at small radius]{\includegraphics[width=0.5\textwidth]{level4_DM_halo_24_2.png}} 
+  \subfloat[DMO simulation. Shape at small radius.]{\includegraphics[width=0.5\textwidth]{level4_DM_halo_24_2.png}} 
   \hfill
-  \subfloat[DM shape at large radius]{\includegraphics[width=0.5\textwidth]{level4_DM_halo_24_4.png}} 
+  \subfloat[DMO simulation. Shape at large radius.]{\includegraphics[width=0.5\textwidth]{level4_DM_halo_24_4.png}} 
   \hfill
 
-  \subfloat[MHD shape at small radius]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_2.png}} 
+  \subfloat[MHD simulation. Shape at small radius.]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_2.png}} 
   \hfill
-  \subfloat[MHD shape at large radius]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_4.png}} 
+  \subfloat[MHD simulation. Shape at large radius.]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_4.png}} 
   \hfill 
-  \caption{DM density in a slice with width one tenth of the virial radius.
-  The black ellipses show the result of the fitting procedure. 
-  Upper panels correspond to DM only simulations, lower panels to MHD simulations.
+  \caption{DM density in logarithmic scale within a slice of one tenth
+    of the virial radius in width. 
+    The cut is perpendicular to the short axis of the inertia tensor ellipsoid.
+    The black ellipses show the results of the fitting procedure. 
+    Upper panels correspond to DMO simulations, lower panels to MHD
+    simulations.
+    All cases correspond to \texttt{Level4} resolution.
     Left panels show data at small radii, while right panels at large
     radii.    
-  The cut is made along the minor axis of the halo shape.}
+    This halo showcases the most noticeable effect in all halos
+    across the Auriga simulations: DM halos are rounder at all radii
+    after baryonic physics is included.}
 \label{fig:slices}

### 2019-07-17 Document/paper.tex
caption paper 2

@@
 18A-10, Edificio Ip, Bogot\'a, Colombia.\\
-$^{2}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg
-paperGermany.\\
+$^{2}$Heidelberg Institute for Theoretical Studies,
+Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany.\\
 }
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_DM.pdf}
- \includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_MHD.pdf}
+\subfloat[DMO simulations.]{\includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_DM.pdf}}
+\subfloat[MHD simulations.]{\includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_MHD.pdf}}
 \end{center}
-\caption{Axial ratios for the 30 halos in the Level 3 DM simulations
-  on the left and MHD simulations on the right.
-   Each dot represents the shape characterization of each halo 
-   Red circles represent measurements at the virial radius and the
-   blue squares are measurements at 1/8 of the virial radius.   
-   The crosses represent the mean values and standard deviation of
-   each sample.
-   Overall we can see three things. 
-   First, in DM only simulations halos are rounder in the outskirts
+\caption{Axial ratios for all halos in the simulation.
+  Left/right panels correspond to DMO/MHD simulations, respectively.
+  Triangles (squares) represent the measurements at $R_{200}/16$
+  ($R_{200}$) which correspond to physical distances of $14\pm 1$ kpc
+  ($230\pm 15$ kpc) respectively.
+  Here we can visualize three main trends for the whole halo population.
+  First, in DMO simulations halos are rounder in the outskirts
   than in the inner part.
-   Second, halos in MHD are rounder than its DM only counterparts.
-   Third, halos in MHD simulations are slightly rounder in the inner
-   part compared to the outskirts.}
+  Second, halos in MHD are rounder than its DMO counterparts.
+  Third, halos in MHD are less triaxial in the inner regions than in
+  the outskirts}
   \label{fig:triaxiality_plane}
@@
 \begin{figure*}
-\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_DM.pdf}
-\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_MHD.pdf}
-\caption{Cumulative fraction of the triaxiality for all 30 halos in
-  Level 4 simulations. Right/left panel correspond to DM/MHD
+\subfloat[DMO simulations.]{\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_DM.pdf}}
+\subfloat[MHD simulations.]{\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_MHD.pdf}}
+\caption{Cumulative fraction for the triaxiality at five different radii.
+  Right/left panel correspond to DM/MHD
   simulations respectively. 

### 2019-07-17 Document/paper.tex
caption figure 3

@@
 \subfloat[MHD simulations.]{\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_MHD.pdf}}
-\caption{Cumulative fraction for the triaxiality at five different radii.
-  Right/left panel correspond to DM/MHD
-  simulations respectively. 
-  This quantifies the main trends we find: in DM only simulations
-  rounder in the outskirts, halos in MHD are rounder than DM only, and
-  in MHD simulations halos tend to be rounder at the inner regions
-  than its outskirts.}
+\caption{Cumulative distribution for the triaxiality at five different radii.
+  Right/left panel correspond to DMO/MHD simulations, respectively. 
+  In DMO simulations the median triaxiality at all radii is larger
+  than $0.5$; only for $20\%$ the triaxility is smaller than $0.5$.
+  Furthermore, the triaxility increases as one moves towards the inner
+  part of the halo.
+  In MHD simulations the situation is reversed.
+  The median triaxility at all radii is smaller than $0.5$.
+  Moving towards the stellar disk the triaxility decreases towards a median
+  value of $T=0.15$.}
 \label{fig:triaxial_cumulative}

### 2019-07-17 Document/paper.tex
caption 5

@@
   Third, halos in MHD are less triaxial in the inner regions than in
-  the outskirts}
+  the outskirts.}
   \label{fig:triaxiality_plane}
@@
 \includegraphics[width=0.9\columnwidth]{delta_triaxiality_distro.pdf}
-\caption{Cumulative fraction of the changes in the triaxility betwen
-  MHD and DM simulations at different radii. 
-  At all radii at least $80\%$ of the halos became rounder in the MHD
+\caption{
+  Cumulative distribution for the change in triaxility $\Delta T=T_{\rm
+    MHD}-T_{\rm DMO}$ for the same radii used in Figure
+  \ref{fig:triaxial_cumulative}. 
+  At the virial radius all the halos become less triaxial in the MHD
   simulations. 
-  However, the effect is more pronounced at smaller radii.}
+  The change in triaxility becomes stronger in the inner regions of
+  the dark matter halo.}
 \label{fig:delta_triaxial_cumulative}
@@
 \end{center}
-\caption{Cumulative alignment}
+\caption{Cumulative distribution for the alignments between the
+  principal axis of the halo shape and the principal axis of the
+  stellar disk in the MHD simulations for radii $\leq 0.5R_{200}$.
+  Each panel compares the alingment of the corresponding
+  major/middle/minor axis both in the halo and the stellar disk.
+  In the upper row the haloes come from the DMO simulation, 
+  here the central message is that the shells are aligned to each
+  other at every radii.
+  In the lower row the haloes come from the MHD simulation and is a
+  self-consistent comparison with the disks. 
+  In this case the dark matter shells twist and  the degree of the
+  halo-disk alignment changes with distance.
+  The worst halo-disk alignment happens closer to the disk ($14\pm1$ kpc).
+  Interestingly an almost perfect halo-disk alignment happens at an intermediate
+  radius of $0.25R_{200}$ ($56\pm 4$kpc); while at a larger
+  distance $0.5R_{200}$ the two start to missalign.
+}
 \label{fig:cumulative_alignment}

### 2019-07-17 Document/paper.tex
caption 6 and 7

@@
 \begin{center}
-  \subfloat[DM shape at small radius]{\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_DM.pdf}} 
-  \subfloat[DM shape at large radius]{\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_MHD.pdf}} 
+\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_DM.pdf}
+\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_MHD.pdf}
 \end{center}
-\caption{}
+\caption{Axial ratios as a function of time (colour circles) and
+  radius (dashed lines). 
+  The left/right columns correspond to DMO/MHD simulations, respectively. 
+  The colour indicates the redshift at which the shape was measured
+  (always at $R_{200}$ at that time.)
+  The radial shapes goes from $R_{200}$ down to $\sim 1$ kpc.
+  These three halos correspond to a first half the sample for the \texttt{Level3}
+  haloes. 
+}
 \label{fig:triaxial_history_A}
@@
 \begin{center}
-  \subfloat[DM shape at small radius]{\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_B_DM.pdf}} 
-  \subfloat[DM shape at large radius]{\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_B_MHD.pdf}} 
+\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_B_DM.pdf}
+\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_B_MHD.pdf}
 \end{center}
-\caption{}
+\caption{Same as Figure \ref{fig:triaxial_history_A}.
+  These three halos correspond the second half of the sample for the
+  \texttt{Level3} haloes. 
+}
 \label{fig:triaxial_history_B}

### 2019-07-17 Document/paper.tex
edit

@@
 \end{center}
-\caption{A}
+\caption{Correlations between the halo triaxility at different radii
+  and disk properties. 
+In all cases there is a label showing the value of the Spearman's rank
+correlation coefficient.}
 \label{fig:disk_correlations}
@@
 approximated isopotential axial ratios is not bigger than $quantity
-percent$ {\bf }.
-
-{\bf Aqui hace falta una grafica comparando explicitamente los
-  valores para q y para s, esto para diferentes radios.
-  Otro punto importante es que se tiene q, pero como se
-  relaciona s?
-  Ademas hay que calcularlos para los radius aproximados que se
-  presentan en las tablas observacionales y en las de simulaciones.
-  10-20kpc se acerca a 1/8Rvir, 20-25 1/4Rvir, 60kpc aproximadamente 1/2Rvir
-}
+percent$.
 

### 2019-07-17 Document/paper.tex
caption

@@
   and disk properties. 
-In all cases there is a label showing the value of the Spearman's rank
-correlation coefficient.}
+  The label with the $\rho$ value corresponds to the Spearman's rank
+  correlation coefficient.
+  The x-axis in the first column is the gas density at the center of
+  the galaxy with in a sphere of radius  $1$ kpc \citep{Pakmor17};
+  the second column shows the disk to total mass ratio and the last
+  column includes the disk optical radius defined to be the radius at which the
+  $B$-band surface brightness drops below 25 mag arcsec$^-2$ \citep{ariga}.
+}
 \label{fig:disk_correlations}

### 2019-07-17 Document/paper.tex
caption figure 8

--- 2019-07-17 Document/paper.tex
@@
 \caption{Correlations between the halo triaxility at different radii
-  and disk properties. 
-In all cases there is a label showing the value of the Spearman's rank
-correlation coefficient.}
+  and baryonic disk properties. 
+  The label with the $\rho$ value corresponds to the Spearman's rank
+  correlation coefficient.
+  The line is the best linear minimum squares fit.
+  The x-axis in the first column is the gas density at the center of
+  the galaxy with in a sphere of radius  $1$ kpc \citep{Pakmor17};
+  the second column shows the disk to total mass ratio and the last
+  column includes the disk optical radius defined to be the radius at which the
+  $B$-band surface brightness drops below 25 mag arcsec$^-2$
+  \citep{auriga}.
+  The largest correlations are found for the two smaller radii and
+  dilute as one approached $R_{200}$.
+  Large and massive stellar disks with a low gas content are
+  correlated with low dark matter triaxilities.
+}
 \label{fig:disk_correlations}

### 2019-07-17 Document/paper.tex
caption last figure

@@
   column includes the disk optical radius defined to be the radius at which the
-  $B$-band surface brightness drops below 25 mag arcsec$^-2$
-  \citep{auriga}.
+  $B$-band surface brightness drops below 25 mag arcsec$^-2$ \citep{auriga}.
   The largest correlations are found for the two smaller radii and
@@
   Large and massive stellar disks with a low gas content are
-  correlated with low dark matter triaxilities.
-}
+  correlated with low dark matter triaxilities.}
 \label{fig:disk_correlations}
@@
 \end{center}
-\caption{A}
+\caption{Comparison of our results against other simulations
+  by \citet{Chua19} (Illustris) and observational constraints for the 
+dark matter halo shape in the Milky Way by \citet{LM10} (LM10) and
+\citet{Bovy16} (BBFK16).   
+We report our results in the MHD simulations in such a way as to
+bracket the radii in the other estimates.
+We find that our results are broadly consistent with the Illustris
+simulations given the broad dispersion in both data sets.
+The consistency with the constraints by \citet{Bovy16} is marginal,
+only 1/5 of the halos in our sample seem to be consistent within the
+observational reults.
+The result by \citet{LM10} would place the Milky Way halo as an
+atypical object in the $\Lambda$ CDM context.} 
 \label{fig:observations}
@@
 
-%\begin{figure*}
-%  \centering
-%  \subfloat[Perfectly aligned Axes]{\includegraphics[width=0.6\columnwidth]{./pics/well_axes.png}}
-%  \hfill
-%  \subfloat[Somewhat aligned Axes]{\includegraphics[width=0.6\columnwidth]{./pics/rotating_axes.png}}
-%  \hfill
-%  \subfloat[Chaotic Axes]{\includegraphics[width=0.6\columnwidth]{./pics/chaotic_axes.png}}
-%  \hfill
-%  \caption{Star: Minor Axis
-%    Triangle: Medium Axis
-%    Square: Major Axis
-%    Color: Radii at which shape was sampled (show radii sampled)
-%    Contour color: If orientation is above or below in this projection
-%    Cross (black): Orientation of the stellar disk
-%    Conclusion: Axes (minor) are not (generally) aligned with the
-%    stellar disk nor are they usually aligned with each other from
-%    different radii. We show some cases that may happen.} 
-%  \label{fig:alignment}
-%\end{figure*}
-
-\textbf{Discussion about the distribution of alignments and their
-  evolution in time: Precesion or temporary instabilities?}
-
 \section{Discussion}

### 2019-07-17 Document/paper.tex
esquelto
edit

@@
   \centering
-  \subfloat[DMO simulation. Shape at small radius.]{\includegraphics[width=0.5\textwidth]{level4_DM_halo_24_2.png}} 
+  \subfloat[DMO simulation. Shape at small
+    radius.]{\includegraphics[width=0.5\textwidth]{level4_DM_halo_24_2.png}}  
   \hfill
-  \subfloat[DMO simulation. Shape at large radius.]{\includegraphics[width=0.5\textwidth]{level4_DM_halo_24_4.png}} 
+  \subfloat[DMO simulation. Shape at large
+    radius.]{\includegraphics[width=0.5\textwidth]{level4_DM_halo_24_4.png}}  
   \hfill
 
-  \subfloat[MHD simulation. Shape at small radius.]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_2.png}} 
+  \subfloat[MHD simulation. Shape at small
+    radius.]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_2.png}}  
   \hfill
-  \subfloat[MHD simulation. Shape at large radius.]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_4.png}} 
+  \subfloat[MHD simulation. Shape at large
+    radius.]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_4.png}}  
   \hfill 
@@
 \begin{center}
-\includegraphics[width=1.0\textwidth]{cumulative_alignment_DM.pdf}
-\includegraphics[width=1.0\textwidth]{cumulative_alignment_MHD.pdf}
-\end{center}
-\caption{Cumulative distribution for the alignments between the
-  principal axis of the halo shape and the principal axis of the
-  stellar disk in the MHD simulations for radii $\leq 0.5R_{200}$.
-  Each panel compares the alingment of the corresponding
-  major/middle/minor axis both in the halo and the stellar disk.
-  In the upper row the haloes come from the DMO simulation, 
-  here the central message is that the shells are aligned to each
-  other at every radii.
-  In the lower row the haloes come from the MHD simulation and is a
-  self-consistent comparison with the disks. 
-  In this case the dark matter shells twist and  the degree of the
-  halo-disk alignment changes with distance.
-  The worst halo-disk alignment happens closer to the disk ($14\pm1$ kpc).
-  Interestingly an almost perfect halo-disk alignment happens at an intermediate
-  radius of $0.25R_{200}$ ($56\pm 4$kpc); while at a larger
-  distance $0.5R_{200}$ the two start to missalign.
-}
-\label{fig:cumulative_alignment}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
 \includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_DM.pdf}
@@
 \label{fig:triaxial_history_B}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=1.0\textwidth]{cumulative_alignment_DM.pdf}
+\includegraphics[width=1.0\textwidth]{cumulative_alignment_MHD.pdf}
+\end{center}
+\caption{Cumulative distribution for the alignments between the
+  principal axis of the halo shape and the principal axis of the
+  stellar disk in the MHD simulations for radii $\leq 0.5R_{200}$.
+  Each panel compares the alingment of the corresponding
+  major/middle/minor axis both in the halo and the stellar disk.
+  In the upper row the haloes come from the DMO simulation, 
+  here the central message is that the shells are aligned to each
+  other at every radii.
+  In the lower row the haloes come from the MHD simulation and is a
+  self-consistent comparison with the disks. 
+  In this case the dark matter shells twist and  the degree of the
+  halo-disk alignment changes with distance.
+  The worst halo-disk alignment happens closer to the disk ($14\pm1$ kpc).
+  Interestingly an almost perfect halo-disk alignment happens at an intermediate
+  radius of $0.25R_{200}$ ($56\pm 4$kpc); while at a larger
+  distance $0.5R_{200}$ the two start to missalign.
+}
+\label{fig:cumulative_alignment}
 \end{figure*}
@@
 This method yields results in good agreement to the isodensity
-contours in the inner halo region, roughly for radii smaller than one
-quarter the virial radius as explored by
-\citep{Vera-Ciro_et_al._2011}.
+contours for radii $leq 140$ kpc as explored by
+\citep{VeraCiro11}.
 
-We measure the shape using the reduced inertia tensor \citep{Allgood_et_al._2006},
+In particular, we measure the shape using the reduced inertia tensor
+\citep{Allgood_et_al._2006},
 
@@
 less than $10^{-6}$.  
+After convergence we define a unique radius $R$ as the geometrical
+mean of the axial lenghts $R=(abc)^{1/3}$.
+We use this radial coordinate $R$ to parameterize the spatial changes
+in halo shape we report in the following sections.
+
 This is the same method used to estimate the halo shape in the DM-only
-Aquarius simulations \citep{Vera-Ciro_et_al._2011}.
+Aquarius simulations \citep{VeraCiro11}.
 
-Following the convergence critery by \cite{Vera-Crito_et_al.2011} we
+Following the convergence criterion by \cite{Vera-Crito_et_al.2011} we
 restrict the sampling of the ellipsoidal parameters to radii  between
 $\sim 2$kpc and $R_{200}$, where  $R_{200}$ correspond to the  radius
-enclosing a sphere with 200 times the average dark matter density of
-the Universe.  
+enclosing a sphere with 200 times the critical density of the Universe.
 On average, over the 30 halos in the \texttt{Level4} sample
-$R_{200}=200\pm 10$kpc. 
-For \texttt{Level3} halos we go down to distances $\sim 0.2$ kpc.
+$R_{200}=230\pm 15$kpc. 
+For \texttt{Level3} halos we go down to distances of $\sim 0.2$ kpc.
 
@@
 radius.
-The upper panels in Figure \ref{fig:slices} illustrates this effect.
+The upper panels in Figure \ref{fig:slices} illustrate this effect.
 The contours show a projected DM slice while the ellipsoid corresponds
@@
 two different radii $R_{200}/8 (\sim 20$kpc$)$ and $R_{200}$. 
-The outer part of the halo is systematically rounder tha its inner
+The outer part of the halo is systematically rounder than its inner
 region. 
@@
 These plots confirm the results already reported in the
-literature \citep{Vera-Ciro_et_al._2011}.
+literature \citep{VeraCiro11}.
 
@@
 
-Next we want to test to what extend the global effect of decreasing
+To quantify to what extend the global effect of decreasing
 triaxility in MHD simulations compared to the DMO sample 
@@
 In the previous section we stablished that DMO halos at $z=0$ have
-a steady and monotenouse trend towards decreasing triaxility with
+a steady and monotonous trend towards decreasing triaxility with
 increasing radius.
-\cite{Vera-Ciro_et_al._2011} found that this  radial trend at $z=0$ 
+\cite{VeraCiro11} found that this  radial trend at $z=0$ 
 correlates with the halo shape as a function of cosmic time, i.e.
 the halo becomes less triaxial as cosmic time progresses. 
-This correlation was interpreted as each radial shell retaining memory
-of the accreting conditions at the virial radius at the time of
-collapse.
+The hypotesis put forward by \cite{VeraCiro11} is that the correlation
+raises as each radial shell retains memory of the accreting conditions
+at the virial radius at the time of collapse.
 
@@
 the presence of baryons affect this memory effect.
+In Figures \ref{fig:triaxial_history_A} and
+\ref{fig:triaxial_history_B} we follow the shape evolution measured at
+$R_{200}$ since redshift $z=1$ to the present, these results are
+represened by the coloroured dots.
+We compare this temporal evolution against the radial evolution at
+$z=0$ represented by the dash black lines.
+
 The left column of Figure \ref{fig:redshift_triaxial} shows the six
@@
 corresponds to the radial trend at $z=0$.
-The close overlap of the spatial and temporal trends confirms the
-memory effect found by \cite{Vera-Ciro_et_al.2011}.
+The left/right columns correspond to the DMO/MHD simulations, respectively.
 
-In the MHD sample the memory effect is less evident. 
-The right column of Figure \ref{fig:redshif_triaxial} shows the
-corresponding results for the six halos in the MHD sample.
+We start by analyzing to what extent the memory effect is
+already present in the DMO sample. 
+The first feature that jumps out is that \texttt{Au-21} in the DMO
+simulation does not have a simple shape evolution history.
+By visual inspection we find that an extended merging substructure
+intereacted in the main halo showing up in the shape measurements,
+making it more difficult to interpret the memory hypothesis.
+For this reason we exclude this halo from the analysis.
 
-%Discuss if this correlation may be recovered if compared for example
-%at Disk radius in stead of virial radius.\\
+For the other five halos we find simpler temporal and spatial
+evolution histories. 
+Halo \texttt{Au-6} (Figure
+\ref{fig:triaxial_history_A}) shows a broad
+correlation between the two tracks; close to the cases of halos
+\texttt{Aq-4-C} and \texttt{Aq-4-D} in \cite{VeraCiro11}.
+The four other halos (\texttt{Au-16} in Figure
+\ref{fig:triaxial_history_A}; \texttt{Au-23}, \texttt{Au-24},
+\texttt{Au-27} in Figure \ref{fig:triaxial_history_B}) are four
+cases where the temporal evolution if followed very closely by the
+radial trends.
+We conclude that in the DMO sample 4 out of the 5 high resolution
+halos closely follow the memory hypothesis trends and the remaning
+halo shows a reasonable correlation.
+
+The situation in the MHD simulations is more diverse.
+As expected by the results in the previous section the broad location
+in the triaxility plane of the temporal and radial evolution in the
+MHD simulation is completeley different from its DMO counterpart. 
+In terms of the memory hypothesis we see two different trends.
+We have the case of Halos \texttt{Au-6} and \texttt{Au-16}
 
@@
 
-\section{Discussion}
-
-\subsection{What drives the rounding effect?}
+\subsection{Correlation with baryonic disk properties}
 
@@
 
-\section{Conclusions}
+\section{Discussion}
+
+{\bf Comparison with other detailed simulations.}
+
+{\bf Comparison with other statistical simulations.}
+
+{\bf Comparison against observations.}
+
+{\bf Implications for observational studies in our Galaxy}
+
+\section{Discussion and Conclusions}
+
+In this paper we measured the shape of thirty isolated Milky Way like 
+dark matter haloes simulated in the Auriga project using the zoom-in
+technique. 
+Six of these haloes are also simulated at higher resolution.
+The simulations
 

### 2019-07-17 Document/paper.tex
edit

@@
 {Dark matter halo shape in the Auriga simulations: radial
-  dependence, time evolution and correlation with baryon disk
-  properties}
+  dependence, time evolution and baryon disk alignment}
 \author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
@@
 
-\subsection{The effect of baryons at $z=0$}
+\subsection{Radial trends at $z=0$}
 
@@
 MHD simulation is completeley different from its DMO counterpart. 
-In terms of the memory hypothesis we see two different trends.
-We have the case of Halos \texttt{Au-6} and \texttt{Au-16}
+In terms of the correlations expected by the memory hypothesis we see
+two different trends.
+We have the case of Halos \texttt{Au-6}, \texttt{Au-16} and
+\texttt{Au-27} there is still a reasonable correlation between
+temporal and radial evolution. 
+However for halos \texttt{Au-23} and \texttt{Au-24} the radial trends
+go in directions that are not even covered by the temporal evolution.
 
-\subsection{DM halo - Stellar Disk Alignment}
+Taken at face value, these results show that it is not possible to
+generalize the memory hypotesis to dark matter halos in MHD
+simulations.
+This means that some halos present a amnesia to its formation history,
+more specifically there are cases where the radial shape profile at
+present time does not have any correlation to its evolutionary
+history.
+
+\subsection{Alignments with the stellar disk}
 
 A common assumption in observational models of the MW DM halo is that
-its minor axis is perfectly aligned with the disk axis.
-Although it is a reasonable assumption to guarantee the
-stability of the galactic disk in simplified models of isolated
-galaxies, this might not hold in an explicit cosmological context.
-
-To examine the validity of this assumption  we sampled the shape at 5
-different radii and plotted  directions in a cartesian coordinate
-system where the $z$-axis always corresponds to the minor axis
-measured at the virial radius.
+its minor axis is perfectly aligned with the stellar disk minor axis.
+Although it is a reasonable assumption to guarantee the stability of
+the galactic disk in simplified models of isolated galaxies, this
+might not hold in an explicit cosmological context. 
+To examine the degree of validity of this assumption we study in this
+section the alignment between the eigenvectors of the inertia tensor of
+stellar particles within $0.1R_{200}$ ($\approx 23\pm 2$ kpc) and the
+eigenvectors of the dark matter halo shape.
 

### 2019-07-17 Document/paper.tex
edit

@@
 eigenvectors of the dark matter halo shape.
+All the measurements are done at $z=0$.
+
+In Figure \ref{fig:cumulative_alignment} we summarize our main results
+regarding these alignments with the halo shape measured at five
+different radii.
+The upper row shows the alignment of the halos in the DMO simulations
+with the stellar disk in the MHD simulations.
+The main objective of this measurement is to calibrate the radial
+evolution of the DM halo shape. 
+We find that the DM shape remains constant with radius.
+
+The lower row shows
 

### 2019-07-17 Document/paper.tex
edit

@@
 \begin{center}
-\subfloat[DMO simulations.]{\includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_DM.pdf}}
-\subfloat[MHD simulations.]{\includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_MHD.pdf}}
+\subfloat[DMO simulations.]{\includegraphics[width=0.8\columnwidth]{Lvl_4_Triax_Plane_DM.pdf}}
+\subfloat[MHD simulations.]{\includegraphics[width=0.8\columnwidth]{Lvl_4_Triax_Plane_MHD.pdf}}
 \end{center}
@@
 \begin{figure*}
-\subfloat[DMO simulations.]{\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_DM.pdf}}
-\subfloat[MHD simulations.]{\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_MHD.pdf}}
+\subfloat[DMO simulations.]{\includegraphics[width=0.8\columnwidth]{triaxialiy_distro_DM.pdf}}
+\subfloat[MHD simulations.]{\includegraphics[width=0.8\columnwidth]{triaxialiy_distro_MHD.pdf}}
 \caption{Cumulative distribution for the triaxiality at five different radii.
@@
 section the alignment between the eigenvectors of the inertia tensor of
-stellar particles within $0.1R_{200}$ ($\approx 23\pm 2$ kpc) and the
+stellar particles within $0.1R_{200}$ ($\sim 23\pm 2$ kpc) and the
 eigenvectors of the dark matter halo shape.
@@
 
-The lower row shows
+The lower row in Figure \ref{fig:cumulative_alignment} shows the
+alignments with the halo in the MHD simulations. 
+This time the halo shape changes and twists at different radii.
+However around the radius of $0.25R_{200}$ there is an alignment
+almost perfect between the shapes of the stellar disk and the dark
+matter halo. 
+Above and below this radius there are halos with a lower degree of
+alignment.
+Across the three different alignments we measure we verify that the
+strongest one is indeed the one between the two minor axis.
 
-{\bf En este caso hace falta la figura con la distribuci\'on integrada de cos theta}.
-Figure \ref{fig:alignment} shows the cumulative distribution of
-$\cos\theta$, where $\theta$ is the angle betwen the DM halo minor
-axis and the stellar disk angular momentum.  
-Each line shows the results at different radii.
-We find that the majority of the disks are aligned with the minor axis
-of their DM halo within $\approx 30^{\circ}$. 
-Furthermore, if there is a good alignment measured at the virial
-radius, this alignment is well conserved at smaller radii.
-
-{\bf En este caso hace falta la figura de la evoluci\'on de cos theta
-  como funci\'on del redshift}
-However, there are some disks that show strong missalignments. 
-To better understand the missalignments we plot the evolution of
-$\cos\theta$ with time to find that the missalignment has been present
-for the last XXX Gyr.
-This trend is summarized in Figure \ref{fig:alignment_history}.
+Statistically the strongest missalignment is found with the halo shape
+at a radius of $R_{200}/16\sim (14\pm1)$ kpc. 
+At this radius the mean angle and its standard deviation between the
+two minor axis is $18 \pm 21$ degrees, with one extreme case
+(\texttt{Au-4}) where the angle is close to $78$ degrees. 
+In contrast at $0.25 R_{200}$ the angle between the two axis is
+$2\pm 3$ degrees without any extreme outlier.
 

### 2019-07-17 Document/paper.tex
edit

@@
 
-\subsection{Correlation with baryonic disk properties}
+\section{Discussion and Conclusions}
 
-From our characterization of radial shapes it is clear that
-MHD halos are rounder than DM halos every sampled radii. 
+In this paper we measured the shape of thirty isolated Milky Way like 
+dark matter haloes simulated in the Auriga project using the zoom-in
+technique. 
+We also used six of these haloes that were simulated at higher
+resolution. 
+The Auriga project simulated these halos with two different setups:
+dark matter only (DMO) simulation and full magnetohydrodynamics (MHD)
+includeing star formation and feedback.
+We used the shape measurement algorithm by \cite{Allgood06} on the
+dark matter halos of these two kinds of simulations.
+
+We find that MHD halos are rounder than DMO halos every sampled radii. 
+MHD halos tend towards more oblate shapes (T < 0.5)
+despite DM halos tendency towards more prolate shapes (T>0.5). 
 It is also noticeable that the rounding effect of baryons is stronger
-at the disk regime, where the DM halo is almost perfectly oblate. 
-Furthermore, MHD halos tend towards more oblate shapes (T < 0.5)
-despite DM halos tendency towards more prolate shapes (T>0.5). 
+at the disk regime, where the haloes are close to oblate.
+
 This rounding effect can be explained by gravitational effect of the
@@
 
-\section{Discussion and Conclusions}
-
-In this paper we measured the shape of thirty isolated Milky Way like 
-dark matter haloes simulated in the Auriga project using the zoom-in
-technique. 
-Six of these haloes are also simulated at higher resolution.
-The simulations
-
 \section*{Acknowledgements}

### 2019-07-17 Document/paper.tex
edit

@@
   column includes the disk optical radius defined to be the radius at which the
-  $B$-band surface brightness drops below 25 mag arcsec$^-2$ \citep{auriga}.
+  $B$-band surface brightness drops below 25 mag arcsec$^{-2}$ \citep{auriga}.
   The largest correlations are found for the two smaller radii and
@@
 
+\section{Discussion}
+
+The first effect that we put in evidence in this paper is the effect
+of baryons in producing rounder DM halos.
+This effect has been already reported in other simulations \citep{Debattista08, Bryan13,
+  Butsky16, Chua19, Artale19}.
+The strength of the change depends on the numerical resolution, the
+method to resolve the hydrodynamics and the models describing star
+formation and stellar feedback.
+The key concept behind these results is that the baryon distribution
+influences and correlates with the dark matter halo shape.
+
+In order to explore this idea in the Auriga simulations we looked for
+correlations with stellar disk properties. 
+Looking into the measurements already reported by \cite{auriga} and
+\cite{pakmor17} we find three baryonic quantities that have the
+strongest correlation with DM halo triaxiality: the central gas
+density in a sphere of radius $1$kpc, the disk to total mass ratio and
+the optical radius.
+
+Figure \ref{fig:disk_correlations} summarizes the correlations of
+these quantities with the triaxility at five diferent radii.
+We ues the Spearmen's rank correlation coefficient to quantify the
+correlation strength.
+
+\citep{Debatistta08} shape aligment with respects to the disk changes
+but saturates beyond the disk radius.
+
+{\bf Comparison with other detailed simulations.}
+
+{\bf Comparison with other statistical simulations.}
+
+{\bf Comparison against observations.}
+
+{\bf Implications for observational studies in our Galaxy}
+
+\section{Conclusions}
 \section{Discussion and Conclusions}
@@
 
-Following that linea reasoning, one would also expect that the rounding
-effect of baryons is related to some  galactic parameters such as its
-component masses and radii. 
-We look for these kind of correlations and to find that the strongest
-can be found for the stellar density.
-However, the correlation is relatively low ({\bf cuanto vale el
-  coeficiente de correlation}) most likely due to the different
-formation histories.
-In other words, the effect of the baryonic disk on the shape of the DM halo
-does not fully explain the deviation from oblateness of MHD halos at
-$r<10$kpc.
-
-{\bf Finalmente cuales son las cantidades disponibles en el disco?
-  cuales son las que muestran una mayor correlacion? Haria falta un
-  plot con todas las correlaciones y la mencion de alguna prueba de
-  machine learning del fit lineal para ver cuales son los parametros
-  mas importantes.}
-
-  We measured the sphericity of a halo shape defined as the distance 
-  from the point that characterizes the shape in the triaxiality plane
-  to the point $(q=1,s=1)$, which represents a perfect sphere. Taking this 
-  as our metric of interest, the sphericity question becomes a search for
-  important variables and tendencies that affect this quantity. For this case,
-  given the small sample of 30 halos, we chose to study this problem with different 
-  3 methods to account for the lacking statistical consistency. We analyzed the effect
-  of the Star disk Radius, Baryonic fraction, Gas density, BH density, Gas Radius and
-  Star density.\\
-
-  We started with a simple linear Lasso regression to force a classification of 
-  important variables. Then, we converted this problem in a binary classification problem
-  by partitioning the samples in two balanced groups according to the studied metric which was then fitted using Random forest.
-  Finally, we concluded this analysis with an MCMC sampling of the likelyhood of a linear model
-  with varying slope and intercept parameters.\\
-
-  The results of each method are presented below:
-
-\textit{ Talk about source of triaxiality at the inner parts of the
-  halos (bar?). This source of triaxiality at the inner parts explains
-  why the axial ratios are $\approx 0.95$ and not exactly $1$. We
-  should also discuss that the decrease in the axial ratios for bigger
-  radii may actually be bigger/steeper but it is dimmed by the
-  contribution of inner parts.}
-
-%\begin{figure}
-%  \includegraphics[width=\columnwidth]{./pics/Delta asphericity Vs Star Density.png}
-%  \caption{Difference in asphericities between MHD and DM shapes Vs
-%    Star Density of the simulation. Unsure about this graphic. Take
-%    delta asphericity as the strength of the rounding effect of
-%    baryons.}  
-%  \label{fig:Star_Density_effect}
-%\end{figure}
-
-Half of the observational constraints are computed in terms of
-isodensity contours, the other half in terms of isopotential contours.
-To compare our results against the second kind we must either
-translate the isodensity results or recompute in terms of isopotential
-regions.
-For this purpose, we run a simple iterative algorithm to find an
-approximation of the shape of the isopotential contour.
-
-First, we calculate the mean and standard deviation of the potential over a
-spherical shell of width equals to $10\%$ of the radius at which it is
-sampled. 
-Then, we calculate the inertia tensor of particles with potential
-within $1\sigma$ around the mean potential and calculate its triaxial
-characterization with the reduced inertia tensor. 
-We repeat the
-process of calculating the potential mean and standard deviation until
-convergence is achieved with tolerance of $10^{-4}$.
-
-In Figure \ref{fig:density_potential} we compare the two approaches to
-measure the axial rations and plot the analytic expectation for $q$, 
-$(1-q_{\phi})\approx \frac{1}{3}(1-q_{\rho})$
-\citep{Binney_and_Tremaine_2008}, taking the volume-enclosed axial
-ratios  as an approximation for the isodensity contour ratios
-$q_{\rho}$. 
-This plot is computed at four different radii.
-
-Although the analytic expression is meant to be used on the outer
-regions of logarithmic axisymmetric halos, it works well as a first
-approximation for nearly axisymmetric halos as those produced by our
-simulations 
-We find that the difference between the measured and the
-approximated isopotential axial ratios is not bigger than $quantity
-percent$.
-
-\section{Discussion}
-
-{\bf Comparison with other detailed simulations.}
-
-{\bf Comparison with other statistical simulations.}
-
-{\bf Comparison against observations.}
-
-{\bf Implications for observational studies in our Galaxy}
-
 \section*{Acknowledgements}

### 2019-07-17 Document/paper.tex
edit

@@
 influences and correlates with the dark matter halo shape. 
+The broad tendency is that massive stellar disks correlate with
+spherical dark matter distributions.
 
-In order to explore this idea in the Auriga simulations we looked for
-correlations with stellar disk properties. 
+In order to explore this idea in the Auriga simulations we quantify
+the  correlation between halo shape with baronyc disk properties. 
 Looking into the measurements already reported by \cite{auriga} and
-\cite{pakmor17} we find three baryonic quantities that have the
+\cite{Pakmor17} we find three baryonic quantities that have the
 strongest correlation with DM halo triaxiality: the central gas
@@
 these quantities with the triaxility at five diferent radii.
-We ues the Spearmen's rank correlation coefficient to quantify the
+We use the Spearmen's rank correlation coefficient to quantify the
 correlation strength.
+This confirms our expectations. The strongest correlations are found
+with the halo shape measured at radii smaller than $\sim 28$kpc, which
+is close to the upper limit of the disk optical radius among our
+simulation sample. 
+The trend is such that halos with large triaxiality correlate with
+high gas density and stellar disks with low mass and small size.
+In turn, massive and large stellar disks with in a low density gas
+environment correlate with low triaxiliaty.
+
+Using the six halos in the high resolution sample we find that the
+memory effect put foward by \cite{VeraCiro11}, that is the correlation
+between the historical and radial evolution of the shape, only holds
+for a fraction of the sample and is clearly broken for two halos in
+the sample.
+Given the small size of the sample we use to study this effect we
+cannot find any significant correlation with other disk properties in
+order to understand the shape amnesia. 
+This effect has not been studied in detail in other simulations. 
+We consider that understanding this effect is the first promising
+extension of our studies to better understand dark matter halo shape
+correlation with disk properties in Milky Way type galaxies.
+avenues to continue a deeper study on dark matter halo shape.
+
+The second promising extension of our results deals with the shape
+alignment as a function of radius.
+In concordance
 
@@
 \section{Conclusions}
-\section{Discussion and Conclusions}
 
@@
 
+The second part of our study on the historical shape finds that in the
+presence of baryons the memory effect found by \citep{VeraCiro11} does
+not hold for all halos in the high resolution sample.
+
 \section*{Acknowledgements}

### 2019-07-17 Document/paper.tex
edit

@@
 alignment as a function of radius.
-In concordance
-
-\citep{Debatistta08} shape aligment with respects to the disk changes
-but saturates beyond the disk radius.
-
-{\bf Comparison with other detailed simulations.}
-
-{\bf Comparison with other statistical simulations.}
+In concordance with previous results in DM only simulations we find
+that the shells of halo shape are well aligned at different radii.
+The surprising result we find is that in the presences of baryons
+these shells twist as a function of radius.
+\citep{Debattista08} found a similar effect, but only at radii smaller
+than the disk radius. At radii larger than the disk radius, they find,
+the dark matter shells stop twisting.
+The twisting effect is robust across our sample of 30 halos. 
+Also surprisingly at a radius of $0.25R_{200}\approx 56$ kpc the
+alignment between the stellar disk and the dark matter halo is almost
+perfect.
 

### 2019-07-17 Document/paper.tex
edit

@@
 
+The measurements we have done in the simulations can be compared
+against observational results.
+We use the observational constraints by \cite{LM10} and \cite{Bovy16}
+to place our results in an observational context.
+\cite{LM10} used observations of the long Sagittarius tidal stream to
+constrain the shape of the gravitational potential.
+Their point of depart is that previous studies that assumed an
+axisymetric Galactic potential were not able to fit all the available
+dynamic constraints for the Sagittarius stream, therefore they
+proposed a rigid triaxial potential, with coaxial potential
+ellipsoids, for the dark matter component.  
+Their results are able to constrain the triaxility of this potential
+component, translating these results into a triaxiality of the density
+contours they report $(c/a)=0.44$ and $(b/a)=0.97$ at a radius of
+$\sim 40$kpc. They do not report any uncertainties for these two
+values. 
+Looking at their plots of their quality of fit criterion as a function
+of dark halo axial scales (Figure 5), we choose a conservative $10\%$
+relative uncertainty, close to the uncertainty in those parameters.
+The element that made the results by \cite{LM10} (LM10 hereafter) surprising is that
+the minor axis of the halo shape is parallel, not perpendicular, to
+stellar disk plane.
+
+The results by \cite{Bovy16} (BBFK16 hereafter) have the same general approach but use
+instead the GD-1 \citep{2006ApJ...641L..37G} and Pal 5 \citep{2009AJ....137.3378O}
+streams to constraint the shape of the dark matter component of the
+galacic halo potential.
+They use general models with large degrees of freedom for the galactic
+potential in order to measure to what extent these two streams are sensitive
+to the triaxiality of the dark matter halo component.
+The DM component is written directly as a triaxial density profile
+with coaxial ellipsoids and the corresponding potential is found by
+numerical integration.
+They find that the width of the Pal 5 stream constraints $b/a\approx
+1$ and therefore fix it to $b/a=1$, finally they report their most stringent
+constrain of $c/a=0.93\pm0.16$ at a radius of $\approx 19$kpc from the
+Pal 5 stream.
+
+Our Figure \label{fig:observations} shows an explicit comparison in
+the $c/a$-$b/a$ plane of the results by LM10
+
 {\bf Comparison against observations.}

### 2019-07-17 Document/paper.tex
edit

@@
 constrain of $c/a=0.93\pm0.16$ at a radius of $\approx 19$kpc from the
-Pal 5 stream.
+galactic center.
 
 Our Figure \label{fig:observations} shows an explicit comparison in
-the $c/a$-$b/a$ plane of the results by LM10
+the $c/a$-$b/a$ plane against the results by LM10 and BBFK16. 
+We find $6$ halos with $b/a<0.93$ and $c/a>0.77$ that could be
+considered consistent with their shape constraints 
+by BBFK16.
+In contrast, none of the simulated halos is consistent with the LM10
+results.
+
+The results by LM10 would place then the dark matter halo of our Milky
+Way as an extreme outlier in the $\Lambda$ CDM model. 
+This extreme prolateness also correlateswith the extreme
+triaxiality of the 11 classical satellites of the MW ($c/a\approx
+0.2$, and $b/a\approx0.9$) with an spatial distribution 
+also oriented perpendicular to the MW plane, another highly unusual
+feature in the $\Lambda$ CDM model \citep{2018MNRAS.478.5533F}
 

### 2019-07-17 Document/paper.tex
edit

@@
 Way as an extreme outlier in the $\Lambda$ CDM model. 
-This extreme prolateness also correlateswith the extreme
+This extreme prolateness also correlates with the extreme
 triaxiality of the 11 classical satellites of the MW ($c/a\approx
@@
 
-{\bf Comparison against observations.}
-
-{\bf Implications for observational studies in our Galaxy}
+From the results presented in this work we advance the idea that the
+twisting shells in the density is a feature that deserves to be
+explored in the process of constraining shape parameters from tidal
+stream data. 
+The current parameterizations of coaxial density/potential shells
+might be too rigid.
+The inclusion of a new free parameter describing this degree of
+twisting might relax the conflict between the observational
+constraints and the numerical results.
 

### 2019-07-18 Document/paper.tex
new plots
remove level 3 results

@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_DM.pdf}
-\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_MHD.pdf}
-\end{center}
-\caption{Axial ratios as a function of time (colour circles) and
-  radius (dashed lines). 
-  The left/right columns correspond to DMO/MHD simulations, respectively. 
-  The colour indicates the redshift at which the shape was measured
-  (always at $R_{200}$ at that time.)
-  The radial shapes goes from $R_{200}$ down to $\sim 1$ kpc.
-  These three halos correspond to a first half the sample for the \texttt{Level3}
-  haloes. 
-}
-\label{fig:triaxial_history_A}
-\end{figure*}
+%\begin{figure*}
+%\begin{center}
+%\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_DM.pdf}
+%\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_MHD.pdf}
+%\end{center}
+%\caption{Axial ratios as a function of time (colour circles) and
+%  radius (dashed lines). 
+%  The left/right columns correspond to DMO/MHD simulations, respectively. 
+%  The colour indicates the redshift at which the shape was measured
+%  (always at $R_{200}$ at that time.)
+%  The radial shapes goes from $R_{200}$ down to $\sim 1$ kpc.
+%  These three halos correspond to a first half the sample for the \texttt{Level3}
+%  haloes. 
+%}
+%\label{fig:triaxial_history_A}
+%\end{figure*}
+
+%\begin{figure*}
+%\begin{center}
+%\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_B_DM.pdf}
+%\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_B_MHD.pdf}
+%\end{center}
+%\caption{Same as Figure \ref{fig:triaxial_history_A}.
+%  These three halos correspond the second half of the sample for the
+%  \texttt{Level3} haloes. 
+%}
+%\label{fig:triaxial_history_B}
+%\end{figure*}
 
@@
 \begin{center}
-\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_B_DM.pdf}
-\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_B_MHD.pdf}
+\includegraphics[width=1.0\textwidth]{angles_alignment_DM.pdf}
+\includegraphics[width=1.0\textwidth]{angles_alignment_MHD.pdf}
 \end{center}
-\caption{Same as Figure \ref{fig:triaxial_history_A}.
-  These three halos correspond the second half of the sample for the
-  \texttt{Level3} haloes. 
-}
-\label{fig:triaxial_history_B}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=1.0\textwidth]{cumulative_alignment_DM.pdf}
-\includegraphics[width=1.0\textwidth]{cumulative_alignment_MHD.pdf}
-\end{center}
-\caption{Cumulative distribution for the alignments between the
+\caption{Angles between the
   principal axis of the halo shape and the principal axis of the
-  stellar disk in the MHD simulations for radii $\leq 0.5R_{200}$.
-  Each panel compares the alingment of the corresponding
+  stellar disk in the MHD simulations at four different radii $\leq 0.5R_{200}$.
+  Thin lines correspond to each one of the thirty halos in our sample,
+  while the thick line traces the median value.
+  Each panel compares the alignment of the corresponding
   major/middle/minor axis both in the halo and the stellar disk.
   In the upper row the haloes come from the DMO simulation, 
-  here the central message is that the shells are aligned to each
-  other at every radii.
-  In the lower row the haloes come from the MHD simulation and is a
-  self-consistent comparison with the disks. 
-  In this case the dark matter shells twist and  the degree of the
-  halo-disk alignment changes with distance.
-  The worst halo-disk alignment happens closer to the disk ($14\pm1$ kpc).
-  Interestingly an almost perfect halo-disk alignment happens at an intermediate
-  radius of $0.25R_{200}$ ($56\pm 4$kpc); while at a larger
-  distance $0.5R_{200}$ the two start to missalign.
+  showing that the ellipsoids describing the
+  shape are constant as a function of radius for the most part of the
+  sample.
+  In the lower row the haloes come from the MHD simulation providing a 
+  self-consistent comparison with the stellar disks. 
+  In this case the dark matter shells twist in all the halos.
+  The degree of this twisting is different in each halo.
+  Interestingly, an almost perfect halo-disk alignment happens across
+  the sample at an intermediate radius of $0.25R_{200}$ ($56\pm 4$kpc).
 }
@@
 \label{fig:disk_correlations}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.9\textwidth]{correlations_angles_alignment_MHD.pdf}
+\end{center}
+\caption{Changse of angle alignment of the dark
+  matter halo and stellar disk at two different radii ($R_{200}/16$
+  and $0.25R_{200}$) as a function of the baryonic disk properties
+  already explored in Figure \ref{fig:disk_correlations}.  
+  Figure \ref{fig:cumulative_alignment} showed that maximum alignment
+  occurs at $0.25R_{200}$ while in the inner regions ($R_{200}/16$)
+  considerable missalignments occurr.
+ at different radii
+ and baryonic disk properties. 
+ The label with the $\rho$ value corresponds to the Spearman’s rank correlation coefficient. }
+\label{fig:alignment_correlations}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=1.0\textwidth]{correlations_angles_triaxiality_MHD.pdf}
+\end{center}
+\caption{Changse of angle alignment of the dark
+  matter halo and stellar disk at two different radii ($R_{200}/16$
+  and $0.25R_{200}$) as a function of the baryonic disk properties
+  already explored in Figure \ref{fig:disk_correlations}.  
+  Figure \ref{fig:cumulative_alignment} showed that maximum alignment
+  occurs at $0.25R_{200}$ while in the inner regions ($R_{200}/16$)
+  considerable missalignments occurr.
+ at different radii
+ and baryonic disk properties. 
+ The label with the $\rho$ value corresponds to the Spearman’s rank correlation coefficient. }
+\label{fig:alignment_correlations}
 \end{figure*}
@@
 
-\subsection{Shape evolution with cosmic time}
+%\subsection{Shape evolution with cosmic time}
 
-In the previous section we stablished that DMO halos at $z=0$ have
-a steady and monotonous trend towards decreasing triaxility with
-increasing radius.
-\cite{VeraCiro11} found that this  radial trend at $z=0$ 
-correlates with the halo shape as a function of cosmic time, i.e.
-the halo becomes less triaxial as cosmic time progresses. 
-The hypotesis put forward by \cite{VeraCiro11} is that the correlation
-raises as each radial shell retains memory of the accreting conditions
-at the virial radius at the time of collapse.
+%In the previous section we stablished that DMO halos at $z=0$ have
+%a steady and monotonous trend towards decreasing triaxility with
+%increasing radius.
+%\cite{VeraCiro11} found that this  radial trend at $z=0$ 
+%correlates with the halo shape as a function of cosmic time, i.e.
+%the halo becomes less triaxial as cosmic time progresses. 
+%The hypotesis put forward by \cite{VeraCiro11} is that the correlation
+%raises as each radial shell retains memory of the accreting conditions
+%at the virial radius at the time of collapse.
 
-Here we use the six \texttt{level3} halos to measure to what extent
-the presence of baryons affect this memory effect.
-In Figures \ref{fig:triaxial_history_A} and
-\ref{fig:triaxial_history_B} we follow the shape evolution measured at
-$R_{200}$ since redshift $z=1$ to the present, these results are
-represened by the coloroured dots.
-We compare this temporal evolution against the radial evolution at
-$z=0$ represented by the dash black lines.
+%Here we use the six \texttt{level3} halos to measure to what extent
+%the presence of baryons affect this memory effect.
+%In Figures \ref{fig:triaxial_history_A} and
+%\ref{fig:triaxial_history_B} we follow the shape evolution measured at
+%$R_{200}$ since redshift $z=1$ to the present, these results are
+%represened by the coloroured dots.
+%We compare this temporal evolution against the radial evolution at
+%$z=0$ represented by the dash black lines.
 
-The left column of Figure \ref{fig:redshift_triaxial} shows the six
-halos in the triaxility plane. 
-The colour dots show the time evolution while the black line
-corresponds to the radial trend at $z=0$.
-The left/right columns correspond to the DMO/MHD simulations, respectively.
+%The left column of Figure \ref{fig:redshift_triaxial} shows the six
+%halos in the triaxility plane. 
+%The colour dots show the time evolution while the black line
+%corresponds to the radial trend at $z=0$.
+%The left/right columns correspond to the DMO/MHD simulations, respectively.
 
-We start by analyzing to what extent the memory effect is
-already present in the DMO sample. 
-The first feature that jumps out is that \texttt{Au-21} in the DMO
-simulation does not have a simple shape evolution history.
-By visual inspection we find that an extended merging substructure
-intereacted in the main halo showing up in the shape measurements,
-making it more difficult to interpret the memory hypothesis.
-For this reason we exclude this halo from the analysis.
+%We start by analyzing to what extent the memory effect is
+%already present in the DMO sample. 
+%The first feature that jumps out is that \texttt{Au-21} in the DMO
+%simulation does not have a simple shape evolution history.
+%By visual inspection we find that an extended merging substructure
+%intereacted in the main halo showing up in the shape measurements,
+%making it more difficult to interpret the memory hypothesis.
+%For this reason we exclude this halo from the analysis.
 
-For the other five halos we find simpler temporal and spatial
-evolution histories. 
-Halo \texttt{Au-6} (Figure
-\ref{fig:triaxial_history_A}) shows a broad
-correlation between the two tracks; close to the cases of halos
-\texttt{Aq-4-C} and \texttt{Aq-4-D} in \cite{VeraCiro11}.
-The four other halos (\texttt{Au-16} in Figure
-\ref{fig:triaxial_history_A}; \texttt{Au-23}, \texttt{Au-24},
-\texttt{Au-27} in Figure \ref{fig:triaxial_history_B}) are four
-cases where the temporal evolution if followed very closely by the
-radial trends.
-We conclude that in the DMO sample 4 out of the 5 high resolution
-halos closely follow the memory hypothesis trends and the remaning
-halo shows a reasonable correlation.
+%For the other five halos we find simpler temporal and spatial
+%evolution histories. 
+%Halo \texttt{Au-6} (Figure
+%\ref{fig:triaxial_history_A}) shows a broad
+%correlation between the two tracks; close to the cases of halos
+%\texttt{Aq-4-C} and \texttt{Aq-4-D} in \cite{VeraCiro11}.
+%The four other halos (\texttt{Au-16} in Figure
+%\ref{fig:triaxial_history_A}; \texttt{Au-23}, \texttt{Au-24},
+%\texttt{Au-27} in Figure \ref{fig:triaxial_history_B}) are four
+%cases where the temporal evolution if followed very closely by the
+%radial trends.
+%We conclude that in the DMO sample 4 out of the 5 high resolution
+%halos closely follow the memory hypothesis trends and the remaning
+%halo shows a reasonable correlation.
 
-The situation in the MHD simulations is more diverse.
-As expected by the results in the previous section the broad location
-in the triaxility plane of the temporal and radial evolution in the
-MHD simulation is completeley different from its DMO counterpart. 
-In terms of the correlations expected by the memory hypothesis we see
-two different trends.
-We have the case of Halos \texttt{Au-6}, \texttt{Au-16} and
-\texttt{Au-27} there is still a reasonable correlation between
-temporal and radial evolution. 
-However for halos \texttt{Au-23} and \texttt{Au-24} the radial trends
-go in directions that are not even covered by the temporal evolution.
+%The situation in the MHD simulations is more diverse.
+%As expected by the results in the previous section the broad location
+%in the triaxility plane of the temporal and radial evolution in the
+%MHD simulation is completeley different from its DMO counterpart. 
+%In terms of the correlations expected by the memory hypothesis we see
+%two different trends.
+%We have the case of Halos \texttt{Au-6}, \texttt{Au-16} and
+%\texttt{Au-27} there is still a reasonable correlation between
+%temporal and radial evolution. 
+%However for halos \texttt{Au-23} and \texttt{Au-24} the radial trends
+%go in directions that are not even covered by the temporal evolution.
 
-Taken at face value, these results show that it is not possible to
-generalize the memory hypotesis to dark matter halos in MHD
-simulations.
-This means that some halos present a amnesia to its formation history,
-more specifically there are cases where the radial shape profile at
-present time does not have any correlation to its evolutionary
-history.
+%Taken at face value, these results show that it is not possible to
+%generalize the memory hypotesis to dark matter halos in MHD
+%simulations.
+%This means that some halos present a amnesia to its formation history,
+%more specifically there are cases where the radial shape profile at
+%present time does not have any correlation to its evolutionary
+%history.
 
@@
 
+{{\bf alinenaciones y twisting as a function of environment, 
+the difference between accretting and stalled halos, }
+
+%Porciani: stalled halos keep their dark matter density profile
+%while accreting halos have. Shells don't pile up in accreting halos, 
+%they approximately do in stalled halos}
+
+%Porciani: The stalled halos are the most similar to the MW at least in
+%terms of the velocity anisotropy parameter an should be embeded in a
+%thick filament of tha large scale structure.
+
+%IDEA PARA YEIMY: medir scatter en stellar to DM halo mass ratio as a
+%function of the anisotropy parameter or the persistence parameter in 
+%Illustris. Primer proxy para el galaxy formation bias. Esto se puede
+%sacar pronto. (ademas otra medida de los compacto que es la distribucion
+%estelar)
+%esto puede ser comparado con los datos de vipers que tiene un sesgo 
+%donde se ven diferentes clustering a misma masa para galaxias mas o
+%menos concentradas
+
+%otra idea: calcular la entropia del beta skeleton para distinguir 
+%el clustering de dos muestras diferentes. i.e. la entropia para
+%caracterizar assembly bias.
+
 \section{Conclusions}

### 2019-07-18 Document/paper.tex
new order
edit

@@
 
-\title[The shape of dark matter haloes in the Auriga simulations]
-{Dark matter halo shape in the Auriga simulations: radial
-  dependence, time evolution and baryon disk alignment}
+\title[The shape of dark matter haloes at $z=0$ in Auriga]
+{Dark matter halo shape at $z=0$ in the Auriga simulations: radial
+  evolution and baryon disk alignments}
 \author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
@@
 \begin{center}
+\includegraphics[width=1.0\textwidth]{correlations_angles_triaxiality_MHD.pdf}
+\end{center}
+\caption{Changse of angle alignment of the dark
+  matter halo and stellar disk at two different radii ($R_{200}/16$
+  and $0.25R_{200}$) as a function of the baryonic disk properties
+  already explored in Figure \ref{fig:disk_correlations}.  
+  Figure \ref{fig:cumulative_alignment} showed that maximum alignment
+  occurs at $0.25R_{200}$ while in the inner regions ($R_{200}/16$)
+  considerable missalignments occurr.
+ at different radii
+ and baryonic disk properties. 
+ The label with the $\rho$ value corresponds to the Spearman’s rank correlation coefficient. }
+\label{fig:alignment_correlations}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
 \includegraphics[width=0.8\textwidth]{correlation_T_MHD_disk.pdf}
@@
 \includegraphics[width=0.9\textwidth]{correlations_angles_alignment_MHD.pdf}
-\end{center}
-\caption{Changse of angle alignment of the dark
-  matter halo and stellar disk at two different radii ($R_{200}/16$
-  and $0.25R_{200}$) as a function of the baryonic disk properties
-  already explored in Figure \ref{fig:disk_correlations}.  
-  Figure \ref{fig:cumulative_alignment} showed that maximum alignment
-  occurs at $0.25R_{200}$ while in the inner regions ($R_{200}/16$)
-  considerable missalignments occurr.
- at different radii
- and baryonic disk properties. 
- The label with the $\rho$ value corresponds to the Spearman’s rank correlation coefficient. }
-\label{fig:alignment_correlations}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=1.0\textwidth]{correlations_angles_triaxiality_MHD.pdf}
 \end{center}

### 2019-07-18 Document/paper.tex
edit

@@
 {Dark matter halo shape at $z=0$ in the Auriga simulations: radial
-  evolution and baryon disk alignments}
+  evolution and alignments with the stellar disk}
 \author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{

### 2019-07-18 Document/paper.tex
abstract

@@
 \begin{abstract}
-We present shape measurements of dark matter halos in a suit
-of 30 cosmological simulations from the Auriga project.
+We present shape measurements of dark matter halos at redshift $z=0$
+in a suite of 30 cosmological simulations from the Auriga project.
 For all measurements we compare the results in full
 magnetohydrodynamics against dark matter only physics.
-We find a strong influence of baryons in making dark matter halos rounder at all
-radii compared to its dark matter only counterparts.
+We find a strong influence of baryons in making dark matter halos
+rounder at all radii compared to its dark matter only counterparts.
 This change in triaxility its more pronounced towards the inner
 regions of the halo.
-At distances close to the disk rounder dark matter distributions
-correlate with massive stellar disks and low gas density.
-The dark matter shape shows a strong alignment with the
-stellar disk shape as a function of radius, the stronger aligmnet is
-found at $~50$kpc, this alignment weakens at smaller and larger radii. 
-In dark matter only simulations the time evolution of the shape
-measured at the virial radius correlates with the radial shape
-evolution at present day.  
-However, this correlation is lost once the baryonic effects are
-included. 
-We conclude that in our simulation suite that baryonic physics
-produces rounder halos with a strong correlation between its inner
-shape and the stellar and gaseous properties of the disk.
+In simulations with baryons we measure a twist in the dark matter
+shape as a function of radial distance.
+We present this effect as a changing degree of halo shape alignment
+with the stellar disk shape as a function of radius; the stronger
+alignment is found at $0.25R_{200}\sim56$ kpc. 
+This twisting in halo shape is almost absent from dark matter only
+simulations. 
+We show that a coherent halo shape with radius correlates with low
+triaxility values.  
+At distances close to the disk, rounder and coherent dark matter
+distributions correlate with massive stellar disks and low gas density. 
+In a comparison against observational constraints of dark matter halo
+triaxiality for the Milky Way we find that $20\%$ of the galaxies in
+our sample are consitent with observational results that favor
+$b/a\approx 1$ and $c/a>0.77$ but are at odds with other results that
+favor $c/a\approx0.44$. 
 \end{abstract}

### 2019-07-18 Document/paper.tex
new plot

@@
 {Dark matter halo shape at $z=0$ in the Auriga simulations: radial
-  evolution and alignments with the stellar disk}
+  evolution and alignment with the stellar disk}
 \author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2018}
+\pubyear{2019}
 
@@
 in a suite of 30 cosmological simulations from the Auriga project. 
-For all measurements we compare the results in full
-magnetohydrodynamics against dark matter only physics.
+We compare the results in full magnetohydrodynamics against dark
+matter only physics. 
 We find a strong influence of baryons in making dark matter halos
 rounder at all radii compared to its dark matter only counterparts.
-This change in triaxility its more pronounced towards the inner
+This change in triaxility is more pronounced towards the inner
 regions of the halo.
 In simulations with baryons we measure a twist in the dark matter
-shape as a function of radial distance.
-We present this effect as a changing degree of halo shape alignment
-with the stellar disk shape as a function of radius; the stronger
-alignment is found at $0.25R_{200}\sim56$ kpc. 
-This twisting in halo shape is almost absent from dark matter only
-simulations. 
-We show that a coherent halo shape with radius correlates with low
-triaxility values.  
-At distances close to the disk, rounder and coherent dark matter
-distributions correlate with massive stellar disks and low gas density. 
+shape as a function of radial distance; this effect is almost absent
+in dark matter only simulations.
+We quantify this twisting effect as a changing degree of alignment
+bewteen the halo shape with the stellar disk shape as a function of radius.
+An almost perfect alignment between the two components appears at
+$0.25R_{200}\sim56$ kpc.  
+We show that the twist in the radial shape evolution correlates
+positively with triaxility.
+Furthermore, at distances $\lesssim 30$ kpc, rounder and coherent dark
+matter distributions correlate with extended massive stellar disks and
+low gas densities. 
 In a comparison against observational constraints of dark matter halo
-triaxiality for the Milky Way we find that $20\%$ of the galaxies in
-our sample are consitent with observational results that favor
-$b/a\approx 1$ and $c/a>0.77$ but are at odds with other results that
-favor $c/a\approx0.44$. 
+triaxiality for the Milky Way we find that $20\%$ of halos our sample
+are consistent with observational results derived from the Pal 5 stream
+that favor $b/a\approx 1$ and $c/a>0.77$. Including baryons is a
+required element to achieve this level of agreement.
+In contrast, all simulations (dark matter only and with baryons) are at
+odds with the constrains derived from the Saggitarius stream that
+favor $b/a\approx 0.97$ and $c/a\approx0.44$.
 \end{abstract}

### 2019-07-18 Document/paper.tex
edit

@@
 
+\citep{Dubinski91}
+
 Observationally some studies prefer oblate (i.e. a=b>c) configurations at small
@@
 
+Rounding effect of baryons
+\citep{Dubinski94}
+
 The caveat of the studies mentioned above is that they do not
@@
 the round effect.
+
+Abadi2010 -> well aligned countours.
+
 Recently \cite{2018arXiv180907255C} made a study in a cosmological
@@
 on galaxies similar to the MW.
+
+\citep{JingSuto02} report the twisting in their simulations.
+They also find a universal radius where the alignment of the internal 
+region (defined as the region with 2500 times the critical density) 
+is perfect with the shell under consideration.
+They blame it on high c/b and undecided vectors.
+but in our case c/b increases monotonically with radius, and the
+alignment with the disk is not monotonous. In our case this cannot be
+the only explanation as the triaxiliaty correlation with the twist 
+strongly depends on the radius.
+
+\citep{Pedrosa10}
 
@@
 \begin{center}
-\includegraphics[width=1.0\textwidth]{correlations_angles_triaxiality_MHD.pdf}
+\includegraphics[width=1.0\textwidth]{correlations_twisting_triaxiality_MHD.pdf}
 \end{center}

### 2019-07-18 Document/paper.tex
documento

@@
 
-A robust prediction of the Cold Dark Matter (CDM) paradigm is that DM
-halos are ellipsoidal and can be characterized by the principal axes
-$a>b>c$.
+Accurate observations and modeling of our Galaxy can also
+shape our understainding of the Universe as a whole.  
+Explaining its current composition and kinematical state is 
+equivalent to figuring out its formation process in a cosmological
+context. 
+As a first approximation, the Milky Way's (MW) morphology and
+separation into global kinematically coherent components, such as its
+disk and bulge, can be used to support the  existence of a Dark Matter
+(DM) component to explain its dynamics. 
+In this context the most detailed observations and modelling has been
+devoted to the region around the solar neighborhood
+\citep{2000MNRAS.311..361O,2009PASJ...61..227S,2010JCAP...08..004C,2013ApJ...779..115B,Iocco15}.
+
+Improvements in the sensitivity of astronomical observations have 
+extended this kind of modelling to outter regions by measuring
+the stellar streams resulting from infalling globular clusters or
+satellite galaxies that got tidaly disrutpted by the gravitational
+potential of the Milky Way
+\citep{1998ApJ...495..297J,1999MNRAS.307..495H, 1999MNRAS.307..877T}. 
+The interpretation of such fossil records requires the the
+determination of the full three-dimensional gravitational potential of
+the Milky  Way.
+
+The detailed constraints on the shape of this potential can be then
+confronted against the expectations from different galaxy formation
+models in an explicit cosmological context.
+For instance, in the current dominant paradigm of Cold Dark Matter
+(CDM) dominated Universe galaxies are expected to be hosted by
+triaxial DM halos.
+
 This ellipsoidal shape is mostly due to the anisotropical and

### 2019-07-18 Document/paper.tex
intro

--- 2019-07-18 Document/paper.tex
@@
 
-A robust prediction of the Cold Dark Matter (CDM) paradigm is that DM
-halos are ellipsoidal and can be characterized by the principal axes
-$a>b>c$.
+Accurate observations and modeling of our Galaxy 
+shape our understanding of the Universe as a whole.  
+Explaining the Galaxy's matter composition and kinematical state is 
+equivalent to figuring out its formation process in a cosmological
+context. 
+As a first approximation, the Milky Way's (MW) morphology and
+separation into global kinematically coherent components, such as its
+disk and bulge, can be used to support the  existence of a Dark Matter
+(DM) component to explain its dynamics around the solar neighborhood
+\citep{2000MNRAS.311..361O,2009PASJ...61..227S,2010JCAP...08..004C,2013ApJ...779..115B,Iocco15}.
+
+Improvements in the sensitivity of astronomical observations have 
+extended this kind of modelling to outter regions of our Galaxy by measuring
+the stellar streams resulting from infalling globular clusters or
+satellite galaxies that got tidaly disrutpted by the gravitational
+potential of the Milky Way
+\citep{1998ApJ...495..297J,1999MNRAS.307..495H, 1999MNRAS.307..877T}. 
+The interpretation of such fossil records requires the the
+determination of the full three-dimensional gravitational potential of
+the Milky  Way.
+
+The observational constraints on the gravitational potential shape can then
+be confronted against the expectations from different galaxy formation
+models in an explicit cosmological context.
+For instance, in the current dominant paradigm of Cold Dark Matter
+(CDM) dominated Universe galaxies are expected to be hosted by
+triaxial DM halos. To what extent the CDM expectations are born out by
+observations in our Galaxy? Can the MW's DM halo shape be considered
+typical or atypical in a cosmological context?
+
 This ellipsoidal shape is mostly due to the anisotropical and
@@
 rounder as they evolve.
-
-There is however a high degree of uncertainty on what is the degree of
-uncertainty on the degree of ellipticity of the Milky Way DM halo.
-This problem has been addressed both by observations and simulations.
-The difficulty in making an observational measurement lies in the
-indirect nature of the effect; i.e. the ellipticity can only be
-constrained by its effects on quantities such as stellar radial
-velocities.
-In simulations the uncertainty on predicting the MW DM ellipticity is 
-driven by the different physical effects that should be modeled and
-its different possible numerical implementations.
 

### 2019-07-19 Document/paper.tex
edit

@@
 of baryons in producing rounder DM halos.
-This effect has been already reported in other simulations \citep{Debattista08, Bryan13,
-  Butsky16, Chua19, Artale19}.
+
 The strength of the change depends on the numerical resolution, the
 method to resolve the hydrodynamics and the models describing star
-formation and stellar feedback.
-The key concept behind these results is that the baryon distribution
+formation and stellar feedback \citep{Debattista08, Bryan13, Butsky16,
+  Chua19, Artale19}.  
+The key concept unifying these results is that the baryon distribution
 influences and correlates with the dark matter halo shape. 
-The broad tendency is that massive stellar disks correlate with
-spherical dark matter distributions.
+Here we find that the broad tendency is that massive stellar disks
+correlate with spherical dark matter distributions.
 
 In order to explore this idea in the Auriga simulations we quantify
-the  correlation between halo shape with baronyc disk properties. 
+the correlation between halo shape with baryonic disk properties. 
 Looking into the measurements already reported by \cite{auriga} and
@@
 
-Figure \ref{fig:disk_correlations} summarizes the correlations of
+Figure \ref{fig:disk_correlations} shows the correlations of
 these quantities with the triaxility at five diferent radii.
@@
 correlation strength.
-This confirms our expectations. The strongest correlations are found
-with the halo shape measured at radii smaller than $\sim 28$kpc, which
+We find that the strongest correlations are found with the halo shape
+measured at radii smaller than $0.12R_{200}\sim 28$kpc, which 
 is close to the upper limit of the disk optical radius among our
@@
 high gas density and stellar disks with low mass and small size.
-In turn, massive and large stellar disks with in a low density gas
-environment correlate with low triaxiliaty.
+In turn, massive and large stellar disks within a low density gas
+environment correlate with low halo triaxiliaty.
 
-Using the six halos in the high resolution sample we find that the
-memory effect put foward by \cite{VeraCiro11}, that is the correlation
-between the historical and radial evolution of the shape, only holds
-for a fraction of the sample and is clearly broken for two halos in
-the sample.
-Given the small size of the sample we use to study this effect we
-cannot find any significant correlation with other disk properties in
-order to understand the shape amnesia. 
-This effect has not been studied in detail in other simulations. 
-We consider that understanding this effect is the first promising
-extension of our studies to better understand dark matter halo shape
-correlation with disk properties in Milky Way type galaxies.
-avenues to continue a deeper study on dark matter halo shape.
-
-The second promising extension of our results deals with the shape
-alignment as a function of radius.
+Our second results deals with the shape alignment as a function of
+radius. 
 In concordance with previous results in DM only simulations we find
 that the shells of halo shape are well aligned at different radii.
-The surprising result we find is that in the presences of baryons
-these shells twist as a function of radius.
+However, in the presences of baryons these shells twist as a function
+of radius.
 \citep{Debattista08} found a similar effect, but only at radii smaller
@@
 the dark matter shells stop twisting.
-The twisting effect is robust across our sample of 30 halos. 
+In our case the he twisting effect is robust across our sample of 30
+halos at all radii,
+its strenght also correlates with the halo triaxiality for radii
+smaller than $0.12R_{200}$. 
+At larger radii 
 Also surprisingly at a radius of $0.25R_{200}\approx 56$ kpc the

### 2019-07-19 Document/paper.tex
edit

@@
 
-Our second results deals with the shape alignment as a function of
+Our second results deals with the disk-halo shape alignment as a function of
 radius. 
@@
 of radius.
+At a radius of $0.25R_{200}\approx 56$ kpc the alignment between the
+stellar disk and the dark matter halo is almost perfect and degrades
+at other radii. 
+This twisting effect, the change of disk-halo alignment as
+a function of radius, is robust across our sample of 30
+halos at all radii, its strenght correlating strongly with halo
+triaxiality measured at $0.12R_{200}$.
+
+This makes that 
 \citep{Debattista08} found a similar effect, but only at radii smaller
@@
 the dark matter shells stop twisting.
-In our case the he twisting effect is robust across our sample of 30
-halos at all radii,
-its strenght also correlates with the halo triaxiality for radii
-smaller than $0.12R_{200}$. 
-At larger radii 
-Also surprisingly at a radius of $0.25R_{200}\approx 56$ kpc the
-alignment between the stellar disk and the dark matter halo is almost
-perfect.
 

### 2019-07-19 Document/paper.tex
edit

@@
 on galaxies similar to the MW.
-
-\citep{JingSuto02} report the twisting in their simulations.
-They also find a universal radius where the alignment of the internal 
-region (defined as the region with 2500 times the critical density) 
-is perfect with the shell under consideration.
-They blame it on high c/b and undecided vectors.
-but in our case c/b increases monotonically with radius, and the
-alignment with the disk is not monotonous. In our case this cannot be
-the only explanation as the triaxiliaty correlation with the twist 
-strongly depends on the radius.
 
@@
 a function of radius, is robust across our sample of 30
-halos at all radii, its strenght correlating strongly with halo
+halos at all radii, its strenght strongly correlating with halo
 triaxiality measured at $0.12R_{200}$.
 
-This makes that 
-\citep{Debattista08} found a similar effect, but only at radii smaller
-than the disk radius. At radii larger than the disk radius, they find,
-the dark matter shells stop twisting.
+\citep{Debattista08} reported a similar twisting effect, but only at radii smaller
+than the disk radius. 
+At radii larger than the disk radius, they find, the dark matter
+shells stop twisting. 
+\citep{JingSuto02} reported shell alignment twisting in their dark
+matter only simulations as measured in the direction changes of large
+and medium shape axis. 
+They only had three high resolution MW-like halos (with
+$\sim 10^{6}$ inside the virial radius) and could not make a
+statistical statement about the impact of this effect.
+However, they the twisting as an artifact resulting from high values of the
+$c/b$ ratios that make the determination of the medium axis boisy.
+Could then high triaxility values explain the twisting as a result of
+erratic axis directions? 
+If the triaxiality were the main culprit behind the twisting, the
+correlation between the two quantities should be constant at every
+radii.
+In Figure \ref{fig:alignment_correlations} we already showed that this
+correlation strongly depends on radius, we conclude that high
+triaxiality values cannot be the full explanation.
+Furthermore the twisting happens in such a way that it allows and
+almost perfect alignment between the stellar disk at $0.1R{200}$ and
+the halo shape measured at $0.25R_{200}$
 

### 2019-07-19 Document/paper.tex
edit

@@
 
-\citep{Debattista08} reported a similar twisting effect, but only at radii smaller
+\cite{Debattista08} reported a similar twisting effect, but only at radii smaller
 than the disk radius. 
@@
 shells stop twisting. 
-\citep{JingSuto02} reported shell alignment twisting in their dark
+\cite{JingSuto02} also reported shell alignment twisting in their dark
 matter only simulations as measured in the direction changes of large
@@
 
-The measurements we have done in the simulations can be compared
-against observational results.
-We use the observational constraints by \cite{LM10} and \cite{Bovy16}
+We now use the results reported by \cite{LM10} and \cite{Bovy16}
 to place our results in an observational context.
-\cite{LM10} used observations of the long Sagittarius tidal stream to
+\cite{LM10} used observations of the Sagittarius tidal stream to
 constrain the shape of the gravitational potential.
 Their point of depart is that previous studies that assumed an
-axisymetric Galactic potential were not able to fit all the available
-dynamic constraints for the Sagittarius stream, therefore they
-proposed a rigid triaxial potential, with coaxial potential
-ellipsoids, for the dark matter component.  
-Their results are able to constrain the triaxility of this potential
-component, translating these results into a triaxiality of the density
-contours they report $(c/a)=0.44$ and $(b/a)=0.97$ at a radius of
-$\sim 40$kpc. They do not report any uncertainties for these two
-values. 
-Looking at their plots of their quality of fit criterion as a function
-of dark halo axial scales (Figure 5), we choose a conservative $10\%$
-relative uncertainty, close to the uncertainty in those parameters.
-The element that made the results by \cite{LM10} (LM10 hereafter) surprising is that
-the minor axis of the halo shape is parallel, not perpendicular, to
-stellar disk plane.
+axisymetric galactic potential were not able to fit all the available
+dynamic constraints for the Sagittarius stream, therefore making
+necessary the use of a rigid triaxial potential with coaxial potential
+ellipsoids for the dark matter component.  
+Their results constrain the triaxility of this potential
+component. 
+They also translate ther results into a triaxiality of the density
+contours (that could be compared against our results)
+ to be $(c/a)=0.44$ and $(b/a)=0.97$ at a radius of $\sim 40$kpc. 
+They do not report any uncertainties for these two values. 
+Looking at their plots for the quality of fit criterion as a function
+of dark halo axial scales (their Figure 5), we choose a conservative $10\%$
+relative uncertaintyy
+One surprising element in their results is that  the major axis of the
+halo shape is perpendicular to the stellar disk plane.
 
-The results by \cite{Bovy16} (BBFK16 hereafter) have the same general approach but use
+The results by \cite{Bovy16} have the same general approach but use
 instead the GD-1 \citep{2006ApJ...641L..37G} and Pal 5 \citep{2009AJ....137.3378O}
@@
 galacic halo potential.
-They use general models with large degrees of freedom for the galactic
+They use general models with many degrees of freedom for the galactic
 potential in order to measure to what extent these two streams are sensitive
@@
 They find that the width of the Pal 5 stream constraints $b/a\approx
-1$ and therefore fix it to $b/a=1$, finally they report their most stringent
-constrain of $c/a=0.93\pm0.16$ at a radius of $\approx 19$kpc from the
-galactic center.
+1$ and therefore fix it to be $b/a=1$ exactly.
+Using that value they report their most stringent constrain of
+$c/a=0.93\pm0.16$ at a radius of $\approx 19$kpc from the galactic
+center.
 
 Our Figure \label{fig:observations} shows an explicit comparison in
-the $c/a$-$b/a$ plane against the results by LM10 and BBFK16. 
-We find $6$ halos with $b/a<0.93$ and $c/a>0.77$ that could be
-considered consistent with their shape constraints 
-by BBFK16.
-In contrast, none of the simulated halos is consistent with the LM10
-results.
+the $c/a$-$b/a$ plane of our results in MHD simulations against the
+results by LM10 and BBFK16.  
+We find six MHD halos with $b/a<0.93$ and $c/a>0.77$ that could be
+considered consistent with their shape constraints  by BBFK16, while
+only one outlier DMO halo is consistent with those constraints.
+In contrast, none of the simulated halos (MHD nor DMO) is consistent
+with the LM10 results. 
+The change of triaxility with radius in our simulations cannot account
+for these two extremely different observational constraints at
+different radii.
 
-The results by LM10 would place then the dark matter halo of our Milky
+The results by LM10 could then place the dark matter halo of our Milky
 Way as an extreme outlier in the $\Lambda$ CDM model. 
@@
 also oriented perpendicular to the MW plane, another highly unusual
-feature in the $\Lambda$ CDM model \citep{2018MNRAS.478.5533F}
+feature in the $\Lambda$ CDM model \citep{2018MNRAS.478.5533F}.
 

### 2019-07-19 Document/paper.tex
edit

@@
 The change of triaxility with radius in our simulations cannot account
-for these two extremely different observational constraints at
-different radii.
+for these two extremely different shape constraints at different
+radii.
 
@@
 stream data. 
-The current parameterizations of coaxial density/potential shells
-might be too rigid.
-The inclusion of a new free parameter describing this degree of
+The inclusion of a parameterization describing this degree of
 twisting might relax the conflict between the observational
@@
 
-{{\bf alinenaciones y twisting as a function of environment, 
-the difference between accretting and stalled halos, }
-
-%Porciani: stalled halos keep their dark matter density profile
-%while accreting halos have. Shells don't pile up in accreting halos, 
-%they approximately do in stalled halos}
-
-%Porciani: The stalled halos are the most similar to the MW at least in
-%terms of the velocity anisotropy parameter an should be embeded in a
-%thick filament of tha large scale structure.
-
-%IDEA PARA YEIMY: medir scatter en stellar to DM halo mass ratio as a
-%function of the anisotropy parameter or the persistence parameter in 
-%Illustris. Primer proxy para el galaxy formation bias. Esto se puede
-%sacar pronto. (ademas otra medida de los compacto que es la distribucion
-%estelar)
-%esto puede ser comparado con los datos de vipers que tiene un sesgo 
-%donde se ven diferentes clustering a misma masa para galaxias mas o
-%menos concentradas
-
-%otra idea: calcular la entropia del beta skeleton para distinguir 
-%el clustering de dos muestras diferentes. i.e. la entropia para
-%caracterizar assembly bias.
+From the purely numerical point of view a better understading of the
+disk-halo alignment details will certainly require to study how the
+halo and the disk co-evolved as a function of time.
+The effect of the cosmic web (both dark matter and gaseous)
+\citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G} could also be in
+order to gain a full picture.
 
@@
 technique. 
-We also used six of these haloes that were simulated at higher
-resolution. 
 The Auriga project simulated these halos with two different setups:
 dark matter only (DMO) simulation and full magnetohydrodynamics (MHD)
-includeing star formation and feedback.
+including star formation and feedback.
 We used the shape measurement algorithm by \cite{Allgood06} on the
-dark matter halos of these two kinds of simulations.
+dark matter halos of these two kinds of simulations to quantify the
+halo shape as a function of radius and the degree of aligment between
+the stellar disk and the halo.
 
 We find that MHD halos are rounder than DMO halos every sampled radii. 
-MHD halos tend towards more oblate shapes (T < 0.5)
-despite DM halos tendency towards more prolate shapes (T>0.5). 
-It is also noticeable that the rounding effect of baryons is stronger
-at the disk regime, where the haloes are close to oblate.
+MHD halos tend towards more oblate shapes ($T< 1/3$) DMO halos
+tend towards more prolate shapes ($T>2/3$).  
+The rounding effect is more noticeable as one moves closer to galactic
+disk and strongly  correlates with baryonic properties of the disk
+$\leq 0.10R_{200}\approx 20$kpc. 
+More precisely, the triaxility is smaller for large and massive
+stellar disks with low gas densities in its core $\leq 1$ kpc.
 
-This rounding effect can be explained by gravitational effect of the
-flattened axisymmetric galactic disk. 
 It also explanes the weakness of this affect around $\approx 100$kpc,
 where the disk potential is weaker compared to the DM halo potential.
-
-The second part of our study on the historical shape finds that in the
-presence of baryons the memory effect found by \citep{VeraCiro11} does
-not hold for all halos in the high resolution sample.
 

### 2019-07-19 Document/paper.tex
edit

@@
 
+We also found that the alignment betwen the stellar disk and dark
+matter halo changes with the radius.
+At a radius of $0.25R_{200}$ the alignment is almost perfect and
+degrades at smaller and larger distances.
+This alignment evolution implies a radial twisting between the ellipsoids
+describing the halo shape. 
+We quantify this twist with the standard deviation of the angle
+between the two minor axis at radii below $\leq 0.5R_{200}$ and find
+that it strongly correlates is with the disk size and the core gas
+mass density, there is only a weak correlation with the stellar mass
+in the disk.
+
 It also explanes the weakness of this affect around $\approx 100$kpc,

### 2019-07-19 Document/paper.tex
edit

@@
 triaxiality values cannot be the full explanation.
-Furthermore the twisting happens in such a way that it allows and
+Furthermore the twisting happens in such a way that it allows an
 almost perfect alignment between the stellar disk at $0.1R{200}$ and

### 2019-07-19 Document/paper.tex
edit

@@
 lenght and 1850 pc physical. 
-This setup corresponds to \texttt{Level4} resolution.
-From these 30 halos, 6 of them where re-simulated at higher resolution
-taking into account a spatial factor of 2 in each spatial dimension,
-this is the \texttt{Level3} resolution.  
-There are $\sim 4\times 10^6$ dark matter particles within the virial radius
-of \texttt{Level4} halos at $z=0$, this number increases to $\sim 3\times 10^7$ in
-\texttt{Level3} simulations.
-
 In this work all the results that we report at $z=0$ as a function of radius and
@@
 the \texttt{Level4} resolution. 
-For the measurement on shape evolution with time we use the 6 halos in
-the \texttt{Level3} simulations.
 Finally, all  halos described so far have also been simulated at the same
@@
 
-From the results presented in this work we advance the idea that the
-twisting shells in the density is a feature that deserves to be
-explored in the process of constraining shape parameters from tidal
-stream data. 
-The inclusion of a parameterization describing this degree of
-twisting might relax the conflict between the observational
-constraints and the numerical results.
-
-From the purely numerical point of view a better understading of the
-disk-halo alignment details will certainly require to study how the
-halo and the disk co-evolved as a function of time.
-The effect of the cosmic web (both dark matter and gaseous)
-\citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G} could also be in
-order to gain a full picture.
-
 \section{Conclusions}
@@
 
-It also explanes the weakness of this affect around $\approx 100$kpc,
-where the disk potential is weaker compared to the DM halo potential.
+We compared our results against two observational constraints for the
+dark matter halo shape of the Milky Way. 
+The constraints are at two different radii and come from different
+observatinal tracers. 
+We find that $20\%$ halos in the MHD simulations are consistent with
+the constraints by \cite{Bovy16} at $\approx 19$kpc, while none of the
+halos, either in MHD or DMO, has some overlap with the shape
+constraints by \cite{LM10} at $\approx 40$kpc.
+
+From the results presented in this work we advance the idea that the
+twisting shells in the density is a feature that deserves to be
+explored in the process of constraining shape parameters from tidal
+stream data. 
+The inclusion of a parameterization describing this degree of
+twisting might relax the conflict between the observational
+constraints and the numerical results.
+
+From the purely numerical point of view a better understading of the
+disk-halo alignment details will certainly require to study how the
+halo and the disk co-evolved as a function of time.
+Calibrating the effect of the cosmic web (both dark matter and gaseous)
+\citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G}
+could also be required to gain a full picture of this behaviour.
 

### 2019-07-19 Document/paper.tex
edit

@@
 We present shape measurements of dark matter halos at redshift $z=0$
-in a suite of 30 cosmological simulations from the Auriga project. 
+in a suite of 30 zoom-in simulations from the Auriga project. 
 We compare the results in full magnetohydrodynamics against dark
@@
 regions of the halo.
-In simulations with baryons we measure a twist in the dark matter
-shape as a function of radial distance; this effect is almost absent
-in dark matter only simulations.
-We quantify this twisting effect as a changing degree of alignment
-bewteen the halo shape with the stellar disk shape as a function of radius.
-An almost perfect alignment between the two components appears at
-$0.25R_{200}\sim56$ kpc.  
-We show that the twist in the radial shape evolution correlates
-positively with triaxility.
-Furthermore, at distances $\lesssim 30$ kpc, rounder and coherent dark
-matter distributions correlate with extended massive stellar disks and
-low gas densities. 
+At distances $\lesssim 30$ kpc, rounder and coherent dark matter
+distributions correlate with extended massive stellar disks and low gas
+densities.  
+We measure the alignment between the halo and the stellar disk and
+find almost perfect alignment at $0.25R_{200}\sim56$ kpc.   
+The alignment between the two components changes as a function of
+radius implying that the halo shape twists; this effect is almost absent in the dark
+matter only simulations. 
+We quantify the twisting effect wtih the standard deviation of the
+angle between the minor axis of the disk and the halo for radii
+$\leq R_{200}$ to show that the twisting correlates positively with
+extended stellar disks and low gas densities.
 In a comparison against observational constraints of dark matter halo

### 2019-07-19 Document/paper.tex
referencias

@@
 
-This ellipsoidal shape is mostly due to the anisotropical and
-clumpy accretion of matter influenced by environmental structures.
-Numerical studies how that the shape has a strong mass dependence
-\citep{Allgood_et_al._2006}, halos are also rounder at the outerskirts
-than at the inner part. 
-Shape also evolves with cosmic time, halos get
-rounder as they evolve.
+These two questions have been difficult to address because for a long
+time it was difficult to produce realistic galactic disks within the
+CDM context.
+The success of such enterprise has ben the result of high numerical
+resolution and the understanding that baryonic effects such as stellar
+feedback and black hole feedback play an important role in forming a
+galactic disk resembling the Milky Way.
 
-\citep{Dubinski91}
+Along the way the experiments show that the baryonic effects also impact
+the dark matter halo shape making the halo rounder than it otherwise
+be in a dark matter only simulation
+\citep{Dubinski94,Debattista08,Kazantzidis10,Abadi10,Bryan13,Chua19,Artale19}. 
+High resolution simulations have also allowed detailed studies of the
+alignment between the stellar disk and the dark matter halo
+\cite{Bailin05,DeBuhr12,Debattista13,Gomez17}.
 
-Observationally some studies prefer oblate (i.e. a=b>c) configurations at small
+Observationally, some studies prefer oblate configurations at small
 distances around $\leq 20$ kpc
@@
 \citep[see][]{Vera-Ciro_and_Helmi_2013,Law_and_Majewski_2009,Deg_and_Widrow_2013,Banerjee_and_Chanda_2011}.
+
 However, some  studies are inclined towards prolate configurations even at the inner
@@
 \citet{Ibata_et_al._2013}. 
-
-In simulations there is strong evidence claiming that the presence of
-baryons produces axisymmetrical halos.  
-For instance, some studies have shown that the DM halo shape must be
 axisymmetrical to ensure the stability of a hydrodynamical disk
 embeded in a static DM halo.
-Other have studied this rounding effect by simulating the disk as rigid
-potential inside an N-body triaxial DM
-halo \cite{Debattista_et_al._2008,Debattista_et_al._2013,Kazantzidis_et_al._2010}
-finding that the halo responds to the disk by becoming less triaxial.
-
-Rounding effect of baryons
-\citep{Dubinski94}
-
-The caveat of the studies mentioned above is that they do not
-follow baryons in the whole cosmological context. 
-Other studies overcome this limitation by using resimulations 
-\citep{Abadi_et_al._2010,Bryan_et_al._2013} finding that the
-feeback related to star formation in the disk drives the strenght of
-the round effect.
-
-Abadi2010 -> well aligned countours.
-
-Recently \cite{2018arXiv180907255C} made a study in a cosmological
-simulation to compare the effect of including baryons. They do find,
-on average, rounder halo shapes once hydrodynamic effects are
-included, but it is uncertain the strenght of this statistical effect
-on galaxies similar to the MW.
-
-\citep{Pedrosa10}
 
@@
 a function of radius, is robust across our sample of 30
-halos at all radii, its strenght strongly correlating with halo
-triaxiality measured at $0.12R_{200}$.
+halos at all radii.
+However, its strenght is not the same for all galaxies and strongly
+correlates with halo triaxiality measured at $0.12R_{200}$.
 
-\cite{Debattista08} reported a similar twisting effect, but only at radii smaller
+\cite{Bailin05} studied the disk halo alignmnent as a function of
+radius.
+\cite{Gomez17} studied this in Auriga.
+\cite{Debattista13} reported a similar twisting effect, but only at radii smaller
 than the disk radius. 

### 2019-07-19 Document/paper.tex
intro

@@
 
-Accurate observations and modeling of our Galaxy 
-shape our understanding of the Universe as a whole.  
+The understanding of our Universe as a whole is greatly influenced by
+accurate observations and modeling of our Galaxy 
 Explaining the Galaxy's matter composition and kinematical state is 

### 2019-07-19 Document/paper.tex
edit

--- 2019-07-19 Document/paper.tex
@@
 find almost perfect alignment at $0.25R_{200}\sim56$ kpc.   
-The alignment between the two components changes as a function of
-radius implying that the halo shape twists; this effect is almost absent in the dark
-matter only simulations. 
-We quantify the twisting effect wtih the standard deviation of the
+In some cases the alignment between the two components significantly
+changes as a function of radius implying that the halo shape twists;
+this effect is almost absent in the dark matter only simulations. 
+We quantify the twisting effect with the standard deviation of the
 angle between the minor axis of the disk and the halo for radii
-$\leq R_{200}$ to show that the twisting correlates positively with
+$\leq 0.5R_{200}$ to show that this effect correlates positively with
 extended stellar disks and low gas densities.
@@
 required element to achieve this level of agreement.
-In contrast, all simulations (dark matter only and with baryons) are at
-odds with the constrains derived from the Saggitarius stream that
-favor $b/a\approx 0.97$ and $c/a\approx0.44$.
+In contrast, none of the simulations (dark matter only and with
+baryons) can reproduce the constrains derived from the Saggitarius
+stream that favor $b/a\approx 0.97$ and $c/a\approx0.44$. 
 \end{abstract}
@@
 
-Accurate observations and modeling of our Galaxy 
-shape our understanding of the Universe as a whole.  
-Explaining the Galaxy's matter composition and kinematical state is 
-equivalent to figuring out its formation process in a cosmological
-context. 
-As a first approximation, the Milky Way's (MW) morphology and
+The understanding of our Universe as a whole is greatly influenced by
+accurate observations and modeling of our Galaxy. 
+Explaining the matter budget and kinematical state of the Milky Way
+(MW) is  equivalent to figuring out its formation process in a
+cosmological context. 
+As a first approximation, the MW morphology and
 separation into global kinematically coherent components, such as its
@@
 
-Improvements in the sensitivity of astronomical observations have 
-extended this kind of modelling to outter regions of our Galaxy by measuring
-the stellar streams resulting from infalling globular clusters or
+A more detailed description of the full three-dimensional MW
+gravitational potential is possible through the interpretation of 
+fossil records of stellar streams.
+These remanents, resulting from infalling globular clusters or
 satellite galaxies that got tidaly disrutpted by the gravitational
-potential of the Milky Way
+potential of the Milky Way, allow in principle tighter constrains 
+on the shape of the dark matter halo in outter regions of our Galaxy
 \citep{1998ApJ...495..297J,1999MNRAS.307..495H, 1999MNRAS.307..877T}.
-The interpretation of such fossil records requires the the
-determination of the full three-dimensional gravitational potential of
-the Milky  Way.
 
@@
 CDM context.
-The success of such enterprise has ben the result of high numerical
+The success of such enterprise has been the result of high numerical
 resolution and the understanding that baryonic effects such as stellar
@@
 
-Along the way the experiments show that the baryonic effects also impact
+Along the way numerical experiments show that the baryonic effects also impact
 the dark matter halo shape making the halo rounder than it otherwise
@@
 
-Observationally, some studies prefer oblate configurations at small
+Observational constraints of the dark matter halo have been in
+conflict during the last decade.
+Some studies prefer oblate configurations at small
 distances around $\leq 20$ kpc
-\citep[see][]{Law_and_Majewski_2010,Bovy_et_el._2016,Loebman_et_al._2012,Olling_and_Merrifield_2000,Banerjee_and_Chanda_2011} 
-and more triaxial and prolate configurations on the outter distances
-$\geq 20$ kpc 
-\citep[see][]{Vera-Ciro_and_Helmi_2013,Law_and_Majewski_2009,Deg_and_Widrow_2013,Banerjee_and_Chanda_2011}.
-
-However, some  studies are inclined towards prolate configurations even at the inner
-parts of the halo \citep[see][]{Bowden_et_al._2016}, and
+\citep{Law_and_Majewski_2010,Bovy_et_el._2016,Loebman_et_al._2012,Olling_and_Merrifield_2000,Banerjee_and_Chanda_2011} 
+while others tend towards more triaxial and prolate configurations on
+the outter distances $\geq 20$ kpc
+\citep{Vera-Ciro_and_Helmi_2013,Law_and_Majewski_2009,Deg_and_Widrow_2013,Banerjee_and_Chanda_2011}.  
+Some other studies are inclined towards prolate configurations even at the inner
+parts of the halo \citep{Bowden_et_al._2016}, and
 although it previously seemed that a triaxial DM halo on the
-outerskirts would be necessary to fully explain the characterization
+outskirts would be necessary to fully explain the characterization
 of the Sagittarius stream \citep{Law_and_Majewski_2009}, recent studies
@@
 the relaxation of other constraints may make this claim unnecessary
-\citet{Ibata_et_al._2013}. 
-axisymmetrical to ensure the stability of a hydrodynamical disk
-embeded in a static DM halo.
+\citet{Ibata_et_al._2013} axisymmetrical to ensure the stability of
+a hydrodynamical disk embeded in a static DM halo.
 
-All these difficulties (enough numerical resolution, explicit
-cosmological context, appropriate feedback physics to produce
-realistic MW disks) have limited the studies that want to study the
-rounding effect of baryons in MW-like galaxies.
-In this work we overcome all these limitations by analyzing the
-results of state-of-the-art hydrodynamical simulations of isolated
-halos that resemble the Milky Way.
-We also perform a convergence study with simulation performed at
-different resolution levels and explicitly compare the role of DM only
-vs. DM+hydro on the MW DM halo shape.
+In this paper we address the question of measuring the shape of the DM
+halo in MW type galaxies from state-of-the-art simulations from the
+Auriga project.
+These simulations have large enough numerical resolution, and explicit
+cosmological context and an appropriate feedback physics to produce
+realistic MW disks.
+This paper is structured as follows. 
+In Section \ref{sec:numerical} we present the most relevant details of
+the simulations, in Section \ref{sec:method} we present the method
+that we use to measure the DM halo shape. 
+In Section \ref{sec:results} we present our results focusing on the
+radial shape trends at $z=0$ and the alignments with the stellar disk.
+We discuss our results in Section \ref{sec:discussion} to place them
+into the context of other numerical work, explore correlations of the
+shape with baryonic properties in the disk and finally make a direct
+comparison against observational constraints for the MW's dark matter halo shape.
+We finalize with our conclusions in Section \ref{sec:conclusions}.
 
 \section{Numerical Simulations}
+\label{sec:numerical}
 
@@
 \section{Halo Shape Measurement}
+\label{sec:method}
 
@@
 \section{Results}
+\label{sec:results}
 
@@
 
-%\subsection{Shape evolution with cosmic time}
-
-%In the previous section we stablished that DMO halos at $z=0$ have
-%a steady and monotonous trend towards decreasing triaxility with
-%increasing radius.
-%\cite{VeraCiro11} found that this  radial trend at $z=0$ 
-%correlates with the halo shape as a function of cosmic time, i.e.
-%the halo becomes less triaxial as cosmic time progresses. 
-%The hypotesis put forward by \cite{VeraCiro11} is that the correlation
-%raises as each radial shell retains memory of the accreting conditions
-%at the virial radius at the time of collapse.
-
-%Here we use the six \texttt{level3} halos to measure to what extent
-%the presence of baryons affect this memory effect.
-%In Figures \ref{fig:triaxial_history_A} and
-%\ref{fig:triaxial_history_B} we follow the shape evolution measured at
-%$R_{200}$ since redshift $z=1$ to the present, these results are
-%represened by the coloroured dots.
-%We compare this temporal evolution against the radial evolution at
-%$z=0$ represented by the dash black lines.
-
-%The left column of Figure \ref{fig:redshift_triaxial} shows the six
-%halos in the triaxility plane. 
-%The colour dots show the time evolution while the black line
-%corresponds to the radial trend at $z=0$.
-%The left/right columns correspond to the DMO/MHD simulations, respectively.
-
-%We start by analyzing to what extent the memory effect is
-%already present in the DMO sample. 
-%The first feature that jumps out is that \texttt{Au-21} in the DMO
-%simulation does not have a simple shape evolution history.
-%By visual inspection we find that an extended merging substructure
-%intereacted in the main halo showing up in the shape measurements,
-%making it more difficult to interpret the memory hypothesis.
-%For this reason we exclude this halo from the analysis.
-
-%For the other five halos we find simpler temporal and spatial
-%evolution histories. 
-%Halo \texttt{Au-6} (Figure
-%\ref{fig:triaxial_history_A}) shows a broad
-%correlation between the two tracks; close to the cases of halos
-%\texttt{Aq-4-C} and \texttt{Aq-4-D} in \cite{VeraCiro11}.
-%The four other halos (\texttt{Au-16} in Figure
-%\ref{fig:triaxial_history_A}; \texttt{Au-23}, \texttt{Au-24},
-%\texttt{Au-27} in Figure \ref{fig:triaxial_history_B}) are four
-%cases where the temporal evolution if followed very closely by the
-%radial trends.
-%We conclude that in the DMO sample 4 out of the 5 high resolution
-%halos closely follow the memory hypothesis trends and the remaning
-%halo shows a reasonable correlation.
-
-%The situation in the MHD simulations is more diverse.
-%As expected by the results in the previous section the broad location
-%in the triaxility plane of the temporal and radial evolution in the
-%MHD simulation is completeley different from its DMO counterpart. 
-%In terms of the correlations expected by the memory hypothesis we see
-%two different trends.
-%We have the case of Halos \texttt{Au-6}, \texttt{Au-16} and
-%\texttt{Au-27} there is still a reasonable correlation between
-%temporal and radial evolution. 
-%However for halos \texttt{Au-23} and \texttt{Au-24} the radial trends
-%go in directions that are not even covered by the temporal evolution.
-
-%Taken at face value, these results show that it is not possible to
-%generalize the memory hypotesis to dark matter halos in MHD
-%simulations.
-%This means that some halos present a amnesia to its formation history,
-%more specifically there are cases where the radial shape profile at
-%present time does not have any correlation to its evolutionary
-%history.
-
 \subsection{Alignments with the stellar disk}
@@
 \section{Discussion}
+\label{sec:discussion}
 
@@
 \section{Conclusions}
+\label{sec:conclusions}
 

### 2019-07-19 Document/paper.tex
edit

@@
 distances around $\leq 20$ kpc
-\citep{Law_and_Majewski_2010,Bovy_et_el._2016,Loebman_et_al._2012,Olling_and_Merrifield_2000,Banerjee_and_Chanda_2011} 
+\citep{LM10,Bovy16,Loebman_et_al._2012,Olling_and_Merrifield_2000,Banerjee_and_Chanda_2011} 
 while others tend towards more triaxial and prolate configurations on
 the outter distances $\geq 20$ kpc
-\citep{Vera-Ciro_and_Helmi_2013,Law_and_Majewski_2009,Deg_and_Widrow_2013,Banerjee_and_Chanda_2011}.  
+\citep{Vera-Ciro_and_Helmi_2013,Law_and_Majewski_2009,Banerjee_and_Chanda_2011,Deg_and_Widrow_2013}. 
 Some other studies are inclined towards prolate configurations even at the inner
@@
 $\Omega_m=0.307$, $\Omega_b=0.048$, $\Omega_\Lambda=0.693$ and a
-dimensionless Hubble parameter $h=0.6777$ [CITATION PLANCK 2014]
+dimensionless Hubble parameter $h=0.6777$ \citep{2014A&A...571A..16P}
 
@@
 phenomenological descriptions for star formation, chemical enrichment
-from supernovae and its stellar feedback.  The simulation also follows
-the formation and evolution of black holes together with the Active
-Galactic Nuclei feedback \citep{arepo} [CITATIONPAKMORE].
+from supernovae and its stellar feedback.  
+The simulation also follows the formation and evolution of black holes
+together with the Active Galactic Nuclei feedback
+\citep{arepo,2013MNRAS.432..176P}.
 

### 2019-07-19 Document/paper.tex
edit

@@
 $^{1}$Departamento de F\'sica, Universidad de los Andes, Cra. 1 No.
-18A-10, Edificio Ip, Bogot\'a, Colombia.\\
-$^{2}$Heidelberg Institute for Theoretical Studies,
-Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany.\\
+18A-10, Edificio Ip, Bogot\'a, Colombia\\
+$^{2}$Max-Planck-Institut f\"ur Astrophysik, Karl-Schwarzschild-Str. 1, D-85741 Garching, Germany\\
 }
@@
 rounder at all radii compared to its dark matter only counterparts.
-This change in triaxility is more pronounced towards the inner
-regions of the halo.
 At distances $\lesssim 30$ kpc, rounder and coherent dark matter
@@
 changes as a function of radius implying that the halo shape twists;
-this effect is almost absent in the dark matter only simulations. 
-We quantify the twisting effect with the standard deviation of the
-angle between the minor axis of the disk and the halo for radii
-$\leq 0.5R_{200}$ to show that this effect correlates positively with
-extended stellar disks and low gas densities.
-In a comparison against observational constraints of dark matter halo
-triaxiality for the Milky Way we find that $20\%$ of halos our sample
-are consistent with observational results derived from the Pal 5 stream
-that favor $b/a\approx 1$ and $c/a>0.77$. Including baryons is a
-required element to achieve this level of agreement.
-In contrast, none of the simulations (dark matter only and with
-baryons) can reproduce the constrains derived from the Saggitarius
-stream that favor $b/a\approx 0.97$ and $c/a\approx0.44$. 
+this effect correlates with extended stellar disks and
+low gas densities and is almost absent in the dark matter only
+simulations.  
+In a comparison against observational constraints  we find that $20\%$
+of halos are consistent with observational results derived
+from the Pal 5 stream that favor $b/a\approx 1$ and
+$c/a>0.77$. Including baryons is a required element to achieve this
+level of agreement. In contrast, none of the simulations (dark matter
+only and with baryons) can reproduce the constrains derived from the
+Saggitarius stream that favor $b/a\approx 0.97$ and $c/a\approx0.44$.
 \end{abstract}
@@
 dark matter halos in a $\Lambda$CDM cosmology. 
-This simulations come in two versions: dark matter only and
+This simulations come in two versions: dark matter only (DMO) and
 baryonic physics including magetohydrodynamics (MHD).
-A detailed description of the simulations and their
-disk properties can be founc in \citep{auriga}, here we summarize its
-main features.
+A detailed description of the simulations and their disk properties
+can be founc in \citep{auriga}, here we summarize its main features.
 
-The objects in those simulations were selected from a set of 30
+The objects in the simulations were selected from a set of 30
 isolated halos in the Evolution and Assembly of GaLaxies and their
@@
 zoom-in technique with varying physical realism using the moving-mesh AREPO code
-that includes gravity, ideal magnetohydrodynamics (MHD), 
-phenomenological descriptions for star formation, chemical enrichment
-from supernovae and its stellar feedback.  
+that includes gravity, ideal magnetohydrodynamics,  phenomenological
+descriptions for star formation, chemical enrichment from supernovae
+and its stellar feedback.   
 The simulation also follows the formation and evolution of black holes
@@
 lenght and 1850 pc physical. 
-In this work all the results that we report at $z=0$ as a function of radius and
-the correlations with disk properties correspond to the 30 halos in
-the \texttt{Level4} resolution. 
-Finally, all  halos described so far have also been simulated at the same
-resolutions without MHD using dark matter particles only, we refer to
-these halos as the DMO (Dark Matter Only) sample.
+From now on we refer to the haloes simulated with baryonic physics as the
+MHD sample and to the haloes simulated with dark matter only as the
+DMO sample.
 

### 2019-07-19 Document/paper.tex
edit
paper

@@
 of halos are consistent with observational results derived
-from the Pal 5 stream that favor $b/a\approx 1$ and
-$c/a>0.77$. Including baryons is a required element to achieve this
+from the Pal 5 stream that favor an almost spherical shape.
+Including baryons is a required element to achieve this
 level of agreement. In contrast, none of the simulations (dark matter
-only and with baryons) can reproduce the constrains derived from the
-Saggitarius stream that favor $b/a\approx 0.97$ and $c/a\approx0.44$.
+only nor with baryons) match the constrains derived from the
+Sagittarius stream favoring an oblate dark matter halo.
 \end{abstract}
@@
 Observational constraints of the dark matter halo have been in
-conflict during the last decade.
-Some studies prefer oblate configurations at small
-distances around $\leq 20$ kpc
-\citep{LM10,Bovy16,Loebman_et_al._2012,Olling_and_Merrifield_2000,Banerjee_and_Chanda_2011} 
-while others tend towards more triaxial and prolate configurations on
-the outter distances $\geq 20$ kpc
-\citep{Vera-Ciro_and_Helmi_2013,Law_and_Majewski_2009,Banerjee_and_Chanda_2011,Deg_and_Widrow_2013}. 
-Some other studies are inclined towards prolate configurations even at the inner
-parts of the halo \citep{Bowden_et_al._2016}, and
-although it previously seemed that a triaxial DM halo on the
-outskirts would be necessary to fully explain the characterization
-of the Sagittarius stream \citep{Law_and_Majewski_2009}, recent studies
-questioned this claim by reporting inconsistencies with narrow stellar
-streams \citet{Pearson_et_al._2015} or finding that
-the relaxation of other constraints may make this claim unnecessary
-\citet{Ibata_et_al._2013} axisymmetrical to ensure the stability of
-a hydrodynamical disk embeded in a static DM halo.
+tension during the last decade. 
+One can find studies favoring prolate
+\citep{Banerjee_and_Chanda_2011,Bowden_et_al._2016},  oblate
+\citep{LM10,Deg_and_Widrow_2013,Vera-Ciro_and_Helmi_2013} and
+spherical configurations \citep{Bovy16}.  
+Constraints from modeling of stellar streams discard the prolate
+configuration \citep{Pearson_et_al._2015} although some other studies
+still doubt that stellar streams can be used to constrain the halo
+shape once other assumptions, such as the density profile, are relaxed
+\citep{Ibata_et_al._2013}.
 
-In this paper we address the question of measuring the shape of the DM
-halo in MW type galaxies from state-of-the-art simulations from the
+In this paper we contribute to the debate by reporting measurements of
+the DM halo shape in MW type galaxies from state-of-the-art simulations from the
 Auriga project.
@@
 \end{figure}
-
-%\begin{figure*}
-%\begin{center}
-%\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_DM.pdf}
-%\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_MHD.pdf}
-%\end{center}
-%\caption{Axial ratios as a function of time (colour circles) and
-%  radius (dashed lines). 
-%  The left/right columns correspond to DMO/MHD simulations, respectively. 
-%  The colour indicates the redshift at which the shape was measured
-%  (always at $R_{200}$ at that time.)
-%  The radial shapes goes from $R_{200}$ down to $\sim 1$ kpc.
-%  These three halos correspond to a first half the sample for the \texttt{Level3}
-%  haloes. 
-%}
-%\label{fig:triaxial_history_A}
-%\end{figure*}
-
-%\begin{figure*}
-%\begin{center}
-%\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_B_DM.pdf}
-%\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_B_MHD.pdf}
-%\end{center}
-%\caption{Same as Figure \ref{fig:triaxial_history_A}.
-%  These three halos correspond the second half of the sample for the
-%  \texttt{Level3} haloes. 
-%}
-%\label{fig:triaxial_history_B}
-%\end{figure*}
 

### 2019-07-19 Document/paper.tex
edit

@@
-\documentclass[a4paper,fleqn,usenatbib]{mnras}
+\documentclass[usenatbib]{mnras}
 \usepackage[T1]{fontenc}
@@
 
-\newenvironment{Table}
-   {\par\bigskip\noindent\minipage{\columnwidth}\centering}
-   {\endminipage\par\bigskip}
-
-\title[The shape of dark matter haloes at $z=0$ in Auriga]
-{Dark matter halo shape at $z=0$ in the Auriga simulations: radial
-  evolution and alignment with the stellar disk}
+\title[Dark matter halo shapes at $z=0$] {Dark matter halo shapes at
+  $z=0$ in the Auriga simulations} 
 \author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
@@
 % List of institutions
-$^{1}$Departamento de F\'sica, Universidad de los Andes, Cra. 1 No.
+$^{1}$Departamento de F\'isica, Universidad de los Andes, Cra. 1 No.
 18A-10, Edificio Ip, Bogot\'a, Colombia\\
@@
 \begin{abstract}
-We present shape measurements of dark matter halos at redshift $z=0$
-in a suite of 30 zoom-in simulations from the Auriga project. 
+We present shape measurements of Milky Way sized dark matter halos at
+redshift $z=0$ in a suite of 30 zoom simulations from the Auriga
+project. 
 We compare the results in full magnetohydrodynamics against dark
@@
 
-The understanding of our Universe as a whole is greatly influenced by
-accurate observations and modeling of our Galaxy. 
+Our physical picture of the Universe as a whole has be shaped by
+accurate observations and modeling of our own Galaxy. 
 Explaining the matter budget and kinematical state of the Milky Way
@@
 on the shape of the dark matter halo in outter regions of our Galaxy
-\citep{1998ApJ...495..297J,1999MNRAS.307..495H, 1999MNRAS.307..877T}.
+\citep{1998ApJ...495..297J,1999MNRAS.307..495H, 1999MNRAS.307..877T}
+than dynamical measurements close to the solar neighborhodd.
 
@@
 galactic disk resembling the Milky Way.
-
 Along the way numerical experiments show that the baryonic effects also impact
@@
 alignment between the stellar disk and the dark matter halo
-\cite{Bailin05,DeBuhr12,Debattista13,Gomez17}.
+\citep{Bailin05,DeBuhr12,Debattista13,Gomez17}.
 
@@
 Constraints from modeling of stellar streams discard the prolate
-configuration \citep{Pearson_et_al._2015} although some other studies
+configuration \citep{LM10,Pearson_et_al._2015,Bovy16} although some other studies
 still doubt that stellar streams can be used to constrain the halo
@@
 \end{center}
-\caption{Comparison of our results against other simulations
-  by \citet{Chua19} (Illustris) and observational constraints for the 
+\caption{Comparison of our results against 
+observational constraints for the 
 dark matter halo shape in the Milky Way by \citet{LM10} (LM10) and
 \citet{Bovy16} (BBFK16).   
-We report our results in the MHD simulations in such a way as to
-bracket the radii in the other estimates.
-We find that our results are broadly consistent with the Illustris
-simulations given the broad dispersion in both data sets.
-The consistency with the constraints by \citet{Bovy16} is marginal,
-only 1/5 of the halos in our sample seem to be consistent within the
-observational reults.
-The result by \citet{LM10} would place the Milky Way halo as an
-atypical object in the $\Lambda$ CDM context.} 
+We find that  1/5 of the halos in the MHD  sample are consistent with
+the constraints by \citet{Bovy16}.
+In contrast, none of the halos in the MHD and DMO seems to be
+consistent with the results by \citet{LM10}.}
 \label{fig:observations}
@@
 This method yields results in good agreement to the isodensity
-contours for radii $leq 140$ kpc as explored by
+contours for radii $\leq 140$ kpc as explored by
 \citep{VeraCiro11}.
@@
 In particular, we measure the shape using the reduced inertia tensor
-\citep{Allgood_et_al._2006},
+\citep{Allgood06},
 
@@
 gravitational potential in each halo and each is weighted by the k-th
-particle distance 
-$d_k^2=x_k^2+y_k^2+z_k^2$.
+particle distance $d_k^2=x_k^2+y_k^2+z_k^2$.
 
@@
 
-Following the convergence criterion by \cite{Vera-Crito_et_al.2011} we
+Following the convergence criterion by \cite{VeraCiro11} we
 restrict the sampling of the ellipsoidal parameters to radii  between
@@
 $R_{200}=230\pm 15$kpc.
-For \texttt{Level3} halos we go down to distances of $\sim 0.2$ kpc.
 
@@
 
-\subsection{Radial trends at $z=0$}
+\subsection{Radial trends}
 
@@
 triaxility parameter $T$ defined as
+
 \begin{equation}
@@
 \end{equation}
+
 The left panel of this Figure shows that in the DMO sample the
@@
 of dark halo axial scales (their Figure 5), we choose a conservative $10\%$
-relative uncertaintyy
+relative uncertainty.
 One surprising element in their results is that  the major axis of the
@@
 
-In this paper we measured the shape of thirty isolated Milky Way like 
+In this paper we measured the shape of 30 isolated Milky Way like 
 dark matter haloes simulated in the Auriga project using the zoom-in
@@
  \bibliography{references}
+
 \end{document}

### 2019-07-19 Document/paper.tex
replace

@@
 rounder at all radii compared to its dark matter only counterparts.
-At distances $\lesssim 30$ kpc, rounder and coherent dark matter
-distributions correlate with extended massive stellar disks and low gas
+At distances $\lesssim 30$ kpc, rounder dark matter distributions
+correlate with extended massive stellar discs and low gas 
 densities.  
-We measure the alignment between the halo and the stellar disk and
+We measure the alignment between the halo and the stellar disc and
 find almost perfect alignment at $0.25R_{200}\sim56$ kpc.   
@@
 changes as a function of radius implying that the halo shape twists;
-this effect correlates with extended stellar disks and
+this effect correlates with extended stellar discs and
 low gas densities and is almost absent in the dark matter only
@@
 separation into global kinematically coherent components, such as its
-disk and bulge, can be used to support the  existence of a Dark Matter
+disc and bulge, can be used to support the  existence of a Dark Matter
 (DM) component to explain its dynamics around the solar neighborhood
@@
 These two questions have been difficult to address because for a long
-time it was difficult to produce realistic galactic disks within the
+time it was difficult to produce realistic galactic discs within the
 CDM context.
@@
 feedback and black hole feedback play an important role in forming a
-galactic disk resembling the Milky Way.
+galactic disc resembling the Milky Way.
 Along the way numerical experiments show that the baryonic effects also impact
@@
 High resolution simulations have also allowed detailed studies of the
-alignment between the stellar disk and the dark matter halo
+alignment between the stellar disc and the dark matter halo
 \citep{Bailin05,DeBuhr12,Debattista13,Gomez17}.
@@
 cosmological context and an appropriate feedback physics to produce
-realistic MW disks.
+realistic MW discs.
 This paper is structured as follows. 
@@
 In Section \ref{sec:results} we present our results focusing on the
-radial shape trends at $z=0$ and the alignments with the stellar disk.
+radial shape trends at $z=0$ and the alignments with the stellar disc.
 We discuss our results in Section \ref{sec:discussion} to place them
 into the context of other numerical work, explore correlations of the
-shape with baryonic properties in the disk and finally make a direct
+shape with baryonic properties in the disc and finally make a direct
 comparison against observational constraints for the MW's dark matter halo shape.
@@
 baryonic physics including magetohydrodynamics (MHD).
-A detailed description of the simulations and their disk properties
+A detailed description of the simulations and their disc properties
 can be founc in \citep{auriga}, here we summarize its main features.
@@
   The median triaxility at all radii is smaller than $0.5$.
-  Moving towards the stellar disk the triaxility decreases towards a median
+  Moving towards the stellar disc the triaxility decreases towards a median
   value of $T=0.15$.}
@@
   principal axis of the halo shape and the principal axis of the
-  stellar disk in the MHD simulations at four different radii $\leq 0.5R_{200}$.
+  stellar disc in the MHD simulations at four different radii $\leq 0.5R_{200}$.
   Thin lines correspond to each one of the thirty halos in our sample,
@@
   Each panel compares the alignment of the corresponding
-  major/middle/minor axis both in the halo and the stellar disk.
+  major/middle/minor axis both in the halo and the stellar disc.
   In the upper row the haloes come from the DMO simulation, 
@@
   In the lower row the haloes come from the MHD simulation providing a 
-  self-consistent comparison with the stellar disks. 
+  self-consistent comparison with the stellar discs. 
   In this case the dark matter shells twist in all the halos.
   The degree of this twisting is different in each halo.
-  Interestingly, an almost perfect halo-disk alignment happens across
+  Interestingly, an almost perfect halo-disc alignment happens across
   the sample at an intermediate radius of $0.25R_{200}$ ($56\pm 4$kpc).
@@
 \caption{Changse of angle alignment of the dark
-  matter halo and stellar disk at two different radii ($R_{200}/16$
-  and $0.25R_{200}$) as a function of the baryonic disk properties
-  already explored in Figure \ref{fig:disk_correlations}.  
+  matter halo and stellar disc at two different radii ($R_{200}/16$
+  and $0.25R_{200}$) as a function of the baryonic disc properties
+  already explored in Figure \ref{fig:disc_correlations}.  
   Figure \ref{fig:cumulative_alignment} showed that maximum alignment
@@
  at different radii
- and baryonic disk properties. 
+ and baryonic disc properties. 
  The label with the $\rho$ value corresponds to the Spearman’s rank correlation coefficient. }
@@
 \begin{center}
-\includegraphics[width=0.8\textwidth]{correlation_T_MHD_disk.pdf}
+\includegraphics[width=0.8\textwidth]{correlation_T_MHD_disc.pdf}
 \end{center}
 \caption{Correlations between the halo triaxility at different radii
-  and baryonic disk properties. 
+  and baryonic disc properties. 
   The label with the $\rho$ value corresponds to the Spearman's rank
@@
   the galaxy with in a sphere of radius  $1$ kpc \citep{Pakmor17};
-  the second column shows the disk to total mass ratio and the last
-  column includes the disk optical radius defined to be the radius at which the
+  the second column shows the disc to total mass ratio and the last
+  column includes the disc optical radius defined to be the radius at which the
   $B$-band surface brightness drops below 25 mag arcsec$^{-2}$ \citep{auriga}.
@@
   dilute as one approached $R_{200}$.
-  Large and massive stellar disks with a low gas content are
+  Large and massive stellar discs with a low gas content are
   correlated with low dark matter triaxilities.}
-\label{fig:disk_correlations}
+\label{fig:disc_correlations}
 \end{figure*}
@@
 There the median triaxility is alwas smaller than $0.5$ and this
-triaxility is smaller as we move closer to the galactic disk.
+triaxility is smaller as we move closer to the galactic disc.
 
@@
 
-\subsection{Alignments with the stellar disk}
+\subsection{Alignments with the stellar disc}
 
 A common assumption in observational models of the MW DM halo is that
-its minor axis is perfectly aligned with the stellar disk minor axis.
+its minor axis is perfectly aligned with the stellar disc minor axis.
 Although it is a reasonable assumption to guarantee the stability of
-the galactic disk in simplified models of isolated galaxies, this
+the galactic disc in simplified models of isolated galaxies, this
 might not hold in an explicit cosmological context. 
@@
 The upper row shows the alignment of the halos in the DMO simulations
-with the stellar disk in the MHD simulations.
+with the stellar disc in the MHD simulations.
 The main objective of this measurement is to calibrate the radial
@@
 However around the radius of $0.25R_{200}$ there is an alignment
-almost perfect between the shapes of the stellar disk and the dark
+almost perfect between the shapes of the stellar disc and the dark
 matter halo. 
@@
 influences and correlates with the dark matter halo shape. 
-Here we find that the broad tendency is that massive stellar disks
+Here we find that the broad tendency is that massive stellar discs
 correlate with spherical dark matter distributions.
@@
 In order to explore this idea in the Auriga simulations we quantify
-the correlation between halo shape with baryonic disk properties. 
+the correlation between halo shape with baryonic disc properties. 
 Looking into the measurements already reported by \cite{auriga} and
@@
 strongest correlation with DM halo triaxiality: the central gas
-density in a sphere of radius $1$kpc, the disk to total mass ratio and
+density in a sphere of radius $1$kpc, the disc to total mass ratio and
 the optical radius.
 
-Figure \ref{fig:disk_correlations} shows the correlations of
+Figure \ref{fig:disc_correlations} shows the correlations of
 these quantities with the triaxility at five diferent radii.
@@
 measured at radii smaller than $0.12R_{200}\sim 28$kpc, which 
-is close to the upper limit of the disk optical radius among our
+is close to the upper limit of the disc optical radius among our
 simulation sample. 
 The trend is such that halos with large triaxiality correlate with
-high gas density and stellar disks with low mass and small size.
-In turn, massive and large stellar disks within a low density gas
+high gas density and stellar discs with low mass and small size.
+In turn, massive and large stellar discs within a low density gas
 environment correlate with low halo triaxiliaty.
 
-Our second results deals with the disk-halo shape alignment as a function of
+Our second results deals with the disc-halo shape alignment as a function of
 radius. 
@@
 At a radius of $0.25R_{200}\approx 56$ kpc the alignment between the
-stellar disk and the dark matter halo is almost perfect and degrades
+stellar disc and the dark matter halo is almost perfect and degrades
 at other radii. 
-This twisting effect, the change of disk-halo alignment as
+This twisting effect, the change of disc-halo alignment as
 a function of radius, is robust across our sample of 30
@@
 
-\cite{Bailin05} studied the disk halo alignmnent as a function of
+\cite{Bailin05} studied the disc halo alignmnent as a function of
 radius.
@@
 \cite{Debattista13} reported a similar twisting effect, but only at radii smaller
-than the disk radius. 
-At radii larger than the disk radius, they find, the dark matter
+than the disc radius. 
+At radii larger than the disc radius, they find, the dark matter
 shells stop twisting. 
@@
 Furthermore the twisting happens in such a way that it allows an
-almost perfect alignment between the stellar disk at $0.1R{200}$ and
+almost perfect alignment between the stellar disc at $0.1R{200}$ and
 the halo shape measured at $0.25R_{200}$
@@
 One surprising element in their results is that  the major axis of the
-halo shape is perpendicular to the stellar disk plane.
+halo shape is perpendicular to the stellar disc plane.
 
@@
 halo shape as a function of radius and the degree of aligment between
-the stellar disk and the halo.
+the stellar disc and the halo.
 
-We find that MHD halos are rounder than DMO halos every sampled radii. 
-MHD halos tend towards more oblate shapes ($T< 1/3$) DMO halos
+We find that MHD halos are rounder than DMO halos at every radius.
+MHD halos tend towards more oblate shapes ($T<1/3$), while DMO halos
 tend towards more prolate shapes ($T>2/3$).  
 The rounding effect is more noticeable as one moves closer to galactic
-disk and strongly  correlates with baryonic properties of the disk
-$\leq 0.10R_{200}\approx 20$kpc. 
+disc and strongly  correlates with baryonic properties of the disc
 More precisely, the triaxility is smaller for large and massive
-stellar disks with low gas densities in its core $\leq 1$ kpc.
+stellar discs with low gas densities at its core.
 
-We also found that the alignment betwen the stellar disk and dark
-matter halo changes with the radius.
+We also measured the shape alignment of the halo with the stellar
+disc.
 At a radius of $0.25R_{200}$ the alignment is almost perfect and
 degrades at smaller and larger distances.
+We found that in some halos the alignment betwen the stellar disc
+and dark matter halo changes noticeably with the radius.
 This alignment evolution implies a radial twisting between the ellipsoids
@@
 between the two minor axis at radii below $\leq 0.5R_{200}$ and find
-that it strongly correlates is with the disk size and the core gas
-mass density, there is only a weak correlation with the stellar mass
-in the disk.
+that it strongly correlates with the disc size and the core gas
+mass density, there is only a weak correlation with the disc to
+total mass ratio in the disc.
 
@@
 From the purely numerical point of view a better understading of the
-disk-halo alignment details will certainly require to study how the
-halo and the disk co-evolved as a function of time.
+disc-halo alignment details will certainly require to study how the
+halo and the disc co-evolved as a function of time.
 Calibrating the effect of the cosmic web (both dark matter and gaseous)

### 2019-07-21 Document/paper.tex
test

@@
 We compare the results in full magnetohydrodynamics against dark
-matter only physics. 
+matter only simulations. 
 We find a strong influence of baryons in making dark matter halos
@@
 At distances $\lesssim 30$ kpc, rounder dark matter distributions
-correlate with extended massive stellar discs and low gas 
+correlate with extended massive stellar discs and low core gas 
 densities.  
-We measure the alignment between the halo and the stellar disc and
-find almost perfect alignment at $0.25R_{200}\sim56$ kpc.   
-In some cases the alignment between the two components significantly
-changes as a function of radius implying that the halo shape twists;
+We measure the alignment between the halo and the stellar disc at
+different radii and find almost perfect alignment at
+$0.25R_{200}\sim56$ kpc.    
+In some cases the alignment significantly changes as a function of
+radius implying that the halo shape twists; 
 this effect correlates with extended stellar discs and
@@
 In a comparison against observational constraints we find that $20\%$
-of halos are consistent with observational results derived
+of halos in our sample are consistent with observational results derived
 from the Pal 5 stream that favor an almost spherical shape.
@@
 in halo shape we report in the following sections.
-
 This is the same method used to estimate the halo shape in the DM-only
@@
 enclosing a sphere with 200 times the critical density of the Universe.
-On average, over the 30 halos in the \texttt{Level4} sample
-$R_{200}=230\pm 15$kpc.
+On average, over the 30 halos in the sample $R_{200}=230\pm 15$kpc. 
+In our results we express the radius as a fraction of $R_{200}$ in
+order to have a consistent radius scale across all halos.
 
@@
 
-In this paper we measured the shape of 30 isolated Milky Way like 
+In this paper we measured the shape of 30 isolated Milky Way sized
 dark matter haloes simulated in the Auriga project using the zoom-in
 technique. 
-The Auriga project simulated these halos with two different setups:
+The halos were with two different setups:
 dark matter only (DMO) simulation and full magnetohydrodynamics (MHD)
@@
 We used the shape measurement algorithm by \cite{Allgood06} on the
-dark matter halos of these two kinds of simulations to quantify the
-halo shape as a function of radius and the degree of aligment between
-the stellar disc and the halo.
+dark matter halos of these simulations to quantify the halo shape as a
+function of radius and the degree of aligment between the stellar disc
+and the halo.
 
 We find that MHD halos are rounder than DMO halos at every radius.
-MHD halos tend towards more oblate shapes ($T<1/3$), while DMO halos
-tend towards more prolate shapes ($T>2/3$).  
+MHD halos tend towards more oblate, sometimes almost spherical, shapes
+($T<1/3$), while DMO halos tend towards more prolate shapes ($T>2/3$).  
 The rounding effect is more noticeable as one moves closer to galactic
 disc and strongly  correlates with baryonic properties of the disc
-More precisely, the triaxility is smaller for large and massive
+More precisely, the triaxility is smaller for extended and massive
 stellar discs with low gas densities at its core.
@@
 We also measured the shape alignment of the halo with the stellar
-disc.
+disc at different radii.
 At a radius of $0.25R_{200}$ the alignment is almost perfect and
 degrades at smaller and larger distances.
-We found that in some halos the alignment betwen the stellar disc
-and dark matter halo changes noticeably with the radius.
+In some halos the alignment betwen the stellar disc and dark matter
+halo changes noticeably with radius. 
 This alignment evolution implies a radial twisting between the ellipsoids
@@
 between the two minor axis at radii below $\leq 0.5R_{200}$ and find
-that it strongly correlates with the disc size and the core gas
-mass density, there is only a weak correlation with the disc to
-total mass ratio in the disc.
+that the twisting strongly correlates with the disc size and the core
+gas mass density, there is only a weak correlation with the disc to
+total mass ratio.
 
@@
 We find that $20\%$ halos in the MHD simulations are consistent with
-the constraints by \cite{Bovy16} at $\approx 19$kpc, while none of the
-halos, either in MHD or DMO, has some overlap with the shape
-constraints by \cite{LM10} at $\approx 40$kpc.
+the constraints by \cite{Bovy16} at $\approx 19$kpc that correspond to
+an almost spherical halo, while none of the halos, either in MHD or
+DMO, has some overlap with the shape constraints by \cite{LM10} at
+$\approx 40$kpc that is closer to oblate.
+
+From the purely numerical point of view, a better understading of the
+influence of baryons on the different properties we have measure  will
+certainly require to study how the halo and the disc co-evolved as a
+function of time. 
+\cite{VeraCiro11} advanced suggested the idea that the current dark
+matter halo shape strongly correlates with the time evolution of the
+halo as traced by the shape measured at the virial radius.
+The opposed trend of triaxiality as a functio of radius between the
+MHD and the DMO simulations, together with twsiting effect in some of
+the halos seems to suggest that this effect might no longer hold.
+
+Calibrating the effect of the cosmic web (both dark matter and gaseous)
+\citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G}
+could also be required to gain a full picture of this behaviour.
 
@@
 constraints and the numerical results.
-
-From the purely numerical point of view a better understading of the
-disc-halo alignment details will certainly require to study how the
-halo and the disc co-evolved as a function of time.
-Calibrating the effect of the cosmic web (both dark matter and gaseous)
-\citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G}
-could also be required to gain a full picture of this behaviour.
 

### 2019-07-21 Document/paper.tex
conclusiones

@@
 
-From the purely numerical point of view, a better understading of the
-influence of baryons on the different properties we have measure  will
-certainly require to study how the halo and the disc co-evolved as a
-function of time. 
-\cite{VeraCiro11} advanced suggested the idea that the current dark
-matter halo shape strongly correlates with the time evolution of the
-halo as traced by the shape measured at the virial radius.
-The opposed trend of triaxiality as a functio of radius between the
-MHD and the DMO simulations, together with twsiting effect in some of
-the halos seems to suggest that this effect might no longer hold.
+Using dark matter only simulations \cite{VeraCiro11} suggested that
+the current dark matter halo shape strongly correlates with the time
+evolution of the halo as traced by the shape measured at the virial radius. 
+This effect might no longer hold once baryons are included. 
+The opposed trend of triaxiality in MHD simulation as a function of
+radius to the DMO simulations together with the twisting effect in some of 
+the halos seems to suggest that that historical buildup memory is not
+stored in the halo at $z=0$.
 
-Calibrating the effect of the cosmic web (both dark matter and gaseous)
-\citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G}
-could also be required to gain a full picture of this behaviour.
-
-From the results presented in this work we advance the idea that the
-twisting shells in the density is a feature that deserves to be
-explored in the process of constraining shape parameters from tidal
-stream data. 
-The inclusion of a parameterization describing this degree of
-twisting might relax the conflict between the observational
-constraints and the numerical results.
+A more complete understading of the influence of baryons on the
+different properties we have measure will certainly require to study
+how the halo and the disc co-evolved as a function of time and a
+calibrating the effect of the cosmic web (both dark matter and
+gaseous)  \citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G}
+We finalize by suggesting that twisting shells in the density is a
+feature that deserves to be explored in the process of constraining
+shape parameters from tidal stream data.  The inclusion of a
+parameterization describing this degree of twisting might relax the
+conflict between the observational constraints and the numerical
+results.
 

### 2019-07-21 Document/paper.tex
edit

@@
 A more complete understading of the influence of baryons on the
-different properties we have measure will certainly require to study
-how the halo and the disc co-evolved as a function of time and a
-calibrating the effect of the cosmic web (both dark matter and
-gaseous)  \citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G}
-We finalize by suggesting that twisting shells in the density is a
-feature that deserves to be explored in the process of constraining
-shape parameters from tidal stream data.  The inclusion of a
-parameterization describing this degree of twisting might relax the
-conflict between the observational constraints and the numerical
-results.
+different properties we have measured will require two elements, at
+least. First, an study on how the halo and the disc co-evolved as a
+function of time. Second, a calibrating the effect of the cosmic web
+(both dark matter and gaseous) on any evoluionary trend
+\citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G} 
+We finalize by suggesting that the twisting density shells we find in
+some of the halos is feature that deserves to be explored in the
+process of constraining shape parameters from tidal stream data.  The
+inclusion of a parameterization describing this degree of twisting
+might relax the conflict between the observational constraints and the
+numerical results.
 

### 2019-07-21 Document/paper.tex
edit caption

@@
   \caption{DM density in logarithmic scale within a slice of one tenth
-    of the virial radius in width. 
+    of the virial radius.
     The cut is perpendicular to the short axis of the inertia tensor ellipsoid.
-    The black ellipses show the results of the fitting procedure. 
-    Upper panels correspond to DMO simulations, lower panels to MHD
-    simulations.
-    All cases correspond to \texttt{Level4} resolution.
-    Left panels show data at small radii, while right panels at large
-    radii.    
-    This halo showcases the most noticeable effect in all halos
-    across the Auriga simulations: DM halos are rounder at all radii
+    The black ellipses show the results of the fitting procedure
+    described in Section \ref{sec:method}. 
+    Upper/lower panels correspond to DMO/MHD simulations, respectively.
+    Left/right panels show data at small/large radii, respectively.
+    This plot showcases the most noticeable effect in all halos
+    across the Auriga simulations: haloes are rounder at all radii
     after baryonic physics is included.}

### 2019-07-21 Document/paper.tex
push

@@
 \end{center}
-\caption{Axial ratios for all halos in the simulation.
-  Left/right panels correspond to DMO/MHD simulations, respectively.
+\caption{Axial ratios for all simulated halos.
+  Left/right panel corresponds to DMO/MHD simulations, respectively.
   Triangles (squares) represent the measurements at $R_{200}/16$
-  ($R_{200}$) which correspond to physical distances of $14\pm 1$ kpc
-  ($230\pm 15$ kpc) respectively.
-  Here we can visualize three main trends for the whole halo population.
+  ($R_{200}$) that correspond to physical distances of $14\pm 1$ kpc
+  ($230\pm 15$ kpc).
+  Here we visualize three main population trends.
   First, in DMO simulations halos are rounder in the outskirts
@@
   Second, halos in MHD are rounder than its DMO counterparts.
-  Third, halos in MHD are less triaxial in the inner regions than in
-  the outskirts.}
+  Third, halos in MHD are rounder in the inner regions than in
+  the outskirts (opposite to the DMO trend).}
   \label{fig:triaxiality_plane}
@@
 \subfloat[MHD simulations.]{\includegraphics[width=0.8\columnwidth]{triaxialiy_distro_MHD.pdf}}
-\caption{Cumulative distribution for the triaxiality at five different radii.
-  Right/left panel correspond to DMO/MHD simulations, respectively. 
+\caption{Triaxility Cumulative distribution at five different radii.
+  Right/left panel corresponds to DMO/MHD simulations, respectively. 
   In DMO simulations the median triaxiality at all radii is larger
-  than $0.5$; only for $20\%$ the triaxility is smaller than $0.5$.
-  Furthermore, the triaxility increases as one moves towards the inner
-  part of the halo.
-  In MHD simulations the situation is reversed.
-  The median triaxility at all radii is smaller than $0.5$.
-  Moving towards the stellar disc the triaxility decreases towards a median
-  value of $T=0.15$.}
+  than $2/3$. Furthermore, the triaxility increases as one moves
+  towards the inner part of the halo.
+  In MHD simulations these trend reverses.
+  The median triaxility at all radii is smaller than $1/3$ and the
+  halo is less triaxial as on moves towards the stellar disc.}
 \label{fig:triaxial_cumulative}

### 2019-07-21 Document/paper.tex
edit

@@
 \subfloat[MHD simulations.]{\includegraphics[width=0.8\columnwidth]{triaxialiy_distro_MHD.pdf}}
-\caption{Triaxility Cumulative distribution at five different radii.
+\caption{Triaxility cumulative distribution at five different radii.
   Right/left panel corresponds to DMO/MHD simulations, respectively. 
@@
 \caption{
-  Cumulative distribution for the change in triaxility $\Delta T=T_{\rm
-    MHD}-T_{\rm DMO}$ for the same radii used in Figure
-  \ref{fig:triaxial_cumulative}. 
-  At the virial radius all the halos become less triaxial in the MHD
-  simulations. 
-  The change in triaxility becomes stronger in the inner regions of
-  the dark matter halo.}
+  Cumulative distribution for the changes in triaxility in simulations
+  with different physics, $\Delta T=T_{\rm MHD}-T_{\rm DMO}$.
+  At the virial radius all halos become less triaxial in the MHD
+  simulations, the change is stronger towards the halo center.
+  Only a small fraction of the halos ($\sim 1/10$) presents the
+  opposite trend of becoming more triaxial towards the center.}
 \label{fig:delta_triaxial_cumulative}

### 2019-07-21 Document/paper.tex
edit

@@
 \end{center}
-\caption{Angles between the
-  principal axis of the halo shape and the principal axis of the
-  stellar disc in the MHD simulations at four different radii $\leq 0.5R_{200}$.
-  Thin lines correspond to each one of the thirty halos in our sample,
-  while the thick line traces the median value.
+\caption{Angles between the principal axis of the dark matter halo
+  shape and the stellar disc shape as a function of the radius at
+  which the halo shape directions are measured.
   Each panel compares the alignment of the corresponding
-  major/middle/minor axis both in the halo and the stellar disc.
+  major/middle/minor axis.
+  Thin lines correspond to each one of the thirty halos in the sample
+  while the thick line traces the median value at every radius.
   In the upper row the haloes come from the DMO simulation, 
-  showing that the ellipsoids describing the
-  shape are constant as a function of radius for the most part of the
-  sample.
+  showing that the directions in the ellipsoids describing the shape
+  are constant as a function of radius for the most part of the sample.
   In the lower row the haloes come from the MHD simulation providing a 
   self-consistent comparison with the stellar discs. 
-  In this case the dark matter shells twist in all the halos.
-  The degree of this twisting is different in each halo.
+  In this case the dark matter shells twists significantly in a
+  noticeable fraction of the haloes.
   Interestingly, an almost perfect halo-disc alignment happens across
-  the sample at an intermediate radius of $0.25R_{200}$ ($56\pm 4$kpc).
+  the sample at an intermediate radius of $0.25R_{200}$ ($56\pm
+  4$kpc). 
 }
@@
 \end{center}
-\caption{Changse of angle alignment of the dark
-  matter halo and stellar disc at two different radii ($R_{200}/16$
-  and $0.25R_{200}$) as a function of the baryonic disc properties
-  already explored in Figure \ref{fig:disc_correlations}.  
-  Figure \ref{fig:cumulative_alignment} showed that maximum alignment
-  occurs at $0.25R_{200}$ while in the inner regions ($R_{200}/16$)
-  considerable missalignments occurr.
- at different radii
- and baryonic disc properties. 
- The label with the $\rho$ value corresponds to the Spearman’s rank correlation coefficient. }
+\caption{Twisting in the halo-disc alignment (measured as the standard deviation
+  of the alignment angles between two minor shape axis)
+  as a function of the halo triaxialiy at the radius indicated
+  in each panel's title.
+  The label with the $\rho$ value corresponds to the Spearman's rank
+  correlation coefficient while the line shows the result of the
+  minimum squares fit to the data.
+  Twisting does not correlate with triaxility in the same way at every
+  radii. The strongest correlation appears around $0.12R_{200}\approx
+  28\pm2$ kpc.} 
 \label{fig:alignment_correlations}
@@
   $B$-band surface brightness drops below 25 mag arcsec$^{-2}$ \citep{auriga}.
-  The largest correlations are found for the two smaller radii and
-  dilute as one approached $R_{200}$.
-  Large and massive stellar discs with a low gas content are
-  correlated with low dark matter triaxilities.}
+  The largest correlations are found for the two smaller radii
+  ($0.06R_{200}$ and $0.12R_{200}$).
+  Extended and massive stellar discs with a low gas content at its
+  core are correlated with low dark matter triaxilities.
+  The correlation decreases as one approaches larger radii.}
 \label{fig:disc_correlations}

### 2019-07-21 Document/paper.tex
numerical simulations

@@
 dark matter halos in a $\Lambda$CDM cosmology. 
-This simulations come in two versions: dark matter only (DMO) and
-baryonic physics including magetohydrodynamics (MHD).
+This simulations come in two versions: dark matter only and
+baryonic physics including magetohydrodynamics.
 A detailed description of the simulations and their disc properties
-can be founc in \citep{auriga}, here we summarize its main features.
+can be found in \citep{auriga}.
+Here we summarize its main features.
 
@@
 $2\times 10^{12}M_\odot$. 
-The cosmological parameters in these simulatins correspond to
+The cosmological parameters in these simulations correspond to
 $\Omega_m=0.307$, $\Omega_b=0.048$, $\Omega_\Lambda=0.693$ and a
@@
 and its stellar feedback.   
+\citep{arepo,2013MNRAS.432..176P}.
 The simulation also follows the formation and evolution of black holes
 together with the Active Galactic Nuclei feedback
-\citep{arepo,2013MNRAS.432..176P}.
 
@@
 \end{center}
-\caption{Changse of angle alignment of the dark
-  matter halo and stellar disc at two different radii ($R_{200}/16$
-  and $0.25R_{200}$) as a function of the baryonic disc properties
-  already explored in Figure \ref{fig:disc_correlations}.  
-  Figure \ref{fig:cumulative_alignment} showed that maximum alignment
-  occurs at $0.25R_{200}$ while in the inner regions ($R_{200}/16$)
-  considerable missalignments occurr.
- at different radii
- and baryonic disc properties. 
- The label with the $\rho$ value corresponds to the Spearman’s rank correlation coefficient. }
+\caption{Twisting in the halo-disc alingment as a function of the same
+  baryonic disc properties in Figure \ref{fig:disc_correlations}.
+  The label with the $\rho$ value corresponds to the Spearman's rank
+  correlation coefficient.
+  The line is the best linear minimum squares fit.
+  In this case the disc to total mass ratio does not correlate stronly
+  with the alignment twisting.
+  The gas density at the center and the disc optical radius still show
+  a strong correlation.}
 \label{fig:alignment_correlations}
 \end{figure*}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.45\textwidth]{triaxiality_observations.pdf}
-\end{center}
-\caption{Comparison of our results against 
-observational constraints for the 
-dark matter halo shape in the Milky Way by \citet{LM10} (LM10) and
-\citet{Bovy16} (BBFK16).   
-We find that  1/5 of the halos in the MHD  sample are consistent with
-the constraints by \citet{Bovy16}.
-In contrast, none of the halos in the MHD and DMO seems to be
-consistent with the results by \citet{LM10}.}
-\label{fig:observations}
-\end{figure}
 
@@
 
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.7\textwidth]{triaxiality_observations.pdf}
+\end{center}
+\caption{Comparison of our results against 
+observational constraints for the 
+dark matter halo shape in the Milky Way by \citet{LM10} (LM10) and
+\citet{Bovy16} (BBFK16).   
+We find that  1/5 of the halos in the MHD  sample are consistent with
+the constraints by \citet{Bovy16}.
+In contrast, none of the halos in the MHD and DMO seems to be
+consistent with the results by \citet{LM10}.}
+\label{fig:observations}
+\end{figure*}
+
 \section{Conclusions}

### 2019-07-21 Document/paper.tex
edit

@@
   simulations, the change is stronger towards the halo center.
-  Only a small fraction of the halos ($\sim 1/10$) presents the
+  Only a small fraction of the halos ($\sim 1/15$) presents the
   opposite trend of becoming more triaxial towards the center.}
@@
 
-The DM halo shape at a fixed radius is an estimate of either
-the isopotential or isodensity surfaces.  
+The DM halo shape is an estimate of either the isopotential or
+isodensity surfaces.   
 Observational inference models usually estimate the 
@@
 We start the calculations taking into account particles within a
-sphere of radius $R$ and then recharacterize the triaxial parameters
+sphere of radius $R_{\rm initial}$ and then recharacterize the
+triaxial parameters 
 by taking into account particles within an ellipsoid of semi-axes
@@
 $\sim 2$kpc and $R_{200}$, where  $R_{200}$ correspond to the radius
-enclosing a sphere with 200 times the critical density of the Universe.
-On average, over the 30 halos in the sample $R_{200}=230\pm 15$kpc. 
+computed enclosing a sphere with 200 times the critical density of the
+Universe. 
 In our results we express the radius as a fraction of $R_{200}$ in
-order to have a consistent radius scale across all halos.
+order to have a self-consistent dimensionless radius scale across all
+halos. 
+Given the small variance across halos, each dimensionless radius is associated with
+a physical value with a mean value and a standard deviation.
+For instance, over the 30 halos in the sample, the dimensionless
+radius $R_{200}$ corresponds to a physical distance of $230\pm 16$
+kpc.
 
@@
 
-\subsection{Radial trends}
+\subsection{Triaxiality}
 
@@
 all radii.
-These plots confirm the results already reported in the
-literature \citep{VeraCiro11}.
 
@@
 There all halos become rounder at all radii than its DMO
-counterpart.
+version.
 The lower panel in Figure \ref{fig:slices} can be directly compared to
 its MHD counterpart; there we observe how at large radii the halo
-becomes almost spherical. 
+becomes oblate and almost spherical. 
 The right panel in Figure \ref{fig:triaxiality_plane} shows the
 results for the 30 halos in the MHD sample.
-This time the bulk of the halos can be considered oblate and close to
-spherical.
 
@@
 
-The left panel of this Figure shows that in the DMO sample the
-triaxility has a median larger than $0.5$ at all radii, furthermore
-this median value increases as we move towards the inner part of the
+The left panel of Figure \ref{fig:triaxial_cumulative} shows that in
+the DMO sample the triaxility has a median larger than $2/3$ (a
+typical value that marks the transition from triaxiality to
+prolateness) at all radii. 
+Furthermore this median value increases as we move towards the inner part of the
 halo.
-The right panel shows the exact complementary picture in the MHD
-sampe.
-There the median triaxility is alwas smaller than $0.5$ and this
-triaxility is smaller as we move closer to the galactic disc.
+The right panel shows how the correlations in the MHD simulations go
+in the opposite direction with respect to DMO result.s
+There the median triaxility is alwas smaller than $1/3$ (a typical
+values that marks the transition from triaxility to prolateness) and this
+median value decreases as we move towards the inner part of the halo.
 
-To quantify to what extend the global effect of decreasing
-triaxility in MHD simulations compared to the DMO sample 
-holds for individual halos. 
-We compute $\Delta T\equiv T_{\rm MHD}-T_{\rm DMO}$ the difference between the
-triaxility in the MHD and the DMO simulation for each individual halo. 
+We now quantify this change in triaxility at the level of individual halos.
+We compute $\Delta T\equiv T_{\rm MHD}-T_{\rm DMO}$ to quantify the
+change between the triaxility in the MHD and the DMO simulation.
 Figure \label{fig:delta_triaxial_cumulative} shows the cumulative
@@
 Figure \label{fig:delta_triaxial_cumulative}.  
+From this Figure we observe that at $R_{200}$ all the halos have
+reduced its triaxility include baryonic physics.
+At smaller radii this general trend continues, although there is a
+small fraction ($\approx 1/15$) of halos that slightly increased their
+triaxility with MHD physics. 
+However, this small fraction correspond to halos that already were
+outliers in the DMO sample and had triaxilities around $1/3$,
+considerably lower than its parent sample.
 
-\subsection{Alignments with the stellar disc}
+\subsection{Halo-disc alignments}
 

### 2019-07-21 Document/paper.tex
edit

@@
 
-A common assumption in observational models of the MW DM halo is that
+A common assumption in dynamical models of the MW DM halo is that
 its minor axis is perfectly aligned with the stellar disc minor axis.
@@
 the galactic disc in simplified models of isolated galaxies, this
-might not hold in an explicit cosmological context. 
+might not perfectly hold in an explicit cosmological context. 
 To examine the degree of validity of this assumption we study in this
-section the alignment between the eigenvectors of the inertia tensor of
+subsection the alignment between the eigenvectors of the inertia tensor of
 stellar particles within $0.1R_{200}$ ($\sim 23\pm 2$ kpc) and the
 eigenvectors of the dark matter halo shape.
-All the measurements are done at $z=0$.
 

### 2019-07-21 Document/paper.tex
edit

@@
 
-The lower row in Figure \ref{fig:cumulative_alignment} shows the
-alignments with the halo in the MHD simulations. 
-This time the halo shape changes and twists at different radii.
-However around the radius of $0.25R_{200}$ there is an alignment
-almost perfect between the shapes of the stellar disc and the dark
-matter halo. 
-Above and below this radius there are halos with a lower degree of
-alignment.
-Across the three different alignments we measure we verify that the
-strongest one is indeed the one between the two minor axis.
+The upper row in Figure \ref{fig:cumulative_alignment} shows 
+the alignments between the major/intermediate/minor axis of the
+disk and the halo as a function of the dimensionless radius at which
+the halo shape was measured.
+The upper row shows the angle between the DMO halo and the stellar
+disk in the MHD simulation.
+This comparison help us to measure how the shape directions in the
+dark matter shells change with radius.
+For the bulk of the sample the lines are horizontal.
+Only two halos in the sample show a significant change in alignment in
+on the three shape axis.
 
-Statistically the strongest missalignment is found with the halo shape
-at a radius of $R_{200}/16\sim (14\pm1)$ kpc. 
-At this radius the mean angle and its standard deviation between the
-two minor axis is $18 \pm 21$ degrees, with one extreme case
-(\texttt{Au-4}) where the angle is close to $78$ degrees. 
-In contrast at $0.25 R_{200}$ the angle between the two axis is
-$2\pm 3$ degrees without any extreme outlier.
+The lower row in Figure \ref{fig:cumulative_alignment} shows th
+results for the MHD simulations.
+The most striking feature of this plot is that around the radius of
+$0.25R_{200}$ there is an almost perfect halo-disc alignment measured
+in three shape axis.
+Above and below this radius the degree of alignment changes.
+We find the strongest missalignments at a radius of $0.06R_{200}$ when
+the median and the standard deviation of the alignment angles between
+the minor/median/major axis are $18\pm18$, $25\pm22$ and $7\pm21$
+degrees, respectively;  at $0.25R_{200}$ these values drop to $2\pm3$,
+$2\pm4$ an $1\pm 3$ degrees, respectively
+
+This changing alignment as a function of radius can be seen as a
+twisting in the shape ellipsoids. 
+As we are dealing with oblate halos $b/a\approx 1$ and the
+directions corresponding to the medium and major axis could be subject
+to noise.
+For this reason, in order to better quantify the twisting for each
+halo we take the standard deviation of the angle between the two minor
+axis, which should be less succeptible to noise.
+With this measurement, twisting becomes a global property of the halo,
+as the standard deviation is measured over the different radii at
+which we have quantified the alignment.
+
+Figure \ref{fig:alignment_correlations} shows the correlation between
+twisting at the four different radii at which we have measured the
+alignments.
 

### 2019-07-21 Document/paper.tex
edit

@@
   Twisting does not correlate with triaxility in the same way at every
-  radii. The strongest correlation appears around $0.12R_{200}\approx
-  28\pm2$ kpc.} 
+  radii. The strongest correlation appears around $0.12R_{200}$ ($28\pm2$ kpc).} 
 \label{fig:alignment_correlations}
@@
 degrees, respectively;  at $0.25R_{200}$ these values drop to $2\pm3$,
-$2\pm4$ an $1\pm 3$ degrees, respectively
+$2\pm4$ and $1\pm 3$ degrees, respectively
 
@@
 alignments. 
+The median, mean vand standard deviation of the triaxiliy are $3$, $7$ and $8$
+degrees, respectively.
+The correlation between twisting and triaxility also changes with
+radius as measured by the Spearman's rank correlation coefficient.
+The largest correlation shows with the halo triaxility measured at
+$0.12R_{200}$. 
+The most important consequence of this changing degree in correlation
+is that twisting cannot only be explained by large triaxiality values
+and a possibly noisy determination of the shape axis.
 

### 2019-07-21 Document/paper.tex
edit

@@
 
-\section{Discussion}
-\label{sec:discussion}
+\subsection{Correlation with baryonic disc properties}
 
-The first effect that we put in evidence in this paper is the effect
-of baryons in producing rounder DM halos.
-
-The strength of the change depends on the numerical resolution, the
-method to resolve the hydrodynamics and the models describing star
-formation and stellar feedback \citep{Debattista08, Bryan13, Butsky16,
-  Chua19, Artale19}.  
-The key concept unifying these results is that the baryon distribution
-influences and correlates with the dark matter halo shape. 
-Here we find that the broad tendency is that massive stellar discs
-correlate with spherical dark matter distributions.
-
-In order to explore this idea in the Auriga simulations we quantify
-the correlation between halo shape with baryonic disc properties. 
+The presence of baryons produce rounder dark matter halos than its DMO
+counterpart.
+To better understand this relationship we quantify the correlation
+between halo shape with baryonic disc properties.  
 Looking into the measurements already reported by \cite{auriga} and
@@
 We find that the strongest correlations are found with the halo shape
-measured at radii smaller than $0.12R_{200}\sim 28$kpc, which 
-is close to the upper limit of the disc optical radius among our
-simulation sample. 
+measured at radii smaller than $0.12R_{200}$.
 The  trend is such that halos with large triaxiality correlate with
 high gas density and stellar discs with low mass and small size. 
-In turn, massive and large stellar discs within a low density gas
-environment correlate with low halo triaxiliaty.
+In turn, massive and large stellar discs within with low density of
+gas in its core correlate with low halo triaxiliaty.
+
+\section{Discussion}
+\label{sec:discussion}
+
+The first effect that we put in evidence in this paper is the effect
+of baryons in producing rounder DM halos.
+The strength of the change depends on the numerical resolution, the
+method to resolve the hydrodynamics and the models describing star
+formation and stellar feedback \citep{Debattista08, Bryan13, Butsky16,
+  Chua19, Artale19}.  
+The key concept unifying these results is that the baryon distribution
+influences and correlates with the dark matter halo shape. 
+Here we find that the broad tendency is that massive stellar discs
+correlate with spherical dark matter distributions.
 

### 2019-07-21 Document/paper.tex
edit

@@
 
+The halo shape also twists in the presence of baryons, as opposed to
+the situation in DMO simulations where the shape is coherent as a
+function of radius.
+In Figure \ref{fig:alignment_correlations} we show the correlation
+between twisting and the same baryonic properties that showd a high
+degree of correlation with the triaxility.
+In this case the disc to total ratio does not have a significant
+degree of correlation.
+Instead, the disc optical radius and the gas density at the core are
+the most correlated. 
+The correlation is such that extended stellar discs with a very low
+gas density at its core show the most coherent halo shapes.
+
 \section{Discussion}
@@
 correlate with spherical dark matter distributions.
-
-Our second results deals with the disc-halo shape alignment as a function of
-radius. 
-In concordance with previous results in DM only simulations we find
-that the shells of halo shape are well aligned at different radii.
-However, in the presences of baryons these shells twist as a function
-of radius.
-At a radius of $0.25R_{200}\approx 56$ kpc the alignment between the
-stellar disc and the dark matter halo is almost perfect and degrades
-at other radii. 
-This twisting effect, the change of disc-halo alignment as
-a function of radius, is robust across our sample of 30
-halos at all radii.
-However, its strenght is not the same for all galaxies and strongly
-correlates with halo triaxiality measured at $0.12R_{200}$.
 

### 2019-07-21 Document/paper.tex
edit

@@
   correlation coefficient.
-  The line is the best linear minimum squares fit.
+  The line is the best minimum squares fit to a line.
   The x-axis in the first column is the gas density at the center of
@@
   correlation coefficient.
-  The line is the best linear minimum squares fit.
+  The line is the best minimum squares fit to a line.
   In this case the disc to total mass ratio does not correlate stronly
@@
 
-Following the convergence criterion by \cite{VeraCiro11} we
-restrict the sampling of the ellipsoidal parameters to radii between
-$\sim 2$kpc and $R_{200}$, where  $R_{200}$ correspond to the radius
+Following the convergence criterion by \cite{VeraCiro11} in DM only simulations
+we restrict the measurement of the ellipsoidal parameters to radii
+between $2$kpc and $R_{200}$ where  $R_{200}$ corresponds to the radius
 computed enclosing a sphere with 200 times the critical density of the
 Universe. 
+This scale is similar to the gravitational smoothing lenght for
+stellar particles. 
+For this reason, in order to make the DM halo shape results comparable
+against stellar disc shape measurements, we report our DM halo shape
+results above $10$ kpc.
+For the shape of the stellar disk we include all stellar particles
+within a radius of $0.01R_{200}$, that is $\approx 23$kpc.
+
 In our results we express the radius as a fraction of $R_{200}$ in
@@
 of baryons in producing rounder DM halos.
-The strength of the change depends on the numerical resolution, the
-method to resolve the hydrodynamics and the models describing star
-formation and stellar feedback \citep{Debattista08, Bryan13, Butsky16,
-  Chua19, Artale19}.  
+This effect has been already widely reported in the literature.
+It has been found that the strength of the change depends on the
+numerical resolution, the method to resolve the hydrodynamics and the
+models describing star formation and stellar feedback
+\citep{Bailin05,Debattista08, Bryan13, Butsky16, Chua19, Artale19}.  
 The key concept unifying these results is that the baryon distribution
 influences and correlates with the dark matter halo shape. 
-Here we find that the broad tendency is that massive stellar discs
-correlate with spherical dark matter distributions.
+Indeed, as we presented in the previous section on the correlations
+with disc properties, we find that the broad tendency is that extended
+massive stellar discs correlate with spherical dark matter
+distributions.
 
-\cite{Bailin05} studied the disc halo alignmnent as a function of
-radius.
+In contrast, it is more difficult to put into a broader context our
+results on the halo-disc alignment.
+\cite{JingSuto02} reported a shell alignment twisting in their dark
+matter only simulations as measured in the direction changes of large
+and medium shape axis. 
+They only had three high resolution MW-like halos (with
+$\sim 10^{6}$ inside the virial radius) and could not make a
+statistical statement about the impact of this effect.
+However, they see the twisting as an artifact resulting from high values of the
+$b/a$ ratios that make the determination of the medium axis noisy.
+For that reason we measured the twisting using the minor axis
+alignments, however they do not report these alignments
+
+\cite{Bailin05} used seven hydrodinamical simulations studied the disc
+halo alignmnent as a function of radius.
+
 \cite{Gomez17} studied this in Auriga.
@@
 shells stop twisting.
-\cite{JingSuto02} also reported shell alignment twisting in their dark
-matter only simulations as measured in the direction changes of large
-and medium shape axis. 
-They only had three high resolution MW-like halos (with
-$\sim 10^{6}$ inside the virial radius) and could not make a
-statistical statement about the impact of this effect.
-However, they the twisting as an artifact resulting from high values of the
-$c/b$ ratios that make the determination of the medium axis boisy.
-Could then high triaxility values explain the twisting as a result of
-erratic axis directions? 
-If the triaxiality were the main culprit behind the twisting, the
-correlation between the two quantities should be constant at every
-radii.
+
 In Figure \ref{fig:alignment_correlations} we already showed that this

### 2019-07-21 Document/paper.tex
references

@@
 It has been found that the strength of the change depends on the
-numerical resolution, the method to resolve the hydrodynamics and the
+numerical resolution, the gas cooling implementation and the
 models describing star formation and stellar feedback
-\citep{Bailin05,Debattista08, Bryan13, Butsky16, Chua19, Artale19}.  
+\citep{Kazantzidis04,Bailin05,Debattista08, Bryan13, Butsky16, Chua19, Artale19}.  
 The key concept unifying these results is that the baryon distribution
@@
 
-In contrast, it is more difficult to put into a broader context our
-results on the halo-disc alignment.
+In contrast, there are fewer studies reporting on the halo-disc
+alignment as a function of radius.
 \cite{JingSuto02} reported a shell alignment twisting in their dark
@@
 For that reason we measured the twisting using the minor axis
-alignments, however they do not report these alignments
+alignments, however they do not report these alignments.
 
@@
 halo alignmnent as a function of radius.
+For radii smaller than $0.1R_{200}$ they find a strong alignment
+between the two minor axis of the halo and the disc. 
+For larger radii the angle between the components changes showing a
+weak correlation between the two components. 
+\cite{Debattista13} performed a study on the disc-halo aligment
+performing controled experiments on three different halos to study
+changes the evolutionary change that drive the minor axis in the disc
+and the halo to be aligned, their study by construction focuses only
+on radii around $0.1R_{200}$.
+Nevertheless, similarly to \cite{Bailin05}, they also report a strong
+alignment in the region where the disc dominated.
 
 \cite{Gomez17} studied this in Auriga.
-\cite{Debattista13} reported a similar twisting effect, but only at radii smaller
-than the disc radius. 
-At radii larger than the disc radius, they find, the dark matter
-shells stop twisting.
 

### 2019-07-21 Document/paper.tex
edit

@@
 alignment in the region where the disc dominated. 
-
-\cite{Gomez17} studied this in Auriga.
+In conclusion, the twisting in the dark matter halo shapes seems to be
+a feature already reported in the literature with smaller samples than
+the one we use here. 
+The strongest point of depart is that in our case the alignments do
+not grow stronger as one approached the disc.
+It is very likely that the detailed radial dependence of the twisting
+depends on the hydrodynamics and feedback implementations.
 

### 2019-07-21 Document/paper.tex
edit

@@
 
-In Figure \ref{fig:alignment_correlations} we already showed that this
-correlation strongly depends on radius, we conclude that high
-triaxiality values cannot be the full explanation.
-Furthermore the twisting happens in such a way that it allows an
-almost perfect alignment between the stellar disc at $0.1R{200}$ and
-the halo shape measured at $0.25R_{200}$
-
 We now use the results reported by \cite{LM10} and \cite{Bovy16}
@@
 
-Our Figure \label{fig:observations} shows an explicit comparison in
+Figure \ref{fig:observations} shows an explicit comparison in
 the $c/a$-$b/a$ plane of our results in MHD simulations against the
-results by LM10 and BBFK16.  
+results by \cite{LM10} and \cite{Bovy16}.
 We find six MHD halos with $b/a<0.93$ and $c/a>0.77$ that could be
-considered consistent with their shape constraints  by BBFK16, while
+considered consistent with their shape constraints  by \cite{Bovy16}, while
 only one outlier DMO halo is consistent with those constraints.
 In contrast, none of the simulated halos (MHD nor DMO) is consistent
-with the LM10 results. 
+with the results \cite{LM10}. 
 The change of triaxility with radius in our simulations cannot account
@@
 
-The results by LM10 could then place the dark matter halo of our Milky
-Way as an extreme outlier in the $\Lambda$ CDM model. 
-This extreme prolateness also correlates with the extreme
-triaxiality of the 11 classical satellites of the MW ($c/a\approx
-0.2$, and $b/a\approx0.9$) with an spatial distribution 
-also oriented perpendicular to the MW plane, another highly unusual
-feature in the $\Lambda$ CDM model \citep{2018MNRAS.478.5533F}.
+The results by \label{LM10} could then place the dark matter halo of our Milky
+Way as an extreme outlier in the $\Lambda$CDM model. 
+This extreme prolateness also correlates with the extreme triaxiality
+of the 11 classical satellites of the MW ($c/a\approx 0.2$, and
+$b/a\approx0.9$) measured at larger radii, with an spatial
+distribution  also oriented perpendicular to the MW plane, another
+highly unusual feature in the $\Lambda$CDM \citep{2018MNRAS.478.5533F}.
 
@@
 A more complete understading of the influence of baryons on the
-different properties we have measured will require two elements, at
-least. First, an study on how the halo and the disc co-evolved as a
+different properties we have measured will require at least two more elements.
+First, an study on how the halo and the disc co-evolved as a
 function of time. Second, a calibrating the effect of the cosmic web

### 2019-07-21 Document/paper.tex
edit

@@
 
-These two questions have been difficult to address because for a long
+These two questions have been challening to address because for a long
 time it was difficult to produce realistic galactic discs within the
-CDM context.
+CDM context \citep{1997ApJ...478...13N}.
 The success of such enterprise has been the result of high numerical
@@
 galactic disc resembling the Milky Way.
-Along the way numerical experiments show that the baryonic effects also impact
-the dark matter halo shape making the halo rounder than it otherwise
-be in a dark matter only simulation
+Along the way, many numerical experiments have also show that the baryonic
+effects also impact the dark matter halo shape making the halo rounder
+than it otherwise be in a dark matter only simulation
 \citep{Dubinski94,Debattista08,Kazantzidis10,Abadi10,Bryan13,Chua19,Artale19}. 
-High resolution simulations have also allowed detailed studies of the
-alignment between the stellar disc and the dark matter halo
-\citep{Bailin05,DeBuhr12,Debattista13,Gomez17}.
+But only few simulations have presented detailed results on the
+radial evolution of the alignment between the stellar disc and the
+dark matter halo \citep{Bailin05,Debattista13}.
 
 Observational constraints of the dark matter halo have been in
-tension during the last decade. 
+tension and rapidly evolving during the last decade. 
 One can find studies favoring prolate
@@
 
-In this paper we contribute to the debate by reporting measurements of
-the DM halo shape in MW type galaxies from state-of-the-art simulations from the
-Auriga project.
+In this paper we analyze the internal DM halo shape in thirty MW type
+galaxies from state-of-the-art simulations from the Auriga project.
 These simulations have large enough numerical resolution, and explicit
@@
 realistic MW discs.
+Futhermore, the relatively large number of simulated systems allows us
+to have a handle on the statistical significance of our results.
 This paper is structured as follows. 

### 2019-07-21 Document/paper.tex
zip

@@
 \citep{Dubinski94,Debattista08,Kazantzidis10,Abadi10,Bryan13,Chua19,Artale19}. 
-But only few simulations have presented detailed results on the
-radial evolution of the alignment between the stellar disc and the
-dark matter halo \citep{Bailin05,Debattista13}.
+But only few simulations have presented detailed results on another
+important aspect of the disc-halo relationship, namely, the radial
+evolution of the alignment between the stellar disc and the dark
+matter halo \citep{Bailin05,Debattista13}.
 
-Observational constraints of the dark matter halo have been in
-tension and rapidly evolving during the last decade. 
+Observational constraints of the dark matter halo
+have also been in tension and rapidly evolving during the last decade.  
 One can find studies favoring prolate

### 2019-08-01 Document/paper.tex
edits RP

@@
 \usepackage{amssymb}	% Extra maths symbols
-\usepackage{subfig}
 \usepackage{array}
@@
 \newcolumntype{?}{!{\vrule width 1pt}}
-\newcommand{\Msun}{\,{\rm Mpc}$_{\odot}$\,}
+\newcommand{\Msun}{\,{\rm M}$_{\odot}$\,}
 \newcommand{\Mpch}{\,{\rm Mpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
@@
   $z=0$ in the Auriga simulations} 
-\author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
-Jesus Prada,$^{1}$\thanks{E-mail: jd.prada1760@uniandes.edu.co}
-Jaime E. Forero-Romero,$^{1}$
-Volker Springel$^{2}$
-\\
+\author[Prada et al.]{
+\parbox[t]{\textwidth}{
+{Jesus Prada,$^{1}$\thanks{E-mail: jd.prada1760@uniandes.edu.co}}
+{Jaime E. Forero-Romero,$^{1}$}
+{Robert J. J. Grand,$^{2}$}
+{R\"udiger Pakmor,$^{2}$}
+{Volker Springel$^{2}$}
+}
+\\\\
 % List of institutions
@@
 We compare the results in full magnetohydrodynamics against dark
-matter only simulations. 
-We find a strong influence of baryons in making dark matter halos
-rounder at all radii compared to its dark matter only counterparts.
+matter only simulations and find a strong influence of baryons 
+in making dark matter haloes rounder at all radii compared to its dark 
+matter only counterparts.
 At distances $\lesssim 30$ kpc, rounder dark matter distributions
@@
 densities.  
-We measure the alignment between the halo and the stellar disc at
-different radii and find almost perfect alignment at
-$0.25R_{200}\sim56$ kpc.    
+We measure the alignment between the halo and the disc at
+different radii and find a high degree of alignment at all radii for most 
+of the galaxies.
 In some cases the alignment significantly changes as a function of
@@
 only nor with baryons) match the constrains derived from the
-Sagittarius stream favoring an oblate dark matter halo.
+Sagittarius stream that favor an oblate dark matter halo.
 \end{abstract}
@@
 
-Our physical picture of the Universe as a whole has be shaped by
+Our physical picture of the Universe as a whole has been shaped by
 accurate observations and modeling of our own Galaxy. 
-Explaining the matter budget and kinematical state of the Milky Way
-(MW) is  equivalent to figuring out its formation process in a
-cosmological context. 
-As a first approximation, the MW morphology and
-separation into global kinematically coherent components, such as its
-disc and bulge, can be used to support the  existence of a Dark Matter
-(DM) component to explain its dynamics around the solar neighborhood
+For instance, the study of the Milky Way (MW) morphology and its
+separation into global kinematic coherent components, such as its
+disc and bulge, has been used to support the existence of a Dark Matter (DM) component surrounding the Galaxy
 \citep{2000MNRAS.311..361O,2009PASJ...61..227S,2010JCAP...08..004C,2013ApJ...779..115B,Iocco15}. 
+In other words, explaining the matter budget and kinematic state of the MW also put constraints on the wider cosmological context that made possible its evolution.
 
-A more detailed description of the full three-dimensional MW
-gravitational potential is possible through the interpretation of 
-fossil records of stellar streams.
-These remanents, resulting from infalling globular clusters or
-satellite galaxies that got tidaly disrutpted by the gravitational
-potential of the Milky Way, allow in principle tighter constrains 
-on the shape of the dark matter halo in outter regions of our Galaxy
-\citep{1998ApJ...495..297J,1999MNRAS.307..495H, 1999MNRAS.307..877T}
-than dynamical measurements close to the solar neighborhodd.
+A detailed study of the full three-dimensional MW
+gravitational potential could constrain the properties of the DM halo surrounding our Galaxy and even help to pin down the nature of the DM particle.
+For instance, the study of fossil records of stellar streams resulting from infalling globular clusters or
+satellite galaxies that got tidally disrupted by the gravitational
+potential of the MW, could be translated into tight constrains 
+both on the shape of the dark matter halo in the outer regions of our Galaxy \citep{1998ApJ...495..297J,1999MNRAS.307..495H, 1999MNRAS.307..877T} and also bound the properties of dark matter substructures, which also depend on the microphysics of a given DM particle.
 
-The observational constraints on the gravitational potential shape can then
-be confronted against the expectations from different galaxy formation
-models in an explicit cosmological context.
-For instance, in the current dominant paradigm of Cold Dark Matter
+In any case, the observational constraints on the gravitational potential shape must be confronted against the expectations from different galaxy formation models in an explicit cosmological context.
+For instance, in the current paradigm of a Cold Dark Matter
 (CDM) dominated Universe galaxies are expected to be hosted by
-triaxial DM halos. To what extent the CDM expectations are born out by
-observations in our Galaxy? Can the MW's DM halo shape be considered
-typical or atypical in a cosmological context?
+triaxial DM halos. To what extent the CDM expectations are born out by observations in our Galaxy?
 
-These two questions have been challening to address because for a long
-time it was difficult to produce realistic galactic discs within the
-CDM context \citep{1997ApJ...478...13N}.
-The success of such enterprise has been the result of high numerical
-resolution and the understanding that baryonic effects such as stellar
-feedback and black hole feedback play an important role in forming a
-galactic disc resembling the Milky Way.
-Along the way, many numerical experiments have also show that the baryonic
-effects also impact the dark matter halo shape making the halo rounder
-than it otherwise be in a dark matter only simulation
+This question has been challenging to address because it has been difficult to produce realistic galactic discs in simulations within the CDM context \citep{1997ApJ...478...13N}.
+The success of such enterprise has been based on understanding how baryonic effects, such as stellar feedback and black hole feedback, play an important role in forming a galactic disc resembling the MW.
+Along the way, different numerical experiments have also shown that the baryonic
+effects also impact the DM halo shape making it rounder
+than it otherwise be in a DM-only simulation
 \citep{Dubinski94,Debattista08,Kazantzidis10,Abadi10,Bryan13,Chua19,Artale19}. 
-But only few simulations have presented detailed results on another
-important aspect of the disc-halo relationship, namely, the radial
-evolution of the alignment between the stellar disc and the dark
-matter halo \citep{Bailin05,Debattista13}.
+Another important aspect of the disc-halo relationship dynamics, namely, the radial evolution of the alignment between the stellar disc and the DM halo, has also been explored in some simulations \citep{Bailin05,Debattista13}.
 
@@
 realistic MW discs.
-Futhermore, the relatively large number of simulated systems allows us
+Furthermore, the relatively large number of simulated systems allows us
 to have a handle on the statistical significance of our results.
@@
 and 396 pc in physical coordinates afterwards.
-The gravitational softening lenght for gas cells changes with the mean
+The gravitational softening length for gas cells changes with the mean
 cell radius but is limited to be larger than the stellar softening
-lenght and 1850 pc physical. 
+lenght and 500 $h^{-1}$ pc comoving. 
 From now on we refer to the haloes simulated with baryonic physics as the
@@
 \begin{figure*}
-  \centering
-  \subfloat[DMO simulation. Shape at small
-    radius.]{\includegraphics[width=0.5\textwidth]{level4_DM_halo_24_2.png}}  
-  \hfill
-  \subfloat[DMO simulation. Shape at large
-    radius.]{\includegraphics[width=0.5\textwidth]{level4_DM_halo_24_4.png}}  
-  \hfill
-
-  \subfloat[MHD simulation. Shape at small
-    radius.]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_2.png}}  
-  \hfill
-  \subfloat[MHD simulation. Shape at large
-    radius.]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_4.png}}  
-  \hfill 
+\includegraphics[width=0.45\textwidth]{level4_DM_halo_24_2.png}
+\includegraphics[width=0.45\textwidth]{level4_DM_halo_24_4.png}
+\includegraphics[width=0.45\textwidth]{level4_MHD_halo_24_2.png}
+\includegraphics[width=0.45\textwidth]{level4_MHD_halo_24_4.png}
   \caption{DM density in logarithmic scale within a slice of one tenth
@@
 \begin{center}
-\subfloat[DMO simulations.]{\includegraphics[width=0.8\columnwidth]{Lvl_4_Triax_Plane_DM.pdf}}
-\subfloat[MHD simulations.]{\includegraphics[width=0.8\columnwidth]{Lvl_4_Triax_Plane_MHD.pdf}}
+\includegraphics[width=0.8\columnwidth]{Lvl_4_Triax_Plane_DM.pdf}
+\includegraphics[width=0.8\columnwidth]{Lvl_4_Triax_Plane_MHD.pdf}
 \end{center}
-\caption{Axial ratios for all simulated halos.
+\caption{\textbf{RP: Maybe add DMO and MHD directly to the two panels?} Axial ratios for all simulated halos.
   Left/right panel corresponds to DMO/MHD simulations, respectively.
@@
   Third, halos in MHD are rounder in the inner regions than in
-  the outskirts (opposite to the DMO trend).}
+  the outskirts (opposite to the DMO trend).
+\textbf{RP: is that last point really statistically the case?
+The average points that were in the plot before seemed to be consistent within scatter for the MHD run} }
   \label{fig:triaxiality_plane}
@@
 \begin{figure*}
-\subfloat[DMO simulations.]{\includegraphics[width=0.8\columnwidth]{triaxialiy_distro_DM.pdf}}
-\subfloat[MHD simulations.]{\includegraphics[width=0.8\columnwidth]{triaxialiy_distro_MHD.pdf}}
+\includegraphics[width=0.8\columnwidth]{triaxialiy_distro_DM.pdf}
+\includegraphics[width=0.8\columnwidth]{triaxialiy_distro_MHD.pdf}
 \caption{Triaxility cumulative distribution at five different radii.
@@
 \end{center}
-\caption{Angles between the principal axis of the dark matter halo
-  shape and the stellar disc shape as a function of the radius at
+\caption{\textbf{RP: I think the upper row that compares the shape of the halo from the DMO sim with the orientation of the disk in the MHD sim is hard to interpret.
+Maybe instead show in the first row the angle against a fixed axis (e.g.
+total angular momentum of the halo?)} Angles between the principal axis of the dark matter halo
+  shape and the angular momentum of the stellar disc 
+  as a function of the radius at
   which the halo shape directions are measured.
   Each panel compares the alignment of the corresponding
-  major/middle/minor axis.
+  major/middle/minor axis in the halo.
   Thin lines correspond to each one of the thirty halos in the sample
@@
   self-consistent comparison with the stellar discs. 
-  In this case the dark matter shells twists significantly in a
-  noticeable fraction of the haloes.
-  Interestingly, an almost perfect halo-disc alignment happens across
-  the sample at an intermediate radius of $0.25R_{200}$ ($56\pm
-  4$kpc). 
+  In this case the dark matter shells twists significantly in $1/5$ of the sample. For the remaining haloes the alignment is almost constant as a function of radius.
 }
@@
 \end{center}
-\caption{Twisting in the halo-disc alignment (measured as the standard deviation
-  of the alignment angles between two minor shape axis)
+\caption{Twisting in the halo-disc alignment (measured as the standard deviation of the alignment angles)
   as a function of the halo triaxialiy at the radius indicated
@@
   The line is the best minimum squares fit to a line.
-  In this case the disc to total mass ratio does not correlate stronly
-  with the alignment twisting.
+  In this case the disc to total mass ratio does not correlate with the alignment twisting
   The gas density at the center and the disc optical radius still show
-  a strong correlation.}
-\label{fig:alignment_correlations}
+  a strong correlation, albeit weaker than what they had with the triaxility.}
+\label{fig:alignment_correlations2}
 \end{figure*}
@@
 Furthermore, the density contours in thin shells are very sensitive to
-the presence of small satelites.  
+the presence of small satellites.  
 For this reason we measure the shape by taking
@@
 we restrict the measurement of the ellipsoidal parameters to radii
-between $2$kpc and $R_{200}$ where  $R_{200}$ corresponds to the radius
+between $2$ kpc and $R_{200}$ where  $R_{200}$ corresponds to the radius
 computed enclosing a sphere with 200 times the critical density of the
 Universe. 
-This scale is similar to the gravitational smoothing lenght for
+This scale is similar to the gravitational smoothing length for
 stellar particles. 
@@
 results above $10$ kpc.
-For the shape of the stellar disk we include all stellar particles
-within a radius of $0.01R_{200}$, that is $\approx 23$kpc.
+We characterize the stellar disk by measuring the angular momentum vector using the $10\%$ oldest stellar particles.
 
@@
 
-In the DMO sample we find that halos are rounder with increasing
-radius.
+In the DMO sample we find that halos are rounder with increasing radius.
 The upper panels in Figure \ref{fig:slices} illustrate this effect.
@@
 The left panel shows every halo in the $c/a$-$b/a$ plane at
-two different radii $R_{200}/8 (\sim 20$kpc$)$ and $R_{200}$. 
+two different radii $R_{200}/8 (\sim 20$kpc$)$ \textbf{RP: the plots says R200/16} and $R_{200}$. 
 The outer part of the halo is systematically rounder than its inner
@@
 in the opposite direction with respect to DMO result.s
-There the median triaxility is alwas smaller than $1/3$ (a typical
+There the median triaxility is always smaller than $1/3$ (a typical
 values that marks the transition from triaxility to prolateness) and this
@@
 change between the triaxility in the MHD and the DMO simulation.
-Figure \label{fig:delta_triaxial_cumulative} shows the cumulative
+Figure \ref{fig:delta_triaxial_cumulative} shows the cumulative
 distribution at the same radii as in
-Figure \label{fig:delta_triaxial_cumulative}.  
+Figure \ref{fig:delta_triaxial_cumulative}.  
 From this Figure we observe that at $R_{200}$ all the halos have
@@
 At smaller radii this general trend continues, although there is a
-small fraction ($\approx 1/15$) of halos that slightly increased their
+small fraction ($\approx 1/15$) \textbf{RP: just write 2 in out sample?} of halos that slightly increased their
 triaxility with MHD physics. 
@@
 A common assumption in dynamical models of the MW DM halo is that
-its minor axis is perfectly aligned with the stellar disc minor axis.
+its angular momentum is perfectly aligned with the stellar disc minor axis.
 Although it is a reasonable assumption to guarantee the stability of
@@
 To examine the degree of validity of this assumption we study in this
-subsection the alignment between the eigenvectors of the inertia tensor of
-stellar particles within $0.1R_{200}$ ($\sim 23\pm 2$ kpc) and the
+subsection the alignment between the stellar disc's angular momentum
 eigenvectors of the dark matter halo shape.
-
-In Figure \ref{fig:cumulative_alignment} we summarize our main results
-regarding these alignments with the halo shape measured at five
-different radii.
-The upper row shows the alignment of the halos in the DMO simulations
-with the stellar disc in the MHD simulations.
-The main objective of this measurement is to calibrate the radial
-evolution of the DM halo shape. 
-We find that the DM shape remains constant with radius.
 
@@
 the alignments between the major/intermediate/minor axis of the
-disk and the halo as a function of the dimensionless radius at which
-the halo shape was measured.
+halo and the disc angular momentum as a function of the dimensionless radius at which the halo shape was measured.
 The upper row shows the angle between the DMO halo and the stellar
@@
 For the bulk of the sample the lines are horizontal.
-Only two halos in the sample show a significant change in alignment in
-on the three shape axis.
+Only two halos show a significant change of more than 30 degrees across different radii.
 
-The lower row in Figure \ref{fig:cumulative_alignment} shows th
+The lower row in Figure \ref{fig:cumulative_alignment} shows the
 results for the MHD simulations.
-The most striking feature of this plot is that around the radius of
-$0.25R_{200}$ there is an almost perfect halo-disc alignment measured
-in three shape axis.
-Above and below this radius the degree of alignment changes.
-We find the strongest missalignments at a radius of $0.06R_{200}$ when
-the median and the standard deviation of the alignment angles between
-the minor/median/major axis are $18\pm18$, $25\pm22$ and $7\pm21$
-degrees, respectively;  at $0.25R_{200}$ these values drop to $2\pm3$,
-$2\pm4$ and $1\pm 3$ degrees, respectively
+The most striking feature of this plot is that most of the discs have their angular momentum aligned with the minor axis of the halo and perpendicular to the intermediate and major axis.
+The median and the standard deviation of the alignment angles with
+the major/median/minor axis are $82\pm14$, $82\pm16$ and $19\pm20$
+degrees, respectively.
 
-This changing alignment as a function of radius can be seen as a
-twisting in the shape ellipsoids. 
+In six halos the alignment changing significantly as a function of radius, this can be seen as a twisting in the shape ellipsoids. 
 As we are dealing with oblate halos $b/a\approx 1$ and the
@@
 For this reason, in order to better quantify the twisting for each
-halo we take the standard deviation of the angle between the two minor
-axis, which should be less succeptible to noise.
+halo we take the standard deviation of the angle with the minor
+axis, which should be less susceptible to noise.
 With this measurement, twisting becomes a global property of the halo,
@@
 alignments. 
-The median, mean vand standard deviation of the triaxiliy are $3$, $7$ and $8$
-degrees, respectively.
+The median, mean and standard deviation of the twisting are $2$, $6$ and $8$ degrees, respectively.
 The correlation between twisting and triaxility also changes with
@@
 
-The presence of baryons produce rounder dark matter halos than its DMO
+The presence of baryons produces rounder dark matter halos than its DMO
 counterpart.
@@
 Figure \ref{fig:disc_correlations} shows the correlations of
-these quantities with the triaxility at five diferent radii.
+these quantities with the triaxility at five different radii.
 We use the Spearmen's rank correlation coefficient to quantify the
@@
 
-The halo shape also twists in the presence of baryons, as opposed to
+In some cases, the halo shape also twists in the presence of baryons, as opposed to
 the situation in DMO simulations where the shape is coherent as a
 function of radius.
-In Figure \ref{fig:alignment_correlations} we show the correlation
-between twisting and the same baryonic properties that showd a high
+In Figure \ref{fig:alignment_correlations2} we show the correlation
+between twisting and the same baryonic properties that showed a high
 degree of correlation with the triaxility.
@@
 
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.6\textwidth]{triaxiality_observations.pdf}
+\end{center}
+\caption{Comparison of our results against 
+observational constraints for the 
+dark matter halo shape in the Milky Way by \citet{LM10} (LM10) and
+\citet{Bovy16} (BBFK16).   
+We find that  1/5 of the halos in the MHD  sample are consistent with
+the constraints by \citet{Bovy16}.
+In contrast, none of the halos in the MHD and DMO seems to be
+consistent with the results by \citet{LM10}.}
+\label{fig:observations}
+\end{figure*}
+
 The first effect that we put in evidence in this paper is the effect
@@
 models describing star formation and stellar feedback
-\citep{Kazantzidis04,Bailin05,Debattista08, Bryan13, Butsky16, Chua19, Artale19}.  
+\citep{Bailin05,Debattista08, Bryan13, Butsky16, Chua19, Artale19}.  
 The key concept unifying these results is that the baryon distribution
@@
 
-In contrast, there are fewer studies reporting on the halo-disc
-alignment as a function of radius.
-\cite{JingSuto02} reported a shell alignment twisting in their dark
-matter only simulations as measured in the direction changes of large
-and medium shape axis. 
-They only had three high resolution MW-like halos (with
-$\sim 10^{6}$ inside the virial radius) and could not make a
-statistical statement about the impact of this effect.
-However, they see the twisting as an artifact resulting from high values of the
-$b/a$ ratios that make the determination of the medium axis noisy.
-For that reason we measured the twisting using the minor axis
-alignments, however they do not report these alignments.
+% JEFR I've commented this part because the plots are showing the 
+% alignment with the disc angular momentum not shape. 
+% This part has to be adjusted accordingly.
+%\cite{JingSuto02} reported a shell alignment twisting in their dark
+%matter only simulations as measured in the direction changes of large
+%and medium shape axis. 
+%They only had three high resolution MW-like halos (with
+%$\sim 10^{6}$ inside the virial radius) and could not make a
+%statistical statement about the impact of this effect.
+%However, they see the twisting as an artifact resulting from high values %of the
+%$b/a$ ratios that make the determination of the medium axis noisy.
+%For that reason we measured the twisting using the minor axis
+%alignments, however they do not report these alignments.
 
-\cite{Bailin05} used seven hydrodinamical simulations studied the disc
-halo alignmnent as a function of radius.
-For radii smaller than $0.1R_{200}$ they find a strong alignment
-between the two minor axis of the halo and the disc. 
-For larger radii the angle between the components changes showing a
-weak correlation between the two components. 
-\cite{Debattista13} performed a study on the disc-halo aligment
-performing controled experiments on three different halos to study
-changes the evolutionary change that drive the minor axis in the disc
-and the halo to be aligned, their study by construction focuses only
-on radii around $0.1R_{200}$.
-Nevertheless, similarly to \cite{Bailin05}, they also report a strong
-alignment in the region where the disc dominated. 
-In conclusion, the twisting in the dark matter halo shapes seems to be
-a feature already reported in the literature with smaller samples than
-the one we use here. 
-The strongest point of depart is that in our case the alignments do
-not grow stronger as one approached the disc.
-It is very likely that the detailed radial dependence of the twisting
-depends on the hydrodynamics and feedback implementations.
+%\cite{Bailin05} used seven hydrodynamic simulations studied the disc
+%halo alignment as a function of radius.
+%For radii smaller than $0.1R_{200}$ they find a strong alignment
+%between the two minor axis of the halo and the disc. 
+%For larger radii the angle between the components changes showing a
+%weak correlation between the two components. 
+%\cite{Debattista13} performed a study on the disc-halo alignment
+%performing controlled experiments on three different halos to study
+%changes the evolutionary change that drive the minor axis in the disc
+%and the halo to be aligned, their study by construction focuses only
+%on radii around $0.1R_{200}$.
+%Nevertheless, similarly to \cite{Bailin05}, they also report a strong
+%alignment in the region where the disc dominated. 
+%In conclusion, the twisting in the dark matter halo shapes seems to be
+%a feature already reported in the literature with smaller samples than
+%the one we use here. 
+%The strongest point of depart is that in our case the alignments do
+%not grow stronger as one approached the disc.
+%It is very likely that the detailed radial dependence of the twisting
+%depends on the hydrodynamics and feedback implementations.
 
@@
 component. 
-They also translate ther results into a triaxiality of the density
+They also translate their results into a triaxiality of the density
 contours (that could be compared against our results)
@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.7\textwidth]{triaxiality_observations.pdf}
-\end{center}
-\caption{Comparison of our results against 
-observational constraints for the 
-dark matter halo shape in the Milky Way by \citet{LM10} (LM10) and
-\citet{Bovy16} (BBFK16).   
-We find that  1/5 of the halos in the MHD  sample are consistent with
-the constraints by \citet{Bovy16}.
-In contrast, none of the halos in the MHD and DMO seems to be
-consistent with the results by \citet{LM10}.}
-\label{fig:observations}
-\end{figure*}
-
 \section{Conclusions}
@@
 
-We also measured the shape alignment of the halo with the stellar
-disc at different radii.
-At a radius of $0.25R_{200}$ the alignment is almost perfect and
-degrades at smaller and larger distances.
-In some halos the alignment betwen the stellar disc and dark matter
-halo changes noticeably with radius. 
+We also measured the alignment of the halo with the stellar disc's angular momentum at different radii.
+For the majority of the sample the angular momentum is strongly aligned with the minor axis of the halo at all measured radii.
+However, in some halos the alignment changes noticeably with radius. 
 This alignment evolution implies a radial twisting between the ellipsoids
@@
 We quantify this twist with the standard deviation of the angle
-between the two minor axis at radii below $\leq 0.5R_{200}$ and find
-that the twisting strongly correlates with the disc size and the core
-gas mass density, there is only a weak correlation with the disc to
-total mass ratio.
+between the angular momentum and the halo minor axis at radii below $\leq 0.5R_{200}$ and find that higher gas densities correlate with larger twisting values.
 
@@
 The constraints are at two different radii and come from different
-observatinal tracers. 
+observational tracers. 
 We find that $20\%$ halos in the MHD simulations are consistent with
@@
 
-A more complete understading of the influence of baryons on the
+A more complete understanding of the influence of baryons on the
 different properties we have measured will require at least two more elements.
@@
 function of time. Second, a calibrating the effect of the cosmic web
-(both dark matter and gaseous) on any evoluionary trend
+(both dark matter and gaseous) on any evolutionary trend
 \citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G} 

### 2019-08-02 Document/paper.tex
new plot
tables

@@
 \label{fig:slices}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=0.9\textwidth]{shape_resolution.pdf}
+\caption{A}
+\label{fig:resolution}
 \end{figure*}
@@
 
+\begin{table*}
+  \centering 
+  \begin{tabular}{r r r r r r r r r r r}
+  \hline\hline
+  Halo & $(b/a)_{16}$ & $(c/a)_{16}$& $(b/a)_{8}$ & $(c/a)_{8}$& $(b/a)_{4}$ & $(c/a)_{4}$& $(b/a)_{2}$ & $(c/a)_{2}$& $(b/a)_{1}$ & $(c/a)_{1}$ \\
+  \hline
+Au-1 & 0.94 & 0.65 & 0.96 & 0.66 & 0.96 & 0.70 & 0.92 & 0.68 & 0.91 & 0.67\\
+Au-2 & 0.93 & 0.61 & 0.95 & 0.58 & 0.96 & 0.61 & 0.96 & 0.65 & 0.88 & 0.65\\
+Au-3 & 0.97 & 0.66 & 0.96 & 0.66 & 0.94 & 0.70 & 0.93 & 0.76 & 0.94 & 0.79\\
+Au-4 & 0.88 & 0.77 & 0.82 & 0.79 & 0.80 & 0.76 & 0.85 & 0.79 & 0.83 & 0.76\\
+Au-5 & 0.97 & 0.79 & 0.94 & 0.80 & 0.92 & 0.81 & 0.94 & 0.82 & 0.94 & 0.81\\
+Au-6 & 0.98 & 0.60 & 0.96 & 0.60 & 0.92 & 0.63 & 0.86 & 0.63 & 0.78 & 0.61\\
+Au-7 & 0.95 & 0.66 & 0.95 & 0.66 & 0.97 & 0.68 & 0.97 & 0.69 & 0.96 & 0.70\\
+Au-8 & 0.99 & 0.59 & 0.97 & 0.62 & 0.92 & 0.66 & 0.76 & 0.57 & 0.83 & 0.58\\
+Au-9 & 0.94 & 0.75 & 0.93 & 0.73 & 0.92 & 0.73 & 0.93 & 0.79 & 0.92 & 0.82\\
+Au-10 & 0.95 & 0.85 & 0.94 & 0.85 & 0.93 & 0.85 & 0.92 & 0.82 & 0.91 & 0.80\\
+Au-11 & 0.54 & 0.49 & 0.55 & 0.48 & 0.61 & 0.53 & 0.60 & 0.53 & 0.62 & 0.57\\
+Au-12 & 0.95 & 0.77 & 0.88 & 0.81 & 0.90 & 0.84 & 0.92 & 0.81 & 0.95 & 0.82\\
+Au-13 & 0.95 & 0.88 & 0.96 & 0.88 & 0.98 & 0.82 & 0.94 & 0.76 & 0.82 & 0.62\\
+Au-14 & 0.95 & 0.75 & 0.93 & 0.79 & 0.91 & 0.80 & 0.91 & 0.79 & 0.93 & 0.81\\
+Au-15 & 0.99 & 0.67 & 0.98 & 0.75 & 0.94 & 0.79 & 0.93 & 0.81 & 0.88 & 0.76\\
+Au-16 & 0.99 & 0.69 & 0.99 & 0.70 & 0.99 & 0.74 & 0.98 & 0.76 & 0.99 & 0.99\\
+Au-17 & 0.96 & 0.79 & 0.96 & 0.80 & 0.97 & 0.82 & 0.96 & 0.83 & 0.96 & 0.87\\
+Au-18 & 0.93 & 0.76 & 0.92 & 0.74 & 0.86 & 0.72 & 0.81 & 0.71 & 0.74 & 0.66\\
+Au-19 & 0.95 & 0.67 & 0.91 & 0.63 & 0.89 & 0.63 & 0.83 & 0.64 & 0.85 & 0.69\\
+Au-20 & 0.81 & 0.58 & 0.91 & 0.64 & 0.95 & 0.71 & 0.97 & 0.78 & 0.86 & 0.77\\
+Au-21 & 0.98 & 0.74 & 0.97 & 0.82 & 0.97 & 0.87 & 0.99 & 0.88 & 0.99 & 0.99\\
+Au-22 & 0.96 & 0.84 & 0.93 & 0.84 & 0.93 & 0.85 & 0.95 & 0.87 & 0.97 & 0.88\\
+Au-23 & 0.94 & 0.65 & 0.96 & 0.64 & 0.94 & 0.65 & 0.92 & 0.69 & 0.93 & 0.74\\
+Au-24 & 0.99 & 0.67 & 1.00 & 0.63 & 0.99 & 0.65 & 0.97 & 0.68 & 0.98 & 0.70\\
+Au-25 & 0.97 & 0.71 & 0.96 & 0.73 & 0.86 & 0.74 & 0.67 & 0.64 & 0.71 & 0.67\\
+Au-26 & 0.96 & 0.76 & 0.97 & 0.73 & 0.97 & 0.70 & 0.99 & 0.68 & 0.97 & 0.67\\
+Au-27 & 0.98 & 0.73 & 0.97 & 0.75 & 0.97 & 0.79 & 0.96 & 0.79 & 0.95 & 0.77\\
+Au-28 & 0.98 & 0.82 & 0.94 & 0.77 & 0.88 & 0.73 & 0.86 & 0.74 & 0.93 & 0.75\\
+Au-29 & 0.91 & 0.81 & 0.89 & 0.72 & 0.87 & 0.69 & 0.84 & 0.68 & 0.85 & 0.69\\
+Au-30 & 0.89 & 0.73 & 0.78 & 0.64 & 0.69 & 0.53 & 0.80 & 0.58 & 0.91 & 0.63\\
+  \hline\hline
+  \end{tabular}
+  \label{tab}
+  \caption{Magnetic field properties of the Auriga galaxies at $z=0$. For general properties of the disks.}
+\end{table*}
+
+\begin{table*}
+  \centering 
+  \begin{tabular}{c c c c c c c c c c c}
+  \hline\hline
+  Halo & $(b/a)_{16}$ & $(c/a)_{16}$& $(b/a)_{8}$ & $(c/a)_{8}$& $(b/a)_{4}$ & $(c/a)_{4}$& $(b/a)_{2}$ & $(c/a)_{2}$& $(b/a)_{1}$ & $(c/a)_{1}$ \\
+  \hline
+Au-1 & 0.48 & 0.41 & 0.52 & 0.44 & 0.59 & 0.48 & 0.66 & 0.53 & 0.72 & 0.55\\
+Au-2 & 0.66 & 0.47 & 0.72 & 0.49 & 0.76 & 0.51 & 0.80 & 0.54 & 0.79 & 0.55\\
+Au-3 & 0.56 & 0.42 & 0.61 & 0.47 & 0.70 & 0.55 & 0.79 & 0.65 & 0.85 & 0.72\\
+Au-4 & 0.42 & 0.35 & 0.47 & 0.40 & 0.49 & 0.43 & 0.55 & 0.49 & 0.59 & 0.52\\
+Au-5 & 0.49 & 0.41 & 0.53 & 0.47 & 0.56 & 0.51 & 0.59 & 0.56 & 0.66 & 0.59\\
+Au-6 & 0.56 & 0.46 & 0.58 & 0.46 & 0.61 & 0.49 & 0.62 & 0.51 & 0.65 & 0.54\\
+Au-7 & 0.46 & 0.37 & 0.45 & 0.37 & 0.51 & 0.40 & 0.55 & 0.41 & 0.62 & 0.46\\
+Au-8 & 0.75 & 0.47 & 0.84 & 0.53 & 0.85 & 0.58 & 0.76 & 0.54 & 0.82 & 0.55\\
+Au-9 & 0.49 & 0.40 & 0.52 & 0.43 & 0.54 & 0.45 & 0.60 & 0.52 & 0.65 & 0.60\\
+Au-10 & 0.62 & 0.51 & 0.61 & 0.50 & 0.58 & 0.49 & 0.60 & 0.53 & 0.65 & 0.59\\
+Au-11 & 0.47 & 0.37 & 0.36 & 0.29 & 0.32 & 0.28 & 0.41 & 0.37 & 0.47 & 0.45\\
+Au-12 & 0.66 & 0.53 & 0.76 & 0.59 & 0.83 & 0.66 & 0.88 & 0.68 & 0.94 & 0.71\\
+Au-13 & 0.60 & 0.52 & 0.61 & 0.53 & 0.64 & 0.54 & 0.70 & 0.56 & 0.73 & 0.54\\
+Au-14 & 0.97 & 0.67 & 0.95 & 0.66 & 0.90 & 0.64 & 0.89 & 0.69 & 0.87 & 0.75\\
+Au-15 & 0.61 & 0.42 & 0.65 & 0.48 & 0.68 & 0.52 & 0.66 & 0.50 & 0.70 & 0.54\\
+Au-16 & 0.64 & 0.57 & 0.73 & 0.57 & 0.84 & 0.58 & 0.87 & 0.62 & 0.88 & 0.63\\
+Au-17 & 0.98 & 0.79 & 0.98 & 0.83 & 0.95 & 0.84 & 0.91 & 0.81 & 0.93 & 0.87\\
+Au-18 & 0.56 & 0.55 & 0.57 & 0.55 & 0.60 & 0.57 & 0.64 & 0.59 & 0.62 & 0.56\\
+Au-19 & 0.58 & 0.51 & 0.59 & 0.50 & 0.65 & 0.54 & 0.73 & 0.61 & 0.80 & 0.70\\
+Au-20 & 0.61 & 0.44 & 0.68 & 0.48 & 0.72 & 0.51 & 0.76 & 0.59 & 0.81 & 0.70\\
+Au-21 & 0.67 & 0.50 & 0.75 & 0.50 & 0.81 & 0.61 & 0.80 & 0.66 & 0.74 & 0.64\\
+Au-22 & 0.68 & 0.56 & 0.71 & 0.59 & 0.77 & 0.63 & 0.82 & 0.71 & 0.83 & 0.78\\
+Au-23 & 0.54 & 0.41 & 0.58 & 0.44 & 0.62 & 0.49 & 0.70 & 0.57 & 0.77 & 0.66\\
+Au-24 & 0.54 & 0.44 & 0.57 & 0.47 & 0.59 & 0.49 & 0.66 & 0.55 & 0.75 & 0.66\\
+Au-25 & 0.59 & 0.56 & 0.66 & 0.65 & 0.71 & 0.66 & 0.62 & 0.55 & 0.69 & 0.61\\
+Au-26 & 0.52 & 0.41 & 0.58 & 0.43 & 0.65 & 0.43 & 0.73 & 0.47 & 0.75 & 0.51\\
+Au-27 & 0.53 & 0.45 & 0.61 & 0.51 & 0.68 & 0.56 & 0.76 & 0.62 & 0.84 & 0.64\\
+Au-28 & 0.49 & 0.42 & 0.49 & 0.44 & 0.56 & 0.48 & 0.64 & 0.52 & 0.74 & 0.58\\
+Au-29 & 0.50 & 0.40 & 0.56 & 0.45 & 0.61 & 0.48 & 0.69 & 0.54 & 0.72 & 0.60\\
+Au-30 & 0.62 & 0.44 & 0.77 & 0.54 & 0.87 & 0.58 & 0.85 & 0.58 & 0.75 & 0.53\\
+  \hline\hline
+  \end{tabular}
+  \label{tab}
+  \caption{Magnetic field properties of the Auriga galaxies at $z=0$. For general properties of the disks.}
+\end{table*}
+
 \end{document}

### 2019-08-02 Document/paper.tex
edit

@@
 \end{center}
-\caption{\textbf{RP: Maybe add DMO and MHD directly to the two panels?} Axial ratios for all simulated halos.
+\caption{Axial ratios for all simulated halos.
   Left/right panel corresponds to DMO/MHD simulations, respectively.
@@
 The left panel shows every halo in the $c/a$-$b/a$ plane at
-two different radii $R_{200}/8 (\sim 20$kpc$)$ \textbf{RP: the plots says R200/16} and $R_{200}$. 
+two different radii $R_{200}/16 (\sim 20$kpc$)$ and $R_{200}$. 
 The outer part of the halo is systematically rounder than its inner
@@
 reduced its triaxility include baryonic physics.
-At smaller radii this general trend continues, although there is a
-small fraction ($\approx 1/15$) \textbf{RP: just write 2 in out sample?} of halos that slightly increased their
-triaxility with MHD physics. 
+At smaller radii this general trend continues, although 2 haloes (Au-11 and Au-17) 
+in our sample increased their triaxility with MHD physics. 
 However, this small fraction correspond to halos that already were
@@
   \centering 
-  \begin{tabular}{r r r r r r r r r r r}
+  \begin{tabular}{c c c c c c c c c c c}
   \hline\hline

### 2019-08-02 Document/paper.tex
edit

@@
   Triangles (squares) represent the measurements at $R_{200}/16$
-  ($R_{200}$) that correspond to physical distances of $14\pm 1$ kpc
-  ($230\pm 15$ kpc).
+  ($R_{200}$) that correspond to physical distances of $\approx14$ kpc
+  ($\approx 230$ kpc).
   Here we visualize three main population trends.
@@
   than in the inner part.
-  Second, halos in MHD are rounder than its DMO counterparts.
-  Third, halos in MHD are rounder in the inner regions than in
+  Second, halos in MHD are rounder in the inner regions than in
   the outskirts (opposite to the DMO trend). 
-\textbf{RP: is that last point really statistically the case?
-The average points that were in the plot before seemed to be consistent within scatter for the MHD run} }
+  Third, halos in MHD are rounder than its DMO counterparts.
+  The first and second points are claryfied in Figure
+  \ref{fig:triaxial_cumulative} through the cumulative triaxility
+  distributions, 
+  while the third trend is shown in Figure
+  \ref{fig:delta_triaxial_cumulative} through the cumulative
+  distribution in the triaxility changes between MHD and DMO at all
+  radii.}
   \label{fig:triaxiality_plane}
@@
 There we see a highly ellipsoidal halo shape at radii $\sim 3$kpc
-that becomes less triaxial at $\sim 50$ kpc.
+that becomes less triaxial at $\approx 50$ kpc.
 
@@
 The left panel shows every halo in the $c/a$-$b/a$ plane at
-two different radii $R_{200}/16 (\sim 20$kpc$)$ and $R_{200}$. 
+two different radii $R_{200}/16$ $(\approx 14$kpc$)$ and $R_{200}$. 
 The outer part of the halo is systematically rounder than its inner
@@
   \hline
+Au-1 & 0.48 & 0.41 & 0.52 & 0.44 & 0.59 & 0.48 & 0.66 & 0.53 & 0.72 & 0.55\\
+Au-2 & 0.66 & 0.47 & 0.72 & 0.49 & 0.76 & 0.51 & 0.80 & 0.54 & 0.79 & 0.55\\
+Au-3 & 0.56 & 0.42 & 0.61 & 0.47 & 0.70 & 0.55 & 0.79 & 0.65 & 0.85 & 0.72\\
+Au-4 & 0.42 & 0.35 & 0.47 & 0.40 & 0.49 & 0.43 & 0.55 & 0.49 & 0.59 & 0.52\\
+Au-5 & 0.49 & 0.41 & 0.53 & 0.47 & 0.56 & 0.51 & 0.59 & 0.56 & 0.66 & 0.59\\
+Au-6 & 0.56 & 0.46 & 0.58 & 0.46 & 0.61 & 0.49 & 0.62 & 0.51 & 0.65 & 0.54\\
+Au-7 & 0.46 & 0.37 & 0.45 & 0.37 & 0.51 & 0.40 & 0.55 & 0.41 & 0.62 & 0.46\\
+Au-8 & 0.75 & 0.47 & 0.84 & 0.53 & 0.85 & 0.58 & 0.76 & 0.54 & 0.82 & 0.55\\
+Au-9 & 0.49 & 0.40 & 0.52 & 0.43 & 0.54 & 0.45 & 0.60 & 0.52 & 0.65 & 0.60\\
+Au-10 & 0.62 & 0.51 & 0.61 & 0.50 & 0.58 & 0.49 & 0.60 & 0.53 & 0.65 & 0.59\\
+Au-11 & 0.47 & 0.37 & 0.36 & 0.29 & 0.32 & 0.28 & 0.41 & 0.37 & 0.47 & 0.45\\
+Au-12 & 0.66 & 0.53 & 0.76 & 0.59 & 0.83 & 0.66 & 0.88 & 0.68 & 0.94 & 0.71\\
+Au-13 & 0.60 & 0.52 & 0.61 & 0.53 & 0.64 & 0.54 & 0.70 & 0.56 & 0.73 & 0.54\\
+Au-14 & 0.97 & 0.67 & 0.95 & 0.66 & 0.90 & 0.64 & 0.89 & 0.69 & 0.87 & 0.75\\
+Au-15 & 0.61 & 0.42 & 0.65 & 0.48 & 0.68 & 0.52 & 0.66 & 0.50 & 0.70 & 0.54\\
+Au-16 & 0.64 & 0.57 & 0.73 & 0.57 & 0.84 & 0.58 & 0.87 & 0.62 & 0.88 & 0.63\\
+Au-17 & 0.98 & 0.79 & 0.98 & 0.83 & 0.95 & 0.84 & 0.91 & 0.81 & 0.93 & 0.87\\
+Au-18 & 0.56 & 0.55 & 0.57 & 0.55 & 0.60 & 0.57 & 0.64 & 0.59 & 0.62 & 0.56\\
+Au-19 & 0.58 & 0.51 & 0.59 & 0.50 & 0.65 & 0.54 & 0.73 & 0.61 & 0.80 & 0.70\\
+Au-20 & 0.61 & 0.44 & 0.68 & 0.48 & 0.72 & 0.51 & 0.76 & 0.59 & 0.81 & 0.70\\
+Au-21 & 0.67 & 0.50 & 0.75 & 0.50 & 0.81 & 0.61 & 0.80 & 0.66 & 0.74 & 0.64\\
+Au-22 & 0.68 & 0.56 & 0.71 & 0.59 & 0.77 & 0.63 & 0.82 & 0.71 & 0.83 & 0.78\\
+Au-23 & 0.54 & 0.41 & 0.58 & 0.44 & 0.62 & 0.49 & 0.70 & 0.57 & 0.77 & 0.66\\
+Au-24 & 0.54 & 0.44 & 0.57 & 0.47 & 0.59 & 0.49 & 0.66 & 0.55 & 0.75 & 0.66\\
+Au-25 & 0.59 & 0.56 & 0.66 & 0.65 & 0.71 & 0.66 & 0.62 & 0.55 & 0.69 & 0.61\\
+Au-26 & 0.52 & 0.41 & 0.58 & 0.43 & 0.65 & 0.43 & 0.73 & 0.47 & 0.75 & 0.51\\
+Au-27 & 0.53 & 0.45 & 0.61 & 0.51 & 0.68 & 0.56 & 0.76 & 0.62 & 0.84 & 0.64\\
+Au-28 & 0.49 & 0.42 & 0.49 & 0.44 & 0.56 & 0.48 & 0.64 & 0.52 & 0.74 & 0.58\\
+Au-29 & 0.50 & 0.40 & 0.56 & 0.45 & 0.61 & 0.48 & 0.69 & 0.54 & 0.72 & 0.60\\
+Au-30 & 0.62 & 0.44 & 0.77 & 0.54 & 0.87 & 0.58 & 0.85 & 0.58 & 0.75 & 0.53\\
+  \hline\hline
+  \end{tabular}
+  \label{table:DMO}
+  \caption{Magnetic field properties of the Auriga galaxies at $z=0$. For general properties of the disks.}
+\end{table*}
+
+\begin{table*}
+  \centering 
+  \begin{tabular}{c c c c c c c c c c c}
+  \hline\hline
+  Halo & $(b/a)_{16}$ & $(c/a)_{16}$& $(b/a)_{8}$ & $(c/a)_{8}$& $(b/a)_{4}$ & $(c/a)_{4}$& $(b/a)_{2}$ & $(c/a)_{2}$& $(b/a)_{1}$ & $(c/a)_{1}$ \\
+  \hline
 Au-1 & 0.94 & 0.65 & 0.96 & 0.66 & 0.96 & 0.70 & 0.92 & 0.68 & 0.91 & 0.67\\
@@
   \end{tabular}
-  \label{tab}
-  \caption{Magnetic field properties of the Auriga galaxies at $z=0$. For general properties of the disks.}
-\end{table*}
-
-\begin{table*}
-  \centering 
-  \begin{tabular}{c c c c c c c c c c c}
-  \hline\hline
-  Halo & $(b/a)_{16}$ & $(c/a)_{16}$& $(b/a)_{8}$ & $(c/a)_{8}$& $(b/a)_{4}$ & $(c/a)_{4}$& $(b/a)_{2}$ & $(c/a)_{2}$& $(b/a)_{1}$ & $(c/a)_{1}$ \\
-  \hline
-Au-1 & 0.48 & 0.41 & 0.52 & 0.44 & 0.59 & 0.48 & 0.66 & 0.53 & 0.72 & 0.55\\
-Au-2 & 0.66 & 0.47 & 0.72 & 0.49 & 0.76 & 0.51 & 0.80 & 0.54 & 0.79 & 0.55\\
-Au-3 & 0.56 & 0.42 & 0.61 & 0.47 & 0.70 & 0.55 & 0.79 & 0.65 & 0.85 & 0.72\\
-Au-4 & 0.42 & 0.35 & 0.47 & 0.40 & 0.49 & 0.43 & 0.55 & 0.49 & 0.59 & 0.52\\
-Au-5 & 0.49 & 0.41 & 0.53 & 0.47 & 0.56 & 0.51 & 0.59 & 0.56 & 0.66 & 0.59\\
-Au-6 & 0.56 & 0.46 & 0.58 & 0.46 & 0.61 & 0.49 & 0.62 & 0.51 & 0.65 & 0.54\\
-Au-7 & 0.46 & 0.37 & 0.45 & 0.37 & 0.51 & 0.40 & 0.55 & 0.41 & 0.62 & 0.46\\
-Au-8 & 0.75 & 0.47 & 0.84 & 0.53 & 0.85 & 0.58 & 0.76 & 0.54 & 0.82 & 0.55\\
-Au-9 & 0.49 & 0.40 & 0.52 & 0.43 & 0.54 & 0.45 & 0.60 & 0.52 & 0.65 & 0.60\\
-Au-10 & 0.62 & 0.51 & 0.61 & 0.50 & 0.58 & 0.49 & 0.60 & 0.53 & 0.65 & 0.59\\
-Au-11 & 0.47 & 0.37 & 0.36 & 0.29 & 0.32 & 0.28 & 0.41 & 0.37 & 0.47 & 0.45\\
-Au-12 & 0.66 & 0.53 & 0.76 & 0.59 & 0.83 & 0.66 & 0.88 & 0.68 & 0.94 & 0.71\\
-Au-13 & 0.60 & 0.52 & 0.61 & 0.53 & 0.64 & 0.54 & 0.70 & 0.56 & 0.73 & 0.54\\
-Au-14 & 0.97 & 0.67 & 0.95 & 0.66 & 0.90 & 0.64 & 0.89 & 0.69 & 0.87 & 0.75\\
-Au-15 & 0.61 & 0.42 & 0.65 & 0.48 & 0.68 & 0.52 & 0.66 & 0.50 & 0.70 & 0.54\\
-Au-16 & 0.64 & 0.57 & 0.73 & 0.57 & 0.84 & 0.58 & 0.87 & 0.62 & 0.88 & 0.63\\
-Au-17 & 0.98 & 0.79 & 0.98 & 0.83 & 0.95 & 0.84 & 0.91 & 0.81 & 0.93 & 0.87\\
-Au-18 & 0.56 & 0.55 & 0.57 & 0.55 & 0.60 & 0.57 & 0.64 & 0.59 & 0.62 & 0.56\\
-Au-19 & 0.58 & 0.51 & 0.59 & 0.50 & 0.65 & 0.54 & 0.73 & 0.61 & 0.80 & 0.70\\
-Au-20 & 0.61 & 0.44 & 0.68 & 0.48 & 0.72 & 0.51 & 0.76 & 0.59 & 0.81 & 0.70\\
-Au-21 & 0.67 & 0.50 & 0.75 & 0.50 & 0.81 & 0.61 & 0.80 & 0.66 & 0.74 & 0.64\\
-Au-22 & 0.68 & 0.56 & 0.71 & 0.59 & 0.77 & 0.63 & 0.82 & 0.71 & 0.83 & 0.78\\
-Au-23 & 0.54 & 0.41 & 0.58 & 0.44 & 0.62 & 0.49 & 0.70 & 0.57 & 0.77 & 0.66\\
-Au-24 & 0.54 & 0.44 & 0.57 & 0.47 & 0.59 & 0.49 & 0.66 & 0.55 & 0.75 & 0.66\\
-Au-25 & 0.59 & 0.56 & 0.66 & 0.65 & 0.71 & 0.66 & 0.62 & 0.55 & 0.69 & 0.61\\
-Au-26 & 0.52 & 0.41 & 0.58 & 0.43 & 0.65 & 0.43 & 0.73 & 0.47 & 0.75 & 0.51\\
-Au-27 & 0.53 & 0.45 & 0.61 & 0.51 & 0.68 & 0.56 & 0.76 & 0.62 & 0.84 & 0.64\\
-Au-28 & 0.49 & 0.42 & 0.49 & 0.44 & 0.56 & 0.48 & 0.64 & 0.52 & 0.74 & 0.58\\
-Au-29 & 0.50 & 0.40 & 0.56 & 0.45 & 0.61 & 0.48 & 0.69 & 0.54 & 0.72 & 0.60\\
-Au-30 & 0.62 & 0.44 & 0.77 & 0.54 & 0.87 & 0.58 & 0.85 & 0.58 & 0.75 & 0.53\\
-  \hline\hline
-  \end{tabular}
-  \label{tab}
+  \label{table:MHD}
   \caption{Magnetic field properties of the Auriga galaxies at $z=0$. For general properties of the disks.}

### 2019-08-02 Document/paper.tex
latest version

@@
 \begin{figure*}
-\includegraphics[width=0.9\textwidth]{shape_resolution.pdf}
-\caption{A}
-\label{fig:resolution}
-\end{figure*}
-
-\begin{figure*}
 \begin{center}
@@
   a strong correlation, albeit weaker than what they had with the triaxility.}
-\label{fig:alignment_correlations2}
+\label{fig:twisting_correlations}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.9\textwidth]{correlations_ages_angles_alignment_MHD.pdf}
+\end{center}
+\caption{Twisting in the halo-disc alingment as a function of the
+  mean stellar age in the bulge/disc and the lookback formation time of the
+  dark matter halo (time at which it has half of its present mass).
+  The label with the $\rho$ value corresponds to the Spearmans rank
+  correlation coefficient.
+  The line is the best minimum squares fit to a line.}
+\label{fig:twisting_age}
 \end{figure*}
@@
 
+\begin{table*}
+  \centering 
+  \begin{tabular}{c c c c c c c c c c c}
+  \hline\hline
+  Halo & $(b/a)_{16}$ & $(c/a)_{16}$& $(b/a)_{8}$ & $(c/a)_{8}$& $(b/a)_{4}$ & $(c/a)_{4}$& $(b/a)_{2}$ & $(c/a)_{2}$& $(b/a)_{1}$ & $(c/a)_{1}$ \\
+  \hline
+Au-1 & 0.48 & 0.41 & 0.52 & 0.44 & 0.59 & 0.48 & 0.66 & 0.53 & 0.72 & 0.55\\
+Au-2 & 0.66 & 0.47 & 0.72 & 0.49 & 0.76 & 0.51 & 0.80 & 0.54 & 0.79 & 0.55\\
+Au-3 & 0.56 & 0.42 & 0.61 & 0.47 & 0.70 & 0.55 & 0.79 & 0.65 & 0.85 & 0.72\\
+Au-4 & 0.42 & 0.35 & 0.47 & 0.40 & 0.49 & 0.43 & 0.55 & 0.49 & 0.59 & 0.52\\
+Au-5 & 0.49 & 0.41 & 0.53 & 0.47 & 0.56 & 0.51 & 0.59 & 0.56 & 0.66 & 0.59\\
+Au-6 & 0.56 & 0.46 & 0.58 & 0.46 & 0.61 & 0.49 & 0.62 & 0.51 & 0.65 & 0.54\\
+Au-7 & 0.46 & 0.37 & 0.45 & 0.37 & 0.51 & 0.40 & 0.55 & 0.41 & 0.62 & 0.46\\
+Au-8 & 0.75 & 0.47 & 0.84 & 0.53 & 0.85 & 0.58 & 0.76 & 0.54 & 0.82 & 0.55\\
+Au-9 & 0.49 & 0.40 & 0.52 & 0.43 & 0.54 & 0.45 & 0.60 & 0.52 & 0.65 & 0.60\\
+Au-10 & 0.62 & 0.51 & 0.61 & 0.50 & 0.58 & 0.49 & 0.60 & 0.53 & 0.65 & 0.59\\
+Au-11 & 0.47 & 0.37 & 0.36 & 0.29 & 0.32 & 0.28 & 0.41 & 0.37 & 0.47 & 0.45\\
+Au-12 & 0.66 & 0.53 & 0.76 & 0.59 & 0.83 & 0.66 & 0.88 & 0.68 & 0.94 & 0.71\\
+Au-13 & 0.60 & 0.52 & 0.61 & 0.53 & 0.64 & 0.54 & 0.70 & 0.56 & 0.73 & 0.54\\
+Au-14 & 0.97 & 0.67 & 0.95 & 0.66 & 0.90 & 0.64 & 0.89 & 0.69 & 0.87 & 0.75\\
+Au-15 & 0.61 & 0.42 & 0.65 & 0.48 & 0.68 & 0.52 & 0.66 & 0.50 & 0.70 & 0.54\\
+Au-16 & 0.64 & 0.57 & 0.73 & 0.57 & 0.84 & 0.58 & 0.87 & 0.62 & 0.88 & 0.63\\
+Au-17 & 0.98 & 0.79 & 0.98 & 0.83 & 0.95 & 0.84 & 0.91 & 0.81 & 0.93 & 0.87\\
+Au-18 & 0.56 & 0.55 & 0.57 & 0.55 & 0.60 & 0.57 & 0.64 & 0.59 & 0.62 & 0.56\\
+Au-19 & 0.58 & 0.51 & 0.59 & 0.50 & 0.65 & 0.54 & 0.73 & 0.61 & 0.80 & 0.70\\
+Au-20 & 0.61 & 0.44 & 0.68 & 0.48 & 0.72 & 0.51 & 0.76 & 0.59 & 0.81 & 0.70\\
+Au-21 & 0.67 & 0.50 & 0.75 & 0.50 & 0.81 & 0.61 & 0.80 & 0.66 & 0.74 & 0.64\\
+Au-22 & 0.68 & 0.56 & 0.71 & 0.59 & 0.77 & 0.63 & 0.82 & 0.71 & 0.83 & 0.78\\
+Au-23 & 0.54 & 0.41 & 0.58 & 0.44 & 0.62 & 0.49 & 0.70 & 0.57 & 0.77 & 0.66\\
+Au-24 & 0.54 & 0.44 & 0.57 & 0.47 & 0.59 & 0.49 & 0.66 & 0.55 & 0.75 & 0.66\\
+Au-25 & 0.59 & 0.56 & 0.66 & 0.65 & 0.71 & 0.66 & 0.62 & 0.55 & 0.69 & 0.61\\
+Au-26 & 0.52 & 0.41 & 0.58 & 0.43 & 0.65 & 0.43 & 0.73 & 0.47 & 0.75 & 0.51\\
+Au-27 & 0.53 & 0.45 & 0.61 & 0.51 & 0.68 & 0.56 & 0.76 & 0.62 & 0.84 & 0.64\\
+Au-28 & 0.49 & 0.42 & 0.49 & 0.44 & 0.56 & 0.48 & 0.64 & 0.52 & 0.74 & 0.58\\
+Au-29 & 0.50 & 0.40 & 0.56 & 0.45 & 0.61 & 0.48 & 0.69 & 0.54 & 0.72 & 0.60\\
+Au-30 & 0.62 & 0.44 & 0.77 & 0.54 & 0.87 & 0.58 & 0.85 & 0.58 & 0.75 & 0.53\\
+  \hline\hline
+  \end{tabular}
+  \caption{Dark matter halo axial ratios of Auriga galaxies at $z=0$ at
+    different radii in DMO simulations. The subscripts $16$, $8$, $4$, $2$, $1$,
+    indicate that the shape was measured at radii of $R_{200}/16$,
+    $R_{200}/8$, $R_{200}/4$, $R_{200}/2$, $R_{200}$, respectively.   \label{table:DMO}}
+\end{table*}
+
+\begin{table*}
+  \centering 
+  \begin{tabular}{c c c c c c c c c c c}
+  \hline\hline
+  Halo & $(b/a)_{16}$ & $(c/a)_{16}$& $(b/a)_{8}$ & $(c/a)_{8}$& $(b/a)_{4}$ & $(c/a)_{4}$& $(b/a)_{2}$ & $(c/a)_{2}$& $(b/a)_{1}$ & $(c/a)_{1}$ \\
+  \hline
+Au-1 & 0.94 & 0.65 & 0.96 & 0.66 & 0.96 & 0.70 & 0.92 & 0.68 & 0.91 & 0.67\\
+Au-2 & 0.93 & 0.61 & 0.95 & 0.58 & 0.96 & 0.61 & 0.96 & 0.65 & 0.88 & 0.65\\
+Au-3 & 0.97 & 0.66 & 0.96 & 0.66 & 0.94 & 0.70 & 0.93 & 0.76 & 0.94 & 0.79\\
+Au-4 & 0.88 & 0.77 & 0.82 & 0.79 & 0.80 & 0.76 & 0.85 & 0.79 & 0.83 & 0.76\\
+Au-5 & 0.97 & 0.79 & 0.94 & 0.80 & 0.92 & 0.81 & 0.94 & 0.82 & 0.94 & 0.81\\
+Au-6 & 0.98 & 0.60 & 0.96 & 0.60 & 0.92 & 0.63 & 0.86 & 0.63 & 0.78 & 0.61\\
+Au-7 & 0.95 & 0.66 & 0.95 & 0.66 & 0.97 & 0.68 & 0.97 & 0.69 & 0.96 & 0.70\\
+Au-8 & 0.99 & 0.59 & 0.97 & 0.62 & 0.92 & 0.66 & 0.76 & 0.57 & 0.83 & 0.58\\
+Au-9 & 0.94 & 0.75 & 0.93 & 0.73 & 0.92 & 0.73 & 0.93 & 0.79 & 0.92 & 0.82\\
+Au-10 & 0.95 & 0.85 & 0.94 & 0.85 & 0.93 & 0.85 & 0.92 & 0.82 & 0.91 & 0.80\\
+Au-11 & 0.54 & 0.49 & 0.55 & 0.48 & 0.61 & 0.53 & 0.60 & 0.53 & 0.62 & 0.57\\
+Au-12 & 0.95 & 0.77 & 0.88 & 0.81 & 0.90 & 0.84 & 0.92 & 0.81 & 0.95 & 0.82\\
+Au-13 & 0.95 & 0.88 & 0.96 & 0.88 & 0.98 & 0.82 & 0.94 & 0.76 & 0.82 & 0.62\\
+Au-14 & 0.95 & 0.75 & 0.93 & 0.79 & 0.91 & 0.80 & 0.91 & 0.79 & 0.93 & 0.81\\
+Au-15 & 0.99 & 0.67 & 0.98 & 0.75 & 0.94 & 0.79 & 0.93 & 0.81 & 0.88 & 0.76\\
+Au-16 & 0.99 & 0.69 & 0.99 & 0.70 & 0.99 & 0.74 & 0.98 & 0.76 & 0.99 & 0.99\\
+Au-17 & 0.96 & 0.79 & 0.96 & 0.80 & 0.97 & 0.82 & 0.96 & 0.83 & 0.96 & 0.87\\
+Au-18 & 0.93 & 0.76 & 0.92 & 0.74 & 0.86 & 0.72 & 0.81 & 0.71 & 0.74 & 0.66\\
+Au-19 & 0.95 & 0.67 & 0.91 & 0.63 & 0.89 & 0.63 & 0.83 & 0.64 & 0.85 & 0.69\\
+Au-20 & 0.81 & 0.58 & 0.91 & 0.64 & 0.95 & 0.71 & 0.97 & 0.78 & 0.86 & 0.77\\
+Au-21 & 0.98 & 0.74 & 0.97 & 0.82 & 0.97 & 0.87 & 0.99 & 0.88 & 0.99 & 0.99\\
+Au-22 & 0.96 & 0.84 & 0.93 & 0.84 & 0.93 & 0.85 & 0.95 & 0.87 & 0.97 & 0.88\\
+Au-23 & 0.94 & 0.65 & 0.96 & 0.64 & 0.94 & 0.65 & 0.92 & 0.69 & 0.93 & 0.74\\
+Au-24 & 0.99 & 0.67 & 1.00 & 0.63 & 0.99 & 0.65 & 0.97 & 0.68 & 0.98 & 0.70\\
+Au-25 & 0.97 & 0.71 & 0.96 & 0.73 & 0.86 & 0.74 & 0.67 & 0.64 & 0.71 & 0.67\\
+Au-26 & 0.96 & 0.76 & 0.97 & 0.73 & 0.97 & 0.70 & 0.99 & 0.68 & 0.97 & 0.67\\
+Au-27 & 0.98 & 0.73 & 0.97 & 0.75 & 0.97 & 0.79 & 0.96 & 0.79 & 0.95 & 0.77\\
+Au-28 & 0.98 & 0.82 & 0.94 & 0.77 & 0.88 & 0.73 & 0.86 & 0.74 & 0.93 & 0.75\\
+Au-29 & 0.91 & 0.81 & 0.89 & 0.72 & 0.87 & 0.69 & 0.84 & 0.68 & 0.85 & 0.69\\
+Au-30 & 0.89 & 0.73 & 0.78 & 0.64 & 0.69 & 0.53 & 0.80 & 0.58 & 0.91 & 0.63\\
+  \hline\hline
+  \end{tabular}
+
+  \caption{Same as Table \ref{table:DMO} for MHD simulations.   \label{table:MHD}}
+\end{table*}
+
 \section{Conclusions}
@@
 
-\begin{table*}
-  \centering 
-  \begin{tabular}{c c c c c c c c c c c}
-  \hline\hline
-  Halo & $(b/a)_{16}$ & $(c/a)_{16}$& $(b/a)_{8}$ & $(c/a)_{8}$& $(b/a)_{4}$ & $(c/a)_{4}$& $(b/a)_{2}$ & $(c/a)_{2}$& $(b/a)_{1}$ & $(c/a)_{1}$ \\
-  \hline
-Au-1 & 0.48 & 0.41 & 0.52 & 0.44 & 0.59 & 0.48 & 0.66 & 0.53 & 0.72 & 0.55\\
-Au-2 & 0.66 & 0.47 & 0.72 & 0.49 & 0.76 & 0.51 & 0.80 & 0.54 & 0.79 & 0.55\\
-Au-3 & 0.56 & 0.42 & 0.61 & 0.47 & 0.70 & 0.55 & 0.79 & 0.65 & 0.85 & 0.72\\
-Au-4 & 0.42 & 0.35 & 0.47 & 0.40 & 0.49 & 0.43 & 0.55 & 0.49 & 0.59 & 0.52\\
-Au-5 & 0.49 & 0.41 & 0.53 & 0.47 & 0.56 & 0.51 & 0.59 & 0.56 & 0.66 & 0.59\\
-Au-6 & 0.56 & 0.46 & 0.58 & 0.46 & 0.61 & 0.49 & 0.62 & 0.51 & 0.65 & 0.54\\
-Au-7 & 0.46 & 0.37 & 0.45 & 0.37 & 0.51 & 0.40 & 0.55 & 0.41 & 0.62 & 0.46\\
-Au-8 & 0.75 & 0.47 & 0.84 & 0.53 & 0.85 & 0.58 & 0.76 & 0.54 & 0.82 & 0.55\\
-Au-9 & 0.49 & 0.40 & 0.52 & 0.43 & 0.54 & 0.45 & 0.60 & 0.52 & 0.65 & 0.60\\
-Au-10 & 0.62 & 0.51 & 0.61 & 0.50 & 0.58 & 0.49 & 0.60 & 0.53 & 0.65 & 0.59\\
-Au-11 & 0.47 & 0.37 & 0.36 & 0.29 & 0.32 & 0.28 & 0.41 & 0.37 & 0.47 & 0.45\\
-Au-12 & 0.66 & 0.53 & 0.76 & 0.59 & 0.83 & 0.66 & 0.88 & 0.68 & 0.94 & 0.71\\
-Au-13 & 0.60 & 0.52 & 0.61 & 0.53 & 0.64 & 0.54 & 0.70 & 0.56 & 0.73 & 0.54\\
-Au-14 & 0.97 & 0.67 & 0.95 & 0.66 & 0.90 & 0.64 & 0.89 & 0.69 & 0.87 & 0.75\\
-Au-15 & 0.61 & 0.42 & 0.65 & 0.48 & 0.68 & 0.52 & 0.66 & 0.50 & 0.70 & 0.54\\
-Au-16 & 0.64 & 0.57 & 0.73 & 0.57 & 0.84 & 0.58 & 0.87 & 0.62 & 0.88 & 0.63\\
-Au-17 & 0.98 & 0.79 & 0.98 & 0.83 & 0.95 & 0.84 & 0.91 & 0.81 & 0.93 & 0.87\\
-Au-18 & 0.56 & 0.55 & 0.57 & 0.55 & 0.60 & 0.57 & 0.64 & 0.59 & 0.62 & 0.56\\
-Au-19 & 0.58 & 0.51 & 0.59 & 0.50 & 0.65 & 0.54 & 0.73 & 0.61 & 0.80 & 0.70\\
-Au-20 & 0.61 & 0.44 & 0.68 & 0.48 & 0.72 & 0.51 & 0.76 & 0.59 & 0.81 & 0.70\\
-Au-21 & 0.67 & 0.50 & 0.75 & 0.50 & 0.81 & 0.61 & 0.80 & 0.66 & 0.74 & 0.64\\
-Au-22 & 0.68 & 0.56 & 0.71 & 0.59 & 0.77 & 0.63 & 0.82 & 0.71 & 0.83 & 0.78\\
-Au-23 & 0.54 & 0.41 & 0.58 & 0.44 & 0.62 & 0.49 & 0.70 & 0.57 & 0.77 & 0.66\\
-Au-24 & 0.54 & 0.44 & 0.57 & 0.47 & 0.59 & 0.49 & 0.66 & 0.55 & 0.75 & 0.66\\
-Au-25 & 0.59 & 0.56 & 0.66 & 0.65 & 0.71 & 0.66 & 0.62 & 0.55 & 0.69 & 0.61\\
-Au-26 & 0.52 & 0.41 & 0.58 & 0.43 & 0.65 & 0.43 & 0.73 & 0.47 & 0.75 & 0.51\\
-Au-27 & 0.53 & 0.45 & 0.61 & 0.51 & 0.68 & 0.56 & 0.76 & 0.62 & 0.84 & 0.64\\
-Au-28 & 0.49 & 0.42 & 0.49 & 0.44 & 0.56 & 0.48 & 0.64 & 0.52 & 0.74 & 0.58\\
-Au-29 & 0.50 & 0.40 & 0.56 & 0.45 & 0.61 & 0.48 & 0.69 & 0.54 & 0.72 & 0.60\\
-Au-30 & 0.62 & 0.44 & 0.77 & 0.54 & 0.87 & 0.58 & 0.85 & 0.58 & 0.75 & 0.53\\
-  \hline\hline
-  \end{tabular}
-  \label{table:DMO}
-  \caption{Magnetic field properties of the Auriga galaxies at $z=0$. For general properties of the disks.}
-\end{table*}
+\appendix
+\section{AS}
+\label{appendix:physical}
 
-\begin{table*}
-  \centering 
-  \begin{tabular}{c c c c c c c c c c c}
-  \hline\hline
-  Halo & $(b/a)_{16}$ & $(c/a)_{16}$& $(b/a)_{8}$ & $(c/a)_{8}$& $(b/a)_{4}$ & $(c/a)_{4}$& $(b/a)_{2}$ & $(c/a)_{2}$& $(b/a)_{1}$ & $(c/a)_{1}$ \\
-  \hline
-Au-1 & 0.94 & 0.65 & 0.96 & 0.66 & 0.96 & 0.70 & 0.92 & 0.68 & 0.91 & 0.67\\
-Au-2 & 0.93 & 0.61 & 0.95 & 0.58 & 0.96 & 0.61 & 0.96 & 0.65 & 0.88 & 0.65\\
-Au-3 & 0.97 & 0.66 & 0.96 & 0.66 & 0.94 & 0.70 & 0.93 & 0.76 & 0.94 & 0.79\\
-Au-4 & 0.88 & 0.77 & 0.82 & 0.79 & 0.80 & 0.76 & 0.85 & 0.79 & 0.83 & 0.76\\
-Au-5 & 0.97 & 0.79 & 0.94 & 0.80 & 0.92 & 0.81 & 0.94 & 0.82 & 0.94 & 0.81\\
-Au-6 & 0.98 & 0.60 & 0.96 & 0.60 & 0.92 & 0.63 & 0.86 & 0.63 & 0.78 & 0.61\\
-Au-7 & 0.95 & 0.66 & 0.95 & 0.66 & 0.97 & 0.68 & 0.97 & 0.69 & 0.96 & 0.70\\
-Au-8 & 0.99 & 0.59 & 0.97 & 0.62 & 0.92 & 0.66 & 0.76 & 0.57 & 0.83 & 0.58\\
-Au-9 & 0.94 & 0.75 & 0.93 & 0.73 & 0.92 & 0.73 & 0.93 & 0.79 & 0.92 & 0.82\\
-Au-10 & 0.95 & 0.85 & 0.94 & 0.85 & 0.93 & 0.85 & 0.92 & 0.82 & 0.91 & 0.80\\
-Au-11 & 0.54 & 0.49 & 0.55 & 0.48 & 0.61 & 0.53 & 0.60 & 0.53 & 0.62 & 0.57\\
-Au-12 & 0.95 & 0.77 & 0.88 & 0.81 & 0.90 & 0.84 & 0.92 & 0.81 & 0.95 & 0.82\\
-Au-13 & 0.95 & 0.88 & 0.96 & 0.88 & 0.98 & 0.82 & 0.94 & 0.76 & 0.82 & 0.62\\
-Au-14 & 0.95 & 0.75 & 0.93 & 0.79 & 0.91 & 0.80 & 0.91 & 0.79 & 0.93 & 0.81\\
-Au-15 & 0.99 & 0.67 & 0.98 & 0.75 & 0.94 & 0.79 & 0.93 & 0.81 & 0.88 & 0.76\\
-Au-16 & 0.99 & 0.69 & 0.99 & 0.70 & 0.99 & 0.74 & 0.98 & 0.76 & 0.99 & 0.99\\
-Au-17 & 0.96 & 0.79 & 0.96 & 0.80 & 0.97 & 0.82 & 0.96 & 0.83 & 0.96 & 0.87\\
-Au-18 & 0.93 & 0.76 & 0.92 & 0.74 & 0.86 & 0.72 & 0.81 & 0.71 & 0.74 & 0.66\\
-Au-19 & 0.95 & 0.67 & 0.91 & 0.63 & 0.89 & 0.63 & 0.83 & 0.64 & 0.85 & 0.69\\
-Au-20 & 0.81 & 0.58 & 0.91 & 0.64 & 0.95 & 0.71 & 0.97 & 0.78 & 0.86 & 0.77\\
-Au-21 & 0.98 & 0.74 & 0.97 & 0.82 & 0.97 & 0.87 & 0.99 & 0.88 & 0.99 & 0.99\\
-Au-22 & 0.96 & 0.84 & 0.93 & 0.84 & 0.93 & 0.85 & 0.95 & 0.87 & 0.97 & 0.88\\
-Au-23 & 0.94 & 0.65 & 0.96 & 0.64 & 0.94 & 0.65 & 0.92 & 0.69 & 0.93 & 0.74\\
-Au-24 & 0.99 & 0.67 & 1.00 & 0.63 & 0.99 & 0.65 & 0.97 & 0.68 & 0.98 & 0.70\\
-Au-25 & 0.97 & 0.71 & 0.96 & 0.73 & 0.86 & 0.74 & 0.67 & 0.64 & 0.71 & 0.67\\
-Au-26 & 0.96 & 0.76 & 0.97 & 0.73 & 0.97 & 0.70 & 0.99 & 0.68 & 0.97 & 0.67\\
-Au-27 & 0.98 & 0.73 & 0.97 & 0.75 & 0.97 & 0.79 & 0.96 & 0.79 & 0.95 & 0.77\\
-Au-28 & 0.98 & 0.82 & 0.94 & 0.77 & 0.88 & 0.73 & 0.86 & 0.74 & 0.93 & 0.75\\
-Au-29 & 0.91 & 0.81 & 0.89 & 0.72 & 0.87 & 0.69 & 0.84 & 0.68 & 0.85 & 0.69\\
-Au-30 & 0.89 & 0.73 & 0.78 & 0.64 & 0.69 & 0.53 & 0.80 & 0.58 & 0.91 & 0.63\\
-  \hline\hline
-  \end{tabular}
-  \label{table:MHD}
-  \caption{Magnetic field properties of the Auriga galaxies at $z=0$. For general properties of the disks.}
-\end{table*}
+\begin{figure*}
+\includegraphics[width=0.9\textwidth]{shape_resolution.pdf}
+\caption{A}
+\label{fig:resolution}
+\end{figure*}
 

### 2019-08-03 Document/paper.tex
edit

@@
 DMO sample.
+
+\begin{figure*}
+\includegraphics[width=0.9\textwidth]{shape_resolution.pdf}
+\caption{Axial ratios for the six halos simulated at two different
+  resolutions with two different physics (DMO and MHD). 
+  In DMO simulations there is a good agreement between the two
+  resolutions (L3 and L4) at all radii down to scales of $\approx 1$
+  kpc from the center. 
+  In MHD simulations there are noticeable differences at scales below
+  $\approx 10$ kpc. 
+  In this paper we only report results at scales larger $\approx 16$ kpc
+  ($R_{200}/16$).}
+\label{fig:resolution}
+\end{figure*}
 
@@
 we restrict the measurement of the ellipsoidal parameters to radii
-between $2$ kpc and $R_{200}$ where  $R_{200}$ corresponds to the radius
+between $1$ kpc and $R_{200}$ where  $R_{200}$ corresponds to the radius
 computed enclosing a sphere with 200 times the critical density of the
 Universe. 
-This scale is similar to the gravitational smoothing length for
-stellar particles. 
+{\bf However, this scale is similar to the gravitational smoothing length
+for stellar particles.
+For this reason we use the Level3 simulations performed at higher
+resolution to gauge the convergence of the shape measurements in the
+MHD simulations.
+
+Figure \ref{fig:resolution} shows the results for the six halos
+available at the higher Level3 resolution and the corresponding
+halos at our baseline Level4 resolution. 
+The dotted lines compare the DMO simulations showing that down to
+scales of $1$ kpc the two simulations give comparable results.
+In MHD simulations the situation is different, as expected. 
+With the exception of Au-27 the shape ratios $b/a$ and $c/a$ start
+to distantiate from each other for radii smaller than $15$ kpc.
+Above these radii, the differences between the triaxility values at
+Level4 and Level3 in MHD simulations are small and never exceed $0.1$.}
+
 For this reason, in order to make the DM halo shape results comparable
-against stellar disc shape measurements, we report our DM halo shape
+against stellar disc shape measurements, we report all our shape
 results above $10$ kpc.
-We characterize the stellar disk by measuring the angular momentum vector using the $10\%$ oldest stellar particles.
 
@@
 halos. 
-Given the small variance across halos, each dimensionless radius is associated with
-a physical value with a mean value and a standard deviation.
+Given the small variance across halos, each dimensionless radius is
+associated with a physical value with a mean value and a standard deviation.
 For instance, over the 30 halos in the sample, the dimensionless
@@
 kpc.  
+Finally, we also measure the alignment of the halo shape against the
+stellar disc angular momentum. 
+We measure the angular momentum vector using the $10\%$ oldest stellar
+particles within the virial radius.
 
@@
 
-\begin{figure*}
-\includegraphics[width=0.9\textwidth]{shape_resolution.pdf}
-\caption{A}
-\label{fig:resolution}
-\end{figure*}
-
 \end{document}

### 2019-08-03 Document/paper.tex
up

@@
 lenght and 500 $h^{-1}$ pc comoving. 
+{\bf We refer to this setup as the Level4 resolution. 
+Six of these haloes were also simulated at a higher Level3 resolution
+that represent an increase by a factor of 8 in mass and 2 in spatial
+resolution.  
+We use the higher resolution haloes to define a minimal radius above
+which our results can be considered as converged.} 
 From now on we refer to the haloes simulated with baryonic physics as the
@@
   simulations, the change is stronger towards the halo center.
-  Only a small fraction of the halos ($\sim 1/15$) presents the
-  opposite trend of becoming more triaxial towards the center.}
+  Only two haloes in the sample show the opposite trend of becoming
+  more triaxial (but only at the smaller radii).} 
 \label{fig:delta_triaxial_cumulative}
@@
   in each panel's title.
-  The label with the $\rho$ value corresponds to the Spearman's rank
-  correlation coefficient while the line shows the result of the
+  The label with the $\rho$ value corresponds to the Spearmans rank
+  correlation coefficient (mean value and error bars estimated via
+  jackknife resampling) while the line shows the result of the
   minimum squares fit to the data.
@@
   and baryonic disc properties. 
-  The label with the $\rho$ value corresponds to the Spearman's rank
-  correlation coefficient.
+  The label with the $\rho$ value corresponds to the Spearmans rank
+  correlation coefficient (mean value and error bars estimated via
+  jackknife resampling).
   The line is the best minimum squares fit to a line.
@@
   baryonic disc properties in Figure \ref{fig:disc_correlations}.
-  The label with the $\rho$ value corresponds to the Spearman's rank
-  correlation coefficient.
+  The label with the $\rho$ value corresponds to the Spearmans rank
+  correlation coefficient (mean value and error bars estimated via
+  jackknife resampling).
   The line is the best minimum squares fit to a line.
@@
   The label with the $\rho$ value corresponds to the Spearmans rank
-  correlation coefficient.
+  correlation coefficient (mean value and error bars estimated via
+  jackknife resampling).
   The line is the best minimum squares fit to a line.}
@@
 Figure \ref{fig:resolution} shows the results for the six halos
-available at the higher Level3 resolution and the corresponding
-halos at our baseline Level4 resolution. 
+available both at Level3 and Level4 resolutions.
 The dotted lines compare the DMO simulations showing that down to
-scales of $1$ kpc the two simulations give comparable results.
+scales of $1$ kpc the two resolutions yield comparable results
+\citep{VeraCiro11}. 
 In MHD simulations the situation is different, as expected. 
 With the exception of Au-27 the shape ratios $b/a$ and $c/a$ start
-to distantiate from each other for radii smaller than $15$ kpc.
+to differentiate from each other at radii smaller than $15$ kpc.
 Above these radii, the differences between the triaxility values at
-Level4 and Level3 in MHD simulations are small and never exceed $0.1$.}
-
+Level4 and Level3 in MHD simulations are small and never exceed $0.1$.
 For this reason, in order to make the DM halo shape results comparable
-against stellar disc shape measurements, we report all our shape
-results above $10$ kpc.
+in DMO and MHD simulations we only report measurements above $15$
+kpc.}
 

### 2019-08-03 Document/paper.tex
update

@@
 radius implying that the halo shape twists; 
-this effect correlates with extended stellar discs and
-low gas densities and is almost absent in the dark matter only
-simulations.  
+this effect correlates with recently formed bulges and is almost
+absent in the dark matter only simulations.  
 In a comparison against observational constraints we find that $20\%$
@@
 
+\begin{table*}
+  \centering 
+  \begin{tabular}{c c c c c c c c c c c}
+  \hline\hline
+  Halo & $(b/a)_{16}$ & $(c/a)_{16}$& $(b/a)_{8}$ & $(c/a)_{8}$& $(b/a)_{4}$ & $(c/a)_{4}$& $(b/a)_{2}$ & $(c/a)_{2}$& $(b/a)_{1}$ & $(c/a)_{1}$ \\
+  \hline
+Au-1 & 0.48 & 0.41 & 0.52 & 0.44 & 0.59 & 0.48 & 0.66 & 0.53 & 0.72 & 0.55\\
+Au-2 & 0.66 & 0.47 & 0.72 & 0.49 & 0.76 & 0.51 & 0.80 & 0.54 & 0.79 & 0.55\\
+Au-3 & 0.56 & 0.42 & 0.61 & 0.47 & 0.70 & 0.55 & 0.79 & 0.65 & 0.85 & 0.72\\
+Au-4 & 0.42 & 0.35 & 0.47 & 0.40 & 0.49 & 0.43 & 0.55 & 0.49 & 0.59 & 0.52\\
+Au-5 & 0.49 & 0.41 & 0.53 & 0.47 & 0.56 & 0.51 & 0.59 & 0.56 & 0.66 & 0.59\\
+Au-6 & 0.56 & 0.46 & 0.58 & 0.46 & 0.61 & 0.49 & 0.62 & 0.51 & 0.65 & 0.54\\
+Au-7 & 0.46 & 0.37 & 0.45 & 0.37 & 0.51 & 0.40 & 0.55 & 0.41 & 0.62 & 0.46\\
+Au-8 & 0.75 & 0.47 & 0.84 & 0.53 & 0.85 & 0.58 & 0.76 & 0.54 & 0.82 & 0.55\\
+Au-9 & 0.49 & 0.40 & 0.52 & 0.43 & 0.54 & 0.45 & 0.60 & 0.52 & 0.65 & 0.60\\
+Au-10 & 0.62 & 0.51 & 0.61 & 0.50 & 0.58 & 0.49 & 0.60 & 0.53 & 0.65 & 0.59\\
+Au-11 & 0.47 & 0.37 & 0.36 & 0.29 & 0.32 & 0.28 & 0.41 & 0.37 & 0.47 & 0.45\\
+Au-12 & 0.66 & 0.53 & 0.76 & 0.59 & 0.83 & 0.66 & 0.88 & 0.68 & 0.94 & 0.71\\
+Au-13 & 0.60 & 0.52 & 0.61 & 0.53 & 0.64 & 0.54 & 0.70 & 0.56 & 0.73 & 0.54\\
+Au-14 & 0.97 & 0.67 & 0.95 & 0.66 & 0.90 & 0.64 & 0.89 & 0.69 & 0.87 & 0.75\\
+Au-15 & 0.61 & 0.42 & 0.65 & 0.48 & 0.68 & 0.52 & 0.66 & 0.50 & 0.70 & 0.54\\
+Au-16 & 0.64 & 0.57 & 0.73 & 0.57 & 0.84 & 0.58 & 0.87 & 0.62 & 0.88 & 0.63\\
+Au-17 & 0.98 & 0.79 & 0.98 & 0.83 & 0.95 & 0.84 & 0.91 & 0.81 & 0.93 & 0.87\\
+Au-18 & 0.56 & 0.55 & 0.57 & 0.55 & 0.60 & 0.57 & 0.64 & 0.59 & 0.62 & 0.56\\
+Au-19 & 0.58 & 0.51 & 0.59 & 0.50 & 0.65 & 0.54 & 0.73 & 0.61 & 0.80 & 0.70\\
+Au-20 & 0.61 & 0.44 & 0.68 & 0.48 & 0.72 & 0.51 & 0.76 & 0.59 & 0.81 & 0.70\\
+Au-21 & 0.67 & 0.50 & 0.75 & 0.50 & 0.81 & 0.61 & 0.80 & 0.66 & 0.74 & 0.64\\
+Au-22 & 0.68 & 0.56 & 0.71 & 0.59 & 0.77 & 0.63 & 0.82 & 0.71 & 0.83 & 0.78\\
+Au-23 & 0.54 & 0.41 & 0.58 & 0.44 & 0.62 & 0.49 & 0.70 & 0.57 & 0.77 & 0.66\\
+Au-24 & 0.54 & 0.44 & 0.57 & 0.47 & 0.59 & 0.49 & 0.66 & 0.55 & 0.75 & 0.66\\
+Au-25 & 0.59 & 0.56 & 0.66 & 0.65 & 0.71 & 0.66 & 0.62 & 0.55 & 0.69 & 0.61\\
+Au-26 & 0.52 & 0.41 & 0.58 & 0.43 & 0.65 & 0.43 & 0.73 & 0.47 & 0.75 & 0.51\\
+Au-27 & 0.53 & 0.45 & 0.61 & 0.51 & 0.68 & 0.56 & 0.76 & 0.62 & 0.84 & 0.64\\
+Au-28 & 0.49 & 0.42 & 0.49 & 0.44 & 0.56 & 0.48 & 0.64 & 0.52 & 0.74 & 0.58\\
+Au-29 & 0.50 & 0.40 & 0.56 & 0.45 & 0.61 & 0.48 & 0.69 & 0.54 & 0.72 & 0.60\\
+Au-30 & 0.62 & 0.44 & 0.77 & 0.54 & 0.87 & 0.58 & 0.85 & 0.58 & 0.75 & 0.53\\
+  \hline\hline
+  \end{tabular}
+  \caption{Axial ratios of Auriga dark matter halos at $z=0$ at
+    different radii in DMO simulations. The subscripts $16$, $8$, $4$, $2$, $1$,
+    indicate that the shape was measured at radii of $R_{200}/16$,
+    $R_{200}/8$, $R_{200}/4$, $R_{200}/2$, $R_{200}$, respectively.   \label{table:DMO}}
+\end{table*}
+
+\begin{table*}
+  \centering 
+  \begin{tabular}{c c c c c c c c c c c}
+  \hline\hline
+  Halo & $(b/a)_{16}$ & $(c/a)_{16}$& $(b/a)_{8}$ & $(c/a)_{8}$& $(b/a)_{4}$ & $(c/a)_{4}$& $(b/a)_{2}$ & $(c/a)_{2}$& $(b/a)_{1}$ & $(c/a)_{1}$ \\
+  \hline
+Au-1 & 0.94 & 0.65 & 0.96 & 0.66 & 0.96 & 0.70 & 0.92 & 0.68 & 0.91 & 0.67\\
+Au-2 & 0.93 & 0.61 & 0.95 & 0.58 & 0.96 & 0.61 & 0.96 & 0.65 & 0.88 & 0.65\\
+Au-3 & 0.97 & 0.66 & 0.96 & 0.66 & 0.94 & 0.70 & 0.93 & 0.76 & 0.94 & 0.79\\
+Au-4 & 0.88 & 0.77 & 0.82 & 0.79 & 0.80 & 0.76 & 0.85 & 0.79 & 0.83 & 0.76\\
+Au-5 & 0.97 & 0.79 & 0.94 & 0.80 & 0.92 & 0.81 & 0.94 & 0.82 & 0.94 & 0.81\\
+Au-6 & 0.98 & 0.60 & 0.96 & 0.60 & 0.92 & 0.63 & 0.86 & 0.63 & 0.78 & 0.61\\
+Au-7 & 0.95 & 0.66 & 0.95 & 0.66 & 0.97 & 0.68 & 0.97 & 0.69 & 0.96 & 0.70\\
+Au-8 & 0.99 & 0.59 & 0.97 & 0.62 & 0.92 & 0.66 & 0.76 & 0.57 & 0.83 & 0.58\\
+Au-9 & 0.94 & 0.75 & 0.93 & 0.73 & 0.92 & 0.73 & 0.93 & 0.79 & 0.92 & 0.82\\
+Au-10 & 0.95 & 0.85 & 0.94 & 0.85 & 0.93 & 0.85 & 0.92 & 0.82 & 0.91 & 0.80\\
+Au-11 & 0.54 & 0.49 & 0.55 & 0.48 & 0.61 & 0.53 & 0.60 & 0.53 & 0.62 & 0.57\\
+Au-12 & 0.95 & 0.77 & 0.88 & 0.81 & 0.90 & 0.84 & 0.92 & 0.81 & 0.95 & 0.82\\
+Au-13 & 0.95 & 0.88 & 0.96 & 0.88 & 0.98 & 0.82 & 0.94 & 0.76 & 0.82 & 0.62\\
+Au-14 & 0.95 & 0.75 & 0.93 & 0.79 & 0.91 & 0.80 & 0.91 & 0.79 & 0.93 & 0.81\\
+Au-15 & 0.99 & 0.67 & 0.98 & 0.75 & 0.94 & 0.79 & 0.93 & 0.81 & 0.88 & 0.76\\
+Au-16 & 0.99 & 0.69 & 0.99 & 0.70 & 0.99 & 0.74 & 0.98 & 0.76 & 0.99 & 0.99\\
+Au-17 & 0.96 & 0.79 & 0.96 & 0.80 & 0.97 & 0.82 & 0.96 & 0.83 & 0.96 & 0.87\\
+Au-18 & 0.93 & 0.76 & 0.92 & 0.74 & 0.86 & 0.72 & 0.81 & 0.71 & 0.74 & 0.66\\
+Au-19 & 0.95 & 0.67 & 0.91 & 0.63 & 0.89 & 0.63 & 0.83 & 0.64 & 0.85 & 0.69\\
+Au-20 & 0.81 & 0.58 & 0.91 & 0.64 & 0.95 & 0.71 & 0.97 & 0.78 & 0.86 & 0.77\\
+Au-21 & 0.98 & 0.74 & 0.97 & 0.82 & 0.97 & 0.87 & 0.99 & 0.88 & 0.99 & 0.99\\
+Au-22 & 0.96 & 0.84 & 0.93 & 0.84 & 0.93 & 0.85 & 0.95 & 0.87 & 0.97 & 0.88\\
+Au-23 & 0.94 & 0.65 & 0.96 & 0.64 & 0.94 & 0.65 & 0.92 & 0.69 & 0.93 & 0.74\\
+Au-24 & 0.99 & 0.67 & 1.00 & 0.63 & 0.99 & 0.65 & 0.97 & 0.68 & 0.98 & 0.70\\
+Au-25 & 0.97 & 0.71 & 0.96 & 0.73 & 0.86 & 0.74 & 0.67 & 0.64 & 0.71 & 0.67\\
+Au-26 & 0.96 & 0.76 & 0.97 & 0.73 & 0.97 & 0.70 & 0.99 & 0.68 & 0.97 & 0.67\\
+Au-27 & 0.98 & 0.73 & 0.97 & 0.75 & 0.97 & 0.79 & 0.96 & 0.79 & 0.95 & 0.77\\
+Au-28 & 0.98 & 0.82 & 0.94 & 0.77 & 0.88 & 0.73 & 0.86 & 0.74 & 0.93 & 0.75\\
+Au-29 & 0.91 & 0.81 & 0.89 & 0.72 & 0.87 & 0.69 & 0.84 & 0.68 & 0.85 & 0.69\\
+Au-30 & 0.89 & 0.73 & 0.78 & 0.64 & 0.69 & 0.53 & 0.80 & 0.58 & 0.91 & 0.63\\
+  \hline\hline
+  \end{tabular}
+  \caption{Same as Table \ref{table:DMO} for MHD simulations.   \label{table:MHD}}
+\end{table*}
+
 \begin{figure*}
@@
   The label with the $\rho$ value corresponds to the Spearmans rank
-  correlation coefficient (mean value and error bars estimated via
+  correlation coefficient (mean value and uncertainty estimated via
   jackknife resampling) while the line shows the result of the
@@
   The label with the $\rho$ value corresponds to the Spearmans rank
-  correlation coefficient (mean value and error bars estimated via
+  correlation coefficient (mean value and uncertainty estimated via
   jackknife resampling).
@@
 In MHD simulations the situation is different, as expected. 
-With the exception of Au-27 the shape ratios $b/a$ and $c/a$ start
-to differentiate from each other at radii smaller than $15$ kpc.
-Above these radii, the differences between the triaxility values at
+The shape ratios $b/a$ and $c/a$ start to differentiate
+from each other at radii smaller than $15$ kpc, tith the exception of
+Au-27 that shows a good agreement in the shape measuremnts at all radii, 
+Above $15$ kpc, the differences between the triaxility values at
 Level4 and Level3 in MHD simulations are small and never exceed $0.1$. 
@@
 
-\subsection{Triaxiality}
+{\bf The main measurements are summarized in Table \ref{table:DMO} for the
+DMO simulations and Table \ref{table:MHD} for the MHD simulations.
+These results are computed at five different radii $R_{200}/16$,
+$R_{200}/8$, $R_{200}/4$, $R_{200}/2$ and $R_{200}$.
+In the following subsections we present and comment in greater detail
+the results for the triaxility, the halo-disc alignment and the
+correlations with baryonic disc properties.}
+
+\subsection{Triaxility}
 
@@
 function of radius.
-In Figure \ref{fig:alignment_correlations2} we show the correlation
+In Figure \ref{fig:twisting_correlations} we show the correlation
 between twisting and the same baryonic properties that showed a high
@@
 gas density at its core show the most coherent halo shapes.
+
+{\bf Recently \cite{2017MNRAS.469..594B} reported that MW-like DM haloes can
+be roughly splint into two distinct families: stalled and accreting.
+Stalled haloes assembled early and have remained almost unchanged
+in the last $7$ Gyr, while accreting halos have been growing
+constantly.
+\cite{2017MNRAS.469..594B} also link this dicotomy to the dark matter
+filaments feeding the halos. 
+Stalled halos at $z=0$ are embbeded in a single large thick filament, while
+accreting halos are pierced by many thinner filaments. 
+To what extent the twisting and high triaxility present in the MHD
+halos can be linked to this dicotomy?
+In Figure \ref{fig:twisting_age} we show the correlation between the
+twisting and the age of the bulge, the age of the stellar disc and the
+DM halo formation redshift. 
+The ages are estimated directly as the mean value in the stellar age
+distribution for each component, while the formation redshift is
+defined as the redshif at which the halo already has half of its $z=0$
+mass. 
+In the three cases we find a correlation between ages and twisting
+that goes in the direction claimed by \cite{2017MNRAS.469..594B}:
+components with early assembly (i.e. stalled) have a smaller degree of
+twisting.
+A detailed study with respect to the cosmic web location is beyond the
+scope of our paper.}
 
@@
 
-\begin{table*}
-  \centering 
-  \begin{tabular}{c c c c c c c c c c c}
-  \hline\hline
-  Halo & $(b/a)_{16}$ & $(c/a)_{16}$& $(b/a)_{8}$ & $(c/a)_{8}$& $(b/a)_{4}$ & $(c/a)_{4}$& $(b/a)_{2}$ & $(c/a)_{2}$& $(b/a)_{1}$ & $(c/a)_{1}$ \\
-  \hline
-Au-1 & 0.48 & 0.41 & 0.52 & 0.44 & 0.59 & 0.48 & 0.66 & 0.53 & 0.72 & 0.55\\
-Au-2 & 0.66 & 0.47 & 0.72 & 0.49 & 0.76 & 0.51 & 0.80 & 0.54 & 0.79 & 0.55\\
-Au-3 & 0.56 & 0.42 & 0.61 & 0.47 & 0.70 & 0.55 & 0.79 & 0.65 & 0.85 & 0.72\\
-Au-4 & 0.42 & 0.35 & 0.47 & 0.40 & 0.49 & 0.43 & 0.55 & 0.49 & 0.59 & 0.52\\
-Au-5 & 0.49 & 0.41 & 0.53 & 0.47 & 0.56 & 0.51 & 0.59 & 0.56 & 0.66 & 0.59\\
-Au-6 & 0.56 & 0.46 & 0.58 & 0.46 & 0.61 & 0.49 & 0.62 & 0.51 & 0.65 & 0.54\\
-Au-7 & 0.46 & 0.37 & 0.45 & 0.37 & 0.51 & 0.40 & 0.55 & 0.41 & 0.62 & 0.46\\
-Au-8 & 0.75 & 0.47 & 0.84 & 0.53 & 0.85 & 0.58 & 0.76 & 0.54 & 0.82 & 0.55\\
-Au-9 & 0.49 & 0.40 & 0.52 & 0.43 & 0.54 & 0.45 & 0.60 & 0.52 & 0.65 & 0.60\\
-Au-10 & 0.62 & 0.51 & 0.61 & 0.50 & 0.58 & 0.49 & 0.60 & 0.53 & 0.65 & 0.59\\
-Au-11 & 0.47 & 0.37 & 0.36 & 0.29 & 0.32 & 0.28 & 0.41 & 0.37 & 0.47 & 0.45\\
-Au-12 & 0.66 & 0.53 & 0.76 & 0.59 & 0.83 & 0.66 & 0.88 & 0.68 & 0.94 & 0.71\\
-Au-13 & 0.60 & 0.52 & 0.61 & 0.53 & 0.64 & 0.54 & 0.70 & 0.56 & 0.73 & 0.54\\
-Au-14 & 0.97 & 0.67 & 0.95 & 0.66 & 0.90 & 0.64 & 0.89 & 0.69 & 0.87 & 0.75\\
-Au-15 & 0.61 & 0.42 & 0.65 & 0.48 & 0.68 & 0.52 & 0.66 & 0.50 & 0.70 & 0.54\\
-Au-16 & 0.64 & 0.57 & 0.73 & 0.57 & 0.84 & 0.58 & 0.87 & 0.62 & 0.88 & 0.63\\
-Au-17 & 0.98 & 0.79 & 0.98 & 0.83 & 0.95 & 0.84 & 0.91 & 0.81 & 0.93 & 0.87\\
-Au-18 & 0.56 & 0.55 & 0.57 & 0.55 & 0.60 & 0.57 & 0.64 & 0.59 & 0.62 & 0.56\\
-Au-19 & 0.58 & 0.51 & 0.59 & 0.50 & 0.65 & 0.54 & 0.73 & 0.61 & 0.80 & 0.70\\
-Au-20 & 0.61 & 0.44 & 0.68 & 0.48 & 0.72 & 0.51 & 0.76 & 0.59 & 0.81 & 0.70\\
-Au-21 & 0.67 & 0.50 & 0.75 & 0.50 & 0.81 & 0.61 & 0.80 & 0.66 & 0.74 & 0.64\\
-Au-22 & 0.68 & 0.56 & 0.71 & 0.59 & 0.77 & 0.63 & 0.82 & 0.71 & 0.83 & 0.78\\
-Au-23 & 0.54 & 0.41 & 0.58 & 0.44 & 0.62 & 0.49 & 0.70 & 0.57 & 0.77 & 0.66\\
-Au-24 & 0.54 & 0.44 & 0.57 & 0.47 & 0.59 & 0.49 & 0.66 & 0.55 & 0.75 & 0.66\\
-Au-25 & 0.59 & 0.56 & 0.66 & 0.65 & 0.71 & 0.66 & 0.62 & 0.55 & 0.69 & 0.61\\
-Au-26 & 0.52 & 0.41 & 0.58 & 0.43 & 0.65 & 0.43 & 0.73 & 0.47 & 0.75 & 0.51\\
-Au-27 & 0.53 & 0.45 & 0.61 & 0.51 & 0.68 & 0.56 & 0.76 & 0.62 & 0.84 & 0.64\\
-Au-28 & 0.49 & 0.42 & 0.49 & 0.44 & 0.56 & 0.48 & 0.64 & 0.52 & 0.74 & 0.58\\
-Au-29 & 0.50 & 0.40 & 0.56 & 0.45 & 0.61 & 0.48 & 0.69 & 0.54 & 0.72 & 0.60\\
-Au-30 & 0.62 & 0.44 & 0.77 & 0.54 & 0.87 & 0.58 & 0.85 & 0.58 & 0.75 & 0.53\\
-  \hline\hline
-  \end{tabular}
-  \caption{Dark matter halo axial ratios of Auriga galaxies at $z=0$ at
-    different radii in DMO simulations. The subscripts $16$, $8$, $4$, $2$, $1$,
-    indicate that the shape was measured at radii of $R_{200}/16$,
-    $R_{200}/8$, $R_{200}/4$, $R_{200}/2$, $R_{200}$, respectively.   \label{table:DMO}}
-\end{table*}
-
-\begin{table*}
-  \centering 
-  \begin{tabular}{c c c c c c c c c c c}
-  \hline\hline
-  Halo & $(b/a)_{16}$ & $(c/a)_{16}$& $(b/a)_{8}$ & $(c/a)_{8}$& $(b/a)_{4}$ & $(c/a)_{4}$& $(b/a)_{2}$ & $(c/a)_{2}$& $(b/a)_{1}$ & $(c/a)_{1}$ \\
-  \hline
-Au-1 & 0.94 & 0.65 & 0.96 & 0.66 & 0.96 & 0.70 & 0.92 & 0.68 & 0.91 & 0.67\\
-Au-2 & 0.93 & 0.61 & 0.95 & 0.58 & 0.96 & 0.61 & 0.96 & 0.65 & 0.88 & 0.65\\
-Au-3 & 0.97 & 0.66 & 0.96 & 0.66 & 0.94 & 0.70 & 0.93 & 0.76 & 0.94 & 0.79\\
-Au-4 & 0.88 & 0.77 & 0.82 & 0.79 & 0.80 & 0.76 & 0.85 & 0.79 & 0.83 & 0.76\\
-Au-5 & 0.97 & 0.79 & 0.94 & 0.80 & 0.92 & 0.81 & 0.94 & 0.82 & 0.94 & 0.81\\
-Au-6 & 0.98 & 0.60 & 0.96 & 0.60 & 0.92 & 0.63 & 0.86 & 0.63 & 0.78 & 0.61\\
-Au-7 & 0.95 & 0.66 & 0.95 & 0.66 & 0.97 & 0.68 & 0.97 & 0.69 & 0.96 & 0.70\\
-Au-8 & 0.99 & 0.59 & 0.97 & 0.62 & 0.92 & 0.66 & 0.76 & 0.57 & 0.83 & 0.58\\
-Au-9 & 0.94 & 0.75 & 0.93 & 0.73 & 0.92 & 0.73 & 0.93 & 0.79 & 0.92 & 0.82\\
-Au-10 & 0.95 & 0.85 & 0.94 & 0.85 & 0.93 & 0.85 & 0.92 & 0.82 & 0.91 & 0.80\\
-Au-11 & 0.54 & 0.49 & 0.55 & 0.48 & 0.61 & 0.53 & 0.60 & 0.53 & 0.62 & 0.57\\
-Au-12 & 0.95 & 0.77 & 0.88 & 0.81 & 0.90 & 0.84 & 0.92 & 0.81 & 0.95 & 0.82\\
-Au-13 & 0.95 & 0.88 & 0.96 & 0.88 & 0.98 & 0.82 & 0.94 & 0.76 & 0.82 & 0.62\\
-Au-14 & 0.95 & 0.75 & 0.93 & 0.79 & 0.91 & 0.80 & 0.91 & 0.79 & 0.93 & 0.81\\
-Au-15 & 0.99 & 0.67 & 0.98 & 0.75 & 0.94 & 0.79 & 0.93 & 0.81 & 0.88 & 0.76\\
-Au-16 & 0.99 & 0.69 & 0.99 & 0.70 & 0.99 & 0.74 & 0.98 & 0.76 & 0.99 & 0.99\\
-Au-17 & 0.96 & 0.79 & 0.96 & 0.80 & 0.97 & 0.82 & 0.96 & 0.83 & 0.96 & 0.87\\
-Au-18 & 0.93 & 0.76 & 0.92 & 0.74 & 0.86 & 0.72 & 0.81 & 0.71 & 0.74 & 0.66\\
-Au-19 & 0.95 & 0.67 & 0.91 & 0.63 & 0.89 & 0.63 & 0.83 & 0.64 & 0.85 & 0.69\\
-Au-20 & 0.81 & 0.58 & 0.91 & 0.64 & 0.95 & 0.71 & 0.97 & 0.78 & 0.86 & 0.77\\
-Au-21 & 0.98 & 0.74 & 0.97 & 0.82 & 0.97 & 0.87 & 0.99 & 0.88 & 0.99 & 0.99\\
-Au-22 & 0.96 & 0.84 & 0.93 & 0.84 & 0.93 & 0.85 & 0.95 & 0.87 & 0.97 & 0.88\\
-Au-23 & 0.94 & 0.65 & 0.96 & 0.64 & 0.94 & 0.65 & 0.92 & 0.69 & 0.93 & 0.74\\
-Au-24 & 0.99 & 0.67 & 1.00 & 0.63 & 0.99 & 0.65 & 0.97 & 0.68 & 0.98 & 0.70\\
-Au-25 & 0.97 & 0.71 & 0.96 & 0.73 & 0.86 & 0.74 & 0.67 & 0.64 & 0.71 & 0.67\\
-Au-26 & 0.96 & 0.76 & 0.97 & 0.73 & 0.97 & 0.70 & 0.99 & 0.68 & 0.97 & 0.67\\
-Au-27 & 0.98 & 0.73 & 0.97 & 0.75 & 0.97 & 0.79 & 0.96 & 0.79 & 0.95 & 0.77\\
-Au-28 & 0.98 & 0.82 & 0.94 & 0.77 & 0.88 & 0.73 & 0.86 & 0.74 & 0.93 & 0.75\\
-Au-29 & 0.91 & 0.81 & 0.89 & 0.72 & 0.87 & 0.69 & 0.84 & 0.68 & 0.85 & 0.69\\
-Au-30 & 0.89 & 0.73 & 0.78 & 0.64 & 0.69 & 0.53 & 0.80 & 0.58 & 0.91 & 0.63\\
-  \hline\hline
-  \end{tabular}
-
-  \caption{Same as Table \ref{table:DMO} for MHD simulations.   \label{table:MHD}}
-\end{table*}
-
 \section{Conclusions}
@@
 
-\appendix
-\section{AS}
-\label{appendix:physical}
-
 \end{document}

### 2019-08-03 Document/paper.tex
edit

@@
   Third, halos in MHD are rounder than its DMO counterparts.
+  These three points are further clarified in Figure 
   The first and second points are claryfied in Figure
-  \ref{fig:triaxial_cumulative} through the cumulative triaxility
-  distributions, 
-  while the third trend is shown in Figure
-  \ref{fig:delta_triaxial_cumulative} through the cumulative
-  distribution in the triaxility changes between MHD and DMO at all
-  radii.}
+  \ref{fig:triaxial_cumulative} through cumulative triaxility
+  distributions}
   \label{fig:triaxiality_plane}
@@
 \begin{figure*}
-\includegraphics[width=0.8\columnwidth]{triaxialiy_distro_DM.pdf}
-\includegraphics[width=0.8\columnwidth]{triaxialiy_distro_MHD.pdf}
+\includegraphics[width=0.32\textwidth]{triaxialiy_distro_DM.pdf}
+\includegraphics[width=0.32\textwidth]{triaxialiy_distro_MHD.pdf}
+\includegraphics[width=0.32\textwidth]{delta_triaxiality_distro.pdf}
 \caption{Triaxility cumulative distribution at five different radii.
-  Right/left panel corresponds to DMO/MHD simulations, respectively. 
+  Right/middle panel corresponds to the cumulative distribution of
+  triaxiality in DMO/MHD simulations, respectively. 
   In DMO simulations the median triaxiality at all radii is larger
@@
   The median triaxility at all radii is smaller than $1/3$ and the
-  halo is less triaxial as on moves towards the stellar disc.}
-\label{fig:triaxial_cumulative}
-\end{figure*}
-
-\begin{figure}
-\includegraphics[width=0.9\columnwidth]{delta_triaxiality_distro.pdf}
-\caption{
-  Cumulative distribution for the changes in triaxility in simulations
-  with different physics, $\Delta T=T_{\rm MHD}-T_{\rm DMO}$.
+  halo is less triaxial as on moves towards the stellar disc.
+  The right panel, shows the cumulative distribution for the changes
+  in triaxility in simulations with different physics, $\Delta
+  T=T_{\rm MHD}-T_{\rm DMO}$. 
   At the virial radius all halos become less triaxial in the MHD
@@
   more triaxial (but only at the smaller radii).} 
-\label{fig:delta_triaxial_cumulative}
-\end{figure}
+\label{fig:triaxial_cumulative}
+\end{figure*}
 
@@
 \begin{center}
-\includegraphics[width=1.0\textwidth]{angles_alignment_DM.pdf}
-\includegraphics[width=1.0\textwidth]{angles_alignment_MHD.pdf}
+\includegraphics[width=0.9\textwidth]{angles_alignment_DM.pdf}
+\includegraphics[width=0.9\textwidth]{angles_alignment_MHD.pdf}
 \end{center}
@@
   while the thick line traces the median value at every radius.
-  In the upper row the haloes come from the DMO simulation, 
-  showing that the directions in the ellipsoids describing the shape
-  are constant as a function of radius for the most part of the sample.
+  In the upper row the haloes come from the DMO simulation.
+  The first thing to notice is that the major axis is statistically
+  perpendicular to the angular momentum of the disc that will form in
+  the MHD simulations. The other two directions do not show any
+  correlation. 
+  The second important result is that the directions in the ellipsoids
+  describing the shape are constant as a function of radius except two
+  cases. 
   In the lower row the haloes come from the MHD simulation providing a 
   self-consistent comparison with the stellar discs. 
-  In this case the dark matter shells twists significantly in $1/5$ of the sample. For the remaining haloes the alignment is almost constant as a function of radius.
+  In this case the sample presents a good alignment of the angular
+  momentum with the minor halo axis. 
+  Furthermore, the dark matter shells twists significantly in $1/5$ of
+  the sample. For the remaining haloes the alignment is almost
+  constant as a function of radius. 
 }
@@
   The largest correlations are found for the two smaller radii
-  ($0.06R_{200}$ and $0.12R_{200}$).
+  ($R_{200}/16$ and $R_{200}/8$).
   Extended and massive stellar discs with a low gas content at its
@@
 constantly.
-\cite{2017MNRAS.469..594B} also link this dicotomy to the dark matter
-filaments feeding the halos. 
+\cite{2017MNRAS.469..594B} also link the two populations to
+differences in the dark matter filaments feeding the halos. 
 Stalled halos at $z=0$ are embbeded in a single large thick filament, while
@@
 technique. 
-The halos were with two different setups:
+The halos were simulated in two different setups:
 dark matter only (DMO) simulation and full magnetohydrodynamics (MHD)
@@
 dark matter halos of these simulations to quantify the halo shape as a
-function of radius and the degree of aligment between the stellar disc
-and the halo.
+function of radius and the degree of aligment between the angular
+momentum in stellar disc and the dark matter halo.
 
@@
 ($T<1/3$), while DMO halos tend towards more prolate shapes ($T>2/3$).  
-The rounding effect is more noticeable as one moves closer to galactic
+The rounding effect is more noticeable as one moves closer to the galactic
 disc and strongly  correlates with baryonic properties of the disc
@@
 We quantify this twist with the standard deviation of the angle
-between the angular momentum and the halo minor axis at radii below $\leq 0.5R_{200}$ and find that higher gas densities correlate with larger twisting values.
+between the angular momentum and the halo minor axis at radii below
+$\leq 0.5R_{200}$ and find that younger bulges and higher gas
+densities correlate with larger twisting values.
 

### 2019-08-03 Document/paper.tex
triaxiality

@@
   The first and second points are claryfied in Figure
-  \ref{fig:triaxial_cumulative} through cumulative triaxility
+  \ref{fig:triaxial_cumulative} through cumulative triaxiality
   distributions}
@@
 \includegraphics[width=0.32\textwidth]{delta_triaxiality_distro.pdf}
-\caption{Triaxility cumulative distribution at five different radii.
+\caption{Triaxiality cumulative distribution at five different radii.
   Right/middle panel corresponds to the cumulative distribution of
@@
   In DMO simulations the median triaxiality at all radii is larger
-  than $2/3$. Furthermore, the triaxility increases as one moves
+  than $2/3$. Furthermore, the triaxiality increases as one moves
   towards the inner part of the halo.
   In MHD simulations these trend reverses.
-  The median triaxility at all radii is smaller than $1/3$ and the
+  The median triaxiality at all radii is smaller than $1/3$ and the
   halo is less triaxial as on moves towards the stellar disc.
   The right panel, shows the cumulative distribution for the changes
-  in triaxility in simulations with different physics, $\Delta
+  in triaxiality in simulations with different physics, $\Delta
   T=T_{\rm MHD}-T_{\rm DMO}$. 
@@
   minimum squares fit to the data.
-  Twisting does not correlate with triaxility in the same way at every
+  Twisting does not correlate with triaxiality in the same way at every
   radii. The strongest correlation appears around $0.12R_{200}$ ($28\pm2$ kpc).} 
@@
 \end{center}
-\caption{Correlations between the halo triaxility at different radii
+\caption{Correlations between the halo triaxiality at different radii
   and baryonic disc properties. 
@@
   The gas density at the center and the disc optical radius still show
-  a strong correlation, albeit weaker than what they had with the triaxility.}
+  a strong correlation, albeit weaker than what they had with the triaxiality.}
 \label{fig:twisting_correlations}
@@
 Au-27 that shows a good agreement in the shape measuremnts at all radii, 
-Above $15$ kpc, the differences between the triaxility values at
+Above $15$ kpc, the differences between the triaxiality values at
 Level4 and Level3 in MHD simulations are small and never exceed $0.1$. 
@@
 In the following subsections we present and comment in greater detail
-the results for the triaxility, the halo-disc alignment and the
+the results for the triaxiality, the halo-disc alignment and the
 correlations with baryonic disc properties.}
 
-\subsection{Triaxility}
+\subsection{Triaxiality}
 
@@
 different radii using the cumulative distributions for the 
-triaxility parameter $T$ defined as
+triaxiality parameter $T$ defined as
 
@@
 The left panel of Figure \ref{fig:triaxial_cumulative} shows that in
-the DMO sample the triaxility has a median larger than $2/3$ (a
+the DMO sample the triaxiality has a median larger than $2/3$ (a
 typical value that marks the transition from triaxiality to
@@
 halo.
-The right panel shows how the correlations in the MHD simulations go
-in the opposite direction with respect to DMO result.s
-There the median triaxility is always smaller than $1/3$ (a typical
-values that marks the transition from triaxility to prolateness) and this
+The middle panel in the same Figure \ref{fig:triaxial_cumulative}
+shows how the trends in the MHD simulations go 
+in the opposite direction with respect to DMO results.
+There the median triaxiality is always smaller than $1/3$ (a typical
+values that marks the transition from triaxiality to prolateness) and this
 median value decreases as we move towards the inner part of the halo.
 
-We now quantify this change in triaxility at the level of individual halos.
+We now quantify this change in triaxiality at the level of individual halos.
 We compute $\Delta T\equiv T_{\rm MHD}-T_{\rm DMO}$ to quantify the
-change between the triaxility in the MHD and the DMO simulation.
-Figure \ref{fig:delta_triaxial_cumulative} shows the cumulative
-distribution at the same radii as in
-Figure \ref{fig:delta_triaxial_cumulative}.  
-From this Figure we observe that at $R_{200}$ all the halos have
-reduced its triaxility include baryonic physics.
-At smaller radii this general trend continues, although 2 haloes (Au-11 and Au-17) 
-in our sample increased their triaxility with MHD physics. 
+change between the triaxiality in the MHD and the DMO simulation.
+The right panel in Figure \ref{fig:delta_triaxial_cumulative} shows
+the cumulative distribution at the same radii as in the other panels.
+There we observe that at $R_{200}$ all the halos have
+reduced its triaxiality after including baryonic physics.
+At smaller radii this general trend continues, although 2 haloes
+(Au-11 and Au-17)  in our sample increased their triaxiality with MHD physics. 
 However, this small fraction correspond to halos that already were
@@
 The median, mean and standard deviation of the twisting are $2$, $6$ and $8$ degrees, respectively.
-The correlation between twisting and triaxility also changes with
+The correlation between twisting and triaxiality also changes with
 radius as measured by the Spearman's rank correlation coefficient.
-The largest correlation shows with the halo triaxility measured at
+The largest correlation shows with the halo triaxiality measured at
 $0.12R_{200}$. 
@@
 Figure \ref{fig:disc_correlations} shows the correlations of
-these quantities with the triaxility at five different radii.
+these quantities with the triaxiality at five different radii.
 We use the Spearmen's rank correlation coefficient to quantify the
@@
 between twisting and the same baryonic properties that showed a high
-degree of correlation with the triaxility.
+degree of correlation with the triaxiality.
 In this case the disc to total ratio does not have a significant
@@
 accreting halos are pierced by many thinner filaments. 
-To what extent the twisting and high triaxility present in the MHD
+To what extent the twisting and high triaxiality present in the MHD
 halos can be linked to this dicotomy?
@@
 ellipsoids for the dark matter component.  
-Their results constrain the triaxility of this potential
+Their results constrain the triaxiality of this potential
 component. 
@@
 with the results \cite{LM10}. 
-The change of triaxility with radius in our simulations cannot account
+The change of triaxiality with radius in our simulations cannot account
 for these two extremely different shape constraints at different
@@
 disc and strongly  correlates with baryonic properties of the disc
-More precisely, the triaxility is smaller for extended and massive
+More precisely, the triaxiality is smaller for extended and massive
 stellar discs with low gas densities at its core.

### 2019-08-21 Document/paper.tex
volker

@@
 \usepackage{ae,aecompl}
+
+%\usepackage{txfonts}
+%\usepackage{times}
 
@@
 
-\title[Dark matter halo shapes at $z=0$] {Dark matter halo shapes at
-  $z=0$ in the Auriga simulations} 
+\title[Dark matter halo shapes in Auriga] {Dark matter halo shapes in the Auriga simulations} 
 \author[Prada et al.]{
@@
 matter only simulations and find a strong influence of baryons 
-in making dark matter haloes rounder at all radii compared to its dark 
+in making dark matter haloes rounder at all radii compared to their dark 
 matter only counterparts.
@@
 densities.  
-We measure the alignment between the halo and the disc at
+We measure the alignment between the halo and the disc shapes at
 different radii and find a high degree of alignment at all radii for most 
@@
 of halos in our sample are consistent with observational results derived
-from the Pal 5 stream that favor an almost spherical shape.
+from the Pal 5 stream that favours an almost spherical shape.
 Including baryons is a required element to achieve this
-level of agreement. In contrast, none of the simulations (dark matter
-only nor with baryons) match the constrains derived from the
-Sagittarius stream that favor an oblate dark matter halo.
+level of agreement. In contrast, none of the simulations (neither dark matter
+only nor with baryons) match the constraints derived from the
+Sagittarius stream that favour an oblate dark matter halo.
 \end{abstract}
@@
 accurate observations and modeling of our own Galaxy. 
-For instance, the study of the Milky Way (MW) morphology and its
-separation into global kinematic coherent components, such as its
+For instance, the study of the Milky Way's (MW) morphology and its
+separation into different kinematic components, such as 
 disc and bulge, has been used to support the existence of a Dark Matter (DM) component surrounding the Galaxy
 \citep{2000MNRAS.311..361O,2009PASJ...61..227S,2010JCAP...08..004C,2013ApJ...779..115B,Iocco15}. 
-In other words, explaining the matter budget and kinematic state of the MW also put constraints on the wider cosmological context that made possible its evolution.
+Explaining the matter budget and kinematic state of the MW also puts constraints on the wider cosmological context, besides testing specific models of galactic evolution.
 
@@
 satellite galaxies that got tidally disrupted by the gravitational
-potential of the MW, could be translated into tight constrains 
-both on the shape of the dark matter halo in the outer regions of our Galaxy \citep{1998ApJ...495..297J,1999MNRAS.307..495H, 1999MNRAS.307..877T} and also bound the properties of dark matter substructures, which also depend on the microphysics of a given DM particle.
+potential of the MW could be translated into tight constraints 
+both on the shape of the dark matter halo in the outer regions of our Galaxy \citep{1998ApJ...495..297J,1999MNRAS.307..495H, 1999MNRAS.307..877T} and the properties of dark matter substructures, which also depend on the microphysics of a given DM particle candidate.
 
-In any case, the observational constraints on the gravitational potential shape must be confronted against the expectations from different galaxy formation models in an explicit cosmological context.
+In any case, the observational constraints on the gravitational potential shape must be confronted against the expectations from different galaxy formation models in the full cosmological context.
 For instance, in the current paradigm of a Cold Dark Matter
-(CDM) dominated Universe galaxies are expected to be hosted by
-triaxial DM halos. To what extent the CDM expectations are born out by observations in our Galaxy?
+(CDM) dominated universe, galaxies are expected to be hosted by
+triaxial DM halos. To what extent are these CDM expectations born out in observations of our Galaxy?
 
-This question has been challenging to address because it has been difficult to produce realistic galactic discs in simulations within the CDM context \citep{1997ApJ...478...13N}.
-The success of such enterprise has been based on understanding how baryonic effects, such as stellar feedback and black hole feedback, play an important role in forming a galactic disc resembling the MW.
+This question has been challenging to address for many years because it has been difficult to produce realistic galactic discs in simulations within the CDM context \citep{1997ApJ...478...13N}.
+It is now understood that a prerequisite for successful disc formation is an adequate 
+accounting of strong baryonic feedback effects, such as stellar feedback and black hole feedback, because they play an important role in forming late-time galaxies resembling the MW.
 Along the way, different numerical experiments have also shown that the baryonic
-effects also impact the DM halo shape making it rounder
-than it otherwise be in a DM-only simulation
+effects also impact the DM halo shape, making it rounder
+than it would otherwise be in a DM-only simulation
 \citep{Dubinski94,Debattista08,Kazantzidis10,Abadi10,Bryan13,Chua19,Artale19}. 
-Another important aspect of the disc-halo relationship dynamics, namely, the radial evolution of the alignment between the stellar disc and the DM halo, has also been explored in some simulations \citep{Bailin05,Debattista13}.
+Another important aspect of the disc-halo relationship, namely the radial evolution of the alignment between the stellar disc and the DM halo, has also been explored in some simulations \citep{Bailin05,Debattista13}.
 
-Observational constraints of the dark matter halo
-have also been in tension and rapidly evolving during the last decade.  
-One can find studies favoring prolate
+Observational constraints on the dark matter halo shape
+have partly been in mutual tension, and have been rapidly evolving during the last decade, hinting that they are affected by substantial systematic uncertainties.
+One can find studies favouring prolate
 \citep{Banerjee_and_Chanda_2011,Bowden_et_al._2016},  oblate
@@
 spherical configurations \citep{Bovy16}.  
-Constraints from modeling of stellar streams discard the prolate
+Constraints from modeling stellar streams discard the prolate
 configuration \citep{LM10,Pearson_et_al._2015,Bovy16} although some other studies
-still doubt that stellar streams can be used to constrain the halo
-shape once other assumptions, such as the density profile, are relaxed
+still question whether stellar streams can be used to constrain the halo
+shape once certain assumptions, such as the density profile, are relaxed
 \citep{Ibata_et_al._2013}.
 
-In this paper we analyze the internal DM halo shape in thirty MW type
-galaxies from state-of-the-art simulations from the Auriga project.
-These simulations have large enough numerical resolution, and explicit
-cosmological context and an appropriate feedback physics to produce
+In this paper, we analyze the internal DM halo shape in thirty MW-type
+galaxies  from the Auriga project, which are state-of-the-art hydrodynamical simulations of galaxy formation.
+They have large enough numerical resolution, include an explicit
+cosmological context, and have appropriate feedback physics to produce
 realistic MW discs.
 Furthermore, the relatively large number of simulated systems allows us
-to have a handle on the statistical significance of our results.
+to obtain a handle on the statistical significance of our results.
+
 This paper is structured as follows. 
-In Section \ref{sec:numerical} we present the most relevant details of
-the simulations, in Section \ref{sec:method} we present the method
-that we use to measure the DM halo shape. 
-In Section \ref{sec:results} we present our results focusing on the
-radial shape trends at $z=0$ and the alignments with the stellar disc.
-We discuss our results in Section \ref{sec:discussion} to place them
+In Section~\ref{sec:numerical} we describe the most relevant details of
+the simulations, and in Section~\ref{sec:method} we discuss the method
+we use to measure the DM halo shape. 
+In Section~\ref{sec:results} we present our results focusing on the
+radial shape trends at $z=0$, and the alignments with the stellar disc.
+We place our findings in Section~\ref{sec:discussion} 
 into the context of other numerical work, explore correlations of the
-shape with baryonic properties in the disc and finally make a direct
+shape with baryonic properties in the disc, and finally make a direct
 comparison against observational constraints for the MW's dark matter halo shape.
-We finalize with our conclusions in Section \ref{sec:conclusions}.
+We give our conclusions in Section~\ref{sec:conclusions}.
 
@@
 
-The Auriga project offers cosmological zoom in simulations of MW-sized 
-dark matter halos in a $\Lambda$CDM cosmology. 
-This simulations come in two versions: dark matter only and
-baryonic physics including magetohydrodynamics.
-A detailed description of the simulations and their disc properties
-can be found in \citep{auriga}.
-Here we summarize its main features.
+The Auriga project carries out cosmological zoom-in simulations of MW-sized 
+halos in a $\Lambda$CDM cosmology. 
+The simulations come in two versions: dark matter only and full 
+baryonic physics included (this entails magetohydrodynamics, gas cooling, star formation, black hole growth, and associated feedback processes).
+A detailed description of the simulations, the numerical treatment, and the resulting galaxy properties can be found in \citet{auriga}.
+Here we summarize some of the main features.
 
-The objects in the simulations were selected from a set of 30
-isolated halos in the Evolution and Assembly of GaLaxies and their
+The simulated objects were chosen as a set of 30
+isolated halos in the dark matter parent simulation of the Evolution and Assembly of GaLaxies and their
 Environments (EAGLE)  project \citep{Eagle}.   
 These halos were randomly selected from a sample of the most isolated
-halos at $z=0$ whose virial mass $M_{200}$ was between $10^{12}M_\odot$ and
-$2\times 10^{12}M_\odot$. 
-The cosmological parameters in these simulations correspond to
+halos at $z=0$ whose virial mass $M_{200}$ was between $10^{12}\, {\rm M}_\odot$ and
+$2\times 10^{12}\, {\rm M}_\odot$. 
+The cosmological parameters in the simulations correspond to
 $\Omega_m=0.307$, $\Omega_b=0.048$, $\Omega_\Lambda=0.693$ and a
@@
 
-The selected halos were re-simulated at higher resultion by applying a
-zoom-in technique with varying physical realism using the moving-mesh AREPO code
-that includes gravity, ideal magnetohydrodynamics,  phenomenological
-descriptions for star formation, chemical enrichment from supernovae
-and its stellar feedback.   
-\citep{arepo,2013MNRAS.432..176P}.
-The simulation also follows the formation and evolution of black holes
-together with the Active Galactic Nuclei feedback
+The selected halos were then re-simulated at much higher resolution by applying a
+zoom-in technique with variable spatial resolution using the moving-mesh code AREPO  \citep{arepo, 2013MNRAS.432..176P},
+and by using a comprehensive model for galaxy formation physics
+that includes gravity, ideal magnetohydrodynamics,  a phenomenological
+description of star formation, chemical enrichment from supernovae
+and stellar feedback.   
+The simulations also follow the formation and evolution of black holes
+together with  Active Galactic Nuclei (AGN) feedback
 
 The 30 zoom-in halos have a dark matter particle mass of $\sim 3\times
-10^5$\Msun while the barynic mass resolution is $\sim 5\times 10^4$\Msun.
-The softening lenght for gravitational force computation for stellar
+10^5$\Msun while the baryonic mass resolution is $\sim 5\times 10^4$\Msun.
+The gravitational force softening length for stellar
 particles and high-resolution dark matter particles 
-is fixed to be 500 $h^{-1}$ pc in comoving coordinates up to $z=1$,
+is fixed to be 500 $h^{-1}\,{\rm  pc}$ in comoving coordinates up to $z=1$,
 and 396 pc in physical coordinates afterwards.
 The gravitational softening length for gas cells changes with the mean
-cell radius but is limited to be larger than the stellar softening
-lenght and 500 $h^{-1}$ pc comoving. 
-{\bf We refer to this setup as the Level4 resolution. 
-Six of these haloes were also simulated at a higher Level3 resolution
-that represent an increase by a factor of 8 in mass and 2 in spatial
+cell radius but is limited to be at least the stellar softening
+length of 500 $h^{-1}$ pc comoving. 
+ We refer to this setup as the ``Level-4'' resolution, based on the nomenclature of the Auriga project.
+Six of these haloes were also simulated at a higher ``Level-3'' resolution, 
+representing an increase by a factor of 8 in mass and a factor of 2 in spatial
 resolution.  
 We use the higher resolution haloes to define a minimal radius above
-which our results can be considered as converged.} 
+which our results can be considered converged.
 From now on we refer to the haloes simulated with baryonic physics as the
-MHD sample and to the haloes simulated with dark matter only as the
+MHD sample, and to the haloes simulated with dark matter only as the
 DMO sample.
@@
 \includegraphics[width=0.9\textwidth]{shape_resolution.pdf}
-\caption{Axial ratios for the six halos simulated at two different
-  resolutions with two different physics (DMO and MHD). 
-  In DMO simulations there is a good agreement between the two
+\caption{Axes ratios for the six halos simulated at two different
+  resolutions with two different physical models (DMO and MHD). 
+  In DMO simulations there is good agreement between the two
   resolutions (L3 and L4) at all radii down to scales of $\approx 1$
   kpc from the center. 
-  In MHD simulations there are noticeable differences at scales below
+  In MHD simulations, there are noticeable differences at scales below
   $\approx 10$ kpc. 
-  In this paper we only report results at scales larger $\approx 16$ kpc
+  In this paper, we only report results at scales larger than $\approx 16$ kpc
   ($R_{200}/16$).}
@@
   \end{tabular}
-  \caption{Axial ratios of Auriga dark matter halos at $z=0$ at
-    different radii in DMO simulations. The subscripts $16$, $8$, $4$, $2$, $1$,
+  \caption{Axes ratios of Auriga dark matter halos at $z=0$ at
+    different radii in the DMO simulations. The subscripts $16$, $8$, $4$, $2$, and $1$,
     indicate that the shape was measured at radii of $R_{200}/16$,
-    $R_{200}/8$, $R_{200}/4$, $R_{200}/2$, $R_{200}$, respectively.   \label{table:DMO}}
+    $R_{200}/8$, $R_{200}/4$, $R_{200}/2$, and $R_{200}$, respectively.   \label{table:DMO}}
 \end{table*}
@@
   \end{tabular}
-  \caption{Same as Table \ref{table:DMO} for MHD simulations.   \label{table:MHD}}
+  \caption{Same as Table~\ref{table:DMO}, but for the MHD simulations.   \label{table:MHD}}
 \end{table*}
@@
 \includegraphics[width=0.45\textwidth]{level4_MHD_halo_24_4.png}
-  \caption{DM density in logarithmic scale within a slice of one tenth
+  \caption{DM density on a logarithmic color scale within a slice of thickness one tenth
     of the virial radius.
@@
     The black ellipses show the results of the fitting procedure
-    described in Section \ref{sec:method}. 
+    described in Section~\ref{sec:method}. 
     Upper/lower panels correspond to DMO/MHD simulations, respectively.
@@
     This plot showcases the most noticeable effect in all halos
-    across the Auriga simulations: haloes are rounder at all radii
-    after baryonic physics is included.}
+    across the Auriga simulations: haloes become rounder at all radii
+    once baryonic physics is included.}
 \label{fig:slices}
@@
 \end{center}
-\caption{Axial ratios for all simulated halos.
+\caption{Axes ratios for all simulated halos.
   Left/right panel corresponds to DMO/MHD simulations, respectively.
@@
   the outskirts (opposite to the DMO trend). 
-  Third, halos in MHD are rounder than its DMO counterparts.
-  These three points are further clarified in Figure 
-  The first and second points are claryfied in Figure
-  \ref{fig:triaxial_cumulative} through cumulative triaxiality
-  distributions}
+  Third, halos in the MHD simulations are rounder than their DMO counterparts.
+  The first and second points are further 
+  clarified in Figure~\ref{fig:triaxial_cumulative} through cumulative triaxiality
+  distributions.}
   \label{fig:triaxiality_plane}
@@
 \includegraphics[width=0.32\textwidth]{delta_triaxiality_distro.pdf}
-\caption{Triaxiality cumulative distribution at five different radii.
-  Right/middle panel corresponds to the cumulative distribution of
-  triaxiality in DMO/MHD simulations, respectively. 
-  In DMO simulations the median triaxiality at all radii is larger
+\caption{Cumulative distributions of the triaxiality at five different radii.
+  Right/middle panels correspond to the cumulative distribution of
+  triaxiality in the DMO/MHD simulations, respectively. 
+  In DMO simulations, the median triaxiality at all radii is larger
   than $2/3$. Furthermore, the triaxiality increases as one moves
   towards the inner part of the halo.
-  In MHD simulations these trend reverses.
-  The median triaxiality at all radii is smaller than $1/3$ and the
-  halo is less triaxial as on moves towards the stellar disc.
-  The right panel, shows the cumulative distribution for the changes
+  In MHD simulations, this trend reverses.
+  The median triaxiality at all radii is smaller than $1/3$, and the
+  halo becomes less triaxial as on moves towards the stellar disc.
+  The right panel shows the cumulative distribution of the changes
   in triaxiality in simulations with different physics, $\Delta
   T=T_{\rm MHD}-T_{\rm DMO}$. 
-  At the virial radius all halos become less triaxial in the MHD
-  simulations, the change is stronger towards the halo center.
+  At the virial radius, all halos become less triaxial in the MHD
+  simulations, and the change is stronger towards the halo center.
   Only two haloes in the sample show the opposite trend of becoming
-  more triaxial (but only at the smaller radii).} 
+  more triaxial (but only at the smallest radii).} 
 \label{fig:triaxial_cumulative}
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{angles_alignment_DM.pdf}
 \includegraphics[width=0.9\textwidth]{angles_alignment_MHD.pdf}
 \end{center}
-\caption{\textbf{RP: I think the upper row that compares the shape of the halo from the DMO sim with the orientation of the disk in the MHD sim is hard to interpret.
-Maybe instead show in the first row the angle against a fixed axis (e.g.
-total angular momentum of the halo?)} Angles between the principal axis of the dark matter halo
+\caption{Angles between the principal axis of the dark matter halo
   shape and the angular momentum of the stellar disc 
@@
   Each panel compares the alignment of the corresponding
-  major/middle/minor axis in the halo.
+  major, middle, and minor axis in the halo.
   Thin lines correspond to each one of the thirty halos in the sample
-  while the thick line traces the median value at every radius.
-  In the upper row the haloes come from the DMO simulation.
+  while the thick line traces the median value as a function of  radius.
+  In the upper row, the haloes come from the DMO simulation.
   The first thing to notice is that the major axis is statistically
@@
   The second important result is that the directions in the ellipsoids
-  describing the shape are constant as a function of radius except two
+  describing the shape are constant as a function of radius except for two
   cases. 
-  In the lower row the haloes come from the MHD simulation providing a 
+  In the lower row the haloes come from the MHD simulation, providing a 
   self-consistent comparison with the stellar discs. 
-  In this case the sample presents a good alignment of the angular
+  In this case, the sample presents a good alignment of the angular
   momentum with the minor halo axis. 
-  Furthermore, the dark matter shells twists significantly in $1/5$ of
-  the sample. For the remaining haloes the alignment is almost
+  Furthermore, the dark matter shells twist significantly in $1/5$ of
+  the sample. For the remaining haloes, the alignment is almost
   constant as a function of radius. 
@@
   in each panel's title.
-  The label with the $\rho$ value corresponds to the Spearmans rank
+  The label with the $\rho$ value corresponds to the Spearman's rank
   correlation coefficient (mean value and uncertainty estimated via
-  jackknife resampling) while the line shows the result of the
+  jackknife resampling) while the line shows the result of a
   minimum squares fit to the data.
   Twisting does not correlate with triaxiality in the same way at every
-  radii. The strongest correlation appears around $0.12R_{200}$ ($28\pm2$ kpc).} 
+  radius. The strongest correlation appears around $0.12\, R_{200}$ ($28\pm2$ kpc).} 
 \label{fig:alignment_correlations}
@@
   and baryonic disc properties. 
-  The label with the $\rho$ value corresponds to the Spearmans rank
+  The label with the $\rho$ value corresponds to the Spearman's rank
   correlation coefficient (mean value and uncertainty estimated via
@@
   The line is the best minimum squares fit to a line.
-  The x-axis in the first column is the gas density at the center of
-  the galaxy with in a sphere of radius  $1$ kpc \citep{Pakmor17};
-  the second column shows the disc to total mass ratio and the last
+  The $x$-axis in the first column is the gas density at the center of
+  the galaxy within a sphere of radius  $1$ kpc \citep{Pakmor17};
+  the second column shows the disc to total mass ratio, and the last
   column includes the disc optical radius defined to be the radius at which the
@@
   ($R_{200}/16$ and $R_{200}/8$).
-  Extended and massive stellar discs with a low gas content at its
-  core are correlated with low dark matter triaxilities.
+  Extended and massive stellar discs with a low gas content at their
+  cores are correlated with low dark matter triaxialities.
   The correlation decreases as one approaches larger radii.}
@@
 \caption{Twisting in the halo-disc alingment as a function of the same
-  baryonic disc properties in Figure \ref{fig:disc_correlations}.
-  The label with the $\rho$ value corresponds to the Spearmans rank
+  baryonic disc properties as in Figure~\ref{fig:disc_correlations}.
+  The label with the $\rho$ value corresponds to the Spearman's rank
   correlation coefficient (mean value and uncertainty estimated via
@@
   The line is the best minimum squares fit to a line.
-  In this case the disc to total mass ratio does not correlate with the alignment twisting
+  In this case the disc to total mass ratio does not correlate with the alignment twisting.
   The gas density at the center and the disc optical radius still show
-  a strong correlation, albeit weaker than what they had with the triaxiality.}
+  a strong correlation, albeit weaker than the correlation of each with the triaxiality.}
 \label{fig:twisting_correlations}
@@
   mean stellar age in the bulge/disc and the lookback formation time of the
-  dark matter halo (time at which it has half of its present mass).
-  The label with the $\rho$ value corresponds to the Spearmans rank
+  dark matter halo (time at which half of its present mass has assembled).
+  The label with the $\rho$ value corresponds to the Spearman's rank
   correlation coefficient (mean value and uncertainty estimated via
@@
 
-The DM halo shape is an estimate of either the isopotential or
+The DM halo shape is usually estimated either based on the isopotential or
 isodensity surfaces.   
-Observational inference models usually estimate the 
-isopotential contours which are probed by tracers (gas, stars), while
-simulations work with the isodensity contours which can be directly
+Observational inferences typically target the 
+isopotential contours which are probed by some dynamical tracers (gas, stars), while
+simulations more often work with the isodensity contours which can be directly and easily
 calculated from particle positions.  
-Furthermore, the density contours in thin shells are very sensitive to
-the presence of small satellites.  
+Furthermore, it is well known that the density contours in thin shells are very sensitive to
+the presence of small satellites \citep{Springel2004}.  
 For this reason we measure the shape by taking
@@
 contours for radii $\leq 140$ kpc as explored by
-\citep{VeraCiro11}.
+\citet{VeraCiro11}.
 
@@
 \citep{Allgood06},  
-
 \begin{equation}
@@
 \end{equation}
+where the particle positions are measured with respect to the minimum of the
+gravitational potential in each halo and are weighted by the inverse of 
+the k-th particle distance squared, $d_k^2 = \sum_{i=1}^3 x_k^{(i)} x_k^{(i)}$, giving each particle the same
+weight independent of distance.
 
-where the particle positions are measured from the minimum of the
-gravitational potential in each halo and each is weighted by the k-th
-particle distance $d_k^2=x_k^2+y_k^2+z_k^2$.
+Diagonalization of this tensor yields the eigenvectors and
+eigenvalues that approximate the dark matter halo with an ellipsoidal shape.
+The axis lenghts of this ellipsoid, $a\geq b \geq c$, are the square
+roots of the  eigenvalues, and the directions of the principal
+axis are the corresponding eigenvectors.
 
-The diagonalization of this tensor yields the eigenvectors and
-eigenvalues that represent an ellipsoidal dark matter halo.
-The axis lenghts of this ellipsoid $a\geq b \geq c$ are the square
-root of the ${\bf I}$ eigenvalues and the direction of the principal
-axis are the corresponding eigenvectors
-
-We start the calculations taking into account particles within a
-sphere of radius $R_{\rm initial}$ and then recharacterize the
-triaxial parameters 
-by taking into account particles within an ellipsoid of semi-axes
-$r,r/q,r/s$ and re-scaled distance $d^2=x^2+(y/q)^2+(z/s)^2$, where $q
-= b/a$ and $s=c/a$ are the previously calculated axial ratios. 
-We repeat this process until the average deviation of semi-axes is
-less than $10^{-6}$.  
-After convergence we define a unique radius $R$ as the geometrical
-mean of the axial lenghts $R=(abc)^{1/3}$.
+We start the calculations taking into account all particles within a
+sphere of radius $R_{\rm initial}$ and then iteratively recompute the
+triaxial parameters by taking into account those particles within an ellipsoid of semi-axes
+$r$, $r/q$ and $r/s$, and re-scaled distance $d^2=x^2+(y/q)^2+(z/s)^2$, where $q
+= b/a$ and $s=c/a$ are the previously calculated axes ratios. 
+We repeat this process until the average deviation of the semi-axes is
+less than $10^{-6}$. For the converged shape, we define a single characteristic radius $R$ 
+as the geometrical mean of the axes lengths $R=(abc)^{1/3}$.
 We use this radial coordinate $R$ to parameterize the spatial changes
 in halo shape we report in the following sections.
-This is the same method used to estimate the halo shape in the DM-only
+This is essentially the same method used to estimate the halo shape in the DM-only
 Aquarius simulations \citep{VeraCiro11}.
 
-Following the convergence criterion by \cite{VeraCiro11} in DM only simulations
+Following the convergence criterion by \cite{VeraCiro11} for DM-only simulations,
 we restrict the measurement of the ellipsoidal parameters to radii
-between $1$ kpc and $R_{200}$ where  $R_{200}$ corresponds to the radius
-computed enclosing a sphere with 200 times the critical density of the
-Universe. 
-{\bf However, this scale is similar to the gravitational smoothing length
-for stellar particles.
-For this reason we use the Level3 simulations performed at higher
+between $1$ kpc and $R_{200}$, where  $R_{200}$ corresponds to the viral radius
+defined as the sphere  enclosing 200 times the critical density of the
+Universe. However, the inner scale is similar to the gravitational smoothing length
+for stellar particles in our default simulations.
+For this reason, we use the level-3 simulations of Auriga performed at higher
 resolution to gauge the convergence of the shape measurements in the
@@
 Figure \ref{fig:resolution} shows the results for the six halos
-available both at Level3 and Level4 resolutions.
+available both at level-3 and level-4 resolutions.
 The dotted lines compare the DMO simulations showing that down to
-scales of $1$ kpc the two resolutions yield comparable results
+scales of $1$ kpc the two resolutions yield very comparable results
 \citep{VeraCiro11}. 
-In MHD simulations the situation is different, as expected. 
-The shape ratios $b/a$ and $c/a$ start to differentiate
-from each other at radii smaller than $15$ kpc, tith the exception of
-Au-27 that shows a good agreement in the shape measuremnts at all radii, 
-Above $15$ kpc, the differences between the triaxiality values at
-Level4 and Level3 in MHD simulations are small and never exceed $0.1$. 
+In MHD simulations the situation is less clean, as expected. 
+The shape ratios $b/a$ and $c/a$ typically start to differ
+from each other for different resolutions at radii smaller than $15$ kpc, 
+with the exception of Au-27, which  shows good agreement of the shape 
+measurements at all radii. Outside $15$ kpc, the differences between the triaxiality values at
+level-4 and level-3 in the hydrodynamics simulations are small and never exceed $0.1$. 
 For this reason, in order to make the DM halo shape results comparable
-in DMO and MHD simulations we only report measurements above $15$
-kpc.}
+in the dark matter-only and the hydrodynamic simulations we concentrate in 
+the following on measurements for radii larger  than $15$~kpc.
 
-In our results we express the radius as a fraction of $R_{200}$ in
-order to have a self-consistent dimensionless radius scale across all
-halos. 
-Given the small variance across halos, each dimensionless radius is
-associated with a physical value with a mean value and a standard deviation.
-For instance, over the 30 halos in the sample, the dimensionless
-radius $R_{200}$ corresponds to a physical distance of $230\pm 16$
-kpc.  
-Finally, we also measure the alignment of the halo shape against the
-stellar disc angular momentum. 
-We measure the angular momentum vector using the $10\%$ oldest stellar
-particles within the virial radius.
+In our results we express the radius in units  of $R_{200}$ in
+order to have a self-consistent dimensionless radial scale across all
+halos. Given the similarity of the virial radii across halos, each dimensionless radius is
+closely associated with a physical scale with a certain mean value and small standard deviation.
+For instance, over the 30 halos in the sample, a dimensionless
+radius of unity corresponds to a physical distance of $230\pm 16$
+kpc.   Finally, we also measure the alignment of the halo shape against the
+stellar disc angular momentum.  We measure the angular momentum vector 
+using the $10\%$ oldest stellar particles within the virial radius.
 
@@
 
-{\bf The main measurements are summarized in Table \ref{table:DMO} for the
-DMO simulations and Table \ref{table:MHD} for the MHD simulations.
-These results are computed at five different radii $R_{200}/16$,
-$R_{200}/8$, $R_{200}/4$, $R_{200}/2$ and $R_{200}$.
-In the following subsections we present and comment in greater detail
+Our main measurements for the halo shapes are summarized in Table \ref{table:DMO} for the
+DMO simulations, and in Table \ref{table:MHD} for the MHD simulations.
+These results are computed at five different radii, $R_{200}/16$,
+$R_{200}/8$, $R_{200}/4$, $R_{200}/2$, and $R_{200}$.
+In the following subsections, we discuss 
 the results for the triaxiality, the halo-disc alignment and the
-correlations with baryonic disc properties.}
+correlations with baryonic disc properties in greater detail.
 
@@
 
-In the DMO sample we find that halos are rounder with increasing radius.
+In the DMO sample, we find that halos become rounder with increasing radius.
 The upper panels in Figure \ref{fig:slices} illustrate this effect.
 The contours show a projected DM slice while the ellipsoid corresponds
-to the full 3D shape determination. 
-There we see a highly ellipsoidal halo shape at radii $\sim 3$kpc
-that becomes less triaxial at $\approx 50$ kpc.
+to the full 3D shape determination. There we see a highly ellipsoidal halo shape at radii $\sim 3$ kpc
+that becomes less elongated at $\approx 50$ kpc.
 
 We summarize this trend in Figure \ref{fig:triaxiality_plane} by
-plotting the results of all the 30 halos in the DMO sample.
+plotting the results of all 30 halos of the DMO sample.
 The left panel shows every halo in the $c/a$-$b/a$ plane at
-two different radii $R_{200}/16$ $(\approx 14$kpc$)$ and $R_{200}$. 
+two different radii, $R_{200}/16$ $(\approx 14$kpc$)$ and $R_{200}$. 
 The outer part of the halo is systematically rounder than its inner
-region. 
-Nevertheless the halo shape can still be considerated to be prolate at
+region. Nevertheless, the halo shape can still be considered to be prolate at
 all radii.
 
-A different picture presents itself in the MHD sample.
-There all halos become rounder at all radii than its DMO
-version.
-The lower panel in Figure \ref{fig:slices} can be directly compared to
-its MHD counterpart; there we observe how at large radii the halo
-becomes oblate and almost spherical. 
-The right panel in Figure \ref{fig:triaxiality_plane} shows the
+A different picture emerges for the MHD sample.
+There all halos are rounder than their corresponding DMO
+version at all radii. The lower panel of Figure~\ref{fig:slices} can be directly compared to
+its MHD counterpart; there we observe how at large radii the hydrodynamic halo
+becomes oblate and almost spherical. The right panel in Figure~\ref{fig:triaxiality_plane} shows the
 results for the 30 halos in the MHD sample.
 
-In Figure \ref{fig:triaxial_cumulative} we summarize the results at
+In Figure~\ref{fig:triaxial_cumulative}, we summarize the results at
 different radii using the cumulative distributions for the 
-triaxiality parameter $T$ defined as
-
+triaxiality parameter $T$, defined as 
 \begin{equation}
@@
 The left panel of Figure \ref{fig:triaxial_cumulative} shows that in
-the DMO sample the triaxiality has a median larger than $2/3$ (a
+the DMO sample the median triaxiality is larger than $2/3$ (a
 typical value that marks the transition from triaxiality to
-prolateness) at all radii. 
-Furthermore this median value increases as we move towards the inner part of the
-halo.
-The middle panel in the same Figure \ref{fig:triaxial_cumulative}
+prolateness) at all radii. Furthermore this median value increases 
+as we move towards the inner part of the halo.
+The middle panel in the same Figure~\ref{fig:triaxial_cumulative}
 shows how the trends in the MHD simulations go 
-in the opposite direction with respect to DMO results.
+in the opposite direction with respect to the DMO results.
 There the median triaxiality is always smaller than $1/3$ (a typical
-values that marks the transition from triaxiality to prolateness) and this
+value markin the transition from triaxiality to prolateness) and this
 median value decreases as we move towards the inner part of the halo.
@@
 We compute $\Delta T\equiv T_{\rm MHD}-T_{\rm DMO}$ to quantify the
-change between the triaxiality in the MHD and the DMO simulation.
-The right panel in Figure \ref{fig:delta_triaxial_cumulative} shows
+change between the triaxiality in the MHD and the DMO simulations.
+The right panel in Figure~\ref{fig:triaxial_cumulative} shows
 the cumulative distribution at the same radii as in the other panels.
-There we observe that at $R_{200}$ all the halos have
-reduced its triaxiality after including baryonic physics.
+It is evident that at $R_{200}$ all the halos have
+reduced their triaxiality after including baryonic physics.
 At smaller radii this general trend continues, although 2 haloes
-(Au-11 and Au-17)  in our sample increased their triaxiality with MHD physics. 
-However, this small fraction correspond to halos that already were
+(Au-11 and Au-17)  in our sample increase their triaxiality with baryonic physics. 
+However, this small fraction corresponds to halos that already were
 outliers in the DMO sample and had triaxilities around $1/3$,
-considerably lower than its parent sample.
+considerably lower than the mean of the parent sample.
 
@@
 
-A common assumption in dynamical models of the MW DM halo is that
-its angular momentum is perfectly aligned with the stellar disc minor axis.
-Although it is a reasonable assumption to guarantee the stability of
-the galactic disc in simplified models of isolated galaxies, this
-might not perfectly hold in an explicit cosmological context. 
+A common assumption in dynamical models of the MW dark matter halo is that
+its angular momentum is perfectly aligned with the minor axis of the stellar disc.
+Although this is a reasonable assumption due to the stability of
+the galactic disc in this configuration in simplified models of isolated galaxies, this
+might not perfectly hold in a full cosmological context. 
 To examine the degree of validity of this assumption we study in this
 subsection the alignment between the stellar disc's angular momentum
-eigenvectors of the dark matter halo shape.
+eigenvectors and the dark matter halo shape.
 
 The upper row in Figure \ref{fig:cumulative_alignment} shows 
-the alignments between the major/intermediate/minor axis of the
-halo and the disc angular momentum as a function of the dimensionless radius at which the halo shape was measured.
-The upper row shows the angle between the DMO halo and the stellar
+the alignments between the major, intermediate, and minor axis of the
+halo and the disc angular momentum, as a function of the dimensionless radius at which the halo shape was measured. The upper row shows the angle between the DMO halo and the stellar
 disk in the MHD simulation.
@@
 results for the MHD simulations.
-The most striking feature of this plot is that most of the discs have their angular momentum aligned with the minor axis of the halo and perpendicular to the intermediate and major axis.
+The most striking feature of this plot is that most of the discs have their angular momentum aligned with the minor axis of the halo, perpendicular to the intermediate and major axis.
 The median and the standard deviation of the alignment angles with
@@
 
-In six halos the alignment changing significantly as a function of radius, this can be seen as a twisting in the shape ellipsoids. 
-As we are dealing with oblate halos $b/a\approx 1$ and the
+In six halos the alignment changes significantly as a function of radius, 
+as  can be seen by the twisting in the shape ellipsoids. 
+Because we are dealing with oblate halos $b/a\approx 1$, note that the
 directions corresponding to the medium and major axis could be subject
-to noise.
-For this reason, in order to better quantify the twisting for each
-halo we take the standard deviation of the angle with the minor
+to noise. For this reason, and in order to better quantify the twisting for each
+halo, we take the standard deviation of the angle with the minor
 axis, which should be less susceptible to noise.
 With this measurement, twisting becomes a global property of the halo,
-as the standard deviation is measured over the different radii at
+as the standard deviation is measured over all the different radii at
 which we have quantified the alignment.
 
-Figure \ref{fig:alignment_correlations} shows the correlation between
-twisting at the four different radii at which we have measured the
-alignments. 
-The median, mean and standard deviation of the twisting are $2$, $6$ and $8$ degrees, respectively.
+Figure~\ref{fig:alignment_correlations} shows the correlation between
+the twisting at the four different radii at which we have measured the
+alignments. The median, mean and standard deviation of the twisting 
+are $2$, $6$ and $8$ degrees, respectively.
 The correlation between twisting and triaxiality also changes with
 radius as measured by the Spearman's rank correlation coefficient.
-The largest correlation shows with the halo triaxiality measured at
-$0.12R_{200}$. 
-The most important consequence of this changing degree in correlation
-is that twisting cannot only be explained by large triaxiality values
+The largest correlation is obtained for the halo triaxiality measured at
+$0.12R_{200}$. The most important consequence of this changing degree in correlation
+is that twisting cannot be explained only by large triaxiality values
 and a possibly noisy determination of the shape axis.
@@
 
-The presence of baryons produces rounder dark matter halos than its DMO
-counterpart.
-To better understand this relationship we quantify the correlation
-between halo shape with baryonic disc properties.  
+The presence of baryons produces rounder dark matter halos than found for the 
+corresponding DMO \textbf{}counterpart. To better understand this relationship we examine the correlation
+between halo shape and baryonic disc properties.  
 Looking into the measurements already reported by \cite{auriga} and
-\cite{Pakmor17} we find three baryonic quantities that have the
+\cite{Pakmor17}, we find three baryonic quantities that have the
 strongest correlation with DM halo triaxiality: the central gas
-density in a sphere of radius $1$kpc, the disc to total mass ratio and
+density in a sphere of radius $1$ kpc, the disc to total mass ratio, and
 the optical radius.
 
-Figure \ref{fig:disc_correlations} shows the correlations of
+Figure~\ref{fig:disc_correlations} shows the correlations of
 these quantities with the triaxiality at five different radii.
 We use the Spearmen's rank correlation coefficient to quantify the
-correlation strength.
-We find that the strongest correlations are found with the halo shape
-measured at radii smaller than $0.12R_{200}$.
+correlation strength. We find that the strongest correlations are found with the halo shape
+measured at radii smaller than $0.12\, R_{200}$.
 The  trend is such that halos with large triaxiality correlate with
-high gas density and stellar discs with low mass and small size. 
-In turn, massive and large stellar discs within with low density of
-gas in its core correlate with low halo triaxiliaty.
+high gas density, and stellar discs with low mass and small size. 
+In turn, massive and large stellar discs with low density of
+gas in their cores correlate with low halo triaxiliaty.
 
@@
 the situation in DMO simulations where the shape is coherent as a
-function of radius.
-In Figure \ref{fig:twisting_correlations} we show the correlation
+function of radius. In Figure~\ref{fig:twisting_correlations}, we show the correlation
 between twisting and the same baryonic properties that showed a high
@@
 In this case the disc to total ratio does not have a significant
-degree of correlation.
-Instead, the disc optical radius and the gas density at the core are
-the most correlated. 
+degree of correlation. Instead, the disc optical radius and the gas density
+at the core are the most correlated. 
 The correlation is such that extended stellar discs with a very low
-gas density at its core show the most coherent halo shapes.
+gas density at their cores show the most coherent halo shapes.
 
-{\bf Recently \cite{2017MNRAS.469..594B} reported that MW-like DM haloes can
-be roughly splint into two distinct families: stalled and accreting.
+Recently, \citet{2017MNRAS.469..594B} reported that MW-like DM haloes can
+be roughly split into two distinct families: stalled and accreting.
 Stalled haloes assembled early and have remained almost unchanged
 in the last $7$ Gyr, while accreting halos have been growing
-constantly.
-\cite{2017MNRAS.469..594B} also link the two populations to
+constantly. \citet{2017MNRAS.469..594B} also link the two populations to
 differences in the dark matter filaments feeding the halos. 
-Stalled halos at $z=0$ are embbeded in a single large thick filament, while
+Stalled halos at $z=0$ are embedded in a single large thick filament, while
 accreting halos are pierced by many thinner filaments. 
-To what extent the twisting and high triaxiality present in the MHD
-halos can be linked to this dicotomy?
-In Figure \ref{fig:twisting_age} we show the correlation between the
-twisting and the age of the bulge, the age of the stellar disc and the
-DM halo formation redshift. 
-The ages are estimated directly as the mean value in the stellar age
-distribution for each component, while the formation redshift is
-defined as the redshif at which the halo already has half of its $z=0$
-mass. 
-In the three cases we find a correlation between ages and twisting
-that goes in the direction claimed by \cite{2017MNRAS.469..594B}:
-components with early assembly (i.e. stalled) have a smaller degree of
-twisting.
-A detailed study with respect to the cosmic web location is beyond the
-scope of our paper.}
+To what extent can the twisting and high triaxiality present in the MHD
+halos be linked to this dicotomy?
+
+In Figure~\ref{fig:twisting_age} we show the correlation between the
+twisting and the age of the bulge, the age of the stellar disc, and the
+DM halo formation redshift. The ages are estimated directly as the mean 
+value in the stellar age distribution for each component, while the formation redshift is
+defined as the redshift at which the halo has for the first time surpassed half of its final $z=0$
+mass. In the three cases we find a correlation between age and twisting
+that goes in the direction claimed by \citet{2017MNRAS.469..594B}:
+components with early assembly (i.e. stalled halos) have a smaller degree of
+twisting. A detailed study to interpret this with respect to the cosmic 
+web location of the halos is however beyond the scope of this paper.
 
@@
 the constraints by \citet{Bovy16}.
-In contrast, none of the halos in the MHD and DMO seems to be
-consistent with the results by \citet{LM10}.}
+In contrast, none of the halos in the MHD and DMO simulations seems to be
+consistent with the results of \citet{LM10}.}
 \label{fig:observations}
@@
 
-The first effect that we put in evidence in this paper is the effect
-of baryons in producing rounder DM halos.
-This effect has been already widely reported in the literature.
-It has been found that the strength of the change depends on the
-numerical resolution, the gas cooling implementation and the
+The first prominent effect we found in this paper is that  baryons produce
+significantly rounder DM halos. This effect has already been  widely 
+reported in the literature, and we confirm it here for the Auriga simulations.
+It has also been found that the strength of the change depends on the
+numerical resolution, the gas cooling implementation, and the
 models describing star formation and stellar feedback
@@
 influences and correlates with the dark matter halo shape. 
-Indeed, as we presented in the previous section on the correlations
-with disc properties, we find that the broad tendency is that extended
+Indeed, as we demonstrated in the previous section on the correlations
+with disc properties, we find a clear tendency that extended
 massive stellar discs correlate with spherical dark matter
@@
 constrain the shape of the gravitational potential.
-Their point of depart is that previous studies that assumed an
+They point out that previous studies that assumed an
 axisymetric galactic potential were not able to fit all the available
-dynamic constraints for the Sagittarius stream, therefore making
-necessary the use of a rigid triaxial potential with coaxial potential
+dynamic constraints for the Sagittarius stream, motivating 
+their approach of using a rigid triaxial potential with coaxial potential
 ellipsoids for the dark matter component.  
 Their results constrain the triaxiality of this potential
-component. 
-They also translate their results into a triaxiality of the density
-contours (that could be compared against our results)
- to be $(c/a)=0.44$ and $(b/a)=0.97$ at a radius of $\sim 40$kpc. 
+component.  They also translate their results into a triaxiality of the density
+contours (which could be compared against our results)
+ to be $c/a=0.44$ and $b/a=0.97$ at a radius of $\sim 40$~kpc. 
 They do not report any uncertainties for these two values. 
@@
 of dark halo axial scales (their Figure 5), we choose a conservative $10\%$
-relative uncertainty.
-One surprising element in their results is that  the major axis of the
+relative uncertainty. One surprising element in their results is that 
+the major axis of the
 halo shape is perpendicular to the stellar disc plane.
 
-The results by \cite{Bovy16} have the same general approach but use
+The results by \cite{Bovy16} are based on the same general approach but use
 instead the GD-1 \citep{2006ApJ...641L..37G} and Pal 5 \citep{2009AJ....137.3378O}
 streams to constraint the shape of the dark matter component of the
-galacic halo potential.
-They use general models with many degrees of freedom for the galactic
+galacic halo potential. They use general models with many degrees of freedom for the galactic
 potential in order to measure to what extent these two streams are sensitive
@@
 The DM component is written directly as a triaxial density profile
-with coaxial ellipsoids and the corresponding potential is found by
-numerical integration.
-They find that the width of the Pal 5 stream constraints $b/a\approx
-1$ and therefore fix it to be $b/a=1$ exactly.
-Using that value they report their most stringent constrain of
-$c/a=0.93\pm0.16$ at a radius of $\approx 19$kpc from the galactic
+with coaxial ellipsoids, and the corresponding potential is found by
+numerical integration. They find that the width of the Pal~5 stream gives $b/a\approx
+1$, and therefore fix it to be $b/a=1$ exactly. Using this value they report their 
+most stringent constraint of $c/a=0.93\pm0.16$ at a radius of $\approx 19$ kpc from the galactic
 center.
 
-Figure \ref{fig:observations} shows an explicit comparison in
-the $c/a$-$b/a$ plane of our results in MHD simulations against the
+Figure~\ref{fig:observations} shows an explicit comparison in
+the $c/a$--$b/a$ plane of our findings for hydrodynamic simulations against the
 results by \cite{LM10} and \cite{Bovy16}.
 We find six MHD halos with $b/a<0.93$ and $c/a>0.77$ that could be
-considered consistent with their shape constraints  by \cite{Bovy16}, while
-only one outlier DMO halo is consistent with those constraints.
+considered consistent with the shape constraints  by \citet{Bovy16}, while
+only one DMO halo outlier  is consistent with those constraints.
 In contrast, none of the simulated halos (MHD nor DMO) is consistent
-with the results \cite{LM10}. 
-The change of triaxiality with radius in our simulations cannot account
-for these two extremely different shape constraints at different
-radii.
+with the results of \citet{LM10}. The change of triaxiality with radius in 
+our simulations cannot account for these two extremely different 
+shape constraints at different radii.
 
-The results by \label{LM10} could then place the dark matter halo of our Milky
-Way as an extreme outlier in the $\Lambda$CDM model. 
+The results by \citet{LM10} would imply that the dark matter halo of our Milky
+Way is an extreme outlier in the $\Lambda$CDM model. 
 This extreme prolateness also correlates with the extreme triaxiality
 of the 11 classical satellites of the MW ($c/a\approx 0.2$, and
-$b/a\approx0.9$) measured at larger radii, with an spatial
+$b/a\approx0.9$) measured at larger radii, with a spatial
 distribution  also oriented perpendicular to the MW plane, another
-highly unusual feature in the $\Lambda$CDM \citep{2018MNRAS.478.5533F}.
+highly unusual feature in the $\Lambda$CDM model \citep{2018MNRAS.478.5533F}.
 
@@
 
-In this paper we measured the shape of 30 isolated Milky Way sized
+In this paper we have measured the shape of 30 isolated Milky Way sized
 dark matter haloes simulated in the Auriga project using the zoom-in
-technique. 
-The halos were simulated in two different setups:
-dark matter only (DMO) simulation and full magnetohydrodynamics (MHD)
+technique. The halos were simulated using two different setups:
+dark matter only (DMO) simulation, and full magnetohydrodynamics (MHD)
 including star formation and feedback.
-We used the shape measurement algorithm by \cite{Allgood06} on the
+We applied the shape measurement algorithm by \cite{Allgood06} to the
 dark matter halos of these simulations to quantify the halo shape as a
-function of radius and the degree of aligment between the angular
-momentum in stellar disc and the dark matter halo.
+function of radius, and the degree of alignment between the angular
+momentum in stellar disc and the dark matter halo shape.
 
-We find that MHD halos are rounder than DMO halos at every radius.
-MHD halos tend towards more oblate, sometimes almost spherical, shapes
-($T<1/3$), while DMO halos tend towards more prolate shapes ($T>2/3$).  
-The rounding effect is more noticeable as one moves closer to the galactic
-disc and strongly  correlates with baryonic properties of the disc
+We find that MHD halos are rounder than DMO halos at all radii.
+MHD halos tend towards more oblate shapes, sometimes becoming almost spherical
+($T<1/3$), while DMO halos are prone to show more prolate shapes ($T>2/3$).  
+The rounding effect by baryons is more noticeable as one moves closer to the galactic
+centre, and it strongly  correlates with baryonic properties of the disc.
 More precisely, the triaxiality is smaller for extended and massive
-stellar discs with low gas densities at its core.
+stellar discs with low gas densities at their cores.
 
-We also measured the alignment of the halo with the stellar disc's angular momentum at different radii.
-For the majority of the sample the angular momentum is strongly aligned with the minor axis of the halo at all measured radii.
+We also measured the alignment of the halo with the stellar disc's angular
+momentum at different radii. For the majority of the sample, the angular momentum
+is strongly aligned with the minor axis of the halo at all measured radii.
 However, in some halos the alignment changes noticeably with radius. 
 This alignment evolution implies a radial twisting between the ellipsoids
-describing the halo shape. 
-We quantify this twist with the standard deviation of the angle
+describing the halo shape. We quantify this twist with the standard deviation of the angle
 between the angular momentum and the halo minor axis at radii below
-$\leq 0.5R_{200}$ and find that younger bulges and higher gas
+$\leq 0.5\, R_{200}$, and find that younger bulges and higher gas
 densities correlate with larger twisting values.
@@
 We compared our results against two observational constraints for the
-dark matter halo shape of the Milky Way. 
-The constraints are at two different radii and come from different
-observational tracers. 
-We find that $20\%$ halos in the MHD simulations are consistent with
-the constraints by \cite{Bovy16} at $\approx 19$kpc that correspond to
-an almost spherical halo, while none of the halos, either in MHD or
-DMO, has some overlap with the shape constraints by \cite{LM10} at
-$\approx 40$kpc that is closer to oblate.
+dark matter halo shape of the Milky Way. The constraints are at two different radii
+coming from different observational tracers. 
+We find that $20\%$ of the halos in the MHD simulations are consistent with
+the constraints by \cite{Bovy16} at $\approx 19$ kpc,  corresponding to
+an almost spherical halo, while none of the halos, neither in MHD nor
+DMO, has overlap with the shape constraints by \cite{LM10} at
+$\approx 40\,{\rm kpc}$, which argue for a more oblate shape.
 
-Using dark matter only simulations \cite{VeraCiro11} suggested that
+Using dark matter only simulations, \citet{VeraCiro11} suggested that
 the current dark matter halo shape strongly correlates with the time
 evolution of the halo as traced by the shape measured at the virial radius. 
-This effect might no longer hold once baryons are included. 
-The opposed trend of triaxiality in MHD simulation as a function of
-radius to the DMO simulations together with the twisting effect in some of 
-the halos seems to suggest that that historical buildup memory is not
-stored in the halo at $z=0$.
+This effect might largely be washed out and no longer hold once baryons are included. 
+The opposite trend of triaxiality in MHD simulation as a function of
+radius compared to the DMO simulations, together with the twisting effect in some of 
+the halos, seems to suggest that memory of the historical buildup is at most poorly 
+reflected in the shapes of baryonic halo at $z=0$.
 
@@
 different properties we have measured will require at least two more elements.
-First, an study on how the halo and the disc co-evolved as a
-function of time. Second, a calibrating the effect of the cosmic web
+First, a study on how the halo and the disc co-evolved as a
+function of time. Second, a calibration of the effect of the cosmic web
 (both dark matter and gaseous) on any evolutionary trend
-\citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G} 
-We finalize by suggesting that the twisting density shells we find in
-some of the halos is feature that deserves to be explored in the
-process of constraining shape parameters from tidal stream data.  The
+\citep{2014MNRAS.443.1090F, 2017MNRAS.469..594B, 2019MNRAS.487.1607G}.
+We also think  that the twisting density shells we find in
+some of the halos are a feature that deserves further study, especially
+in light of attempts to  constrain halo shape parameters with tidal stream data.  The
 inclusion of a parameterization describing this degree of twisting
-might relax the conflict between the observational constraints and the
+might relax the present conflicts between the observational inferences and the
 numerical results.

### 2019-08-21 Document/paper.tex
edit

@@
 kpc.   Finally, we also measure the alignment of the halo shape against the
-stellar disc angular momentum.  We measure the angular momentum vector 
-using the $10\%$ oldest stellar particles within the virial radius.
+stellar disc angular momentum measured using the $10\%$ oldest stellar
+particles within the virial radius.
 
@@
 The contours show a projected DM slice while the ellipsoid corresponds
-to the full 3D shape determination. There we see a highly ellipsoidal halo shape at radii $\sim 3$ kpc
-that becomes less elongated at $\approx 50$ kpc.
+to the full 3D shape determination. There we see a highly ellipsoidal
+halo shape at radii $\approx 3$ kpc that becomes less elongated at
+$\approx 50$ kpc.
 

### 2019-08-21 Document/paper.tex
edit

@@
   Third, halos in the MHD simulations are rounder than their DMO counterparts.
-  The first and second points are further 
-  clarified in Figure~\ref{fig:triaxial_cumulative} through cumulative triaxiality
-  distributions.}
+  These three points are further clarified in
+  Figure~\ref{fig:triaxial_cumulative} through cumulative triaxiality distributions.}
   \label{fig:triaxiality_plane}
@@
   while the thick line traces the median value as a function of  radius.
-  In the upper row, the haloes come from the DMO simulation.
-  The first thing to notice is that the major axis is statistically
-  perpendicular to the angular momentum of the disc that will form in
-  the MHD simulations. The other two directions do not show any
-  correlation. 
-  The second important result is that the directions in the ellipsoids
-  describing the shape are constant as a function of radius except for two
-  cases. 
-  In the lower row the haloes come from the MHD simulation, providing a 
-  self-consistent comparison with the stellar discs. 
-  In this case, the sample presents a good alignment of the angular
+  The sample presents a good alignment of the angular
   momentum with the minor halo axis. 
-  Furthermore, the dark matter shells twist significantly in $1/5$ of
-  the sample. For the remaining haloes, the alignment is almost
-  constant as a function of radius. 
+  This alignment is also constant in radius.
+  However, the dark matter shells twist significantly in $6$ halos 
+  of our sample making the alignment measurement change. 
 }
@@
 There the median triaxiality is always smaller than $1/3$ (a typical
-value markin the transition from triaxiality to prolateness) and this
+value marking the transition from triaxiality to prolateness) and this
 median value decreases as we move towards the inner part of the halo.
@@
 A common assumption in dynamical models of the MW dark matter halo is that
-its angular momentum is perfectly aligned with the minor axis of the stellar disc.
+its minor axis is perfectly aligned with the angular momentym of the
+stellar disc. 
 Although this is a reasonable assumption due to the stability of
@@
 
-The upper row in Figure \ref{fig:cumulative_alignment} shows 
-the alignments between the major, intermediate, and minor axis of the
-halo and the disc angular momentum, as a function of the dimensionless radius at which the halo shape was measured. The upper row shows the angle between the DMO halo and the stellar
-disk in the MHD simulation.
-This comparison help us to measure how the shape directions in the
-dark matter shells change with radius.
-For the bulk of the sample the lines are horizontal.
-Only two halos show a significant change of more than 30 degrees across different radii.
-
-The lower row in Figure \ref{fig:cumulative_alignment} shows the
-results for the MHD simulations.
-The most striking feature of this plot is that most of the discs have their angular momentum aligned with the minor axis of the halo, perpendicular to the intermediate and major axis.
+Figure \ref{fig:cumulative_alignment} shows the
+results as a function of radius.
+The most striking feature of this plot is that most of the discs have
+their angular momentum aligned with the minor axis of the halo,
+perpendicular to the intermediate and major axis. 
 The median and the standard deviation of the alignment angles with
@@
 degrees, respectively.
+This confirms statistically the expectation of a galactic disc aligned
+with the minor axis of its dark matter halo, although some outliers
+are present in the sample.
 
-In six halos the alignment changes significantly as a function of radius, 
+In six halos the alignment changes significantly as a
+function of radius,  
 as  can be seen by the twisting in the shape ellipsoids. 
@@
 directions corresponding to the medium and major axis could be subject
-to noise. For this reason, and in order to better quantify the twisting for each
+to noise. 
+For this reason, and in order to better quantify the twisting for each
 halo, we take the standard deviation of the angle with the minor
@@
 The largest correlation is obtained for the halo triaxiality measured at
-$0.12R_{200}$. The most important consequence of this changing degree in correlation
+$0.12R_{200}$. 
+The most important consequence of this changing degree in correlation
 is that twisting cannot be explained only by large triaxiality values

### 2019-08-21 Document/paper.tex
edit

@@
   This alignment is also constant in radius.
-  However, the dark matter shells twist significantly in $6$ halos 
-  of our sample making the alignment measurement change. 
+  However, the dark matter shells twist significantly in six halos 
+  of our sample making the alignment change. 
 }
@@
 Figure~\ref{fig:alignment_correlations} shows the correlation between
-the twisting at the four different radii at which we have measured the
-alignments. The median, mean and standard deviation of the twisting 
+the twisting and the corresponding triaxiality at the four different
+radii at which the shape directions are measured.
+The median, mean and standard deviation of the twisting 
 are $2$, $6$ and $8$ degrees, respectively.

### 2019-08-21 Document/paper.tex
edit

@@
 \end{center}
-\caption{Twisting in the halo-disc alignment (measured as the standard deviation of the alignment angles)
+\caption{Twisting in the halo-disc alignment (measured as the standard
+  deviation of the alignment angles at four different radii)
   as a function of the halo triaxialiy at the radius indicated
@@
 There the median triaxiality is always smaller than $1/3$ (a typical
-value marking the transition from triaxiality to prolateness) and this
+value marking the transition from oblateness to triaxiality) and this
 median value decreases as we move towards the inner part of the halo.
@@
 In six halos the alignment changes significantly as a
-function of radius,  
-as  can be seen by the twisting in the shape ellipsoids. 
+function of radius produced by the twisting in the shape ellipsoids. 
+In contrast, the DMO simulations show coherent halo shapes as a
+function of radius without twisting. 
 Because we are dealing with oblate halos $b/a\approx 1$, note that the
@@
 $0.12R_{200}$. 
-The most important consequence of this changing degree in correlation
-is that twisting cannot be explained only by large triaxiality values
-and a possibly noisy determination of the shape axis.
+The most important consequence of this changing degree of positive
+correlation is that twisting cannot be explained only by small
+triaxiality (large asphericity) values and a possibly noisy
+determination of the shape axis.
 
@@
 The presence of baryons produces rounder dark matter halos than found for the 
-corresponding DMO \textbf{}counterpart. To better understand this relationship we examine the correlation
+corresponding DMO counterpart. 
+To better understand this relationship we examine the correlation
 between halo shape and baryonic disc properties.  
@@
 We use the Spearmen's rank correlation coefficient to quantify the
-correlation strength. We find that the strongest correlations are found with the halo shape
+correlation strength. 
+We find that the strongest correlations are found with the halo shape
 measured at radii smaller than $0.12\, R_{200}$.
@@
 
-In some cases, the halo shape also twists in the presence of baryons, as opposed to
-the situation in DMO simulations where the shape is coherent as a
-function of radius. In Figure~\ref{fig:twisting_correlations}, we show the correlation
+In Figure~\ref{fig:twisting_correlations}, we show the correlation
 between twisting and the same baryonic properties that showed a high
@@
 
-Recently, \citet{2017MNRAS.469..594B} reported that MW-like DM haloes can
-be roughly split into two distinct families: stalled and accreting.
+Recently, \citet{2017MNRAS.469..594B} used five zoom simulations 
+to report that MW-like DM haloes can be roughly split into two
+distinct families: stalled and accreting. 
 Stalled haloes assembled early and have remained almost unchanged
@@
 twisting and the age of the bulge, the age of the stellar disc, and the
-DM halo formation redshift. The ages are estimated directly as the mean 
-value in the stellar age distribution for each component, while the formation redshift is
-defined as the redshift at which the halo has for the first time surpassed half of its final $z=0$
-mass. In the three cases we find a correlation between age and twisting
+DM halo age.
+We estimate the stellar ages  directly as the mean value in the
+stellar age distribution for each component, while the
+DM halo age corresponds to the lookback time at which the halo
+consolidated half of its present mass.  
+In the three cases we find a correlation between age and twisting
 that goes in the direction claimed by \citet{2017MNRAS.469..594B}:
 components with early assembly (i.e. stalled halos) have a smaller degree of
-twisting. A detailed study to interpret this with respect to the cosmic 
+twisting. 
+A detailed study to interpret this with respect to the cosmic 
 web location of the halos is however beyond the scope of this paper.
@@
 
-% JEFR I've commented this part because the plots are showing the 
-% alignment with the disc angular momentum not shape. 
-% This part has to be adjusted accordingly.
-%\cite{JingSuto02} reported a shell alignment twisting in their dark
-%matter only simulations as measured in the direction changes of large
-%and medium shape axis. 
-%They only had three high resolution MW-like halos (with
-%$\sim 10^{6}$ inside the virial radius) and could not make a
-%statistical statement about the impact of this effect.
-%However, they see the twisting as an artifact resulting from high values %of the
-%$b/a$ ratios that make the determination of the medium axis noisy.
-%For that reason we measured the twisting using the minor axis
-%alignments, however they do not report these alignments.
+The second part of our findings correspond to the disc-halo alignment.
+The dominant trend is that of a strong alignment between
+the disc and the dark matter halo shape at all radii. 
+In six halos of our sample we find a chaning alignment as a function
+of radius.
+This implies a twisting in the halo shape as a function of
+radius.
 
-%\cite{Bailin05} used seven hydrodynamic simulations studied the disc
-%halo alignment as a function of radius.
-%For radii smaller than $0.1R_{200}$ they find a strong alignment
-%between the two minor axis of the halo and the disc. 
-%For larger radii the angle between the components changes showing a
-%weak correlation between the two components. 
-%\cite{Debattista13} performed a study on the disc-halo alignment
-%performing controlled experiments on three different halos to study
-%changes the evolutionary change that drive the minor axis in the disc
-%and the halo to be aligned, their study by construction focuses only
-%on radii around $0.1R_{200}$.
-%Nevertheless, similarly to \cite{Bailin05}, they also report a strong
-%alignment in the region where the disc dominated. 
-%In conclusion, the twisting in the dark matter halo shapes seems to be
-%a feature already reported in the literature with smaller samples than
-%the one we use here. 
-%The strongest point of depart is that in our case the alignments do
-%not grow stronger as one approached the disc.
-%It is very likely that the detailed radial dependence of the twisting
-%depends on the hydrodynamics and feedback implementations.
+Twisting has been also reported as an uncommon feature in some 
+simulated systems found in the literature. 
+\cite{JingSuto02} reported a shell alignment twisting in their dark
+matter only simulations as measured in the direction changes of large
+and medium shape axis. 
+They only had three high resolution MW-like halos (with
+$\sim 10^{6}$ inside the virial radius) and could not make a
+statistical statement about the impact of this effect.
+However, they see the twisting as an artifact resulting from high
+values  of the $b/a$ ratios that make the determination of the medium
+axis noisy, an effect that we have demonstrated can be discarded for
+our simulations.
+\cite{Bailin05} used seven hydrodynamic simulations to study the disc
+halo alignment as a function of radius.
+For radii smaller than $0.1R_{200}$ they find a strong global
+alignment between the halo and the disc.
+However, in some halos, at larger radii the angle between the
+components twists resulting in a weaker correlation between the disk
+and the halo shape. 
+Considering that twisting is not present in our DMO simulations, it is
+very likely that the detailed radial dependence of the alignments
+between the disc and the halo depends on the hydrodynamics and
+feedback implementations.
 
-We now use the results reported by \cite{LM10} and \cite{Bovy16}
+To finalize, we use the results reported by \cite{LM10} and \cite{Bovy16}
 to place our results in an observational context.
@@
 \section*{Acknowledgements}
+We acknowledge fruitful discussions with Patricia Tissera during the
+preparation of the manuscript.
 This project has received funding from the European Union's Horizon

### 2019-08-21 Document/paper.tex
update

@@
 radius.
+Considering that this effect is not present in our DMO simulations, it is
+very likely that the detailed radial dependence of the alignments
+between the disc and the halo depends on the hydrodynamics and
+feedback implementations.
 
@@
 simulated systems found in the literature. 
-\cite{JingSuto02} reported a shell alignment twisting in their dark
+\cite{JingSuto02} reported it in their dark
 matter only simulations as measured in the direction changes of large
 and medium shape axis. 
-They only had three high resolution MW-like halos (with
-$\sim 10^{6}$ inside the virial radius) and could not make a
-statistical statement about the impact of this effect.
+They only had three high resolution MW-like halos and could not make a
+statistical statement about the significance of this effect.
 However, they see the twisting as an artifact resulting from high
@@
 and the halo shape. 
-Considering that twisting is not present in our DMO simulations, it is
-very likely that the detailed radial dependence of the alignments
-between the disc and the halo depends on the hydrodynamics and
-feedback implementations.
+A more recent study by \cite{2015MNRAS.453..721V} used the EAGLE simulations to
+report the median alignment between the stellar and dark matter
+components in $1008$ galaxies around the MW mass range. 
+Our results agree on the high degree of alignment on average as a
+function of radius.
+However, the authors do not mention whether they find any outliers
+with the kind of twisting we report here.
 
@@
 the halos, seems to suggest that memory of the historical buildup is at most poorly 
-reflected in the shapes of baryonic halo at $z=0$.
+reflected in the shapes at $z=0$.
 

### 2019-08-29 Document/paper.tex
last edits

@@
 \begin{abstract}
-We present shape measurements of Milky Way sized dark matter halos at
+We present shape measurements of Milky Way-sized dark matter halos at
 redshift $z=0$ in a suite of 30 zoom simulations from the Auriga
@@
 cosmological context, and have appropriate feedback physics to produce
-realistic MW discs.
+realistic MW discs \citep{auriga,GBG18,GHF18}.
 Furthermore, the relatively large number of simulated systems allows us
@@
 gravitational potential in each halo and are weighted by the inverse of 
-the k-th particle distance squared, $d_k^2 = \sum_{i=1}^3 x_k^{(i)} x_k^{(i)}$, giving each particle the same
+the $k$-th particle distance squared, $d_k^2 = \sum_{i=1}^3 x_k^{(i)} x_k^{(i)}$, giving each particle the same
 weight independent of distance.
@@
 roots of the  eigenvalues, and the directions of the principal
-axis are the corresponding eigenvectors.
+axes are the corresponding eigenvectors.
 
@@
 A common assumption in dynamical models of the MW dark matter halo is that
-its minor axis is perfectly aligned with the angular momentym of the
+its minor axis is perfectly aligned with the angular momentum of the
 stellar disc. 
@@
 In contrast, the DMO simulations show coherent halo shapes as a
-function of radius without twisting. 
+function of radius without twisting with the exception of a single halo. 
 Because we are dealing with oblate halos $b/a\approx 1$, note that the
@@
 
-The second part of our findings correspond to the disc-halo alignment.
+The second part of our findings concerns the disc-halo alignment.
 The dominant trend is that of a strong alignment between
 the disc and the dark matter halo shape at all radii. 
-In six halos of our sample we find a chaning alignment as a function
+In six halos of our sample we find a changing alignment as a function
 of radius.
@@
 radius.
-Considering that this effect is not present in our DMO simulations, it is
-very likely that the detailed radial dependence of the alignments
+Considering that this effect is virtually absent in our DMO simulations, it is
+very likely that the detailed radial evolution of the alignments
 between the disc and the halo depends on the hydrodynamics and
@@
 \cite{JingSuto02} reported it in their dark
-matter only simulations as measured in the direction changes of large
+matter only simulations as measured through direction changes of large
 and medium shape axis. 
@@
 statistical statement about the significance of this effect.
-However, they see the twisting as an artifact resulting from high
+However, they saw the twisting as an artifact resulting from high
 values  of the $b/a$ ratios that make the determination of the medium
@@
 1$, and therefore fix it to be $b/a=1$ exactly. Using this value they report their 
-most stringent constraint of $c/a=0.93\pm0.16$ at a radius of $\approx 19$ kpc from the galactic
+most stringent constraint of $c/a=0.93\pm0.16$ at a radius of $\approx 19$ kpc from the Galactic
 center.
@@
 function of radius, and the degree of alignment between the angular
-momentum in stellar disc and the dark matter halo shape.
+momentum in the stellar disc and the dark matter halo shape.
 
@@
 
-Using dark matter only simulations, \citet{VeraCiro11} suggested that
+A more complete understanding of the influence of baryons on the
+different properties we have measured will require at least two more elements.
+First, a study on how the halo and the disc co-evolved as a
+function of time. 
+For instance, using dark matter only simulations, \citet{VeraCiro11} suggested that
 the current dark matter halo shape strongly correlates with the time
@@
 reflected in the shapes at $z=0$.
-
-A more complete understanding of the influence of baryons on the
-different properties we have measured will require at least two more elements.
-First, a study on how the halo and the disc co-evolved as a
-function of time. Second, a calibration of the effect of the cosmic web
+The second element to take into account is the effect of the cosmic web
 (both dark matter and gaseous) on any evolutionary trend
 \citep{2014MNRAS.443.1090F, 2017MNRAS.469..594B, 2019MNRAS.487.1607G}.
+
 We also think  that the twisting density shells we find in
